### 2016-10-08 egpaper_for_review.tex
latex files

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfigure}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{External Patch Group Prior Guided Internal Clustering and Subspace Learning for Real Image Denoising}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
Existing image denoising methods largely depends on noise modeling and estimation. The commonly used noise models, additive white Gaussian or Mixture of Gaussians, are inflexible in describing the complex noise on real noisy images or time consuming in parametric estimation, respectively. Hence, this would limit the denoising performance of existing methods. In this paper, we firstly demonstrate that almost all state-of-the-art methods on removing Gaussian noise and real noise are limited in denoising real noisy images. We demonstrate that a simple Patch Group based Prior Learning model on RGB images can achieve better performance than existing denoising methods, especially the ones designed for real noise in natural images. Besides, we employ the external patch group prior learning for internal clustering and subspace learning. This external inormation guided internal denoising methods acheives even better than the external PG prior based methods and the fully internal PG prior based method. Through extensive on standard datasets on real noisy images with groundtruth, we demonstrate that the proposed method achieves much better denoising performance than the other state-of-the-art methods on Gaussian noise removal and real noise removal. 
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
Image denoising is a fundermental problem in computer vision and image processing. It is an ideal platform for testing natural image models and provides high-quality images for other conputer vision tasks such as image registration, segmentation, and pattern recognition, etc. For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,lssc,epll,burger2012image,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN). Recently, several discriminative learning methods \cite{burger2012image,csf,chen2015learning} achieving expressive performance on Gaussian noise removal. These methods require a set of paired images, namely clean ground-truth images and the simulated noisy counterparts degraded by identical noise (mainly additive white Gaussian noise, AWGN), to learn an effective model for image denoising. However, the noise in real images are much more complex than Gaussian, since it depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc). Thus, the model learned with AWGN would become much less effective for denoising real noisy images. What's more, usually real noisy images do not have clean counterparts. Therefore, almost all current discriminative learning methods cannot be directly applied to real noisy images.

In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are designed to deal with real noisy images. Almost all these methods coincidently employ a two-stage framework: in the first stage, assuming a distribution model (usually Gaussian) on the noise and estimate its parameters; in the second stage, performing denoising with the help of the noise modeling and estimation in the first stage. However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008,crosschannel2016}. Although the mixture of Gaussians (MoG) model is possible to approximate any unknown noise \cite{Zhu_2016_CVPR}, estimating its parameters is often time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR} \cite{Bishop}.

The above mentioned limitations indicate that, novel denoising methods are been waiting for which can: 1) avoid noise modeling and estimation; 2) deal with complex noise on real noisy images. In this paper, we attempt to solve the two problems in an integrated way for robust real image denoising. We find that the Patch Group Prior learning based denoising \cite{PGPD} method learned on natural clean RGB images are enough to outperform the above mentioned denoising methods. We also propose a fully internal PG prior based denoising method which achieve better performance than the fully external method. Most importantly, we found that the external PG prior guided internal method can achieve even better and faster performance on real image denoising. The external PG prior learning based model is employed to guide the clustering of internal PGs extracted from the input noisy images. Then for each cluster of PGs, we perform subspace learning by PCA and denoising by weighted sparse coding. The noise level of the noisy images is inheriently expressed in the singular values, which can be used as weights for the sparse coding. We perform comprehensive experiments on real noisy images captured by different CMOS or CCS sensors. The results demonstrate that our method achieves comparable or even better performance on denoising real noisy images. This reveals the potential advantages of combining external and internal information o natural images on robust and complex real noisy image denoising problem.

%The in-camera imaging pipeline usually includes image demosaicing, white balance and color space transform, gamut mapping, tone mapping, and JPEG comression \cite{NewInCamera,crosschannel2016}.

\subsection{Our Contributions}
The contributions of this paper are summarized as follows:
\begin{itemize}
\item To avoid noise modeling and estimation, we propose a noval learning based model which directly transform noisy images into clean conuterparts;
\item To learn without paired training images, we perform the learning on paired image patches extracted from unpaired noisy and clean images;
\item To deal with different structures and nise sources, we employ a "divide-and-coquer" strategy on the training data, and for each paired cluster of similar patches, we learn two dictionaries and transformation function for noisy and clean data;
\item The proposed method achieves better performance than other competing methdos on real noisy image denoising problem.
\end{itemize}

\section{Related Work}
\subsection{Couple dictionary learning}
Coupled dictionary learning (CDL) is a frequently used learning framework for cross-style image synthesis problems, such as image super-resolution, photo-sketch synthesis. CDL aims at learning a pair of dictionaries as well as the relationships between the two cross-domain image styles. Hence, the information from the source image style can be applied to synthesize the image at the target style. The relationships are often assumed to be identical mapping (coupled) \cite{yang2010image}, linear mapping (semi-coupled) \cite{wang2012semi}. Yang et al. \cite{yang2010image} assumed that LR image patches have the same sparse representations as their HR versions do, and proposed a joint dictionary learning model for SR using concatenated HR/LR image features. They later imposed relaxed constraints on the observed dictionary/coefficient pairs across image domains for improved performance. Wang et al. \cite{wang2012semi} further proposed a semi-coupled dictionary
learning (SCDL) scheme by advancing a linear mapping for cross-domain image sparse representation. Their method
has been successfully applied to applications of image SR and cross-style synthesis.

\subsection{Real Image Denoising}
To the best of our knowledge, the study of real image denoising can be dated back to the BLS-GSM model \cite{blsgsm}, in which Portilla et al. proposed to use scale mixture of Gaussian in overcomplete oriented pyramids to estimate the latent clean images. In \cite{fullyblind}, Portilla proposed to use a correlated Gaussian model for noise estimation of each wavelet subband. Based on the robust statistics theory \cite{huber2011robust}, the work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers, which could be removed via Lorentzian robust estimator. In \cite{Liu2008}, Liu et al. proposed to use 'noise level function' (NLF) to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Recently, Gong et al. proposed an optimization based method \cite{almapg}, which models the data fitting term by weighted sum of $\ell_{1}$ and $\ell_{2}$ norms and the regularization term by sparsity prior in the wavelet transform domain. Later, Lebrun el al. proposed a multiscale denoising algorithm called 'Noise Clinic' \cite{noiseclinic} for real image denoising task. This method generalizes the NL-Bayes \cite{nlbayes} to deal with signal, scale, and frequency dependent noise. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates the noise via Mixture of Gaussian (MoG) model \cite{Bishop}. The clean image is recovered from the noisy image by the proposed Low Rank MoG filter (LR-MoG). However, noise level estimation is already a challenging problem and denoising methods are quite sensitive to this parameter. Moreover, these methods are based on shrinkage models that are too simple to reflect reality, which results in over-smoothing of important structures such as small-scale text and textures.

\section{Double Semi-Couple Dictionary Learning}
In this section, we first formulate the real image denoising problem from the perspective of learning based model and then provide the optimization for the problem.
\subsection{Problem Formulation}
For real image denoising, we first collect clean natural images and real noisy images for training. Assume the $\mathbf{X}$ and $\mathbf{Y}$ are unpaired clean image patches and real noisy patches. Let the $\mathbf{X} = \mathbf{D}_{x}\mathbf{A}_{x}$ and $\mathbf{Y} = \mathbf{D}_{y}\mathbf{A}_{y}+\mathbf{V}_{y}$, where $\mathbf{V}_{y}$ is the real noise of which we don't know the distribution. 
\begin{equation}
\begin{split}
&\min_{\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{A}_{x},\mathbf{A}_{y}}
\emph{E}_{data}(\mathbf{X},\mathbf{D}_{x},\mathbf{A}_{x})+
\emph{E}_{data}(\mathbf{Y},\mathbf{D}_{y},\mathbf{A}_{y},\mathbf{V}_{y})
\\
&
+\emph{E}_{map}(f_{1}(\mathbf{A}_{x}),f_{2}(\mathbf{A}_{y}))+
\emph{E}_{reg}(\mathbf{A}_{x},\mathbf{A}_{y},f_{1},f_{2},\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{V}_{y})
\end{split}
\end{equation}

This framework doesn't need noise modeling and estimation. However, we still model the noise by $\mathbf{V}_{y}$ for visualization what we have removed during training. The regularization of the noise by $\|\mathbf{V}_{y}\|_{p}^{p}$ can be flexible, that we can penalize it by Frobenius norm, $\ell_{1}$ norm, or any other norms. We employ Frobenius norm here for modeling simplicity. To model the relationship between the representational coefficients, we propose to use two inversible mapping function $f_{1}$ and $f_{2}$. To measure the error, we employ a penalty function $\emph{F}$.
\begin{equation}
\begin{split}
\min_{\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{A}_{x},\mathbf{A}_{y},\mathbf{U}_{x},\mathbf{U}_{y},\mathbf{V}_{y}}
\|\mathbf{X}-\mathbf{D}_{x}\mathbf{A}_{x}\|_{F}^{2}&
\\
+
\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
+
\alpha
\emph{F}(f_{1}(\mathbf{A}_{x}),f_{2}(\mathbf{A}_{y}))&
\\
+
\beta_{x1}\|\mathbf{A}_{x}\|_{1}
+
\beta_{x2}\|\mathbf{A}_{x}\|_{F}^{2}
+
\beta_{y1}\|\mathbf{A}_{y}\|_{1}
+
\beta_{y2}\|\mathbf{A}_{y}\|_{F}^{2}
&
\\
(+
\gamma_{y}\|\mathbf{V}_{y}\|_{p}^{p})
\\
\text{s.t.}
\quad
\|\mathbf{d}_{x,i}\|_{2}=1
, 
\|\mathbf{d}_{y,i}\|_{2}=1
,
\forall{i}
.
\end{split}
\end{equation}
Here, we want to discuss more on the mapping functions $f_{1}, f_{2}$ and the measure function $\emph{F}$. The mapping function can be linear or nonlinear transformations. The linear function can be defined as a mapping matrix $f_{1}(\mathbf{A}_{x})=\mathbf{U}_{x}\mathbf{A}_{x}$ and $f_{2}(\mathbf{A}_{y})=\mathbf{U}_{y}\mathbf{A}_{y}$. The corresponding penalty terms on the mapping matrices are $\|\mathbf{U}_{x}\|_{F}^{2}$ and $\|\mathbf{U}_{y}\|_{F}^{2}$. The nonlinear function can be defined as sigmoid function $f_{1}(\mathbf{A}_{x})=1/(1+\exp\{-\mathbf{A}_{y}\})$. We can also employ "first-linear-then-nonlinear" or "first-nonlinear-then-linear" strategies. Here, we don't have explict penalty terms for the nonlinear mapping functions. The derivatives of the nonlinear case also need further discussions since it is not easy to obtain closed-form solutions with sigmoid functions. In this paper, we utilize linear transformation matrices as the mapping functions $f_{1}$ and $f_{2}$. The measure penalty function is simply defined by Frobenius norm. Hence, the term is defined as $\|\mathbf{U}_{x}\mathbf{A}_{x}-\mathbf{U}_{y}\mathbf{A}_{y}\|_{F}^{2}$. However, this would generate a trivial solution of $\mathbf{U}_{x}=\mathbf{U}_{y}=\mathbf{0}$. In order to avoid this case, we propose to use the inverse of the mapping matrices, i.e., $\mathbf{U}_{x}^{-1}$ and $\mathbf{U}_{y}^{-1}$.

In summary, we propose a Doubly Inversible and Semi-Coupled Dictionary Learing (DISCDL) model to learn the dictionaries and mapping functions between real noisy images and latent clean natural images. 
\begin{equation}
\begin{split}
\min_{\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{A}_{x},\mathbf{A}_{y},\mathbf{U}_{x},\mathbf{U}_{y},\mathbf{V}_{y}}
\|\mathbf{X}-\mathbf{D}_{x}\mathbf{A}_{x}\|_{F}^{2}&
\\
+
\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
+
\alpha
\|\mathbf{U}_{x}^{-1}\mathbf{A}_{x}-\mathbf{U}_{y}^{-1}\mathbf{A}_{y}\|_{F}^{2}&
\\
+
\beta_{x1}\|\mathbf{A}_{x}\|_{1}
+
\beta_{x2}\|\mathbf{A}_{x}\|_{F}^{2}
+
\beta_{y1}\|\mathbf{A}_{y}\|_{1}
+
\beta_{y2}\|\mathbf{A}_{y}\|_{F}^{2}
&
\\
(+
\gamma_{y}\|\mathbf{V}_{y}\|_{p}^{p})
&
\\
+
\lambda_{x}\|\mathbf{U}_{x}^{-1}\|_{F}^{2}
+
\lambda_{y}\|\mathbf{U}_{y}^{-1}\|_{F}^{2}
\\
\text{s.t.}\quad \|\mathbf{d}_{x,i}\|_{2}=1, \|\mathbf{d}_{y,i}\|_{2}=1, \forall{i}.
\end{split}
\end{equation}
This model has three major differences when compared with SCDL model.
\begin{itemize}
\item We use a matrix $\mathbf{V}_{y}$ to model the noise, and we don't set any prior distribution on it. This term can help us visualize the noise we learned from the data, i.e., the real noisy images. This make our model fully data-driven. Since our assumption (we have no assumption at all) on noise is more flexible than others', the noise we obtain in our model can be more accurate than other statistical models such as Gaussian or Mixture of Gaussians. Besides, it is time-consuming to fit the noise model from the online data. 
\item We use two inversible matrices as the mapping transformations between the coefficients of the real noisy patches and the latent clean patches. This makes our model more flexible than SCDL in which the mapping matrix not explictly inversible. Besides, the SCDL can only transform LR images into HG images while our model can transform two different image styles in both direction.
\item The constraints on dictionary atoms in our model is strictly $\|\mathbf{d}_{x,i}\|_{2}=1, \|\mathbf{d}_{y,i}\|_{2}=1$ while the CDL model and SCDL model are $\|\mathbf{d}_{x,i}\|_{2}\le1, \|\mathbf{d}_{y,i}\|_{2}\le1$. This makes our model more robust on the dictionary learning since both the dictionary atoms and sparse coefficients are interacted with each other. The $\le1$ constraints would like to make the coefficients larger and dictionary atoms smaller or even vanish. However, in the training stage, we care more about the dictionary atoms and would rather ignore the sparse coefficients.  
\end{itemize}

\subsection{Model Optimization}
While the objective function in (3) is not convex, it is convex with each varible when other variables are fixed. We employ alternating direction method of multipliers (ADMM) algorithm here. Specifically, we divide the objective function into four sub-problems: 1) updating the sparse coefficients $\mathbf{A}_{x}, \mathbf{A}_{y}$; 2) updating the normalized dictionaries $\mathbf{D}_{x}, \mathbf{D}_{y}$; 3) updating the noise matrix $\mathbf{V}_{y}$; 4) updating the mapping matirces $\mathbf{U}_{x}, \mathbf{U}_{y}$. We discuss the four steps as follows.

\subsubsection{Updating $\mathbf{A}_{x}$ and $\mathbf{A}_{y}$}

\begin{equation}
\begin{split}
\min_{\mathbf{A}_{x}}
\|\mathbf{X}-\mathbf{D}_{x}\mathbf{A}_{x}\|_{F}^{2}
+
\alpha
\|\mathbf{U}_{x}^{-1}\mathbf{A}_{x}-\mathbf{U}_{y}^{-1}\mathbf{A}_{y}\|_{F}^{2}
&
\\
+
\beta_{x1}\|\mathbf{A}_{x}\|_{1}
+
\beta_{x2}\|\mathbf{A}_{x}\|_{F}^{2},
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\min_{\mathbf{A}_{y}}
\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
&
\\
+
\alpha
\|\mathbf{U}_{x}^{-1}\mathbf{A}_{x}-\mathbf{U}_{y}^{-1}\mathbf{A}_{y}\|_{F}^{2}
+
\beta_{y1}\|\mathbf{A}_{y}\|_{1}
+
\beta_{y2}\|\mathbf{A}_{y}\|_{F}^{2}.
\end{split}
\end{equation}

Take $\mathbf{A}_{x}$ as an example, the first and second terms above can be combined to form a new optimization problems as follows:
\begin{equation}
\min_{\mathbf{A}_{x}}
\|\widetilde{\mathbf{X}}-\widetilde{\mathbf{D}}_{x}\mathbf{A}_{x}\|_{F}^{2}
+
\beta_{x1}\|\mathbf{A}_{x}\|_{1}
+
\beta_{x2}\|\mathbf{A}_{x}\|_{F}^{2},
\end{equation}
where 
$
\widetilde{\mathbf{X}}
=
\left(\begin{array}{c}
\mathbf{X}
\\
\sqrt{\alpha}\mathbf{U}_{y}^{-1}\mathbf{A}_{y}
\end{array}\right)
$
and
$
\widetilde{\mathbf{D}}
=
\left(\begin{array}{c}
\mathbf{D}_{x}
\\
\sqrt{\alpha}\mathbf{U}_{x}^{-1}
\end{array}\right)
$.
For $\mathbf{A}_{y}$, it is similar with $\mathbf{A}_{x}$.
\begin{equation}
\min_{\mathbf{A}_{y}}
\|\widetilde{\mathbf{Y}}-\widetilde{\mathbf{D}}_{y}\mathbf{A}_{y}\|_{F}^{2}
+
\beta_{y1}\|\mathbf{A}_{y}\|_{1}
+
\beta_{y2}\|\mathbf{A}_{y}\|_{F}^{2},
\end{equation}
where 
$
\widetilde{\mathbf{Y}}
=
\left(\begin{array}{c}
\mathbf{Y}-\mathbf{V}_{y}
\\
\sqrt{\alpha}\mathbf{U}_{x}^{-1}\mathbf{A}_{x}
\end{array}\right)
$
and
$
\widetilde{\mathbf{D}}
=
\left(\begin{array}{c}
\mathbf{D}_{y}
\\
\sqrt{\alpha}\mathbf{U}_{y}^{-1}
\end{array}\right)
$.
These simplified versions have the exactly same formulation as standard sparse coding and can be simply solved by tools such as SPAMS.

The $\mathbf{U}_{x}^{-1}$ and $\mathbf{U}_{y}^{-1}$ are inversible. This will be discussed in subsection "Updating U".

\subsubsection{Updating $\mathbf{D}_{x}$ and $\mathbf{D}_{y}$}
\begin{equation}
\min_{\mathbf{D}_{x}}
\|\mathbf{X}-\mathbf{D}_{x}\mathbf{A}_{x}\|_{F}^{2}
\quad
\text{s.t.}
\quad
\|\mathbf{d}_{x,i}\|_{2}=1,
\forall{i}.
\end{equation}

\begin{equation}
\begin{split}
\min_{\mathbf{D}_{y}}
\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
\quad 
\text{s.t.}
\quad 
\|\mathbf{d}_{y,i}\|_{2}=1,
\forall{i}.
\end{split}
\end{equation}
These two are quadraically constrained quadratic program (QCQP) problem and can be solved by Lagrange dual techniques.

\subsubsection{Updating $\mathbf{V}_{y}$}
The noise matrix is initialized as a zero matirx and updated by solving the following probelm:
\begin{equation}
\begin{split}
\min_{\mathbf{V}_{y}}
\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
+
\gamma_{y}\|\mathbf{V}_{y}\|_{F}^{2}
\end{split}
\end{equation}
This is a ridge regression problem. We can obtain the analytical solution of $\mathbf{V}_{y}$ by 
\begin{equation}
\mathbf{V}_{y} = (\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y})/(1+\gamma_{y}).
\end{equation}

\subsubsection{Alternate Updating $\mathbf{V}_{y}$}
The noise matrix is initialized as a zero matirx and updated by solving the following probelm:
\begin{equation}
\begin{split}
\min_{\mathbf{V}_{y}}
\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
\end{split}
\end{equation}
This is a standard least square problem. We can obtain the analytical solution of $\mathbf{V}_{y}$ by 
\begin{equation}
\mathbf{V}_{y} = \mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}.
\end{equation}

\subsubsection{Updating $\mathbf{U}_{x}$ and $\mathbf{U}_{y}$}

\begin{equation}
\begin{split}
\min_{\mathbf{U}_{x}^{-1}}
\alpha
\|\mathbf{U}_{y}^{-1}\mathbf{A}_{y}-\mathbf{U}_{x}^{-1}\mathbf{A}_{x}\|_{F}^{2}
+
\lambda_{x}\|\mathbf{U}_{x}^{-1}\|_{F}^{2}
\\
\min_{\mathbf{U}_{y}^{-1}}
\alpha
\|\mathbf{U}_{x}^{-1}\mathbf{A}_{x}-\mathbf{U}_{y}^{-1}\mathbf{A}_{y}\|_{F}^{2}
+
\lambda_{y}\|\mathbf{U}_{y}^{-1}\|_{F}^{2}
\end{split}
\end{equation}
The above problems are also ridge regression problems and have analytical solutions of $\mathbf{U}_{x}$ and $\mathbf{U}_{y}$ as follows:
\begin{equation}
\begin{split}
\mathbf{U}_{x}^{-1} = \mathbf{U}_{y}^{-1}\mathbf{A}_{y}\mathbf{A}_{x}^{T}(\mathbf{A}_{x}\mathbf{A}_{x}^{T}+(\gamma_{x}/\alpha)\mathbf{I})^{-1}
\\
\mathbf{U}_{y}^{-1} = \mathbf{U}_{x}^{-1}\mathbf{A}_{x}\mathbf{A}_{y}^{T}(\mathbf{A}_{y}\mathbf{A}_{y}^{T}+(\gamma_{y}/\alpha)\mathbf{I})^{-1}
\end{split}
\end{equation}
Here, we verify that $\mathbf{U}_{x}^{-1}$ and $\mathbf{U}_{y}^{-1}$ are inversible. The $\mathbf{U}_{x}^{-1}$ and $\mathbf{U}_{y}^{-1}$ are both initialized as an identity matrix, of suitable dimension, which is inversible. That is, we have $\mathbf{U}_{y}^{(0)} = \mathbf{I}$ when we compute $\mathbf{U}_{x}^{-1}$. If $\mathbf{A}_{y}\mathbf{A}_{x}^{T}$ is inversible, then $\mathbf{U}_{x}^{-1}$ is inversible. In fact, we have $\mathbf{A}_{y},\mathbf{A}_{x}\in \mathbb{R}^{d\times N}$. $d$ is the dimension of the sample. For a patch of size $8\times8$, $d=64$. The $N$ is the number of samples in the training data. Remember that we have much more samples when compared to the dimension of patches, that is $N\gg d$. It is less likely that  $\mathbf{A}_{y}\mathbf{A}_{x}^{T}\in \mathbb{R}^{d\times d}$ has a rank structure lower than $d$. In other words,  $\mathbf{A}_{y}\mathbf{A}_{x}^{T}\in \mathbb{R}^{d\times d}$ is less likely to be singular if we have enough training data. The experiments also confirm our conjecture. Besides, we can also add small disburtation to guarantee that $\mathbf{A}_{y}\mathbf{A}_{x}^{T}\in \mathbb{R}^{d\times d}$ is inversible.

Once $\mathbf{U}_{x}^{-1}$ is inversible, we can also verify that $\mathbf{U}_{y}^{-1}$ is inversible in a similar way.

\subsection{Real Image Denoising}
Two methods:

The first one is that
\begin{equation}
\begin{split}
\min_{\mathbf{a}_{x,i},\mathbf{a}_{y,i}}
\|\mathbf{x}_{i}-\mathbf{D}_{x}\mathbf{a}_{x,i}\|_{2}^{2}
+
\|\mathbf{y}_{i}-\mathbf{D}_{y}\mathbf{a}_{y,i}-\mathbf{v}_{y,i}\|_{2}^{2}
\\
+
\alpha
\|\mathbf{U}_{x}^{-1}\mathbf{a}_{x,i}-\mathbf{U}_{y}^{-1}\mathbf{a}_{y,i}\|_{2}^{2}&
\\
+
\beta_{x}\|\mathbf{a}_{x,i}\|_{1}
+
\beta_{x2}\|\mathbf{a}_{x,i}\|_{2}^{2}
+
\beta_{y}\|\mathbf{a}_{y,i}\|_{1}
+
\beta_{y2}\|\mathbf{a}_{y,i}\|_{2}^{2}
&
\\
(+
\gamma_{y}\|\mathbf{v}_{y,i}\|_{1})
\end{split}
\end{equation}
and finally we get $\widehat{\mathbf{x}}_{i}=\mathbf{D}_{x}\widehat{\mathbf{a}}_{x,i}$.

The second one is to solve
\begin{equation}
\begin{split}
\min_{\mathbf{a}_{y,i},\mathbf{v}_{y,i}}
\|\mathbf{y}_{i}-\mathbf{D}_{y}\mathbf{a}_{y,i}-\mathbf{v}_{y,i}\|_{2}^{2}
+
\alpha
\|\mathbf{U}_{x}^{-1}\mathbf{a}_{x,i}-\mathbf{U}_{y}^{-1}\mathbf{a}_{y,i}\|_{2}^{2}&
\\
+
\beta_{y1}\|\mathbf{a}_{y,i}\|_{1}
+
\beta_{y2}\|\mathbf{a}_{y,i}\|_{2}^{2}
&
\\
(+
\gamma_{y}\|\mathbf{v}_{y,i}\|_{1}).
\end{split}
\end{equation}
Once we get $\widehat{\mathbf{a}}_{y,i}$ from $\mathbf{y}_{i}$, $\widehat{\mathbf{a}}_{x,i}\approx\mathbf{U}_{x}\mathbf{U}_{y}^{-1}\widehat{\mathbf{a}}_{y,i}$ and $\widehat{\mathbf{x}_{i}}\approx\mathbf{D}_{x}\widehat{\mathbf{a}}_{x,i}$.

Experiments demonstrate that the first method can get better performance than the second one while the second one can get faster speed than the first one.

We can also initialized the solution from the second one.

\section{The Overall Algorithm}

\subsection{Pair Sample Construction from Unpaired Samples}
In cross style transfer methods such as CDL and SCDL, the authors assume that the two different styles have paired data, i.e., for each data sample in one style, we can find paired data sample in the other style. However, in real world, the data from two different sources may be unpaired. For example, the real noisy images should not have groundtruth clean images of the same scene. The real low-resolution images should not have corresponding high-resolution images in the real world. The real blurry images should not have corresponding clear and high quality images in real world.

To deal with unpaired data, we could collect real noisy images and clean natural images from two different sources. The real noisy images are from the example images (18 images) of the Neat Image website while the clean natural images are from the training set (200 images) of the Berkeley Segmentation Dataset (BSDS500). To make use of the unpaired data samples, we employ searching strategy to construct the training dataset. That is, for each noisy image patch, we utilize the k-Nearest Neighbor (k-NN) algorithm to find the most similar patch in the clean images as the paired groundtruth patch. The similarity is measured by the Euclidean distance (also called squared error or $\ell_{2}$ norm).

\subsection{Structual Clustering and Model Selection}
In fact, different image structures should have different influences on dictioanry as well as the mapping function. Patches with flat region should have low rank structure within dictionary elements and identity mapping between noisy and latent clean patches. Patches with complex details should have more comprehensive dictionary elements within dictionary elements and more complex mapping function between noisy and clean patches. A single mapping function cannot deal with all these complex relationships. Hence, a structual clustering procedure is needed for complex solution. In this paper, we propose to employ Gaussian Mixture Model to cluster different image patches into different groups and learn dictionary and mapping function for each group.

\subsection{Adaptive Iterations of Different Noise Levels}
For real image denoising, we can perform well on images which have similar noise levels with the training dataset. How can we deal with the real noisy images whose noise levels are higher than the training dataset? The answer is to remove the noise by more iterations. The input image of each iteration is the recovered image of previous iteration. This makes sense since we can still view the recovered image as a real noisy image.

This will also bring a second problem, that how we could automatically terminate the iteration. This can be solved by two methods. One way is to compare the images between two iterations and calculate their difference, the iteration can be terminated if the difference is smaller than a threshold. The other way is to estimate the noise level of the current image and terminate the iterations when the noise level is lower than a preset threshold. We employ the second way and set the threshold as 0.0001 in our experiments. In fact, most of our testing images will be denoised well in one iteration.

\subsection{Efficient Model Selection by Gating Network}
In the Gaussian component selection procedure, if we employ the full posterior estimation, the speed is not fast. Our algorithm can be speeded up by introducing the Gating network model.

%------------------------------------------------------------------------
\section{Experiments}

We compare with popular software NeatImage which is one of the best denoising software available. All these methods need noise estimation which is vary hard to perform if there is no uniform regions are available in the testing image. The NeatImage will fail to perform automatical parameters settings if there is no uniform regions.

\subsection{Parameters}
We don't fine tune the parameters both in the training and testing datasets.

\subsection{Real Image Denoising}
We compare the proposed method with the famous BM3D \cite{bm3d} and WNNM \cite{wnnm}, Cascade of Shrinkage Fields (CSF) \cite{csf}, trainable reaction diffusion (TRD) \cite{chen2015learning}, plain neural network based method MLP \cite{burger2012image}, the blind image denoising method Noise Clinic \cite{noiseclinic}, and the commercial software Neat Image. The RGB images are firstly transformed into YCbCr channels and restored by these methods. Then the denoised RGB image is obtained by transforming the restored YCbCr image back.

We evaluate the competing denoising methods from various research directions on two datasets. Both the two datasets comes from the \cite{crosschannel2016}. The first contains 3 cropped images of size $512\times512$. The other dataset contains 42 images cropped to size of $500\times500$ from the 17 images provided in \cite{crosschannel2016}. The 60 images contain most of the scenes in the 17 images \cite{crosschannel2016}.
\begin{table*}
\caption{Average PSNR(dB) results of different methods on 3 real noisy images captured by Canon EOS 5D mark3 at ISO3200 in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
Image & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{CSF}&\textbf{TRD}&\textbf{MLP}& \textbf{Noise Clinic}& \textbf{Neat Image}&\textbf{Ours}
\\
\hline
1& 37.00 & 37.08 & 37.09 &  37.46  &  37.51  &  32.91  & \textbf{ 38.76}  & 37.68   & 38.63  
\\
\hline
2& 33.88 & 33.95  &  33.95  &  34.90  &  35.04  & 31.94   &  35.69  &  34.87  & \textbf{ 35.96 }
\\
\hline
3& 33.83  & 33.85  & 33.85   & 34.15   &   34.07 & 30.89   & \textbf{35.54 }  &  34.77  &  35.51 
\\
\hline
Average & 34.90  &  34.96 &  34.96  & 35.50   & 35.54   &  31.91  &  36.67  &  35.77  &  \textbf{ 36.70}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\caption{Average SSIM results of different methods on 3 real noisy images captured by Canon EOS 5D mark3 at ISO3200 in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
Image & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{CSF}&\textbf{TRD}&\textbf{MLP}& \textbf{Noise Clinic}& \textbf{Neat Image}&\textbf{Ours}
\\
\hline
1& 0.9345 & 0.9368  & 0.9372  & 0.9599   &  0.9607  & 0.9043   &  0.9689  & 0.9600   &\textbf{ 0.9712  }
\\
\hline
2& 0.8919 &  0.8848 &  0.8951 & 0.9159   &  0.9187  &  0.8498  &  0.9427  &  0.9308  & \textbf{ 0.9434 }
\\
\hline
3& 0.9128  & 0.9136 & 0.9136  & 0.9254   &  0.9279  &  0.8635  &  0.9476  & 0.9463   & \textbf{ 0.9529 }
\\
\hline
Average &  0.9131  & 0.9117 &  0.9153 & 0.9337   & 0.9358   &  0.8725  & 0.9531   & 0.9457   &  \textbf{0.9558} 
\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\caption{Average PSNR(dB) and SSIM results of different methods on 42 cropped images from 17 real noisy images in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
Measure & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{CSF}&\textbf{TRD}&\textbf{MLP}& \textbf{Noise Clinic}& \textbf{Neat Image}&\textbf{Ours}
\\
\hline
PSNR& 34.36 & 34.36 & 34.40 & 36.11 & 36.05 & 34.41 & 37.68 & 36.58 & 36.15
\\
\hline
SSIM& 0.8552 & 0.8553 & 0.8577 & 0.9215 & 0.9211 & 0.9012 & 0.9470 & 0.9145 & 0.9236
\\
\hline
\end{tabular}
\end{center}
\end{table*}

\section{Conclusion and Future Work}

In the future, we will evaluate the proposed method on other conputer vision tasks such as single image super-resolution, photo-sketch synthesis, and cross-domain image recognition. Our proposed method can be improved if we use better training images, fine tune the parameters via cross-validation. We believe that our framework can be useful not just for real image denoising, but for image super-resolution, image cross-style synthesis, and recognition tasks. This will be our line of future work.

{\small
\bibliographystyle{unsrt}
\bibliography{egbib}
}

\end{document}

### 2016-10-10 egpaper_for_review.tex
modf

@@
 \begin{itemize}
-\item To avoid noise modeling and estimation, we propose a noval learning based model which directly transform noisy images into clean conuterparts;
-\item To learn without paired training images, we perform the learning on paired image patches extracted from unpaired noisy and clean images;
-\item To deal with different structures and nise sources, we employ a "divide-and-coquer" strategy on the training data, and for each paired cluster of similar patches, we learn two dictionaries and transformation function for noisy and clean data;
-\item The proposed method achieves better performance than other competing methdos on real noisy image denoising problem.
+\item We propose a noval method which combine the external and internal PG prior for real noisy image denoising problem;
+\item Our method doesn't need noise modeling and estimation, and the noise levels of real noisy images are automatically expresssed by the singular values of learned subspace;
+\item We achieve much better performance, visual quality, PSNR, SSIM, and speed for real image denoising problem.
+
 \end{itemize}
@@
 \section{Related Work}
-\subsection{Couple dictionary learning}
-Coupled dictionary learning (CDL) is a frequently used learning framework for cross-style image synthesis problems, such as image super-resolution, photo-sketch synthesis.
-CDL aims at learning a pair of dictionaries as well as the relationships between the two cross-domain image styles.
-Hence, the information from the source image style can be applied to synthesize the image at the target style.
-The relationships are often assumed to be identical mapping (coupled) \cite{yang2010image}, linear mapping (semi-coupled) \cite{wang2012semi}.
-Yang et al.
-\cite{yang2010image} assumed that LR image patches have the same sparse representations as their HR versions do, and proposed a joint dictionary learning model for SR using concatenated HR/LR image features.
-They later imposed relaxed constraints on the observed dictionary/coefficient pairs across image domains for improved performance.
-Wang et al.
-\cite{wang2012semi} further proposed a semi-coupled dictionary
-learning (SCDL) scheme by advancing a linear mapping for cross-domain image sparse representation. Their method
-has been successfully applied to applications of image SR and cross-style synthesis.
+\subsection{Patch Group Prior of Natural Images}
+Patch prior is an approximation of the prior of natural images.
+There are several famous work on this area such as the K-SVD algorithm \cite{ksvd}.
+The seminar work on patch prior modeling is the expected patch log likelihood (EPLL), which models the space of natural image patches via Gaussian Mixture Model.
+Recently, the Patch Group prior \cite{pgpd} is proposed to directly model the non-local self similarity within natural images.
+The patch group prior demonstrate better properties via better image denoising performance on natural images.
+However, PGPD only utilizes the information of clean natural images, but not fully make full of the NSS information of noisy input images.
+In this paper, we combine the information of external natural clean images and internal real noisy images to achieve adaptive patch group prior modeling.
+In fact, we use the external Pacth Group prior to guide the structural clustering of internal patch groups in real noisy images.
+For each cluster of PGs, we propose to use PCA for subspace learning.
+The eigenvectors are the basis of this subspace and hence can be used as an orthonormal dictionary.
+The eigenvalues reflect the information describing the noise levels and hence can be used as parameters for image denoising.
+Noted that the dictionary and parameters are obtained via a fully unsupervised way by subspace learning.
+Therefore, our model is highly adaptive to the noisy input images.
 
@@
 
-\section{Double Semi-Couple Dictionary Learning}
+\section{Patch Group Prior Guided Internal Structural Clustering and Subspace Learning}
 In this section, we first formulate the real image denoising problem from the perspective of learning based model and then provide the optimization for the problem.

### 2016-10-10 egpaper_for_review.tex
aa

@@
 \usepackage{subfigure}
+\usepackage{upgreek}
 
@@
 %%%%%%%%% TITLE
-\title{External Patch Group Prior Guided Internal Clustering and Subspace Learning for Real Image Denoising}
+\title{External Patch Group Prior Guided Internal Subspace Learning for Real Image Denoising}
 
@@
 \maketitle
-%\thispagestyle{empty}
 
@@
 Existing image denoising methods largely depends on noise modeling and estimation.
-The commonly used noise models, additive white Gaussian or Mixture of Gaussians, are inflexible in describing the complex noise on real noisy images or time consuming in parametric estimation, respectively.
-Hence, this would limit the denoising performance of existing methods.
+The commonly used noise models, additive white Gaussian, are inflexible in describing the complex noise on real noisy images.
+This would limit the performance of existing methods on denoising real noisy images.
 In this paper, we firstly demonstrate that almost all state-of-the-art methods on removing Gaussian noise and real noise are limited in denoising real noisy images.
@@
 \item We achieve much better performance, visual quality, PSNR, SSIM, and speed for real image denoising problem.
-
 \end{itemize}
@@
 
-\section{Patch Group Prior Guided Internal Structural Clustering and Subspace Learning}
-In this section, we first formulate the real image denoising problem from the perspective of learning based model and then provide the optimization for the problem.
-\subsection{Problem Formulation}
-For real image denoising, we first collect clean natural images and real noisy images for training.
-Assume the $\mathbf{X}$ and $\mathbf{Y}$ are unpaired clean image patches and real noisy patches.
-Let the $\mathbf{X} = \mathbf{D}_{x}\mathbf{A}_{x}$ and $\mathbf{Y} = \mathbf{D}_{y}\mathbf{A}_{y}+\mathbf{V}_{y}$, where $\mathbf{V}_{y}$ is the real noise of which we don't know the distribution.
-\begin{equation}
+\section{Patch Group Prior Guided Internal Subspace Learning}
+In this section, we formulate the framework of external Patch Group prior guided internal subspace learning.
+We first introduce the patch group prior leaning on clean natural RGB images.
+Then we formulate the external guided internal subspace learning.
+Finally, we discuss the differences between external subspaces and the corresponding internal subspace.
+
+\subsection{External Patch Group Prior Learning on Clean Natural Images}
+Images often demonstrate highly nonlocal self-similarity (NSS) property, which refers to the fact that a patch always have similar patches to it around the image.
+This property is a key successful factor in image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm} and restoration methods \cite{}.
+In \cite{pgpd}, the NSS property is recently learned as an external prior in a patch group manner.
+In this section, we formulate the Patch Group prior on clean natural images.
+
+For each local patch (size: $p\times p \times 3$ for RGB channels) of a given clean image, we can find the first $M$ most similar nonlocal patches to it across the whole image.
+In practice, this can be done by Euclidean distance based block matching in a large enough local window of size $W\times W$.
+A PG is formed by grouping the $M$ similar patches, denoted by $\{\mathbf{x}_{m}\}_{m=1}^{M}$, where $\mathbf{x}_{m}\in \mathbb{R}^{p^{2}\times1}$ is a patch vector.
+The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and $\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}$ is the group mean subtracted patch vector.
+We call
+\begin{equation}\label{equ1}
+\setlength{\abovedisplayskip}{2pt}
+\setlength{\belowdisplayskip}{2pt}
+\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}\}, m=1,...,M
+\end{equation}
+the group mean subtracted PG, and it will be used to learn the NSS prior in our work.
+
+\subsection{PG-GMM Learning}
+From a given set of natural images, we can extract $N$ PGs, and we denote one PG as
+\begin{equation}\label{equ2}
+\setlength{\abovedisplayskip}{2pt}
+\setlength{\belowdisplayskip}{2pt}
+\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N.
+\end{equation}
+The PGs $\{\mathbf{\overline{X}}_{n}\}$ contain a rich amount of NSS information of natural images, and the problem turns to how to learn explicit prior models from $\{\mathbf{\overline{X}}_{n}\}$.
+Considering that Gaussian Mixture Model (GMM) has been successfully used to model the image patch priors in EPLL \cite{epll} and PLE \cite{ple}, we propose to extend patch based GMM to patch group based GMM (PG-GMM) for NSS prior learning.
+
+With PG-GMM, we aim to learn a set of $K$ Gaussians $\{\mathcal{N}(\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})\}$ from $N$ training PGs $\{\mathbf{\overline{X}}_{n}\}$, while requiring that all the $M$ patches $\{\mathbf{\overline{x}}_{n,m}\}$  in PG $\mathbf{\overline{X}}_{n}$ belong to the same Gaussian component and assume that the patches in the PG are independently sampled.
+Note that such an assumption is commonly used in patch based image modeling \cite{ksvd,lssc}.
+Then, the likelihood of $\{\mathbf{\overline{X}}_{n}\}$ can be calculated as
+\begin{equation}\label{equ3}
+\setlength{\abovedisplayskip}{3pt}
+\setlength{\belowdisplayskip}{3pt}
+P(\mathbf{\overline{X}}_{n})  = \sum\nolimits_{k=1}^{K}\pi_{k}\prod\nolimits_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k}).
+\end{equation}
+By assuming that all the PGs are independently sampled, the overall objective likelihood function is $\mathcal{L} = \prod_{n=1}^{N}P(\mathbf{\overline{X}}_{n})$.
+Taking the log of it, we maximize the following objective function for PG-GMM learning
+\begin{equation}\label{equ4}
+\setlength{\abovedisplayskip}{3pt}
+\setlength{\belowdisplayskip}{3pt}
 \begin{split}
-&\min_{\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{A}_{x},\mathbf{A}_{y}}
-\emph{E}_{data}(\mathbf{X},\mathbf{D}_{x},\mathbf{A}_{x})+
-\emph{E}_{data}(\mathbf{Y},\mathbf{D}_{y},\mathbf{A}_{y},\mathbf{V}_{y})
-\\
-&
-+\emph{E}_{map}(f_{1}(\mathbf{A}_{x}),f_{2}(\mathbf{A}_{y}))+
-\emph{E}_{reg}(\mathbf{A}_{x},\mathbf{A}_{y},f_{1},f_{2},\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{V}_{y})
+\ln\mathcal{L}=\sum_{n=1}^{N} \ln(\sum_{k=1}^{K}\pi_{k}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})).
 \end{split}
@@
 
-This framework doesn't need noise modeling and estimation.
-However, we still model the noise by $\mathbf{V}_{y}$ for visualization what we have removed during training.
-The regularization of the noise by $\|\mathbf{V}_{y}\|_{p}^{p}$ can be flexible, that we can penalize it by Frobenius norm, $\ell_{1}$ norm, or any other norms.
-We employ Frobenius norm here for modeling simplicity.
-To model the relationship between the representational coefficients, we propose to use two inversible mapping function $f_{1}$ and $f_{2}$.
-To measure the error, we employ a penalty function $\emph{F}$.
-\begin{equation}
-\begin{split}
-\min_{\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{A}_{x},\mathbf{A}_{y},\mathbf{U}_{x},\mathbf{U}_{y},\mathbf{V}_{y}}
-\|\mathbf{X}-\mathbf{D}_{x}\mathbf{A}_{x}\|_{F}^{2}&
-\\
-+
-\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
-+
-\alpha
-\emph{F}(f_{1}(\mathbf{A}_{x}),f_{2}(\mathbf{A}_{y}))&
-\\
-+
-\beta_{x1}\|\mathbf{A}_{x}\|_{1}
-+
-\beta_{x2}\|\mathbf{A}_{x}\|_{F}^{2}
-+
-\beta_{y1}\|\mathbf{A}_{y}\|_{1}
-+
-\beta_{y2}\|\mathbf{A}_{y}\|_{F}^{2}
-&
-\\
-(+
-\gamma_{y}\|\mathbf{V}_{y}\|_{p}^{p})
-\\
-\text{s.t.}
-\quad
-\|\mathbf{d}_{x,i}\|_{2}=1
-, 
-\|\mathbf{d}_{y,i}\|_{2}=1
-,
-\forall{i}
-.
-\end{split}
-\end{equation}
-Here, we want to discuss more on the mapping functions $f_{1}, f_{2}$ and the measure function $\emph{F}$.
-The mapping function can be linear or nonlinear transformations.
-The linear function can be defined as a mapping matrix $f_{1}(\mathbf{A}_{x})=\mathbf{U}_{x}\mathbf{A}_{x}$ and $f_{2}(\mathbf{A}_{y})=\mathbf{U}_{y}\mathbf{A}_{y}$.
-The corresponding penalty terms on the mapping matrices are $\|\mathbf{U}_{x}\|_{F}^{2}$ and $\|\mathbf{U}_{y}\|_{F}^{2}$.
-The nonlinear function can be defined as sigmoid function $f_{1}(\mathbf{A}_{x})=1/(1+\exp\{-\mathbf{A}_{y}\})$.
-We can also employ "first-linear-then-nonlinear" or "first-nonlinear-then-linear" strategies.
-Here, we don't have explict penalty terms for the nonlinear mapping functions.
-The derivatives of the nonlinear case also need further discussions since it is not easy to obtain closed-form solutions with sigmoid functions.
-In this paper, we utilize linear transformation matrices as the mapping functions $f_{1}$ and $f_{2}$.
-The measure penalty function is simply defined by Frobenius norm.
-Hence, the term is defined as $\|\mathbf{U}_{x}\mathbf{A}_{x}-\mathbf{U}_{y}\mathbf{A}_{y}\|_{F}^{2}$.
-However, this would generate a trivial solution of $\mathbf{U}_{x}=\mathbf{U}_{y}=\mathbf{0}$.
-In order to avoid this case, we propose to use the inverse of the mapping matrices, i.e., $\mathbf{U}_{x}^{-1}$ and $\mathbf{U}_{y}^{-1}$.
-
-In summary, we propose a Doubly Inversible and Semi-Coupled Dictionary Learing (DISCDL) model to learn the dictionaries and mapping functions between real noisy images and latent clean natural images.
-\begin{equation}
-\begin{split}
-\min_{\mathbf{D}_{x},\mathbf{D}_{y},\mathbf{A}_{x},\mathbf{A}_{y},\mathbf{U}_{x},\mathbf{U}_{y},\mathbf{V}_{y}}
-\|\mathbf{X}-\mathbf{D}_{x}\mathbf{A}_{x}\|_{F}^{2}&
-\\
-+
-\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
-+
-\alpha
-\|\mathbf{U}_{x}^{-1}\mathbf{A}_{x}-\mathbf{U}_{y}^{-1}\mathbf{A}_{y}\|_{F}^{2}&
-\\
-+
-\beta_{x1}\|\mathbf{A}_{x}\|_{1}
-+
-\beta_{x2}\|\mathbf{A}_{x}\|_{F}^{2}
-+
-\beta_{y1}\|\mathbf{A}_{y}\|_{1}
-+
-\beta_{y2}\|\mathbf{A}_{y}\|_{F}^{2}
-&
-\\
-(+
-\gamma_{y}\|\mathbf{V}_{y}\|_{p}^{p})
-&
-\\
-+
-\lambda_{x}\|\mathbf{U}_{x}^{-1}\|_{F}^{2}
-+
-\lambda_{y}\|\mathbf{U}_{y}^{-1}\|_{F}^{2}
-\\
-\text{s.t.}\quad \|\mathbf{d}_{x,i}\|_{2}=1, \|\mathbf{d}_{y,i}\|_{2}=1, \forall{i}.
-\end{split}
-\end{equation}
-This model has three major differences when compared with SCDL model.
-\begin{itemize}
-\item We use a matrix $\mathbf{V}_{y}$ to model the noise, and we don't set any prior distribution on it.
-This term can help us visualize the noise we learned from the data, i.e., the real noisy images.
-This make our model fully data-driven.
-Since our assumption (we have no assumption at all) on noise is more flexible than others', the noise we obtain in our model can be more accurate than other statistical models such as Gaussian or Mixture of Gaussians.
-Besides, it is time-consuming to fit the noise model from the online data.
-\item We use two inversible matrices as the mapping transformations between the coefficients of the real noisy patches and the latent clean patches.
-This makes our model more flexible than SCDL in which the mapping matrix not explictly inversible.
-Besides, the SCDL can only transform LR images into HG images while our model can transform two different image styles in both direction.
-\item The constraints on dictionary atoms in our model is strictly $\|\mathbf{d}_{x,i}\|_{2}=1, \|\mathbf{d}_{y,i}\|_{2}=1$ while the CDL model and SCDL model are $\|\mathbf{d}_{x,i}\|_{2}\le1, \|\mathbf{d}_{y,i}\|_{2}\le1$.
-This makes our model more robust on the dictionary learning since both the dictionary atoms and sparse coefficients are interacted with each other.
-The $\le1$ constraints would like to make the coefficients larger and dictionary atoms smaller or even vanish.
-However, in the training stage, we care more about the dictionary atoms and would rather ignore the sparse coefficients.
-\end{itemize}
+In Fig., we show two different eigenvectors and eigenvalues.\ One can see that before mean subtraction, the two PGs have very different local structures.\ After mean subtraction, the two PGs will have very similar variations.\ This greatly facilitates the prior learning because the possible number of patterns is reduced, while the training samples of each pattern are increased.
+We will discuss further the benefits of mean subtraction and the associated prior model learning in Section 2.4.
 

### 2016-10-10 egpaper_for_review.tex
aa

@@
 
-For each local patch (size: $p\times p \times 3$ for RGB channels) of a given clean image, we can find the first $M$ most similar nonlocal patches to it across the whole image.
-In practice, this can be done by Euclidean distance based block matching in a large enough local window of size $W\times W$.
-A PG is formed by grouping the $M$ similar patches, denoted by $\{\mathbf{x}_{m}\}_{m=1}^{M}$, where $\mathbf{x}_{m}\in \mathbb{R}^{p^{2}\times1}$ is a patch vector.
+In external PG prior learning on clean natural images, a PG is obtained via finding the $M$ most similar nonlocal patches to the local patch (size: $p\times p \times 3$ for RGB channels) in a given clean image.
+The similarity is measured by Euclidean distance or other distance measurements.
+In this work, we find similar PGs through the Euclidean distance based block matching in a large enough local window of size $W\times W$.
+The PG is denoted by $\{\mathbf{x}_{m}\}_{m=1}^{M}$, where $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ is a patch vector.
 The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and $\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}$ is the group mean subtracted patch vector.
@@
 \end{equation}
-the group mean subtracted PG, and it will be used to learn the NSS prior in our work.
+the group mean subtracted PG, and it will be used to learn the NSS prior in our work. All these are similar with the definitions in \cite{pgpd}.
 
-\subsection{PG-GMM Learning}
-From a given set of natural images, we can extract $N$ PGs, and we denote one PG as
+From a given set of natural images, we can extract $N$ PGs, and  PG as
 \begin{equation}\label{equ2}
@@
 \end{equation}
-The PGs $\{\mathbf{\overline{X}}_{n}\}$ contain a rich amount of NSS information of natural images, and the problem turns to how to learn explicit prior models from $\{\mathbf{\overline{X}}_{n}\}$.
-Considering that Gaussian Mixture Model (GMM) has been successfully used to model the image patch priors in EPLL \cite{epll} and PLE \cite{ple}, we propose to extend patch based GMM to patch group based GMM (PG-GMM) for NSS prior learning.
+We employ the patch group based Gaussian Mixture Model (PG-GMM) for NSS prior learning. The learning process is the same with that in \cite{pgpd}.
 
@@
 \end{equation}
-By assuming that all the PGs are independently sampled, the overall objective likelihood function is $\mathcal{L} = \prod_{n=1}^{N}P(\mathbf{\overline{X}}_{n})$.
-Taking the log of it, we maximize the following objective function for PG-GMM learning
+By assuming that all the PGs are independently sampled, the overall objective log-likelihood function is
 \begin{equation}\label{equ4}
@@
 \end{equation} 
+We maximize the above objective function for PG-GMM learning.
+Finally, we obtain the GMM model with three sets of parameters including mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}=\mathbf{0}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.
+Noted that in PGPD \cite{pgpd}, the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
 
-In Fig., we show two different eigenvectors and eigenvalues.\ One can see that before mean subtraction, the two PGs have very different local structures.\ After mean subtraction, the two PGs will have very similar variations.\ This greatly facilitates the prior learning because the possible number of patterns is reduced, while the training samples of each pattern are increased.
-We will discuss further the benefits of mean subtraction and the associated prior model learning in Section 2.4.
+\subsection{External PG Prior Guided Internal Subspace Learning}
 
-\subsection{Model Optimization}
-While the objective function in (3) is not convex, it is convex with each varible when other variables are fixed.
-We employ alternating direction method of multipliers (ADMM) algorithm here.
-Specifically, we divide the objective function into four sub-problems: 1) updating the sparse coefficients $\mathbf{A}_{x}, \mathbf{A}_{y}$; 2) updating the normalized dictionaries $\mathbf{D}_{x}, \mathbf{D}_{y}$; 3) updating the noise matrix $\mathbf{V}_{y}$; 4) updating the mapping matirces $\mathbf{U}_{x}, \mathbf{U}_{y}$.
-We discuss the four steps as follows.
-
-\subsubsection{Updating $\mathbf{A}_{x}$ and $\mathbf{A}_{y}$}
-
-\begin{equation}
-\begin{split}
-\min_{\mathbf{A}_{x}}
-\|\mathbf{X}-\mathbf{D}_{x}\mathbf{A}_{x}\|_{F}^{2}
-+
-\alpha
-\|\mathbf{U}_{x}^{-1}\mathbf{A}_{x}-\mathbf{U}_{y}^{-1}\mathbf{A}_{y}\|_{F}^{2}
-&
-\\
-+
-\beta_{x1}\|\mathbf{A}_{x}\|_{1}
-+
-\beta_{x2}\|\mathbf{A}_{x}\|_{F}^{2},
-\end{split}
-\end{equation}
-\begin{equation}
-\begin{split}
-\min_{\mathbf{A}_{y}}
-\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
-&
-\\
-+
-\alpha
-\|\mathbf{U}_{x}^{-1}\mathbf{A}_{x}-\mathbf{U}_{y}^{-1}\mathbf{A}_{y}\|_{F}^{2}
-+
-\beta_{y1}\|\mathbf{A}_{y}\|_{1}
-+
-\beta_{y2}\|\mathbf{A}_{y}\|_{F}^{2}.
-\end{split}
-\end{equation}
-
-Take $\mathbf{A}_{x}$ as an example, the first and second terms above can be combined to form a new optimization problems as follows:
-\begin{equation}
-\min_{\mathbf{A}_{x}}
-\|\widetilde{\mathbf{X}}-\widetilde{\mathbf{D}}_{x}\mathbf{A}_{x}\|_{F}^{2}
-+
-\beta_{x1}\|\mathbf{A}_{x}\|_{1}
-+
-\beta_{x2}\|\mathbf{A}_{x}\|_{F}^{2},
-\end{equation}
-where 
-$
-\widetilde{\mathbf{X}}
-=
-\left(\begin{array}{c}
-\mathbf{X}
-\\
-\sqrt{\alpha}\mathbf{U}_{y}^{-1}\mathbf{A}_{y}
-\end{array}\right)
-$
-and
-$
-\widetilde{\mathbf{D}}
-=
-\left(\begin{array}{c}
-\mathbf{D}_{x}
-\\
-\sqrt{\alpha}\mathbf{U}_{x}^{-1}
-\end{array}\right)
-$.
-For $\mathbf{A}_{y}$, it is similar with $\mathbf{A}_{x}$.
-\begin{equation}
-\min_{\mathbf{A}_{y}}
-\|\widetilde{\mathbf{Y}}-\widetilde{\mathbf{D}}_{y}\mathbf{A}_{y}\|_{F}^{2}
-+
-\beta_{y1}\|\mathbf{A}_{y}\|_{1}
-+
-\beta_{y2}\|\mathbf{A}_{y}\|_{F}^{2},
-\end{equation}
-where 
-$
-\widetilde{\mathbf{Y}}
-=
-\left(\begin{array}{c}
-\mathbf{Y}-\mathbf{V}_{y}
-\\
-\sqrt{\alpha}\mathbf{U}_{x}^{-1}\mathbf{A}_{x}
-\end{array}\right)
-$
-and
-$
-\widetilde{\mathbf{D}}
-=
-\left(\begin{array}{c}
-\mathbf{D}_{y}
-\\
-\sqrt{\alpha}\mathbf{U}_{y}^{-1}
-\end{array}\right)
-$.
-These simplified versions have the exactly same formulation as standard sparse coding and can be simply solved by tools such as SPAMS.
-
-The $\mathbf{U}_{x}^{-1}$ and $\mathbf{U}_{y}^{-1}$ are inversible. This will be discussed in subsection "Updating U".
-
-\subsubsection{Updating $\mathbf{D}_{x}$ and $\mathbf{D}_{y}$}
-\begin{equation}
-\min_{\mathbf{D}_{x}}
-\|\mathbf{X}-\mathbf{D}_{x}\mathbf{A}_{x}\|_{F}^{2}
-\quad
-\text{s.t.}
-\quad
-\|\mathbf{d}_{x,i}\|_{2}=1,
-\forall{i}.
-\end{equation}
-
-\begin{equation}
-\begin{split}
-\min_{\mathbf{D}_{y}}
-\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
-\quad 
-\text{s.t.}
-\quad 
-\|\mathbf{d}_{y,i}\|_{2}=1,
-\forall{i}.
-\end{split}
-\end{equation}
-These two are quadraically constrained quadratic program (QCQP) problem and can be solved by Lagrange dual techniques.
-
-\subsubsection{Updating $\mathbf{V}_{y}$}
-The noise matrix is initialized as a zero matirx and updated by solving the following probelm:
-\begin{equation}
-\begin{split}
-\min_{\mathbf{V}_{y}}
-\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
-+
-\gamma_{y}\|\mathbf{V}_{y}\|_{F}^{2}
-\end{split}
-\end{equation}
-This is a ridge regression problem. We can obtain the analytical solution of $\mathbf{V}_{y}$ by 
-\begin{equation}
-\mathbf{V}_{y} = (\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y})/(1+\gamma_{y}).
-\end{equation}
-
-\subsubsection{Alternate Updating $\mathbf{V}_{y}$}
-The noise matrix is initialized as a zero matirx and updated by solving the following probelm:
-\begin{equation}
-\begin{split}
-\min_{\mathbf{V}_{y}}
-\|\mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}-\mathbf{V}_{y}\|_{F}^{2}
-\end{split}
-\end{equation}
-This is a standard least square problem. We can obtain the analytical solution of $\mathbf{V}_{y}$ by 
-\begin{equation}
-\mathbf{V}_{y} = \mathbf{Y}-\mathbf{D}_{y}\mathbf{A}_{y}.
-\end{equation}
-
-\subsubsection{Updating $\mathbf{U}_{x}$ and $\mathbf{U}_{y}$}
-
-\begin{equation}
-\begin{split}
-\min_{\mathbf{U}_{x}^{-1}}
-\alpha
-\|\mathbf{U}_{y}^{-1}\mathbf{A}_{y}-\mathbf{U}_{x}^{-1}\mathbf{A}_{x}\|_{F}^{2}
-+
-\lambda_{x}\|\mathbf{U}_{x}^{-1}\|_{F}^{2}
-\\
-\min_{\mathbf{U}_{y}^{-1}}
-\alpha
-\|\mathbf{U}_{x}^{-1}\mathbf{A}_{x}-\mathbf{U}_{y}^{-1}\mathbf{A}_{y}\|_{F}^{2}
-+
-\lambda_{y}\|\mathbf{U}_{y}^{-1}\|_{F}^{2}
-\end{split}
-\end{equation}
-The above problems are also ridge regression problems and have analytical solutions of $\mathbf{U}_{x}$ and $\mathbf{U}_{y}$ as follows:
-\begin{equation}
-\begin{split}
-\mathbf{U}_{x}^{-1} = \mathbf{U}_{y}^{-1}\mathbf{A}_{y}\mathbf{A}_{x}^{T}(\mathbf{A}_{x}\mathbf{A}_{x}^{T}+(\gamma_{x}/\alpha)\mathbf{I})^{-1}
-\\
-\mathbf{U}_{y}^{-1} = \mathbf{U}_{x}^{-1}\mathbf{A}_{x}\mathbf{A}_{y}^{T}(\mathbf{A}_{y}\mathbf{A}_{y}^{T}+(\gamma_{y}/\alpha)\mathbf{I})^{-1}
-\end{split}
-\end{equation}
-Here, we verify that $\mathbf{U}_{x}^{-1}$ and $\mathbf{U}_{y}^{-1}$ are inversible.
-The $\mathbf{U}_{x}^{-1}$ and $\mathbf{U}_{y}^{-1}$ are both initialized as an identity matrix, of suitable dimension, which is inversible.
-That is, we have $\mathbf{U}_{y}^{(0)} = \mathbf{I}$ when we compute $\mathbf{U}_{x}^{-1}$.
-If $\mathbf{A}_{y}\mathbf{A}_{x}^{T}$ is inversible, then $\mathbf{U}_{x}^{-1}$ is inversible.
-In fact, we have $\mathbf{A}_{y},\mathbf{A}_{x}\in \mathbb{R}^{d\times N}$.
-$d$ is the dimension of the sample.
-For a patch of size $8\times8$, $d=64$.
-The $N$ is the number of samples in the training data.
-Remember that we have much more samples when compared to the dimension of patches, that is $N\gg d$.
-It is less likely that  $\mathbf{A}_{y}\mathbf{A}_{x}^{T}\in \mathbb{R}^{d\times d}$ has a rank structure lower than $d$.
-In other words,  $\mathbf{A}_{y}\mathbf{A}_{x}^{T}\in \mathbb{R}^{d\times d}$ is less likely to be singular if we have enough training data.
-The experiments also confirm our conjecture.
-Besides, we can also add small disburtation to guarantee that $\mathbf{A}_{y}\mathbf{A}_{x}^{T}\in \mathbb{R}^{d\times d}$ is inversible.
-
-Once $\mathbf{U}_{x}^{-1}$ is inversible, we can also verify that $\mathbf{U}_{y}^{-1}$ is inversible in a similar way.
-
-\subsection{Real Image Denoising}
-Two methods:
-
-The first one is that
-\begin{equation}
-\begin{split}
-\min_{\mathbf{a}_{x,i},\mathbf{a}_{y,i}}
-\|\mathbf{x}_{i}-\mathbf{D}_{x}\mathbf{a}_{x,i}\|_{2}^{2}
-+
-\|\mathbf{y}_{i}-\mathbf{D}_{y}\mathbf{a}_{y,i}-\mathbf{v}_{y,i}\|_{2}^{2}
-\\
-+
-\alpha
-\|\mathbf{U}_{x}^{-1}\mathbf{a}_{x,i}-\mathbf{U}_{y}^{-1}\mathbf{a}_{y,i}\|_{2}^{2}&
-\\
-+
-\beta_{x}\|\mathbf{a}_{x,i}\|_{1}
-+
-\beta_{x2}\|\mathbf{a}_{x,i}\|_{2}^{2}
-+
-\beta_{y}\|\mathbf{a}_{y,i}\|_{1}
-+
-\beta_{y2}\|\mathbf{a}_{y,i}\|_{2}^{2}
-&
-\\
-(+
-\gamma_{y}\|\mathbf{v}_{y,i}\|_{1})
-\end{split}
-\end{equation}
-and finally we get $\widehat{\mathbf{x}}_{i}=\mathbf{D}_{x}\widehat{\mathbf{a}}_{x,i}$.
-
-The second one is to solve
-\begin{equation}
-\begin{split}
-\min_{\mathbf{a}_{y,i},\mathbf{v}_{y,i}}
-\|\mathbf{y}_{i}-\mathbf{D}_{y}\mathbf{a}_{y,i}-\mathbf{v}_{y,i}\|_{2}^{2}
-+
-\alpha
-\|\mathbf{U}_{x}^{-1}\mathbf{a}_{x,i}-\mathbf{U}_{y}^{-1}\mathbf{a}_{y,i}\|_{2}^{2}&
-\\
-+
-\beta_{y1}\|\mathbf{a}_{y,i}\|_{1}
-+
-\beta_{y2}\|\mathbf{a}_{y,i}\|_{2}^{2}
-&
-\\
-(+
-\gamma_{y}\|\mathbf{v}_{y,i}\|_{1}).
-\end{split}
-\end{equation}
-Once we get $\widehat{\mathbf{a}}_{y,i}$ from $\mathbf{y}_{i}$, $\widehat{\mathbf{a}}_{x,i}\approx\mathbf{U}_{x}\mathbf{U}_{y}^{-1}\widehat{\mathbf{a}}_{y,i}$ and $\widehat{\mathbf{x}_{i}}\approx\mathbf{D}_{x}\widehat{\mathbf{a}}_{x,i}$.
-
-Experiments demonstrate that the first method can get better performance than the second one while the second one can get faster speed than the first one.
-
-We can also initialized the solution from the second one.
+\subsection{Comparing External PG Prior and Guided Internal Subspace Learning}
 

### 2016-10-11 egpaper_for_review.tex
aa

@@
 
-\section{Patch Group Prior Guided Internal Subspace Learning}
+\section{External Patch Group Prior Guided Internal Subspace Learning}
 In this section, we formulate the framework of external Patch Group prior guided internal subspace learning.
@@
 \begin{equation}\label{equ1}
-\setlength{\abovedisplayskip}{2pt}
-\setlength{\belowdisplayskip}{2pt}
 \mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}\}, m=1,...,M
@@
 \begin{equation}\label{equ2}
-\setlength{\abovedisplayskip}{2pt}
-\setlength{\belowdisplayskip}{2pt}
 \mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N.
@@
 \begin{equation}\label{equ3}
-\setlength{\abovedisplayskip}{3pt}
-\setlength{\belowdisplayskip}{3pt}
 P(\mathbf{\overline{X}}_{n})  = \sum\nolimits_{k=1}^{K}\pi_{k}\prod\nolimits_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k}).
@@
 \begin{equation}\label{equ4}
-\setlength{\abovedisplayskip}{3pt}
-\setlength{\belowdisplayskip}{3pt}
 \begin{split}
@@
 \subsection{External PG Prior Guided Internal Subspace Learning}
+For each $\mathbf{\overline{Y}}$, we select the most suitable Gaussian component to it from the trained PG-GMM.
+Since the noise on real images are small when compared to the signals and the noise on real images are dependent on the signals, the covariance matrix of the $k$th component is still $\mathbf{\Sigma}_{k}$.
+The selection can be done by checking the posterior probability that $\mathbf{\overline{Y}}$ belongs to the $k$th Gaussian component:
+\begin{equation}\label{equ8}
+P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})}.
+\end{equation}
+Finally, the component with the highest probability $\ln P(k|\mathbf{\overline{Y}})$ is selected to process $\mathbf{\overline{Y}}$.
+
+Suppose that the $k$th Gaussian component is selected for PG $\mathbf{\overline{Y}}$.
+For notation simplicity, we remove the subscript $k$ and denote by $\mathbf{\Sigma}$ the covariance matrix of this component.
+In PG-GMM, the PGs actually represent the variations of the similar patches in a group, and these variations are assigned to the same Gaussian distribution.
+By singular value decomposition (SVD), $\mathbf{\Sigma}$ can be factorized as
+\begin{equation}\label{equ10}
+\mathbf{\Sigma} = \mathbf{D}\mathbf{\Lambda}\mathbf{D}^{T},
+\end{equation}
+where $\mathbf{D}$ is an orthonormal matrix composed by the eigenvectors of $\mathbf{\Sigma}$ and $\mathbf{\Lambda}$ is the diagonal matrix of eigenvalues.
+With PG-GMM, the eigenvectors  in $\mathbf{D}$ capture the statistical structures of NSS variations in natural images, while the eigenvalues in $\mathbf{\Lambda}$ represent the significance of these eigenvectors.
+Fig.\ 4 shows the eigenvectors for 3 Gaussian components.
+It can be seen that these eigenvectors encode the possible variations of the PGs.
+For one Gaussian component, the first eigenvector represents its largest variation, while the last eigenvector represents its smallest variation.
+For different Gaussian components, we can see that their eigenvectors (with the same index) are very different.
+Hence, $\mathbf{D}$ can be used to represent the structural variations of the PGs in that component.
+
+\begin{equation}\label{equ15}
+\min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{\overline{y}}_{m}-\mathbf{D}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{p^{2}}\frac{c*2\sqrt{2}\sigma^{2}}{\mathbf{\lambda}_{i}}|\boldsymbol{\upalpha}_{i}|.
+\end{equation}
+By comparing (\ref{equ15}) with (\ref{equ11}), we can see that the $i$th entry of the weighting vector $\mathbf{w}$ should be
+\begin{equation}\label{equ16}
+\setlength{\abovedisplayskip}{3pt}
+\setlength{\belowdisplayskip}{3pt}
+\mathbf{w}_{i} = c*2\sqrt{2}\sigma^{2}/(\mathbf{\lambda}_{i}+\varepsilon),
+\end{equation}
+where $\varepsilon$ is a small positive number to avoid dividing by zero.
+With $\mathbf{w}$ determined by (\ref{equ16}), let's see what the solution of (\ref{equ11}) should be.
+Since the dictionary $\mathbf{D}$ is orthonormal, it is not difficult to find out that (\ref{equ11}) has a closed-form solution (detailed derivation can be found in the supplementary material):
+\begin{equation}\label{equ17}
+\setlength{\abovedisplayskip}{3pt}
+\setlength{\belowdisplayskip}{4pt}
+\hat{\boldsymbol{\upalpha}}= \text{sgn}(\mathbf{D^{T}\overline{y}}_{m})\odot \text{max}(|\mathbf{D^{T}\overline{y}}_{m}|-\mathbf{w}/2,0),
+\end{equation}
+where $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication, and $|\mathbf{D^{T}\overline{y}}_{m}|$ is the absolute value of each entry of vector $|\mathbf{D^{T}\overline{y}}_{m}|$.
+The closed-form solution makes our weighted sparse coding process very efficient.
+\vspace{-0.05in}
 
@@
 
-\section{The Overall Algorithm}
-
-\subsection{Pair Sample Construction from Unpaired Samples}
-In cross style transfer methods such as CDL and SCDL, the authors assume that the two different styles have paired data, i.e., for each data sample in one style, we can find paired data sample in the other style.
-However, in real world, the data from two different sources may be unpaired.
-For example, the real noisy images should not have groundtruth clean images of the same scene.
-The real low-resolution images should not have corresponding high-resolution images in the real world.
-The real blurry images should not have corresponding clear and high quality images in real world.
-
-To deal with unpaired data, we could collect real noisy images and clean natural images from two different sources.
-The real noisy images are from the example images (18 images) of the Neat Image website while the clean natural images are from the training set (200 images) of the Berkeley Segmentation Dataset (BSDS500).
-To make use of the unpaired data samples, we employ searching strategy to construct the training dataset.
-That is, for each noisy image patch, we utilize the k-Nearest Neighbor (k-NN) algorithm to find the most similar patch in the clean images as the paired groundtruth patch.
-The similarity is measured by the Euclidean distance (also called squared error or $\ell_{2}$ norm).
-
-\subsection{Structual Clustering and Model Selection}
-In fact, different image structures should have different influences on dictioanry as well as the mapping function.
-Patches with flat region should have low rank structure within dictionary elements and identity mapping between noisy and latent clean patches.
-Patches with complex details should have more comprehensive dictionary elements within dictionary elements and more complex mapping function between noisy and clean patches.
-A single mapping function cannot deal with all these complex relationships.
-Hence, a structual clustering procedure is needed for complex solution.
-In this paper, we propose to employ Gaussian Mixture Model to cluster different image patches into different groups and learn dictionary and mapping function for each group.
+\section{The Enhanced Algorithm}
 
@@
 
+\subsection{The Overall Algorithm}
 %------------------------------------------------------------------------
 \section{Experiments}
+In this section, we perform real image image denoising experiments on three standard datasets.
+The first dataset is real noisy images with mean images as ground truths.
+The second dataset is provided by the website of Noise Clinic.
+The third dataset is provided by the Commercial software Neat Image.
+The second and third dataset do not have ground truth images.
 
-We compare with popular software NeatImage which is one of the best denoising software available.
+\subsection{Parameters Setting}
+The proposed method contains the PG prior learning stage, the external prior guided internal subspace learning stage, and the denoising stage.
+In the learning stage, similar to the PGPD, there are four parameters, $p$, $M$, $W$, and $K$.
+We set $p=6$ and hence the patch size is $6\times 6 \times 3$.
+The winodw size for searching PGs is W = 31.
+The number of similar patches is $N=10$, the number of cluters is set as $K = 33$.
+In the external prior guided learning stage, there is no parameters.
+In the denoising stage, there are one paramters, i.e., the $\lambda$ which is used to regularize the sparse term.
+
+\subsection{Comparison Methods}
+We compare with previous state-of-the-art Gaussian noise removal methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and the recently proposed TRD \cite{chencvpr2015}.
+We also compare with three competing real image denoising methods such as Noise Clinic, Neat Image, and the CCNoise method proposed recently.
+The popular software NeatImage which is one of the best denoising software available.
 All these methods need noise estimation which is vary hard to perform if there is no uniform regions are available in the testing image.
@@
 
-\subsection{Parameters}
-We don't fine tune the parameters both in the training and testing datasets.
-
 \subsection{Real Image Denoising}
-We compare the proposed method with the famous BM3D \cite{bm3d} and WNNM \cite{wnnm}, Cascade of Shrinkage Fields (CSF) \cite{csf}, trainable reaction diffusion (TRD) \cite{chen2015learning}, plain neural network based method MLP \cite{burger2012image}, the blind image denoising method Noise Clinic \cite{noiseclinic}, and the commercial software Neat Image.
-The RGB images are firstly transformed into YCbCr channels and restored by these methods.
-Then the denoised RGB image is obtained by transforming the restored YCbCr image back.
-
 We evaluate the competing denoising methods from various research directions on two datasets.

### 2016-10-11 egpaper_for_review.tex
a

@@
 In this section, we perform real image image denoising experiments on three standard datasets.
-The first dataset is real noisy images with mean images as ground truths.
-The second dataset is provided by the website of Noise Clinic.
-The third dataset is provided by the Commercial software Neat Image.
+The first dataset is real noisy images with mean images as ground truths provided by \cite{crosschannel2016}.
+The second dataset is provided by the website of Noise Clinic \cite{noiseclinic}.
+The third dataset is provided by the Commercial software Neat Image \cite{neatimage}.
 The second and third dataset do not have ground truth images.
@@
 We set $p=6$ and hence the patch size is $6\times 6 \times 3$.
-The winodw size for searching PGs is W = 31.
+The winodw size for searching PGs is $W = 31$.
 The number of similar patches is $N=10$, the number of cluters is set as $K = 33$.
@@
 \subsection{Real Image Denoising}
-We evaluate the competing denoising methods from various research directions on two datasets.
+We  the competing denoising methods from various research directions on two datasets.
 Both the two datasets comes from the \cite{crosschannel2016}.
-The first contains 3 cropped images of size $512\times512$.
-The other dataset contains 42 images cropped to size of $500\times500$ from the 17 images provided in \cite{crosschannel2016}.
-The 60 images contain most of the scenes in the 17 images \cite{crosschannel2016}.
-\begin{table*}
-\caption{Average PSNR(dB) results of different methods on 3 real noisy images captured by Canon EOS 5D mark3 at ISO3200 in \cite{crosschannel2016}.}
+The first dataset contains 17 images of size over $7000\times5000$.
+Since this dataset contains recurrent contents across different images, we crop 60 small images of size $500\times500$ from these 17 images in \cite{crosschannel2016}.
+
+The PSNR and SSIM resluts are listed in table \ref{tab1}.
+\begin{table*}\label{tab1}
+\caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
 \label{tab1}
@@
 \renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
 \hline
-Image & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{CSF}&\textbf{TRD}&\textbf{MLP}& \textbf{Noise Clinic}& \textbf{Neat Image}&\textbf{Ours}
+Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}& \textbf{NI}& \textbf{NC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
 \\
 \hline
-1& 37.00 & 37.08 & 37.09 &  37.46  &  37.51  &  32.91  & \textbf{ 38.76}  & 37.68   & 38.63  
+PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 &  36.53  &  37.57  & 37.66 & 37.92 &  \textbf{ 38.46}
 \\
 \hline
-2& 33.88 & 33.95  &  33.95  &  34.90  &  35.04  & 31.94   &  35.69  &  34.87  & \textbf{ 35.96 }
-\\
-\hline
-3& 33.83  & 33.85  & 33.85   & 34.15   &   34.07 & 30.89   & \textbf{35.54 }  &  34.77  &  35.51 
-\\
-\hline
-Average & 34.90  &  34.96 &  34.96  & 35.50   & 35.54   &  31.91  &  36.67  &  35.77  &  \textbf{ 36.70}
+SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598  & 0.9241  &  0.9514  & 0.9495  & 0.9625 &   \textbf{0.9677}
 \\
@@
 
-\begin{table*}
-\caption{Average SSIM results of different methods on 3 real noisy images captured by Canon EOS 5D mark3 at ISO3200 in \cite{crosschannel2016}.}
+\begin{table*}\label{tab2}
+\caption{Average PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
 \label{tab1}
@@
 \renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|}
 \hline
-Image & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{CSF}&\textbf{TRD}&\textbf{MLP}& \textbf{Noise Clinic}& \textbf{Neat Image}&\textbf{Ours}
+Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}& \textbf{NI}& \textbf{NC}& \textbf{CC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
 \\
 \hline
-1& 0.9345 & 0.9368  & 0.9372  & 0.9599   &  0.9607  & 0.9043   &  0.9689  & 0.9600   &\textbf{ 0.9712  }
+PSNR & 33.41  &  33.48 &  33.48  & 36.49   & 35.33 &  35.49   &  36.43  &  36.88  & 36.69 & 36.75 &  \textbf{ 37.04}
 \\
 \hline
-2& 0.8919 &  0.8848 &  0.8951 & 0.9159   &  0.9187  &  0.8498  &  0.9427  &  0.9308  & \textbf{ 0.9434 }
-\\
-\hline
-3& 0.9128  & 0.9136 & 0.9136  & 0.9254   &  0.9279  &  0.8635  &  0.9476  & 0.9463   & \textbf{ 0.9529 }
-\\
-\hline
-Average &  0.9131  & 0.9117 &  0.9153 & 0.9337   & 0.9358   &  0.8725  & 0.9531   & 0.9457   &  \textbf{0.9558} 
+SSIM & 0.8483  & 0.8511  & 0.8512   & 0.9444 & 0.9250  & 0.9126  &  0.9364  & 0.9481  & 0.9486 & 0.9485 &  \textbf{ 0.9509}
 \\
@@
 
-\begin{table*}
-\caption{Average PSNR(dB) and SSIM results of different methods on 42 cropped images from 17 real noisy images in \cite{crosschannel2016}.}
-\label{tab1}
-\begin{center}
-\renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
-\hline
-Measure & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{CSF}&\textbf{TRD}&\textbf{MLP}& \textbf{Noise Clinic}& \textbf{Neat Image}&\textbf{Ours}
-\\
-\hline
-PSNR& 34.36 & 34.36 & 34.40 & 36.11 & 36.05 & 34.41 & 37.68 & 36.58 & 36.15
-\\
-\hline
-SSIM& 0.8552 & 0.8553 & 0.8577 & 0.9215 & 0.9211 & 0.9012 & 0.9470 & 0.9145 & 0.9236
-\\
-\hline
-\end{tabular}
-\end{center}
-\end{table*}
+%\\
+%\hline
+%1 &    &    &     &     &    &      &     &     &   & 38.30  &  \textbf{ 40.13 }
+%\\
+%\hline
+%2 &    &    &     &     &    &      &     &     &   & 37.09  &  \textbf{ 36.99 }
+%\\
+%\hline
+%3 &    &    &     &     &    &      &     &     &   & 36.58  &  \textbf{ 36.92 }
+%\\
+%\hline
+%4 &    &    &     &     &    &      &     &     &   & 34.85  &  \textbf{ 35.11 }
+%\\
+%\hline
+%5 &    &    &     &     &    &      &     &     &   &  36.12 &  \textbf{ 36.50 }
+%\\
+%\hline
+%6 &    &    &     &     &    &      &     &     &   & 38.92  &  \textbf{ 38.74 }
+%\\
+%\hline
+%7 &    &    &     &     &    &      &     &     &   & 38.30  &  \textbf{ 38.30 }
+%\\
+%\hline
+%8 &    &    &     &     &    &      &     &     &   &  39.48 &  \textbf{ 40.26 }
+%\\
+%\hline
+%9 &    &    &     &     &    &      &     &     &   & 38.72  &  \textbf{ 38.68 }
+%\\
+%\hline
+%10 &    &    &     &     &    &      &     &     &   & 38.38  &  \textbf{ 38.35 }
+%\\
+%\hline
+%11 &    &    &     &     &    &      &     &     &   & 36.42  &  \textbf{ 36.77 }
+%\\
+%\hline
+%12 &    &    &     &     &    &      &     &     &   & 38.35  &  \textbf{ 38.41 }
+%\\
+%\hline
+%13 &    &    &     &     &    &      &     &     &   & 33.26  &  \textbf{ 33.61 }
+%\\
+%\hline
+%14 &    &    &     &     &    &      &     &     &   &   &  \textbf{ 33.40 }
+%\\
+%\hline
+%15 &    &    &     &     &    &      &     &     &   &   &  \textbf{ 33.47 }
 

### 2016-10-12 egpaper_for_review.tex
a

@@
 \item Our method doesn't need noise modeling and estimation, and the noise levels of real noisy images are automatically expresssed by the singular values of learned subspace;
-\item We achieve much better performance, visual quality, PSNR, SSIM, and speed for real image denoising problem.
+\item We achieve much better performance on visual quality, PSNR, SSIM, and speed, than other competing methods for real image denoising problem.
 \end{itemize}
@@
 Therefore, our model is highly adaptive to the noisy input images.
+
+\subsection{Internal v.s. External Image Denoising}
+The internal patch recurrence across multiple scales of a natural image has been successfully applied in many image restoration problems such as single image super-resolution \cite{Irani2009sr}, image denoising \cite{Irani2013separating}, blind image deblurring \cite{Irani2014deblur}, and image dehazing \cite{Irani2016dehazing}, etc.
+These work demonstrate that internal information is enough for denoising additive white Gaussian noise.
+The reason is that the AWGN noise is independent of the original clean images, and therefore it will be 缩小 when the image is scaled to smaller size.
+However, the real noise is dependent on the signal \cite{crosschannel2016} and it has fixed patterns from several main sources \cite{healey1994radiometric}.
+The internal information may be not enough for real image denoising problem.
+Noted that even in denoising AWGN, the introduce of external information will also improve the performance denoising methods \cite{luo2015adaptive}.
+In this paper, we demonstrate that for real noise which is signal dependent, it is essential to make use of external clean data.
 
@@
 
-\subsection{Comparing External PG Prior and Guided Internal Subspace Learning}
+\subsection{What does External Data help the Internal Subspace Learning?}
+The external data can help the internal learning in two ways.
+On one hand, it can guide the noisy image patches to be divided into correct subspaces through clustering.
+If we cluster the noisy patches in an automatical way, just like the PLE \cite{ple} did, the signal dependent noise would be hardly removed.
+With the help of clean external data, the noisy patches can be divided into correct subspaces.
+Besides, external data guided internal clustering is much more efficient than directly clustering the noisy data due to the time consuming fitting procedure.
+On the other hand, due to the correct division of internal noisy data, the dictionary and paranters for subspace learning could be more adaptive to the testing real noisy image.
+Hence, it would achieve better denoising performance than the methods only using the external information.
+
+\subsection{The Internal Subspace is truly the subspace of external space}
+Plot a Figure to demonstrate the data distributed in external space and the assigned internal subspace.
+The internal subspace is only a subspace of the external space.
+Hence, if we use the external data to perform denoising, the performance would be limited due to the dependence of noise on signal.
+If we combine the external and internal data for subspace learning, the learned subspace would be too generative and would therefore not specifically suitable for the testing data.
 
@@
 
-\subsection{Adaptive Iterations of Different Noise Levels}
+\subsection{Iterative Regularization}
+Perfoming image denoising in one iteration is not enough for real noise since the noise is signal dependent.
+The removed noise in one iteration is largely dependent on the signal.
+Therefore, it is essential to add back some residuals removed in this iteration for the denoising of the next iteration.
+
+\subsection{Effectively dealing with different noisy images}
 For real image denoising, we can perform well on images which have similar noise levels with the training dataset.
@@
 \subsection{The Overall Algorithm}
+
 %------------------------------------------------------------------------
@@
 \hline
-PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 &  36.53  &  37.57  & 37.66 & 37.92 &  \textbf{ 38.46}
+PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 &  36.53  &  37.57  &     & 38.07 &  \textbf{ 38.46}
 \\
 \hline
-SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598  & 0.9241  &  0.9514  & 0.9495  & 0.9625 &   \textbf{0.9677}
+SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598  & 0.9241  &  0.9514  &     & 0.9625 &   \textbf{0.9677}
 \\
@@
 \hline
-PSNR & 33.41  &  33.48 &  33.48  & 36.49   & 35.33 &  35.49   &  36.43  &  36.88  & 36.69 & 36.75 &  \textbf{ 37.04}
+PSNR & 33.41  &  33.48 &  33.48  & 34.32   & 35.33 &  35.49   &  36.43  &  36.88  & 36.69 & 36.73 &  \textbf{ 37.04}
 \\
 \hline
-SSIM & 0.8483  & 0.8511  & 0.8512   & 0.9444 & 0.9250  & 0.9126  &  0.9364  & 0.9481  & 0.9486 & 0.9485 &  \textbf{ 0.9509}
+SSIM & 0.8483  & 0.8511  & 0.8512   & 0.9113 & 0.9250  & 0.9126  &  0.9364  & 0.9481  & 0.9479 & 0.9419 &  \textbf{ 0.9509}
 \\

### 2016-10-12 ID_supp.tex
a

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfigure}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE
\title{A Noise Estimation Free Framework for Robust Real Image Denoising}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

 %%%%%%%%% BODY TEXT
\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}}
{\footnotesize (a) Noisy Image \\ (35.05dB/0.9486) }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}}
{\footnotesize (b) Mean Image}
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}}
{\footnotesize (c) CBM3D \\ (35.06dB/0.9491)}
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}}
{\footnotesize (d) CSF \\ (33.17dB/0.9545)}
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}}
{\footnotesize (e) MLP \\ (33.04dB/0.9492)}
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}}
{\footnotesize (f) Noise Clinic \\ (36.62dB/0.9743) }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}}
{\footnotesize (g) Neat Image \\ (35.87dB/0.9656) }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}}
{\footnotesize (h) Offline \\ (35.14dB/0.9715)}
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}}
{\footnotesize (i) Online \\ (36.29dB/0.9763)}
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}}
{\footnotesize (j) Guided \\ (\textbf{36.95}dB/\textbf{0.9785})}
\end{minipage}
}
\caption{Denoised images of the old image "$Canon EOS 5D Mark3 ISO 3200 C1$" by different methods. The images are better to be zoomed in on screen.}
\label{fig1}
\end{figure*}

\begin{figure*}
\centering
\subfigure{
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Noisy_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}}
{\footnotesize (a) Noisy Image \\ (35.92dB/0.8998) }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Mean_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}}
{\footnotesize (b) Mean Image}
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CBM3D_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}}
{\footnotesize (c) CBM3D \\ (35.94dB/0.9008) }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CSF_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}}
{\footnotesize (d) CSF \\ (38.24dB/0.9670) }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_MLP_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}}
{\footnotesize (e) MLP \\ (36.38dB/0.9539)}
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NC_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}}
{\footnotesize (f) Noise Clinic \\ (39.18dB/0.9668) }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NI_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}}
{\footnotesize (g) Neat Image \\ (38.58dB/0.9534) }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Offline_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}}
{\footnotesize (h) Offline \\ (39.78dB/0.9770)}
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Online_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}}
{\footnotesize (i) Online \\ (39.33dB/0.9747) }
\end{minipage}
\begin{minipage}[t]{0.2\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Guided_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}}
{\footnotesize (j) Guided \\ (\textbf{39.91}dB/\textbf{0.9761})}
\end{minipage}
}
\caption{Denoised images of the old image "$Nikon D800 ISO 1600 B3$" by different methods. The images are better to be zoomed in on screen.}
\label{fig1}
\end{figure*}
{\small
\bibliographystyle{unsrt}
\bibliography{egbib}
}

\end{document}

### 2016-10-12 egpaper_for_review.tex
a

@@
 
-\subsection{The Internal Subspace is truly the subspace of external space}
+\subsection{The Internal PGs Spaces Are Subspaces of Corresponding External PG Spaces}
+In this subsection, we compare the distribution of external PGs extracted from clean natural images and real noisy images.
+For better illumination, we randomly selected a cluster and project the original clean PGs onto a 2-D plane.
 Plot a Figure to demonstrate the data distributed in external space and the assigned internal subspace.
@@
 \hline
-PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 &  36.53  &  37.57  &     & 38.07 &  \textbf{ 38.46}
+PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 &  36.53  &  37.57  &  38.19   & 38.07 &  \textbf{ 38.46}
 \\
 \hline
-SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598  & 0.9241  &  0.9514  &     & 0.9625 &   \textbf{0.9677}
+SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598  & 0.9241  &  0.9514  &  0.9663   & 0.9625 &   \textbf{0.9677}
 \\
@@
 \end{table*}
+
+\begin{figure*}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (b) Mean Image}
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (c) CBM3D \\ (33.33dB/0.8935)  }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (d) CSF \\ (35.39dB/0.9677) }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (e) MLP \\ (34.22dB/0.9603) }
+\end{minipage}
+}
+\subfigure{
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (f) Noise Clinic \\ (35.33dB/0.9520)  }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (g) Neat Image \\ (34.39dB/0.9314)  }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Offline_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (h) Offline \\ (36.29dB/0.9705)}
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Online_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (i) Online \\ (35.80dB/0.9641) }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (j) Guided \\ (\textbf{37.28}dB/\textbf{0.9729})}
+\end{minipage}
+}
+\caption{Denoised images of the old image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
+\label{fig1}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Noisy_5dmark3_iso3200_3_real.png}}
+{\footnotesize (a) Noisy Image \\ (33.83dB/0.9128)  }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Mean_5dmark3_iso3200_3_real.png}}
+{\footnotesize (b) Mean Image}
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CBM3D_5dmark3_iso3200_3_real.png}}
+{\footnotesize (c) CBM3D \\ (33.84dB/0.9134)   }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CSF_5dmark3_iso3200_3_real.png}}
+{\footnotesize (d) CSF \\ (32.62dB/0.9031)  }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_MLP_5dmark3_iso3200_3_real.png}}
+{\footnotesize (e) MLP \\ (32.36dB/0.8993)  }
+\end{minipage}
+}
+\subfigure{
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NC_5dmark3_iso3200_3_real.png}}
+{\footnotesize (f) Noise Clinic \\ (35.54dB/0.9476)  }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NI_5dmark3_iso3200_3_real.png}}
+{\footnotesize (g) Neat Image \\ (34.77dB/0.9463)  }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_WNNM_5dmark3_iso3200_3_real.png}}
+{\footnotesize (h) WNNM \\ (33.86dB/0.9143)}
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CCNoise_5dmark3_iso3200_3.png}}
+{\footnotesize (i) CCNoise \\ (34.91dB/0.9478)  }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Guided_5dmark3_iso3200_3_real.png}}
+{\footnotesize (j) Guided \\ (\textbf{37.01}dB/\textbf{0.9676})}
+\end{minipage}
+}
+\caption{Denoised images of the old image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
+\label{fig1}
+\end{figure*}
 

### 2016-10-12 egpaper_for_review.tex
a

@@
 
-\subsection{Comparison Methods}
+\subsection{Comparison on External and Internal methods}
+In this subsection, we compared the proposed external prior guided internal subspace learning model on real image denoising.
+The three methods are evaluated on the dataset provided in \cite{crosschannel2016}.
+We calculate the PSNR, SSIM \cite{ssim} and visual quality of these three methods.
+We also compare the speed.
+The PSNR and SSIM results on 60 cropped images from \cite{crosschannel2016} are listed in Table 1.
+The images are cropped into size of $500\times 500$ for better illustration.
+We also compare the three methods on visual quality in Figure.
+
+\subsection{Comparison With other Competing Methods}
 We compare with previous state-of-the-art Gaussian noise removal methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and the recently proposed TRD \cite{chencvpr2015}.
@@
 \subsection{Real Image Denoising}
+
 We  the competing denoising methods from various research directions on two datasets.

### 2016-10-13 egpaper_for_review.tex
a

@@
 It is an ideal platform for testing natural image models and provides high-quality images for other conputer vision tasks such as image registration, segmentation, and pattern recognition, etc.
-For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,lssc,epll,burger2012image,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN).
-Recently, several discriminative learning methods \cite{burger2012image,csf,chen2015learning} achieving expressive performance on Gaussian noise removal.
+For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN).
+However, the images captured by CMOS or CCD cameras will undertake an in-camera imaging pipeline.
+The in-camera imaging pipeline includes mainly image demosaicing, white balance and color space transform, gamut mapping, tone mapping, and JPEG comression \cite{NewInCamera,crosschannel2016}.
+Therefore, the noise in real images are much more complex than Gaussian, and depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc).
+The models designed to deal with AWGN would become much less effective on real noisy images.
+
+%Recently, several discriminative learning methods \cite{burger2012image,csf,chen2015learning} achieving expressive performance on Gaussian noise removal.
 These methods require a set of paired images, namely clean ground-truth images and the simulated noisy counterparts degraded by identical noise (mainly additive white Gaussian noise, AWGN), to learn an effective model for image denoising.
-However, the noise in real images are much more complex than Gaussian, since it depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc).
-Thus, the model learned with AWGN would become much less effective for denoising real noisy images.
-What's more, usually real noisy images do not have clean counterparts.
-Therefore, almost all current discriminative learning methods cannot be directly applied to real noisy images.
 
@@
 Almost all these methods coincidently employ a two-stage framework: in the first stage, assuming a distribution model (usually Gaussian) on the noise and estimate its parameters; in the second stage, performing denoising with the help of the noise modeling and estimation in the first stage.
-However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008,crosschannel2016}.
-Although the mixture of Gaussians (MoG) model is possible to approximate any unknown noise \cite{Zhu_2016_CVPR}, estimating its parameters is often time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR} \cite{Bishop}.
+However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008}.
+Although the mixture of Gaussians (MoG) model is possible to approximate any unknown noise \cite{Zhu_2016_CVPR}, estimating its parameters is often time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR,Bishop}.
+To evaluate the performanec of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}.
+This image is captured by a Nikon D800 camera while the ISO is set as 3200.
+The "ground truth" image is also provided with which we can calculate objective measurements.
+More details about this dataset can be found at the experimental section.
+The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image.
+This proves that the above mentioned methods are not effective on denoising complex noise on real images.
+\begin{figure*}\label{fig1}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (b) CBM3D \cite{cbm3d} \\ (33.33dB/0.8935)  }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (d) CSF \cite{csf}\\ (35.39dB/0.9677) }
+\end{minipage}
+}
+\subfigure{
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (e) MLP \cite{mlp}\\ (34.22dB/0.9603) }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (f) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (g) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (h) Mean Image }
+\end{minipage}
+}
+\caption{Denoised images of the real noisy image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
+\end{figure*}
 
-The above mentioned limitations indicate that, novel denoising methods are been waiting for which can: 1) avoid noise modeling and estimation; 2) deal with complex noise on real noisy images.
-In this paper, we attempt to solve the two problems in an integrated way for robust real image denoising.
-We find that the Patch Group Prior learning based denoising \cite{PGPD} method learned on natural clean RGB images are enough to outperform the above mentioned denoising methods.
-We also propose a fully internal PG prior based denoising method which achieve better performance than the fully external method.
+In this paper, we attempt to deal with complex noise in real images by intergrating the external and internal information.
+Since the real noise is signal dependent \cite{crosschannel2016,healey1994radiometric}, the prior information in external natural images can be employed to avoid the high correlation between noise and siganl in internal images.
+On the other hand, the internal prior is adaptive to the image and can recover better the latent clean image.
+Based on these observations, we make detailed study on internal and external information for real image denoising task.
+We made several observations.
+Firstly, we found that the Patch Group Prior learning based denoising method \cite{pgpd} learned on clean RGB images are enough to outperform the above mentioned denoising methods.
+Secondly, we also found that a fully internal PG prior based denoising method which achieve better performance than the fully external method.
 Most importantly, we found that the external PG prior guided internal method can achieve even better and faster performance on real image denoising.
-The external PG prior learning based model is employed to guide the clustering of internal PGs extracted from the input noisy images.
+In fact, the external PG prior learning based model is employed to guide the clustering of internal PGs extracted from the input noisy images.
 Then for each cluster of PGs, we perform subspace learning by PCA and denoising by weighted sparse coding.
-The noise level of the noisy images is inheriently expressed in the singular values, which can be used as weights for the sparse coding.
 We perform comprehensive experiments on real noisy images captured by different CMOS or CCS sensors.
@@
 This reveals the potential advantages of combining external and internal information o natural images on robust and complex real noisy image denoising problem.
-
-%The in-camera imaging pipeline usually includes image demosaicing, white balance and color space transform, gamut mapping, tone mapping, and JPEG comression \cite{NewInCamera,crosschannel2016}.
 
@@
 
+The rest of this paper will be summerized as follows: in Section 2, we will introduce the related work close to our work; in Section 3, we will introduce our proposed external prior guided internal subspace learning framework for real image denoising; in Section 4, we will demonstrate the denoising experiments on several standard dataset; in Section 5, we will conclude our paper and give our future work.
 \section{Related Work}
@@
 The images are cropped into size of $500\times 500$ for better illustration.
-We also compare the three methods on visual quality in Figure.
+We also compare the three methods on visual quality in Figure \ref{fig2}.
+
+\begin{figure*}\label{fig2}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (h) Offline \\ (36.29dB/0.9705)}
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (i) Online \\ (35.80dB/0.9641) }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (j) Guided \\ (\textbf{37.28}dB/\textbf{0.9729})}
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (h) Mean Image }
+\end{minipage}
+}
+\caption{Denoised images of the old image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
+\end{figure*}
 
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
-\end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (b) Mean Image}
-\end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (c) CBM3D \\ (33.33dB/0.8935)  }
-\end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (d) CSF \\ (35.39dB/0.9677) }
-\end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (e) MLP \\ (34.22dB/0.9603) }
-\end{minipage}
-}
-\subfigure{
-\begin{minipage}[t]{0.2\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (f) Noise Clinic \\ (35.33dB/0.9520)  }
-\end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (g) Neat Image \\ (34.39dB/0.9314)  }
-\end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Offline_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (h) Offline \\ (36.29dB/0.9705)}
-\end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Online_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (i) Online \\ (35.80dB/0.9641) }
-\end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (j) Guided \\ (\textbf{37.28}dB/\textbf{0.9729})}
-\end{minipage}
-}
-\caption{Denoised images of the old image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
-\label{fig1}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\subfigure{
-\begin{minipage}[t]{0.2\textwidth}
-\centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Noisy_5dmark3_iso3200_3_real.png}}
@@
 \caption{Denoised images of the old image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
-\label{fig1}
+\label{fig3}
 \end{figure*}

### 2016-10-13 egpaper_for_review.tex
a

@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (c) MLP \cite{mlp}\\ (34.22dB/0.9603) }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (e) MLP \cite{mlp}\\ (34.22dB/0.9603) }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (e) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Mean_5dmark3_iso3200_3_real.png}}
-{\footnotesize (b) Mean Image}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CBM3D_5dmark3_iso3200_3_real.png}}
+{\footnotesize (b) CBM3D \\ (33.84dB/0.9134)   }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CBM3D_5dmark3_iso3200_3_real.png}}
-{\footnotesize (c) CBM3D \\ (33.84dB/0.9134)   }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_MLP_5dmark3_iso3200_3_real.png}}
+{\footnotesize (c) MLP \\ (32.36dB/0.8993)  }
 \end{minipage}
+\centering
 \begin{minipage}[t]{0.2\textwidth}
-\centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CSF_5dmark3_iso3200_3_real.png}}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_MLP_5dmark3_iso3200_3_real.png}}
-{\footnotesize (e) MLP \\ (32.36dB/0.8993)  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_WNNM_5dmark3_iso3200_3_real.png}}
+{\footnotesize (e) WNNM \\ (33.86dB/0.9143)}
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_WNNM_5dmark3_iso3200_3_real.png}}
-{\footnotesize (h) WNNM \\ (33.86dB/0.9143)}
-\end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
-\centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CCNoise_5dmark3_iso3200_3.png}}
-{\footnotesize (i) CCNoise \\ (34.91dB/0.9478)  }
+{\footnotesize (h) CCNoise \\ (34.91dB/0.9478)  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Guided_5dmark3_iso3200_3_real.png}}
-{\footnotesize (j) Guided \\ (\textbf{37.01}dB/\textbf{0.9676})}
+{\footnotesize (i) Guided \\ (\textbf{37.01}dB/\textbf{0.9676})}
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Mean_5dmark3_iso3200_3_real.png}}
+{\footnotesize (j) Mean Image}
 \end{minipage}
@@
 \label{fig3}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_dog.png}}
+{\footnotesize (a) Noisy Image   }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
+{\footnotesize (b) CBM3D}
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
+{\footnotesize (c) MLP }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_dog.png}}
+{\footnotesize (d) CSF    }
+\end{minipage}
+}
+\subfigure{
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
+{\footnotesize (e) WNNM    }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
+{\footnotesize (f) Noise Clinic   }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
+{\footnotesize (g) Neat Image    }
+\end{minipage}
+\begin{minipage}[t]{0.25\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_dog.png}}
+{\footnotesize (h) Guided  }
+\end{minipage}
+}
+\caption{Denoised images of the old image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
+\label{fig4}
 \end{figure*}

### 2016-10-13 egpaper_for_review.tex
a

@@
 \subfigure{
-\begin{minipage}[t]{0.25\textwidth}
+\begin{minipage}[t]{0.2\textwidth}
 \centering
@@
 \end{minipage}
-\begin{minipage}[t]{0.25\textwidth}
+\begin{minipage}[t]{0.2\textwidth}
 \centering
@@
 \end{minipage}
-}
-\subfigure{
-\begin{minipage}[t]{0.25\textwidth}
+\begin{minipage}[t]{0.2\textwidth}
 \centering
@@
 \end{minipage}
-\begin{minipage}[t]{0.25\textwidth}
+}
+\subfigure{
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (f) TRD \cite{chen2015learning} \\ (35.97dB/0.9705)   }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
 \centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (f) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
+{\footnotesize (g) PGPD \cite{pgpd} \\ (35.33dB/0.9520)  }
 \end{minipage}
-\begin{minipage}[t]{0.25\textwidth}
+\begin{minipage}[t]{0.2\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (h) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
+\end{minipage}
+\begin{minipage}[t]{0.2\textwidth}
 \centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (g) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
+{\footnotesize (i) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
 \end{minipage}
-\begin{minipage}[t]{0.25\textwidth}
+\begin{minipage}[t]{0.2\textwidth}
 \centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (h) Mean Image }
+{\footnotesize (j) Mean Image }
 \end{minipage}
@@
 \begin{equation}\label{equ15}
-\min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{\overline{y}}_{m}-\mathbf{D}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{p^{2}}\frac{c*2\sqrt{2}\sigma^{2}}{\mathbf{\lambda}_{i}}|\boldsymbol{\upalpha}_{i}|.
+\min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{\overline{y}}_{m}-\mathbf{D}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{p^{2}}\frac{c}{\mathbf{\lambda}_{i}}|\boldsymbol{\upalpha}_{i}|.
 \end{equation}
@@
 \setlength{\belowdisplayskip}{3pt}
-\mathbf{w}_{i} = c*2\sqrt{2}\sigma^{2}/(\mathbf{\lambda}_{i}+\varepsilon),
+\mathbf{w}_{i} = c/(\mathbf{\lambda}_{i}+\varepsilon),
 \end{equation}
@@
 The NeatImage will fail to perform automatical parameters settings if there is no uniform regions.
+\footnote{To compare with CCNoise, we first transform the denoised images into double format.}
 
@@
 \renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|}
 \hline
-Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}& \textbf{NI}& \textbf{NC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
+Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
 \\
 \hline
-PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 &  36.53  &  37.57  &  38.19   & 38.07 &  \textbf{ 38.46}
+PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 & 37.75 &  36.53  &  37.57  &  38.19   & 38.07 &  \textbf{ 38.46}
 \\
 \hline
-SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598  & 0.9241  &  0.9514  &  0.9663   & 0.9625 &   \textbf{0.9677}
+SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  &  0.9663   & 0.9625 &   \textbf{0.9677}
 \\
@@
 \hline
-Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}& \textbf{NI}& \textbf{NC}& \textbf{CC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
+Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
 \\
 \hline
-PSNR & 33.41  &  33.48 &  33.48  & 34.32   & 35.33 &  35.49   &  36.43  &  36.88  & 36.69 & 36.73 &  \textbf{ 37.04}
+PSNR & 33.41  &  33.48 &  33.48  & 34.32   & 35.33 &  35.65 &  35.49   &  36.43  &  36.88  & 36.69 & 36.73 &  \textbf{ 37.04}
 \\
 \hline
-SSIM & 0.8483  & 0.8511  & 0.8512   & 0.9113 & 0.9250  & 0.9126  &  0.9364  & 0.9481  & 0.9479 & 0.9419 &  \textbf{ 0.9509}
+SSIM & 0.8483  & 0.8511  & 0.8512   & 0.9113 & 0.9250 &  0.9280  & 0.9126  &  0.9364  & 0.9481  & 0.9479 & 0.9419 &  \textbf{ 0.9509}
 \\

### 2016-10-14 egpaper_for_review.tex
a

@@
 \usepackage{upgreek}
+\usepackage{multirow}
 
@@
 \subfigure{
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
@@
 \end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
@@
 \end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (g) PGPD \cite{pgpd} \\ (35.33dB/0.9520)  }
+{\footnotesize (g) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
 \end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (h) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
-\end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (i) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
+{\footnotesize (h) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
 \end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (i) Ours \\ (\textbf{37.28}dB/\textbf{0.9729})  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
@@
 The results demonstrate that our method achieves comparable or even better performance on denoising real noisy images.
+An initial glimpse of our method is also listed in Figure \ref{fig1}.
 This reveals the potential advantages of combining external and internal information o natural images on robust and complex real noisy image denoising problem.
@@
 The rest of this paper will be summerized as follows: in Section 2, we will introduce the related work close to our work; in Section 3, we will introduce our proposed external prior guided internal subspace learning framework for real image denoising; in Section 4, we will demonstrate the denoising experiments on several standard dataset; in Section 5, we will conclude our paper and give our future work.
+
 \section{Related Work}
 \subsection{Patch Group Prior of Natural Images}
-Patch prior is an approximation of the prior of natural images.
-There are several famous work on this area such as the K-SVD algorithm \cite{ksvd}.
-The seminar work on patch prior modeling is the expected patch log likelihood (EPLL), which models the space of natural image patches via Gaussian Mixture Model.
-Recently, the Patch Group prior \cite{pgpd} is proposed to directly model the non-local self similarity within natural images.
-The patch group prior demonstrate better properties via better image denoising performance on natural images.
-However, PGPD only utilizes the information of clean natural images, but not fully make full of the NSS information of noisy input images.
-In this paper, we combine the information of external natural clean images and internal real noisy images to achieve adaptive patch group prior modeling.
-In fact, we use the external Pacth Group prior to guide the structural clustering of internal patch groups in real noisy images.
+The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self similar (NSS) property of natural images.
+The NSS property is commonly used in image restoration tasks \cite{nlm,bm3d,lssc,wnnm,pgpd}.
+The PG prior largely reduces the space of images to be modeled when compared to the patch prior \cite{epll}.
+The better modeling on NSS is demonstrated via better image denoising performance on natural images.
+However, in \cite{pgpd}, only the PGs of clean natural images is utilized, while the PGs of noisy input images are ignored.
+In this paper, we aim at making use of both PGs from natural clean images and real noisy images for better denoising performance.
+
+%In fact, we use the external Pacth Group prior to guide the structural clustering of internal patch groups in real noisy images.
 For each cluster of PGs, we propose to use PCA for subspace learning.
@@
 \subsection{Internal v.s. External Image Denoising}
-The internal patch recurrence across multiple scales of a natural image has been successfully applied in many image restoration problems such as single image super-resolution \cite{Irani2009sr}, image denoising \cite{Irani2013separating}, blind image deblurring \cite{Irani2014deblur}, and image dehazing \cite{Irani2016dehazing}, etc.
-These work demonstrate that internal information is enough for denoising additive white Gaussian noise.
-The reason is that the AWGN noise is independent of the original clean images, and therefore it will be 缩小 when the image is scaled to smaller size.
-However, the real noise is dependent on the signal \cite{crosschannel2016} and it has fixed patterns from several main sources \cite{healey1994radiometric}.
-The internal information may be not enough for real image denoising problem.
-Noted that even in denoising AWGN, the introduce of external information will also improve the performance denoising methods \cite{luo2015adaptive}.
-In this paper, we demonstrate that for real noise which is signal dependent, it is essential to make use of external clean data.
+For natural images, the internal patch recurrence across multiple scales has been successfully applied in many image restoration problems \cite{Irani2009sr,Irani2013separating,Irani2014deblur,Irani2016dehazing}.
+These work demonstrate that internal information is enough for many ill-posed problems including denoising additive white Gaussian noise.
+The rationale is, since the AWGN noise is independent of the original clean images, it will be reduced if the image is scaled to a smaller size.
+However, the noise in real images is generated mostly from the camera sensors, which is highly complex and signal dependent \cite{crosschannel2016}.
+Besides, according to the seminar workd of \cite{healey1994radiometric}, the noise in real images has fixed patterns from several main sources.
+Therefore, we can hardly seperate the complex noise from the signals without the help of external (correct) information of natural clean images.
+Only using the internal information may be not enough for real image denoising problem.
+On the other hand, the methods only using the external information may be not adaptive for real noisy images.
+Recently, the methods of \cite{mlp,csf,chen2015learning} had been proposed to learn, on both internal and external images, a process directly mapping the noisy patches to denoised ones.
+These discriminatice learning based methods are only effective on additive white Gaussian noise and ineffective on complex and signal dependent noise in real images.
+This has been shown in Figure \ref{fig1}.
+In this paper, wour goal is to make use of external information to guide the subspace learning of internal PGs for image denoising task.
 
@@
 
-\subsection{External Patch Group Prior Learning on Clean Natural Images}
-Images often demonstrate highly nonlocal self-similarity (NSS) property, which refers to the fact that a patch always have similar patches to it around the image.
-This property is a key successful factor in image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm} and restoration methods \cite{}.
-In \cite{pgpd}, the NSS property is recently learned as an external prior in a patch group manner.
-In this section, we formulate the Patch Group prior on clean natural images.
+\subsection{External Patch Group Prior Learning}
+Natural images often demonstrate repepitive patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm,pgpd} and restoration methods \cite{}.
+In \cite{pgpd}, the NSS property is directly learned as an external prior in a patch group manner.
+In this section, we formulate the Patch Group prior on natural color images.
 
-In external PG prior learning on clean natural images, a PG is obtained via finding the $M$ most similar nonlocal patches to the local patch (size: $p\times p \times 3$ for RGB channels) in a given clean image.
-The similarity is measured by Euclidean distance or other distance measurements.
-In this work, we find similar PGs through the Euclidean distance based block matching in a large enough local window of size $W\times W$.
-The PG is denoted by $\{\mathbf{x}_{m}\}_{m=1}^{M}$, where $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ is a patch vector.
+In \cite{pgpd}, the patch group (PG) is defined as a group of similar patches to the local patch.
+The patch group mean is destracted, and hence different groups patches can share similar PGs.
+Therefore the space to be modeled is largely reduced.
+In this work, we extract PGs from RGB images.
+Each patch is of size $p\times p \times 3$.
+For each local patch, we search its similar patches around it through the Euclidean distance in a local window of size $W\times W$.
+The PG is denoted by $\{\mathbf{x}_{m}\}_{m=1}^{M}$, where $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ is a color image patch vector.
 The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and $\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}$ is the group mean subtracted patch vector.
-We call
+The PG is defined as
 \begin{equation}\label{equ1}
 \mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}\}, m=1,...,M
-\end{equation}
-the group mean subtracted PG, and it will be used to learn the NSS prior in our work. All these are similar with the definitions in \cite{pgpd}.
+\end{equation}, and it represent the external NSS prior on color images. In Figure \ref{fig2}
 
-From a given set of natural images, we can extract $N$ PGs, and  PG as
+Assume we have extracted $N$ PGs from a given set of natural images, and the $n$-th PG is defined as
 \begin{equation}\label{equ2}
@@
 \subfigure{
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (a) Noisy Image \\ (34.66dB/0.9178)   }
 \end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (h) Offline \\ (36.29dB/0.9705)}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (h) Offline \\ (34.97dB/0.9441) }
 \end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (i) Online \\ (35.80dB/0.9641) }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (i) Online \\ (36.86dB/0.9622) }
 \end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (j) Guided \\ (\textbf{37.28}dB/\textbf{0.9729})}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (j) Guided \\ (\textbf{37.09}dB/\textbf{0.9638})}
 \end{minipage}
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
 {\footnotesize (h) Mean Image }
@@
 }
-\caption{Denoised images of the old image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
+\end{figure*}
+
+\begin{figure*}\label{fig2}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (a) Noisy Image \\ (36.15dB/0.9523)    }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (h) Offline \\ (37.12dB/0.9776) }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (i) Online \\ (35.70dB/0.9755)  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (j) Guided \\ (\textbf{37.94}dB/\textbf{0.9804})}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (h) Mean Image }
+\end{minipage}
+}
+\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
 \end{figure*}
@@
 \hline
-Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
+ & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
 \\
 \hline
-PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 & 37.75 &  36.53  &  37.57  &  38.19   & 38.07 &  \textbf{ 38.46}
+PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 & 37.75 &  36.53  &  37.57  &  38.19   & 38.07 &  \textbf{ 38.51}
 \\
 \hline
-SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  &  0.9663   & 0.9625 &   \textbf{0.9677}
+SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  &  0.9663   & 0.9625 &   \textbf{0.9674}
 \\
@@
 \renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
 \hline
-Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
+Camera Settings & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Guided} 
 \\
 \hline
-PSNR & 33.41  &  33.48 &  33.48  & 34.32   & 35.33 &  35.65 &  35.49   &  36.43  &  36.88  & 36.69 & 36.73 &  \textbf{ 37.04}
+\multirow{3}{*}{\small{Canon 5D Mark III}} 
+& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & 38.76 & 38.37 & \textbf{40.32}
+\\ 
+\cline{2-11} 
+\multirow{3}{*}{ISO = 3200}   
+& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & 35.69 & 35.37 & \textbf{37.12}
+\\ 
+\cline{2-11}    
+& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & 35.54 & 34.91 & \textbf{37.09}  
 \\
 \hline
-SSIM & 0.8483  & 0.8511  & 0.8512   & 0.9113 & 0.9250 &  0.9280  & 0.9126  &  0.9364  & 0.9481  & 0.9479 & 0.9419 &  \textbf{ 0.9509}
+\multirow{3}{*}{Nikon D600} 
+& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & \textbf{35.57} & 34.98 & 35.23
+\\ 
+\cline{2-11} 
+\multirow{3}{*}{ISO = 3200}   
+& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & \textbf{36.70} & 35.95 & 36.57
+\\ 
+\cline{2-11}    
+& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & 40.51 & 38.68 & \textbf{39.28} & 41.15 & 38.73
+\\
+\hline
+\multirow{3}{*}{Nikon D800} 
+& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & 38.01 & 37.99 & \textbf{38.52}
+\\ 
+\cline{2-11} 
+\multirow{3}{*}{ISO = 1600}   
+& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & \textbf{40.36} & \textbf{40.36}
+\\ 
+\cline{2-11}    
+& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & 38.30 & \textbf{38.81}
+\\
+\hline
+\multirow{3}{*}{Nikon D800} 
+& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & \textbf{39.01} & 38.32
+\\ 
+\cline{2-11} 
+\multirow{3}{*}{ISO = 3200}   
+& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & \textbf{36.75} & \textbf{36.73}
+\\ 
+\cline{2-11}    
+& 32.91 & 32.98 & 32.96 & 38.54 & 40.05 & \textbf{40.59} & 36.91 & 36.76 & 39.06 & 38.29
+\\
+\hline
+\multirow{3}{*}{Nikon D800} 
+& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & 34.25 & 31.28 & 33.49 & \textbf{34.61} & 33.37
+\\ 
+\cline{2-11} 
+\multirow{3}{*}{ISO = 6400}   
+& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & \textbf{33.21} & \textbf{33.23}
+\\ 
+\cline{2-11}    
+& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & 33.22 & \textbf{33.29}
+\\
+\hline
+Average PSNR & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & 36.88 & \textbf{ 37.07}
+\\
+\hline
+Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & 0.9481 & \textbf{ 0.9501}
 \\
@@
 \centering
-\begin{minipage}[t]{0.2\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CSF_5dmark3_iso3200_3_real.png}}
@@
 }
-\caption{Denoised images of the old image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
 \label{fig3}
@@
 \subfigure{
-\begin{minipage}[t]{0.25\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
@@
 \end{minipage}
-\begin{minipage}[t]{0.25\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
@@
 }
-\caption{Denoised images of the old image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
 \label{fig4}
 \end{figure*}
-
-%\\
-%\hline
-%1 &    &    &     &     &    &      &     &     &   & 38.30  &  \textbf{ 40.13 }
-%\\
-%\hline
-%2 &    &    &     &     &    &      &     &     &   & 37.09  &  \textbf{ 36.99 }
-%\\
-%\hline
-%3 &    &    &     &     &    &      &     &     &   & 36.58  &  \textbf{ 36.92 }
-%\\
-%\hline
-%4 &    &    &     &     &    &      &     &     &   & 34.85  &  \textbf{ 35.11 }
-%\\
-%\hline
-%5 &    &    &     &     &    &      &     &     &   &  36.12 &  \textbf{ 36.50 }
-%\\
-%\hline
-%6 &    &    &     &     &    &      &     &     &   & 38.92  &  \textbf{ 38.74 }
-%\\
-%\hline
-%7 &    &    &     &     &    &      &     &     &   & 38.30  &  \textbf{ 38.30 }
-%\\
-%\hline
-%8 &    &    &     &     &    &      &     &     &   &  39.48 &  \textbf{ 40.26 }
-%\\
-%\hline
-%9 &    &    &     &     &    &      &     &     &   & 38.72  &  \textbf{ 38.68 }
-%\\
-%\hline
-%10 &    &    &     &     &    &      &     &     &   & 38.38  &  \textbf{ 38.35 }
-%\\
-%\hline
-%11 &    &    &     &     &    &      &     &     &   & 36.42  &  \textbf{ 36.77 }
-%\\
-%\hline
-%12 &    &    &     &     &    &      &     &     &   & 38.35  &  \textbf{ 38.41 }
-%\\
-%\hline
-%13 &    &    &     &     &    &      &     &     &   & 33.26  &  \textbf{ 33.61 }
-%\\
-%\hline
-%14 &    &    &     &     &    &      &     &     &   &   &  \textbf{ 33.40 }
-%\\
-%\hline
-%15 &    &    &     &     &    &      &     &     &   &   &  \textbf{ 33.47 }
 

### 2016-10-14 egpaper_for_review.tex
a

@@
 \centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (c) MLP \cite{mlp}\\ (34.22dB/0.9603) }
+{\footnotesize (d) MLP \cite{mlp}\\ (34.22dB/0.9603) }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (d) CSF \cite{csf}\\ (35.39dB/0.9677) }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (e) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
+{\footnotesize (e) CSF \cite{csf}\\ (35.39dB/0.9677) }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Noisy_5dmark3_iso3200_3_real.png}}
-{\footnotesize (a) Noisy Image \\ (33.83dB/0.9128)  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_5dmark3_iso3200_1_real.png}}
+{\footnotesize (a) Noisy Image \\ (37.00dB/0.9345) }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CBM3D_5dmark3_iso3200_3_real.png}}
-{\footnotesize (b) CBM3D \\ (33.84dB/0.9134)   }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
+{\footnotesize (b) CBM3D \\ (37.02dB/0.9351)}
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_MLP_5dmark3_iso3200_3_real.png}}
-{\footnotesize (c) MLP \\ (32.36dB/0.8993)  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_5dmark3_iso3200_1_real.png}}
+{\footnotesize (c) WNNM \\ (37.01dB/0.9347)}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_5dmark3_iso3200_1_real.png}}
+{\footnotesize (d) MLP \\ (33.90dB/0.9171) }
 \end{minipage}
@@
 \begin{minipage}[t]{0.195\textwidth}
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CSF_5dmark3_iso3200_3_real.png}}
-{\footnotesize (d) CSF \\ (32.62dB/0.9031)  }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_WNNM_5dmark3_iso3200_3_real.png}}
-{\footnotesize (e) WNNM \\ (33.86dB/0.9143)}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
+{\footnotesize (e) TRD \\ (36.18dB/0.9454)   }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NC_5dmark3_iso3200_3_real.png}}
-{\footnotesize (f) Noise Clinic \\ (35.54dB/0.9476)  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
+{\footnotesize (f) Noise Clinic \\ (38.76dB/0.9689) }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_NI_5dmark3_iso3200_3_real.png}}
-{\footnotesize (g) Neat Image \\ (34.77dB/0.9463)  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
+{\footnotesize (g) Neat Image \\ (37.68dB/0.9600) }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_CCNoise_5dmark3_iso3200_3.png}}
-{\footnotesize (h) CCNoise \\ (34.91dB/0.9478)  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
+{\footnotesize (h) CCNoise \\ (38.37dB/0.9678) }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Guided_5dmark3_iso3200_3_real.png}}
-{\footnotesize (i) Guided \\ (\textbf{37.01}dB/\textbf{0.9676})}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
+{\footnotesize (i) Guided \\ (\textbf{40.26}dB/\textbf{0.9800})}
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/br_Mean_5dmark3_iso3200_3_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_5dmark3_iso3200_1_real.png}}
 {\footnotesize (j) Mean Image}
@@
 }
-\caption{Denoised images of the image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the image "Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
 \label{fig3}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
-{\footnotesize (c) MLP }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
+{\footnotesize (c) WNNM    }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_dog.png}}
-{\footnotesize (d) CSF    }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
+{\footnotesize (d) MLP }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
-{\footnotesize (e) WNNM    }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_dog.png}}
+{\footnotesize (e) TRD }
 \end{minipage}

### 2016-10-14 egpaper_for_review.tex
a

@@
 \end{equation}
-We employ the patch group based Gaussian Mixture Model (PG-GMM) for NSS prior learning. The learning process is the same with that in \cite{pgpd}.
-
-With PG-GMM, we aim to learn a set of $K$ Gaussians $\{\mathcal{N}(\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})\}$ from $N$ training PGs $\{\mathbf{\overline{X}}_{n}\}$, while requiring that all the $M$ patches $\{\mathbf{\overline{x}}_{n,m}\}$  in PG $\mathbf{\overline{X}}_{n}$ belong to the same Gaussian component and assume that the patches in the PG are independently sampled.
+We employ the patch group based Gaussian Mixture Model (PG-GMM) for NSS prior learning.
+We aim to learn a set of $K$ Gaussians $\{\mathcal{N}(\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})\}$ from $N$ training PGs $\{\mathbf{\overline{X}}_{n}\}$, while requiring that all the $M$ patches $\{\mathbf{\overline{x}}_{n,m}\}$  in PG $\mathbf{\overline{X}}_{n}$ belong to the same Gaussian component and assume that the patches in the PG are independently sampled.
 Note that such an assumption is commonly used in patch based image modeling \cite{ksvd,lssc}.
@@
 \subsection{The Overall Algorithm}
+With the solution $\hat{\boldsymbol{\upalpha}}$ in (\ref{equ17}), the clean patch in a PG can be estimated as $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$.
+Then the clean image $\hat{\mathbf{x}}$ can be reconstructed by aggregating all the estimated PGs.
+In practice, we could perform the above denoising procedures for several iterations for better denoising outputs.
+In iteration $t$, we use the iterative regularization strategy \cite{osher2005iterative} to add back to the recovered image $\hat{\mathbf{x}}^{(t-1)}$ some estimation residual in iteration $t-1$.
+The standard deviation of noise in iteration $t$ is adjusted as $\sigma^{(t)} = \eta*\sqrt{\sigma^{2}-\|\mathbf{y}-\mathbf{y}^{(t-1)}\|_{2}^{2}}$, where $\eta$ is a constant.
+The proposed denoising algorithm is summarized in Algorithm 1 (Alg.
+1).
+
+In the proposed algorithm, there are $N$ PGs in an image and $M$ patches in each PG.
+Then the computational cost for Gaussian component selection is $O(p^{6}NMK)$.\ The cost for iterative regularization and noise estimation is negligible.
+The cost for closed-form weighted sparse coding is $O(p^{4}NM)$.
+Suppose that there are $T$ iterations, the overall complexity of our denoising algorithm is $O(p^{6}NMKT)$.
+
+\begin{table}
+\label{alg1}
+\begin{tabular}{l}
+\hline
+\textbf{Alg. 1}: Patch Group Prior based Denoising (PGPD)
+\\
+\hline
+\textbf{Input:} Noisy image $\mathbf{y}$, PG-GMM model
+\\
+1. Initialization: $\hat{\mathbf{x}}^{(0)}=\mathbf{y},\mathbf{y}^{(0)}=\mathbf{y}$;
+\\
+\textbf{for} $t = 1:IteNum$ \textbf{do}
+\\
+2. Iterative Regularization:
+\\
+\quad\quad\quad $\mathbf{y}^{(t)}=\hat{\mathbf{x}}^{(t-1)}+\delta(\mathbf{y}-\mathbf{y}^{(t-1)})$;
+\\
+3. Estimate the standard deviation of noise;
+\\
+\quad\textbf{for} each PG $\mathbf{Y}$ \textbf{do}
+\\
+4.\quad Calculate group mean $\boldsymbol{\upmu}_{y}$ and form PG $\mathbf{\overline{Y}}$;
+\\
+5.\quad Gaussian component selection via (\ref{equ9});
+\\
+6.\quad Denoising by Weighted Sparse Coding (\ref{equ15});
+\\
+7.\quad Recover each patch in this PG via $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$;
+\\
+\quad\textbf{end for}
+\\
+8. Aggregate the recovered PGs to form the recovered
+\\
+\quad image $\hat{\mathbf{x}}^{(t)}$;
+\\
+\textbf{end for}
+\\
+\textbf{Output:} The recovered image $\hat{\mathbf{x}}^{(IteNum)}$.\\
+\hline
+\end{tabular}
+\end{table}
 
@@
 \section{Experiments}
-In this section, we perform real image image denoising experiments on three standard datasets.
-The first dataset is real noisy images with mean images as ground truths provided by \cite{crosschannel2016}.
+In this section, we perform real image denoising experiments on three standard datasets.
+The first dataset is real noisy images with mean images as ground truths provided by \cite{crosschannel2016}, some samples are shown in Figure \ref{fig5}.
 The second dataset is provided by the website of Noise Clinic \cite{noiseclinic}.
@@
 The second and third dataset do not have ground truth images.
+\begin{figure}[t]
+\centering
+\subfigure{
+\begin{minipage}{0.15\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Canon_EOS_5D_Mark3_ISO_3200_C3.png}
+\end{minipage}
+\begin{minipage}{0.15\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Nikon_D600_ISO_3200_C1.png}
+\end{minipage}
+\begin{minipage}{0.15\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Nikon_D800_ISO_1600_B2.png}
+\end{minipage}
+}\vspace{-0.14in}
+\subfigure{
+\begin{minipage}{0.15\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Nikon_D800_ISO_3200_A1.png}
+\end{minipage}
+\begin{minipage}{0.15\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Nikon_D800_ISO_3200_A5.png}
+\end{minipage}
+\begin{minipage}{0.15\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Nikon_D800_ISO_6400_B1.png}
+\end{minipage}
+}
+\caption{Some testing images in the dataset \cite{crosschannel2016}.}
+\label{fig5}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\subfigure{
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_52.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_66.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_73.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}
+\end{minipage}
+}\vspace{-0.14in}
+\subfigure{
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B2_80.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_1600_B3_82.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_21.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A4_51.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_6400_B3_95.png}
+\end{minipage}
+\begin{minipage}{0.055\textwidth}
+\includegraphics[width=1\textwidth]{images/resize_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}
+\end{minipage}
+}
+\caption{Some cropped images of the dataset \cite{crosschannel2016}.}
+\label{fig5}
+\end{figure}
 
@@
 We also compare the three methods on visual quality in Figure \ref{fig2}.
+Compare the denoised images listed in Figure \ref{fig2} and Figure \ref{fig2}, we can see that the Offline method is better at edges, smooth regions while the Online method is good at complex textures.
+The reason is two folds.
+Firstly, the Offline method is learned on clean images and hence is better at representing edges, structuals, and smooth area.
+The online method is influenced by the noise and hence some noise cannot be removed.
+Secondly, the Online method is better at recovering complex area sicne they could learn adaptive dictionaries for the specific area.
+The Offline method cannot recover the complex area since they did not learn the similar structures from the external natural clean images.
 
@@
 \subsection{Comparison With other Competing Methods}
-We compare with previous state-of-the-art Gaussian noise removal methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and the recently proposed TRD \cite{chencvpr2015}.
+We compare with previous state-of-the-art Gaussian noise removal methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and the recently proposed TRD \cite{chen2015learning}.
 We also compare with three competing real image denoising methods such as Noise Clinic, Neat Image, and the CCNoise method proposed recently.
@@
 \footnote{To compare with CCNoise, we first transform the denoised images into double format.}
-
-\subsection{Real Image Denoising}
 
@@
 \cline{2-11}    
-& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & 40.51 & 38.68 & \textbf{39.28} & 41.15 & 38.73
+& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & 40.51 & 38.68 & 39.28 & \textbf{41.15} & 38.73
 \\

### 2016-10-14 egpaper_for_review.tex
a

@@
 The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and $\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}$ is the group mean subtracted patch vector.
-The PG is defined as
-\begin{equation}\label{equ1}
-\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}\}, m=1,...,M
-\end{equation}, and it represent the external NSS prior on color images. In Figure \ref{fig2}
-
-Assume we have extracted $N$ PGs from a given set of natural images, and the $n$-th PG is defined as
-\begin{equation}\label{equ2}
-\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N.
-\end{equation}
+The PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}\}, m=1,...,M$, and it represent the external NSS prior on color images.
+Assume we have extracted $N$ PGs from a given set of natural images, and the $n$-th PG is defined as $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.
 We employ the patch group based Gaussian Mixture Model (PG-GMM) for NSS prior learning.
@@
 Then, the likelihood of $\{\mathbf{\overline{X}}_{n}\}$ can be calculated as
-\begin{equation}\label{equ3}
+\begin{equation}\label{equ1}
 P(\mathbf{\overline{X}}_{n})  = \sum\nolimits_{k=1}^{K}\pi_{k}\prod\nolimits_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k}).
@@
 By assuming that all the PGs are independently sampled, the overall objective log-likelihood function is
-\begin{equation}\label{equ4}
+\begin{equation}\label{equ2}
 \begin{split}
@@
 The selection can be done by checking the posterior probability that $\mathbf{\overline{Y}}$ belongs to the $k$th Gaussian component:
-\begin{equation}\label{equ8}
+\begin{equation}\label{equ3}
 P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})}.
@@
 In PG-GMM, the PGs actually represent the variations of the similar patches in a group, and these variations are assigned to the same Gaussian distribution.
-By singular value decomposition (SVD), $\mathbf{\Sigma}$ can be factorized as
-\begin{equation}\label{equ10}
-\mathbf{\Sigma} = \mathbf{D}\mathbf{\Lambda}\mathbf{D}^{T},
-\end{equation}
-where $\mathbf{D}$ is an orthonormal matrix composed by the eigenvectors of $\mathbf{\Sigma}$ and $\mathbf{\Lambda}$ is the diagonal matrix of eigenvalues.
+By singular value decomposition (SVD), $\mathbf{\Sigma}$ can be factorized as $\mathbf{\Sigma} = \mathbf{D}\mathbf{\Lambda}\mathbf{D}^{T}$, where $\mathbf{D}$ is an orthonormal matrix composed by the eigenvectors of $\mathbf{\Sigma}$ and $\mathbf{\Lambda}$ is the diagonal matrix of eigenvalues.
 With PG-GMM, the eigenvectors  in $\mathbf{D}$ capture the statistical structures of NSS variations in natural images, while the eigenvalues in $\mathbf{\Lambda}$ represent the significance of these eigenvectors.
@@
 
-\begin{equation}\label{equ15}
+\begin{equation}\label{equ5}
 \min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{\overline{y}}_{m}-\mathbf{D}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{p^{2}}\frac{c}{\mathbf{\lambda}_{i}}|\boldsymbol{\upalpha}_{i}|.
@@
 By comparing (\ref{equ15}) with (\ref{equ11}), we can see that the $i$th entry of the weighting vector $\mathbf{w}$ should be
-\begin{equation}\label{equ16}
+\begin{equation}\label{equ6}
 \setlength{\abovedisplayskip}{3pt}
@@
 Since the dictionary $\mathbf{D}$ is orthonormal, it is not difficult to find out that (\ref{equ11}) has a closed-form solution (detailed derivation can be found in the supplementary material):
-\begin{equation}\label{equ17}
+\begin{equation}\label{equ7}
 \setlength{\abovedisplayskip}{3pt}

### 2016-10-15 egpaper_for_review.tex
a

@@
 
+\subsection{Discussion on Parameter $\lambda$}
+The proposed method only has a key parameter, namely the regularization paramters $\lambda$.
+To demonstrate that the proposed method is robust to the variance of $\lambda$, we vary the parameter $\lambda$ across a wide range and obtain the PSNR and SSIM results as a function of the parameter $\lambda$.
+The results is shown in Figure \ref{fig10}, from which we can see that the proposed method can achieve a PSNR (SSIM) over 38.2dB (0.9620) when $\lambda$ varies from $1e-3$ to $4e-4$.
+This shows that the proposed method is indeed robust to the chosen of the paramter $\lambda$.
+\begin{figure}
+\includegraphics[width=1\linewidth]{images/param.png}
+\caption{The PSNR/SSIM results as a function of the parameter $\lambda$.}
+\label{fig10}
+\end{figure}
+
 \section{Conclusion and Future Work}

### 2016-10-15 egpaper_for_review.tex
nodify

@@
 \end{equation} 
-We maximize the above objective function for PG-GMM learning.
-Finally, we obtain the GMM model with three sets of parameters including mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}=\mathbf{0}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.
-Noted that in PGPD \cite{pgpd}, the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
+We maximize the above objective function for PG-GMM learning and  finally obtain the GMM model with learned parameters including mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}=\mathbf{0}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.
+Noted that the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
 
-\subsection{External PG Prior Guided Internal Subspace Learning}
-For each $\mathbf{\overline{Y}}$, we select the most suitable Gaussian component to it from the trained PG-GMM.
-Since the noise on real images are small when compared to the signals and the noise on real images are dependent on the signals, the covariance matrix of the $k$th component is still $\mathbf{\Sigma}_{k}$.
+\subsection{External Prior Guided Internal Subspace Learning}
+Given a rael noisy image, we extract noisy PGs from it and save the mean vectors of each PG for recovering.
+The mean substracted PG is defined as $\mathbf{\overline{Y}}$.
+To project this PG into a most adaptive subspace, we select the most suitable Gaussian component to it from the PG-GMM trained in previous section.
 The selection can be done by checking the posterior probability that $\mathbf{\overline{Y}}$ belongs to the $k$th Gaussian component:
@@
 \end{equation}
-Finally, the component with the highest probability $\ln P(k|\mathbf{\overline{Y}})$ is selected to process $\mathbf{\overline{Y}}$.
+Since the noise on real images are mostly small when compared to the signals, the covariance matrix of the $k$th component is still $\mathbf{\Sigma}_{k}$.
+Finally, the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}})$ is selected as the most suitable subspace for $\mathbf{\overline{Y}}$.
 
-Suppose that the $k$th Gaussian component is selected for PG $\mathbf{\overline{Y}}$.
-For notation simplicity, we remove the subscript $k$ and denote by $\mathbf{\Sigma}$ the covariance matrix of this component.
-In PG-GMM, the PGs actually represent the variations of the similar patches in a group, and these variations are assigned to the same Gaussian distribution.
-By singular value decomposition (SVD), $\mathbf{\Sigma}$ can be factorized as $\mathbf{\Sigma} = \mathbf{D}\mathbf{\Lambda}\mathbf{D}^{T}$, where $\mathbf{D}$ is an orthonormal matrix composed by the eigenvectors of $\mathbf{\Sigma}$ and $\mathbf{\Lambda}$ is the diagonal matrix of eigenvalues.
-With PG-GMM, the eigenvectors  in $\mathbf{D}$ capture the statistical structures of NSS variations in natural images, while the eigenvalues in $\mathbf{\Lambda}$ represent the significance of these eigenvectors.
-Fig.\ 4 shows the eigenvectors for 3 Gaussian components.
-It can be seen that these eigenvectors encode the possible variations of the PGs.
-For one Gaussian component, the first eigenvector represents its largest variation, while the last eigenvector represents its smallest variation.
-For different Gaussian components, we can see that their eigenvectors (with the same index) are very different.
-Hence, $\mathbf{D}$ can be used to represent the structural variations of the PGs in that component.
-
+Though each PG has been projected into its most suitable subspace, the pre-learned subspace is still too general to represent the noisy PG extracted from the real noisy image.
+That is, the noisy PGs projected into one cluster can still constisted a subspace which is of lower dimensions than the subspace pre-learned from the external PGs.
+This can be demonstrated by compare the distribution of external PGs and internal PGs in the same clusters.
+We randomly select one cluster, and collect the celan PGs extracted from external dataset (Kodak 24 images) and the niosy PGs from the testing image.
+Since the original PGs are of $3p^{2}$ dimensions, we apply PCA to project the PGs into 2 dimensions for better visualization.
+The results is shown in Figure \ref{fig}, from which we can see clearly that the projected PGs are mainly in a smaller region of the external PGs, which proves that the internal PGs are only consisted a subspace in a lower dimension than the PGs collected from external subspace.
+To better and adaptively charactering the internal PGs from the testing image, we need learn a more specific dictionary for noisy PGs assigned into each cluster.
+For notation simplicity, we ignore the index of subspace $k$.
+The internal PGs $\mathbf{Y}$ form a subspace which can be obtained by singular value decomposition (SVD),
+\begin{equation}\label{equ4}
+\mathbf{Y}=\mathbf{U}\mathbf{S}\mathbf{V}'
+\end{equation}
+The singular vectors capture the statistical structures of NSS variations in natural images, while the singular values in $\mathbf{S}$ represent the significance of these singular vectors.
+Fig.\ 4 shows the singular vectors for one Gaussian component.
+We employ the $\mathbf{U}$ as the adaptive dictioanry to represent the structural variations of the PGs in that component.
 \begin{equation}\label{equ5}
-\min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{\overline{y}}_{m}-\mathbf{D}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{p^{2}}\frac{c}{\mathbf{\lambda}_{i}}|\boldsymbol{\upalpha}_{i}|.
+\min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{\overline{y}}_{m}-\mathbf{U}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{3p^{2}}\lambda_{i}|\boldsymbol{\upalpha}_{i}|.
 \end{equation}
-By comparing (\ref{equ15}) with (\ref{equ11}), we can see that the $i$th entry of the weighting vector $\mathbf{w}$ should be
+The $i$th entry of the regularization parameter $\lambda_{i}$ 
 \begin{equation}\label{equ6}
-\setlength{\abovedisplayskip}{3pt}
-\setlength{\belowdisplayskip}{3pt}
-\mathbf{w}_{i} = c/(\mathbf{\lambda}_{i}+\varepsilon),
+\lambda_{i} = \frac{\lambda}{\mathbf{S}_{i}+\varepsilon},
 \end{equation}
 where $\varepsilon$ is a small positive number to avoid dividing by zero.
-With $\mathbf{w}$ determined by (\ref{equ16}), let's see what the solution of (\ref{equ11}) should be.
-Since the dictionary $\mathbf{D}$ is orthonormal, it is not difficult to find out that (\ref{equ11}) has a closed-form solution (detailed derivation can be found in the supplementary material):
+Since the dictionary $\mathbf{U}$ is orthonormal, it is not difficult to find out that (\ref{equ4}) has a closed-form solution (detailed derivation can be found in the supplementary material):
 \begin{equation}\label{equ7}
@@
 \setlength{\belowdisplayskip}{4pt}
-\hat{\boldsymbol{\upalpha}}= \text{sgn}(\mathbf{D^{T}\overline{y}}_{m})\odot \text{max}(|\mathbf{D^{T}\overline{y}}_{m}|-\mathbf{w}/2,0),
+\hat{\boldsymbol{\upalpha}}= \text{sgn}(\mathbf{U^{T}\overline{y}}_{m})\odot \text{max}(|\mathbf{U^{T}\overline{y}}_{m}|-\mathbf{\Lambda},\mathbf{0}),
 \end{equation}
-where $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication, and $|\mathbf{D^{T}\overline{y}}_{m}|$ is the absolute value of each entry of vector $|\mathbf{D^{T}\overline{y}}_{m}|$.
+where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication, and $|\mathbf{U^{T}\overline{y}}_{m}|$ is the absolute value of each entry of vector $|\mathbf{U^{T}\overline{y}}_{m}|$.
 The closed-form solution makes our weighted sparse coding process very efficient.
@@
 
-\subsection{What does External Data help the Internal Subspace Learning?}
+\subsection{What does External Prior help the Internal Subspace Learning?}
 The external data can help the internal learning in two ways.
@@
 
-\subsection{The Internal PGs Spaces Are Subspaces of Corresponding External PG Spaces}
+\subsection{The Internal Spaces Are Subspaces of External PG Spaces}
 In this subsection, we compare the distribution of external PGs extracted from clean natural images and real noisy images.
@@
 \subsection{The Overall Algorithm}
-With the solution $\hat{\boldsymbol{\upalpha}}$ in (\ref{equ17}), the clean patch in a PG can be estimated as $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$.
+With the solution $\hat{\boldsymbol{\upalpha}}$ in (\ref{equ7}), the clean patch in a PG can be estimated as $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$.
 Then the clean image $\hat{\mathbf{x}}$ can be reconstructed by aggregating all the estimated PGs.
@@
 In iteration $t$, we use the iterative regularization strategy \cite{osher2005iterative} to add back to the recovered image $\hat{\mathbf{x}}^{(t-1)}$ some estimation residual in iteration $t-1$.
-The standard deviation of noise in iteration $t$ is adjusted as $\sigma^{(t)} = \eta*\sqrt{\sigma^{2}-\|\mathbf{y}-\mathbf{y}^{(t-1)}\|_{2}^{2}}$, where $\eta$ is a constant.
 The proposed denoising algorithm is summarized in Algorithm 1 (Alg.
 1).
-
-In the proposed algorithm, there are $N$ PGs in an image and $M$ patches in each PG.
-Then the computational cost for Gaussian component selection is $O(p^{6}NMK)$.\ The cost for iterative regularization and noise estimation is negligible.
-The cost for closed-form weighted sparse coding is $O(p^{4}NM)$.
-Suppose that there are $T$ iterations, the overall complexity of our denoising algorithm is $O(p^{6}NMKT)$.
 
@@
 \hline
-\textbf{Alg. 1}: Patch Group Prior based Denoising (PGPD)
+\textbf{Alg. 1}: External Guided Internal Subspace Denoising
 \\
@@
 \\
-5.\quad Gaussian component selection via (\ref{equ9});
-\\
-6.\quad Denoising by Weighted Sparse Coding (\ref{equ15});
-\\
-7.\quad Recover each patch in this PG via $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$;
+5.\quad Gaussian component selection via (\ref{equ3});
 \\
@@
 \\
-8. Aggregate the recovered PGs to form the recovered
+\quad\textbf{for} each Internal Subspace \textbf{do}
 \\
-\quad image $\hat{\mathbf{x}}^{(t)}$;
+6.\quad Internal Subspace Learning by (\ref{equ4});
+\\
+7.\quad Recover each patch in all PGs via $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$;
+\\
+\quad\textbf{end for}
+\\
+8. Aggregate the recovered PGs of all subspaces to form
+\\
+\quad the recovered image $\hat{\mathbf{x}}^{(t)}$;
 \\

### 2016-10-16 egpaper_for_review.tex
a

@@
 \begin{equation}\label{equ4}
-\mathbf{Y}=\mathbf{U}\mathbf{S}\mathbf{V}'
+\mathbf{Y}=\mathbf{U}\mathbf{S}\mathbf{V}^{T}
 \end{equation}
@@
 Fig.\ 4 shows the singular vectors for one Gaussian component.
+
+\subsection{What does External Prior help the Internal Subspace Learning?}
+Until now, we have divided the noisy PGs into multiple internal subspaces.
+Here we take a deep analysis on how the external NSS prior guide the subspace learning of internal PGs.
+The help are at least threefold.
+Firstly, through MAP in (\ref{equ3}), the external prior guides the noisy PGs to be clustered into the correct subspaces.
+If we cluster the noisy PGs in an automatical way, the subspaces we learned will be highly degraded by the signal dependent noise.
+Secondly, the guidance of external prior for internal clustering is more efficient than directly clustering the internal noisy PGs.
+It only needs to calculate the MAP probability via the equation (\ref{equ3}) while the internal clustering via GMM is time-consuming on EM algorithm \cite{em}.
+Thirdly, due to the correct guidance of external prior, the structual decomposition via SVD of each subspace is more adaptive.
+This will bring better denoising performance than the methods only using the external information.
+
+\subsection{Discussion on Internal Subspace Structure}
+The Internal PGs are in fact lying in the subspaces of external PG Spaces.
+To defend this argument, we compare the distribution of external PGs extracted from clean natural images and real noisy images.
+For better illumination, we randomly selected a cluster and project the original clean PGs $\mathbf{X}$ onto a 2-D plane.
+This could be done via $\mathbf{Xp}=\mathbf{U(:.1:2)}^{T}\mathbf{X}$, where $\mathbf{U}$ is the singular vector matrix of that cluster.
+The noisy PGs $\mathbf{Y}$ assigned in this cluster is also projected into 2-D via $\mathbf{Yp}=\mathbf{U(:.1:2)}^{T}\mathbf{Y}$.
+The Figure \ref{} reflects the distribution on the 2-D plane of the projected clean PGs from external natural images and the projected noisy PGs from internal image.
+We can see that the internal noisy PGs are indeed lying in a subspace of the external PGs.
+Hence, if we directly use the external prior learned from clean PGs, the learned subspaces would be too generative to be suitable for the testing data.
+
+Through SVD, the PGs in each internal subspace can be divided into singular vectors and singular values.
+The singular vectors are the basis of the corresponding subspace while the singular values reflect the importance of these basis.
+The basis can be used as dictionary to code the noisy PGs.
+And the sigular values are adaptive parameters for internal noisy PGs.
+We can compare the singular values of one internal subspace and the corresponding space of external PGs.
+The result is shown in Figure \ref{}.
+From which we can see that the noisy subspace often have higher values than external space consisted of clean PGs.
+This gap is clearly made of the noise and can be used for image denoising in a natural way.
+
+\section{The Denoising Algorithm}
 We employ the $\mathbf{U}$ as the adaptive dictioanry to represent the structural variations of the PGs in that component.
@@
 The closed-form solution makes our weighted sparse coding process very efficient.
-\vspace{-0.05in}
-
-\subsection{What does External Prior help the Internal Subspace Learning?}
-The external data can help the internal learning in two ways.
-On one hand, it can guide the noisy image patches to be divided into correct subspaces through clustering.
-If we cluster the noisy patches in an automatical way, just like the PLE \cite{ple} did, the signal dependent noise would be hardly removed.
-With the help of clean external data, the noisy patches can be divided into correct subspaces.
-Besides, external data guided internal clustering is much more efficient than directly clustering the noisy data due to the time consuming fitting procedure.
-On the other hand, due to the correct division of internal noisy data, the dictionary and paranters for subspace learning could be more adaptive to the testing real noisy image.
-Hence, it would achieve better denoising performance than the methods only using the external information.
-
-\subsection{The Internal Spaces Are Subspaces of External PG Spaces}
-In this subsection, we compare the distribution of external PGs extracted from clean natural images and real noisy images.
-For better illumination, we randomly selected a cluster and project the original clean PGs onto a 2-D plane.
-Plot a Figure to demonstrate the data distributed in external space and the assigned internal subspace.
-The internal subspace is only a subspace of the external space.
-Hence, if we use the external data to perform denoising, the performance would be limited due to the dependence of noise on signal.
-If we combine the external and internal data for subspace learning, the learned subspace would be too generative and would therefore not specifically suitable for the testing data.
-
-\section{The Enhanced Algorithm}
 
@@
 The other way is to estimate the noise level of the current image and terminate the iterations when the noise level is lower than a preset threshold.
-We employ the second way and set the threshold as 0.0001 in our experiments.
+We employ the second way and set the threshold as 0.002 in our experiments.
 In fact, most of our testing images will be denoised well in one iteration.
 
-\subsection{Efficient Model Selection by Gating Network}
-In the Gaussian component selection procedure, if we employ the full posterior estimation, the speed is not fast. Our algorithm can be speeded up by introducing the Gating network model.
+%\subsection{Efficient Model Selection by Gating Network}
+%In the Gaussian component selection procedure, if we employ the full posterior estimation, the speed is not fast. Our algorithm can be speeded up by introducing the Gating network model.
 
@@
 \hline
-PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 & 37.75 &  36.53  &  37.57  &  38.19   & 38.07 &  \textbf{ 38.51}
+PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 & 37.75 &  36.53  &  37.57  &  38.19   & 38.07 &  \textbf{ 38.55}
 \\
 \hline
-SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  &  0.9663   & 0.9625 &   \textbf{0.9674}
+SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  &  0.9663   & 0.9625 &   \textbf{0.9675}
 \\
@@
 \multirow{3}{*}{\small{Canon 5D Mark III}} 
-& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & 38.76 & 38.37 & \textbf{40.32}
+& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & 38.76 & 38.37 & \textbf{40.41}
 \\ 
@@
 \multirow{3}{*}{ISO = 3200}   
-& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & 35.69 & 35.37 & \textbf{37.12}
+& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & 35.69 & 35.37 & \textbf{37.14}
 \\ 
 \cline{2-11}    
-& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & 35.54 & 34.91 & \textbf{37.09}  
+& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & 35.54 & 34.91 & \textbf{37.11}  
 \\
@@
 \multirow{3}{*}{Nikon D600} 
-& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & \textbf{35.57} & 34.98 & 35.23
+& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & \textbf{35.57} & 34.98 & 35.25
 \\ 
@@
 \multirow{3}{*}{ISO = 3200}   
-& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & \textbf{36.70} & 35.95 & 36.57
+& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & \textbf{36.70} & 35.95 & 36.60
 \\ 
 \cline{2-11}    
-& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & 40.51 & 38.68 & 39.28 & \textbf{41.15} & 38.73
+& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & 40.51 & 38.68 & 39.28 & \textbf{41.15} & 38.78
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & 38.01 & 37.99 & \textbf{38.52}
+& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & 38.01 & 37.99 & \textbf{38.59}
 \\ 
@@
 \multirow{3}{*}{ISO = 1600}   
-& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & \textbf{40.36} & \textbf{40.36}
+& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & 40.36 & \textbf{40.44}
 \\ 
 \cline{2-11}    
-& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & 38.30 & \textbf{38.81}
+& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & 38.30 & \textbf{38.85}
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & \textbf{39.01} & 38.32
+& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & \textbf{39.01} & 38.34
 \\ 
@@
 \multirow{3}{*}{ISO = 3200}   
-& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & \textbf{36.75} & \textbf{36.73}
+& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & \textbf{36.75} & \textbf{36.74}
 \\ 
@@
 \multirow{3}{*}{ISO = 6400}   
-& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & \textbf{33.21} & \textbf{33.23}
+& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & \textbf{33.21} & \textbf{33.21}
 \\ 
 \cline{2-11}    
-& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & 33.22 & \textbf{33.29}
+& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & 33.22 & \textbf{33.27}
 \\
 \hline
-Average PSNR & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & 36.88 & \textbf{ 37.07}
+Average PSNR & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & 36.88 & \textbf{ 37.09}
 \\
 \hline
-Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & 0.9481 & \textbf{ 0.9501}
+Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & 0.9481 & \textbf{ 0.9502}
 \\

### 2016-10-16 egpaper_for_review.tex
a

@@
 \section{The Denoising Algorithm}
+\subsection{Adaptive Sparse Coding}
 We employ the $\mathbf{U}$ as the adaptive dictioanry to represent the structural variations of the PGs in that component.
@@
 \begin{equation}\label{equ6}
-\lambda_{i} = \frac{\lambda}{\mathbf{S}_{i}+\varepsilon},
+\lambda_{i} = \lambda/(\mathbf{S}_{i}+\varepsilon),
 \end{equation}
@@
 In the external prior guided learning stage, there is no parameters.
-In the denoising stage, there are one paramters, i.e., the $\lambda$ which is used to regularize the sparse term.
+In the denoising stage, the paramter $\lambda = 0.002$ is used to regularize the sparse term.
 
@@
 To demonstrate that the proposed method is robust to the variance of $\lambda$, we vary the parameter $\lambda$ across a wide range and obtain the PSNR and SSIM results as a function of the parameter $\lambda$.
-The results is shown in Figure \ref{fig10}, from which we can see that the proposed method can achieve a PSNR (SSIM) over 38.2dB (0.9620) when $\lambda$ varies from $1e-3$ to $4e-4$.
+The results is shown in Figure \ref{fig10}, from which we can see that the proposed method can achieve a PSNR (SSIM) over 38.5dB (0.9660) when $\lambda$ varies from $0.0015$ to $0.0025$.
 This shows that the proposed method is indeed robust to the chosen of the paramter $\lambda$.

### 2016-10-16 egpaper_for_review.tex
aa

@@
 \usepackage{multirow}
+\usepackage{color}
 
@@
 \ifcvprfinal\pagestyle{empty}\fi
+
 \begin{document}
@@
 For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN).
-However, the images captured by CMOS or CCD cameras will undertake an in-camera imaging pipeline.
-The in-camera imaging pipeline includes mainly image demosaicing, white balance and color space transform, gamut mapping, tone mapping, and JPEG comression \cite{NewInCamera,crosschannel2016}.
+However, in real world, the noise in real images are much more complex than than Gaussian.
+The cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc.
+These conditions would produce noise as a by-product.
+Besides, the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016} would also change the noise distribution.
 Therefore, the noise in real images are much more complex than Gaussian, and depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc).
@@
 This has been shown in Figure \ref{fig1}.
-In this paper, wour goal is to make use of external information to guide the subspace learning of internal PGs for image denoising task.
+In this paper, our goal is to make use of external information to guide the subspace learning of internal PGs for image denoising task.
 
@@
 The clean image is recovered from the noisy image by the proposed Low Rank MoG filter (LR-MoG).
-However, noise level estimation is already a challenging problem and denoising methods are quite sensitive to this parameter.
-Moreover, these methods are based on shrinkage models that are too simple to reflect reality, which results in over-smoothing of important structures such as small-scale text and textures.
+In this paper, we proposed a noval denoising method achieving much better performance than previous real denoising methods.
 
@@
 
-\subsection{Parameters Setting}
-The proposed method contains the PG prior learning stage, the external prior guided internal subspace learning stage, and the denoising stage.
-In the learning stage, similar to the PGPD, there are four parameters, $p$, $M$, $W$, and $K$.
-We set $p=6$ and hence the patch size is $6\times 6 \times 3$.
-The winodw size for searching PGs is $W = 31$.
-The number of similar patches is $N=10$, the number of cluters is set as $K = 33$.
-In the external prior guided learning stage, there is no parameters.
+\subsection{Implementation Details}
+Our proposed method contains two stages, the external prior guided internal subspace learning stage and the adaptive denoising stage.
+In the learning stage, there are 4 parameters: the patch size $p$, the number of patches in a PG $M$, the window size $W$ for PG searching and the number of clusters $K$.
+We set $p = 6$ (hence the patch size is $6\times 6 \times 3$), $M=10$, $W = 31$, $K=32$.
+We extracted about 3.6 million PGs from the Kodak PhotoCD Dataset, which includes 24 high quality color images, to train the external prior via PG-GMM.
 In the denoising stage, the paramter $\lambda = 0.002$ is used to regularize the sparse term.
+The $\delta$ in iterative regularization is set as $\delta = 0.09$.
 
@@
 The Offline method cannot recover the complex area since they did not learn the similar structures from the external natural clean images.
+
+\begin{table}\label{tab1}
+\caption{Average PSNR(dB)/SSIM results of external, internal, and guided methods on 60 cropped real noisy images in \cite{crosschannel2016}.}
+\label{tab1}
+\begin{center}
+\renewcommand\arraystretch{1}
+\begin{tabular}{|c||c|c|c|c|}
+\hline
+ & \textbf{Noisy} &\textbf{Offline} &\textbf{Online} &\textbf{Guided}  
+\\
+\hline
+PSNR & 34.51 & 38.19 & 38.07 & \textbf{38.55} 
+\\
+\hline
+SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9675}
+\\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
 
@@
 The first dataset contains 17 images of size over $7000\times5000$.
-Since this dataset contains recurrent contents across different images, we crop 60 small images of size $500\times500$ from these 17 images in \cite{crosschannel2016}.
+Since this dataset contains repetitive contents across different images, we crop 60 small images of size $500\times500$ from these 17 images in \cite{crosschannel2016}.
 
-The PSNR and SSIM resluts are listed in table \ref{tab1}.
+The PSNR and SSIM resluts are listed in Table \ref{tab1}.
+The number in red color and blue color means the best and second best results, respectively.
+From the Table \ref{tab1}, we can see that the external based method can already surpass largely the previous denoising methods.
+The improvement on PSNR over the second best method, i.e., TRD, is 0.44dB.
+The
 \begin{table*}\label{tab1}
@@
 \renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
 \hline
- & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
+ & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Guided}  &\textbf{Guided2} 
 \\
 \hline
-PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 & 37.75 &  36.53  &  37.57  &  38.19   & 38.07 &  \textbf{ 38.55}
+PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.55} & \color{red}{ 38.80}
 \\
 \hline
-SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  &  0.9663   & 0.9625 &   \textbf{0.9675}
+SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9675} & \color{red}{0.9694}
 \\
@@
 \hline
-Camera Settings & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Guided} 
+Camera Settings & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Guided2} 
 \\
@@
 \multirow{3}{*}{\small{Canon 5D Mark III}} 
-& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & 38.76 & 38.37 & \textbf{40.41}
+& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & \color{blue}{38.76} & 38.37 & \color{red}{40.44}
 \\ 
@@
 \multirow{3}{*}{ISO = 3200}   
-& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & 35.69 & 35.37 & \textbf{37.14}
+& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & \color{blue}{35.69} & 35.37 & \color{red}{37.16}
 \\ 
 \cline{2-11}    
-& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & 35.54 & 34.91 & \textbf{37.11}  
+& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & \color{blue}{35.54} & 34.91 & \color{red}{37.06}  
 \\
@@
 \multirow{3}{*}{Nikon D600} 
-& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & \textbf{35.57} & 34.98 & 35.25
+& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & \color{red}{35.57} & 34.98 & \color{blue}{35.28}
 \\ 
@@
 \multirow{3}{*}{ISO = 3200}   
-& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & \textbf{36.70} & 35.95 & 36.60
+& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & \color{red}{36.70} & 35.95 & \color{blue}{36.62}
 \\ 
 \cline{2-11}    
-& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & 40.51 & 38.68 & 39.28 & \textbf{41.15} & 38.78
+& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & \color{blue}{40.51} & 38.68 & 39.28 & \color{red}{41.15} & 39.05
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & 38.01 & 37.99 & \textbf{38.59}
+& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & \color{blue}{38.01} & 37.99 & \color{red}{38.67}
 \\ 
@@
 \multirow{3}{*}{ISO = 1600}   
-& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & 40.36 & \textbf{40.44}
+& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & \color{blue}{40.36} & \color{red}{40.81}
 \\ 
 \cline{2-11}    
-& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & 38.30 & \textbf{38.85}
+& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & \color{blue}{38.30} & \color{red}{38.77}
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & \textbf{39.01} & 38.34
+& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & \color{red}{39.01} & \color{blue}{38.57}
 \\ 
@@
 \multirow{3}{*}{ISO = 3200}   
-& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & \textbf{36.75} & \textbf{36.74}
+& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & \color{blue}{36.75} & \color{red}{36.82}
 \\ 
 \cline{2-11}    
-& 32.91 & 32.98 & 32.96 & 38.54 & 40.05 & \textbf{40.59} & 36.91 & 36.76 & 39.06 & 38.29
+& 32.91 & 32.98 & 32.96 & 38.54 & \color{blue}{40.05} & \color{red}{40.59} & 36.91 & 36.76 & 39.06 & 38.68
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & 34.25 & 31.28 & 33.49 & \textbf{34.61} & 33.37
+& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & \color{blue}{34.25} & 31.28 & 33.49 & \color{red}{34.61} & 33.48
 \\ 
@@
 \multirow{3}{*}{ISO = 6400}   
-& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & \textbf{33.21} & \textbf{33.21}
+& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & \color{blue}{33.21} & \color{red}{33.29}
 \\ 
 \cline{2-11}    
-& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & 33.22 & \textbf{33.27}
+& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & \color{blue}{33.22} & \color{red}{33.48}
 \\
 \hline
-Average PSNR & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & 36.88 & \textbf{ 37.09}
+Average PSNR & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & \color{blue}{36.88} & \color{red}{ 37.21}
 \\
 \hline
-Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & 0.9481 & \textbf{ 0.9502}
+Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & \color{blue}{0.9481} & \color{red}{ 0.9506}
 \\

### 2016-10-17 egpaper_for_review.tex
a

@@
 
-\subsection{Iterative Regularization}
-Perfoming image denoising in one iteration is not enough for real noise since the noise is signal dependent.
-The removed noise in one iteration is largely dependent on the signal.
-Therefore, it is essential to add back some residuals removed in this iteration for the denoising of the next iteration.
+\subsection{Fast Patch Group Searching by Integral Image}
+The searching of patch groups in images is inefficient if we search non-local similar patches to each local patch.
+To speed up the searching process and make our proposed method faster, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching.
+The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size.
+That is to say, we do not need do distance measure for each patch.
+It was first proposed under the name of summed area table\cite{viola2004robust}
 
@@
 \hline
-PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.55} & \color{red}{ 38.80}
+PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.68} & \color{red}{ 38.89}
 \\
 \hline
-SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9675} & \color{red}{0.9694}
+SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9676} & \color{red}{0.9704}
 \\

### 2016-10-20 egpaper_for_review.tex
a

@@
 \subsection{Adaptive Sparse Coding}
-We employ the $\mathbf{U}$ as the adaptive dictioanry to represent the structural variations of the PGs in that component.
+To remove the real noise, we employ the sparse coding framework.
+And in order to be adaptive to the input image, we employ the internal learned $\mathbf{U}$ of each cluster as an adaptive dictioanry to represent the structural variations of the PGs in that cluster.
+The \emph{mutual incoherence} $\mu(\mathbf{U})$ \cite{donoho2003optimally}, which is difined as
+\begin{equation}
+\mu(\mathbf{U})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}}
+\end{equation},
+is a measure of quality of dictionary. Since the $\mathbf{U}$ is orthonormal, its \emph{mutual incoherence} is naturally $0$ and therefore better than other redundant dictionaries.
+
 \begin{equation}\label{equ5}
@@
 \\
-2. Iterative Regularization:
-\\
-\quad\quad\quad $\mathbf{y}^{(t)}=\hat{\mathbf{x}}^{(t-1)}+\delta(\mathbf{y}-\mathbf{y}^{(t-1)})$;
-\\
-3. Estimate the standard deviation of noise;
-\\
 \quad\textbf{for} each PG $\mathbf{Y}$ \textbf{do}
 \\
-4.\quad Calculate group mean $\boldsymbol{\upmu}_{y}$ and form PG $\mathbf{\overline{Y}}$;
+2.\quad Calculate group mean $\boldsymbol{\upmu}_{y}$ and form PG $\mathbf{\overline{Y}}$;
 \\
-5.\quad Gaussian component selection via (\ref{equ3});
+3.\quad Gaussian component selection via (\ref{equ3});
 \\
@@
 \\
-6.\quad Internal Subspace Learning by (\ref{equ4});
+4.\quad Internal Subspace Learning by (\ref{equ4});
 \\
-7.\quad Recover each patch in all PGs via $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$;
+5.\quad Recover each patch in all PGs via $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$;
 \\
@@
 \\
-8. Aggregate the recovered PGs of all subspaces to form
+6. Aggregate the recovered PGs of all subspaces to form
 \\
@@
 \hline
-PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.68} & \color{red}{ 38.89}
+PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.72} & \color{red}{ 38.90}
 \\
 \hline
-SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9676} & \color{red}{0.9704}
+SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9694} & \color{red}{0.9702}
 \\
@@
 \multirow{3}{*}{\small{Canon 5D Mark III}} 
-& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & \color{blue}{38.76} & 38.37 & \color{red}{40.44}
+& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & \color{blue}{38.76} & 38.37 & \color{red}{40.50}
 \\ 
@@
 \multirow{3}{*}{ISO = 3200}   
-& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & \color{blue}{35.69} & 35.37 & \color{red}{37.16}
+& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & \color{blue}{35.69} & 35.37 & \color{red}{37.22}
 \\ 
 \cline{2-11}    
-& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & \color{blue}{35.54} & 34.91 & \color{red}{37.06}  
+& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & \color{blue}{35.54} & 34.91 & \color{red}{37.13}  
 \\
@@
 \multirow{3}{*}{Nikon D600} 
-& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & \color{red}{35.57} & 34.98 & \color{blue}{35.28}
+& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & \color{red}{35.57} & 34.98 & \color{blue}{35.34}
 \\ 
@@
 \multirow{3}{*}{ISO = 3200}   
-& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & \color{red}{36.70} & 35.95 & \color{blue}{36.62}
+& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & \color{red}{36.70} & 35.95 & \color{blue}{36.69}
 \\ 
 \cline{2-11}    
-& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & \color{blue}{40.51} & 38.68 & 39.28 & \color{red}{41.15} & 39.05
+& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & \color{blue}{40.51} & 38.68 & 39.28 & \color{red}{41.15} & 39.17
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & \color{blue}{38.01} & 37.99 & \color{red}{38.67}
+& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & \color{blue}{38.01} & 37.99 & \color{red}{38.82}
 \\ 
@@
 \multirow{3}{*}{ISO = 1600}   
-& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & \color{blue}{40.36} & \color{red}{40.81}
+& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & \color{blue}{40.36} & \color{red}{40.98}
 \\ 
 \cline{2-11}    
-& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & \color{blue}{38.30} & \color{red}{38.77}
+& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & \color{blue}{38.30} & \color{red}{38.90}
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & \color{red}{39.01} & \color{blue}{38.57}
+& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & \color{red}{39.01} & \color{blue}{38.69}
 \\ 
@@
 \cline{2-11}    
-& 32.91 & 32.98 & 32.96 & 38.54 & \color{blue}{40.05} & \color{red}{40.59} & 36.91 & 36.76 & 39.06 & 38.68
+& 32.91 & 32.98 & 32.96 & 38.54 & \color{blue}{40.05} & \color{red}{40.59} & 36.91 & 36.76 & 39.06 & 38.80
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & \color{blue}{34.25} & 31.28 & 33.49 & \color{red}{34.61} & 33.48
+& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & \color{blue}{34.25} & 31.28 & 33.49 & \color{red}{34.61} & 33.31
 \\ 
@@
 \multirow{3}{*}{ISO = 6400}   
-& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & \color{blue}{33.21} & \color{red}{33.29}
+& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & \color{red}{33.21} & \color{blue}{33.18}
 \\ 
 \cline{2-11}    
-& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & \color{blue}{33.22} & \color{red}{33.48}
+& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & \color{blue}{33.22} & \color{red}{33.35}
 \\
 \hline
-Average PSNR & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & \color{blue}{36.88} & \color{red}{ 37.21}
+Average PSNR & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & \color{blue}{36.88} & \color{red}{ 37.26}
 \\
 \hline
-Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & \color{blue}{0.9481} & \color{red}{ 0.9506}
+Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & \color{blue}{0.9481} & \color{red}{ 0.9505}
 \\

### 2016-10-22 CVPR2017_Review_Unified.tex
add

--- 2016-10-20 egpaper_for_review.tex
@@
 %%%%%%%%% TITLE
-\title{External Patch Group Prior Guided Internal Subspace Learning for Real Image Denoising}
+\title{External Patch Group Prior Guided Adaptive Orthogonal Dictionary Learning for Real Image Denoising}
 
@@
 
-\subsection{External Prior Guided Internal Subspace Learning}
+\subsection{External Prior Guided Adaptive Orthogonal Dictionary Learning}
 Given a rael noisy image, we extract noisy PGs from it and save the mean vectors of each PG for recovering.
@@
 \begin{equation}\label{equ4}
-\mathbf{Y}=\mathbf{U}\mathbf{S}\mathbf{V}^{T}
+\begin{split}
+&\min_{\mathbf{D}\in \mathbb{R}^{3p^2\times r}}\|\mathbf{Y}-[\mathbf{D}_{e};\mathbf{D}_{i}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}
+\\
+&
+\text{s.t.}
+\quad
+\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+\end{split}
 \end{equation}

### 2016-10-22 CVPR2017_Review_Unified.tex
a

--- 2016-10-20 egpaper_for_review.tex
@@
 \usepackage{color}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 %%%%%%%%% TITLE
-\title{External Patch Group Prior Guided Internal Subspace Learning for Real Image Denoising}
+\title{External Patch Group Prior Guided Internal Orthogonal Dictionary Learning for Real Image Denoising}
 
@@
 
-\subsection{Internal v.s. External Image Denoising}
+\subsection{Internal v.s. External Dictionary Learning}
 For natural images, the internal patch recurrence across multiple scales has been successfully applied in many image restoration problems \cite{Irani2009sr,Irani2013separating,Irani2014deblur,Irani2016dehazing}.
@@
 
-\section{External Patch Group Prior Guided Internal Subspace Learning}
+\section{External Patch Group Prior Guided Internal Orthogonal Dictionary Learning}
 In this section, we formulate the framework of external Patch Group prior guided internal subspace learning.
@@
 
-\subsection{External Prior Guided Internal Subspace Learning}
+\subsection{External Prior Guided Internal Orthogonal Dictionary Learning}
 Given a rael noisy image, we extract noisy PGs from it and save the mean vectors of each PG for recovering.
@@
 \begin{equation}\label{equ4}
-\mathbf{Y}=\mathbf{U}\mathbf{S}\mathbf{V}^{T}
+\begin{split}
+&\min_{\mathbf{D}\in \mathbb{R}^{3p^2\times r},\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
+\|\mathbf{Y}-[\mathbf{D}_{e};\mathbf{D}_{i}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}
+\\
+&
+\text{s.t.}
+\quad
+\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+\end{split}
 \end{equation}
@@
 
-\subsection{What does External Prior help the Internal Subspace Learning?}
+\subsection{Optimization with Closed-form Solution}
+Similar to the K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem \ref{equ4}.
+In fact, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}$ and for $t=0, 1, ..., T-1$, alternatively do
+
+\textbf{Updating Weighted Sparse Coding}: given the initialization orthogonal dictioanry $\textbf{D}_{i}^{(t)}$, the sparce coefficients 
+$\textbf{A}^{(t)}$ are obtained via solving
+\begin{equation}
+\textbf{A}^{(t)}:=\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
+\|\mathbf{Y}-[\mathbf{D}_{e};\mathbf{D}_{i}^{(t)}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}
+\end{equation}
+
+\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(0)}$, the sparce coefficients 
+$\textbf{A}^{(t)}$ are obtained via solving
+\begin{equation}
+\begin{split}
+\textbf{D}_{i}^{(t+1)}:=
+&
+\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
+\|\mathbf{Y}-[\mathbf{D}_{e};\mathbf{D}_{i}]\mathbf{A}^{(t)}\|_{F}^{2}
+\\
+&
+\text{s.t.}
+\quad
+\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+\end{split}
+\end{equation}
+
+\subsection{Discussion on External Prior and Internal Orthogonal Dictionary Learning}
 Until now, we have divided the noisy PGs into multiple internal subspaces.
@@
 
-\subsection{Discussion on Internal Subspace Structure}
 The Internal PGs are in fact lying in the subspaces of external PG Spaces.
@@
 \hline
-\textbf{Alg. 1}: External Guided Internal Subspace Denoising
+\textbf{Alg. 1}: External Guided Internal Dictionary Learning
 \\

### 2016-10-22 CVPR2017_Review_Unified.tex
add

@@
 \begin{split}
-&\min_{\mathbf{D}\in \mathbb{R}^{3p^2\times r},\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
-\|\mathbf{Y}-[\mathbf{D}_{e};\mathbf{D}_{i}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}
+&\min_{\mathbf{D}_{i}\in \mathbb{R}^{3p^2\times r},\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
+\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}
 \\
@@
 
-\textbf{Updating Weighted Sparse Coding}: given the initialization orthogonal dictioanry $\textbf{D}_{i}^{(t)}$, the sparce coefficients 
+\textbf{Updating Sparse Coefficients}: given the initialization orthogonal dictioanry $\textbf{D}_{i}^{(t)}$, the sparce coefficients 
 $\textbf{A}^{(t)}$ are obtained via solving
-\begin{equation}
+\begin{equation}\label{equ5}
 \textbf{A}^{(t)}:=\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
-\|\mathbf{Y}-[\mathbf{D}_{e};\mathbf{D}_{i}^{(t)}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}
+\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}.
 \end{equation}
+This problem has closed-form solution by $\mathbf{A}^{*}=T_{\lambda}(\mathbf{\hat{D}}^{T}\mathbf{Y})$, 
+where $T_{\lambda}(\mathbf{A}) = \text{sgn}(\mathbf{A})\odot\max(\mathbf{A},\lambda)$ is a soft-thresholding function.
 
@@
 $\textbf{A}^{(t)}$ are obtained via solving
-\begin{equation}
+\begin{equation}\label{equ6} 
 \begin{split}
@@
 &
-\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
-\|\mathbf{Y}-[\mathbf{D}_{e};\mathbf{D}_{i}]\mathbf{A}^{(t)}\|_{F}^{2}
+\argmin_{\textbf{D}_{i}\in\mathbb{R}^{3p^2\times r}}
+\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}]\mathbf{A}^{(t)}\|_{F}^{2}
 \\
@@
 \end{split}
+\end{equation}
+Dividing the sparse coefficients $\mathbf{A}=[\mathbf{A}_{e}^{T}\ \mathbf{A}_{i}^{T}]^{T}$, where $\mathbf{A}_{e}$ and $\mathbf{A}_{i}$ denote the coefficients over external and internal dictionary $\mathbf{D}_{e}$ and $\mathbf{D}_{i}$.
+According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ6})
+%\begin{equation}
+%\begin{split}
+%\min_{\textbf{D}_{i}\in\mathbb{R}^{3p^2\times r}}
+%&\|\mathbf{Y}-\mathbf{D}_{e}\mathbf{A}_{e}+\mathbf{D}_{i}\mathbf{A}_{i}\|_{F}^{2}
+%\\
+%&
+%\text{s.t.}
+%\quad
+%\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+%\end{split}
+%\end{equation}
+has a closed-form solution $\mathbf{D}_{i}^{*}=\mathbf{U}\mathbf{V}^{T}$, where $\mathbf{U}$ and $\mathbf{V}$ are
+the orthogonal matrices obtained by the following SVD
+\begin{equation}\label{equ7}
+(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{T})\mathbf{Y}\mathbf{A}_{i}^{T}
+=
+\mathbf{U}\Sigma\mathbf{V}^{T}
+\end{equation}
+With these solutions, the final obtained dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ are orthogonal ictionary. This can be proved by the following equation
+\begin{equation}\label{equ8}
+\mathbf{D}^{T}\mathbf{D} = 
+\left(\begin{array}{c}
+\mathbf{D}_{e}^{T}
+\\
+\mathbf{D}_{i}^{T}
+\end{array}\right)
+(\mathbf{D}_{e}\ \mathbf{D}_{i})
+=
+\left(\begin{array}{cc}
+\mathbf{D}_{e}^{T}\mathbf{D}_{e}\ \mathbf{D}_{e}^{T}\mathbf{D}_{i}
+\\
+\mathbf{D}_{i}^{T}\mathbf{D}_{e}\ \mathbf{D}_{i}^{T}\mathbf{D}_{i}
+\end{array}\right)
+=
+\mathbf{I}
 \end{equation}
@@
 This will bring better denoising performance than the methods only using the external information.
+The \emph{mutual incoherence} $\mu(\mathbf{U})$ \cite{donoho2003optimally}, which is difined as
+\begin{equation}\label{equ9}
+\mu(\mathbf{U})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}}
+\end{equation},
+is a measure of quality of dictionary.
 
@@
 \section{The Denoising Algorithm}
-\subsection{Adaptive Sparse Coding}
+\subsection{Fast Patch Group Searching by Integral Image}
+The searching of patch groups in images is inefficient if we search non-local similar patches to each local patch.
+To speed up the searching process and make our proposed method faster, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching.
+The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size.
+That is to say, we do not need do distance measure for each patch.
+It was first proposed under the name of summed area table\cite{viola2004robust}
+
+\subsection{Prior Weights for Sparse Coding}
 To remove the real noise, we employ the sparse coding framework.
 And in order to be adaptive to the input image, we employ the internal learned $\mathbf{U}$ of each cluster as an adaptive dictioanry to represent the structural variations of the PGs in that cluster.
-The \emph{mutual incoherence} $\mu(\mathbf{U})$ \cite{donoho2003optimally}, which is difined as
-\begin{equation}
-\mu(\mathbf{U})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}}
-\end{equation},
-is a measure of quality of dictionary. Since the $\mathbf{U}$ is orthonormal, its \emph{mutual incoherence} is naturally $0$ and therefore better than other redundant dictionaries.
+Since the $\mathbf{U}$ is orthonormal, its \emph{mutual incoherence} is naturally $0$ and therefore better than other redundant dictionaries.
 
-\begin{equation}\label{equ5}
+\begin{equation}\label{equ10}
 \min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{\overline{y}}_{m}-\mathbf{U}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{3p^{2}}\lambda_{i}|\boldsymbol{\upalpha}_{i}|.
@@
 The $i$th entry of the regularization parameter $\lambda_{i}$ 
-\begin{equation}\label{equ6}
+\begin{equation}\label{equ11}
 \lambda_{i} = \lambda/(\mathbf{S}_{i}+\varepsilon),
@@
 Since the dictionary $\mathbf{U}$ is orthonormal, it is not difficult to find out that (\ref{equ4}) has a closed-form solution (detailed derivation can be found in the supplementary material):
-\begin{equation}\label{equ7}
+\begin{equation}\label{equ12}
 \setlength{\abovedisplayskip}{3pt}
@@
 
-\subsection{Fast Patch Group Searching by Integral Image}
-The searching of patch groups in images is inefficient if we search non-local similar patches to each local patch.
-To speed up the searching process and make our proposed method faster, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching.
-The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size.
-That is to say, we do not need do distance measure for each patch.
-It was first proposed under the name of summed area table\cite{viola2004robust}
-
-\subsection{Effectively dealing with different noisy images}
-For real image denoising, we can perform well on images which have similar noise levels with the training dataset.
+%\subsection{Effectively dealing with different noisy images}
+%For real image denoising, we can perform well on images which have similar noise levels with the training dataset.
 How can we deal with the real noisy images whose noise levels are higher than the training dataset?
@@
 
-This will also bring a second problem, that how we could automatically terminate the iteration.
+%This will also bring a second problem, that how we could automatically terminate the iteration.
 This can be solved by two methods.
@@
 1).
-
 \begin{table}
@@
 \hline
-\textbf{Alg. 1}: External Guided Internal Dictionary Learning
+\textbf{Alg. 1}: External Prior Guided Internal Orthogonal 
+\\
+\quad \quad \quad Dictionary Learning for Denoising
 \\

### 2016-10-23 CVPR2017_Review_Unified.tex
add

@@
 \begin{abstract}
-Existing image denoising methods largely depends on noise modeling and estimation.
-The commonly used noise models, additive white Gaussian, are inflexible in describing the complex noise on real noisy images.
-This would limit the performance of existing methods on denoising real noisy images.
-In this paper, we firstly demonstrate that almost all state-of-the-art methods on removing Gaussian noise and real noise are limited in denoising real noisy images.
-We demonstrate that a simple Patch Group based Prior Learning model on RGB images can achieve better performance than existing denoising methods, especially the ones designed for real noise in natural images.
-Besides, we employ the external patch group prior learning for internal clustering and subspace learning.
-This external inormation guided internal denoising methods acheives even better than the external PG prior based methods and the fully internal PG prior based method.
-Through extensive on standard datasets on real noisy images with groundtruth, we demonstrate that the proposed method achieves much better denoising performance than the other state-of-the-art methods on Gaussian noise removal and real noise removal.
+The noise caused by camera sensors and the environment will influence the quality of images captured by many vision systems.
+For image denoising problem, the external and internal priors are playing key roles in many different methdos.
+External priors learn from external clean images to restore noisy images while internal ones exploit properies of given images for denoising.
+The external priors are more generative and efficient on recovering structures existing in most images while the internal priors are more adaptive on recovering detials existed in given noisy images.
+Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise.
+Therefore, only exploiting the external or internal priors are not enough for real image denoising.
+In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising.
+The internal orthogonal dictionary learning process has closed-form solutions and hence very efficient for online denoising.
+The experiments on standard datasets demonstrate that, that the proposed method achieves much better denoising performance than the other state-of-the-art methods on real image denoising.
 \end{abstract}
@@
 \section{Introduction} 
-Image denoising is a fundermental problem in computer vision and image processing.
-It is an ideal platform for testing natural image models and provides high-quality images for other conputer vision tasks such as image registration, segmentation, and pattern recognition, etc.
+Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images.
+The camera sensors and outdoor low light conditions will unavoidly bring noise to the captured images.
+The impact is that the image details will be lost or hardly visible.
+As a result, image denoising is an essential procedure for the reliability of these vision systems.
+In the research ara, image denoising is also an ideal platform for testing natural image models and provides high-quality images for other conputer vision tasks such as image registration, segmentation, and pattern recognition, etc.
+
 For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN).
-However, in real world, the noise in real images are much more complex than than Gaussian.
-The cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc.
-These conditions would produce noise as a by-product.
-Besides, the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016} would also change the noise distribution.
-Therefore, the noise in real images are much more complex than Gaussian, and depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc).
-The models designed to deal with AWGN would become much less effective on real noisy images.
+In real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc.
+Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}.
+Therefore, the noise in real images are much more complex than Gaussian.
+It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc).
+The models designed for AWGN would become much less effective on real noisy images.
 
-%Recently, several discriminative learning methods \cite{burger2012image,csf,chen2015learning} achieving expressive performance on Gaussian noise removal.
-These methods require a set of paired images, namely clean ground-truth images and the simulated noisy counterparts degraded by identical noise (mainly additive white Gaussian noise, AWGN), to learn an effective model for image denoising.
-
-In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are designed to deal with real noisy images.
+In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are developed to deal with real noisy images.
 Almost all these methods coincidently employ a two-stage framework: in the first stage, assuming a distribution model (usually Gaussian) on the noise and estimate its parameters; in the second stage, performing denoising with the help of the noise modeling and estimation in the first stage.

### 2016-10-23 CVPR2017_Review_Unified.tex
a

@@
 \begin{abstract}
-The noise caused by camera sensors and the environment will influence the quality of images captured by many vision systems.
 For image denoising problem, the external and internal priors are playing key roles in many different methdos.
-External priors learn from external clean images to restore noisy images while internal ones exploit properies of given images for denoising.
+External priors learn from external images to restore noisy images while internal ones exploit priors of given images for denoising.
 The external priors are more generative and efficient on recovering structures existing in most images while the internal priors are more adaptive on recovering detials existed in given noisy images.
-Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise.
-Therefore, only exploiting the external or internal priors are not enough for real image denoising.
 In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising.
@@
 \end{abstract}
+%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise.
+Therefore, only exploiting the external or internal priors are not enough for real image denoising.
 
@@
 Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}.
-Therefore, the noise in real images are much more complex than Gaussian.
+Therefore, the noise in real images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric}.
 It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc).
@@
 In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are developed to deal with real noisy images.
-Almost all these methods coincidently employ a two-stage framework: in the first stage, assuming a distribution model (usually Gaussian) on the noise and estimate its parameters; in the second stage, performing denoising with the help of the noise modeling and estimation in the first stage.
+Almost all these methods employ a two-stage framework: estimating the parameters of the assumed noise model (usually Gaussian) and performing denoising with the help of the noise modeling and estimation in the first stage.
 However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008}.
-Although the mixture of Gaussians (MoG) model is possible to approximate any unknown noise \cite{Zhu_2016_CVPR}, estimating its parameters is often time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR,Bishop}.
+Although the mixture of Gaussians (MoG) model is possible to approximate any noise distribution \cite{Bishop}, estimating its parameters is time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR}.
 To evaluate the performanec of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}.
-This image is captured by a Nikon D800 camera while the ISO is set as 3200.
-The "ground truth" image is also provided with which we can calculate objective measurements.
-More details about this dataset can be found at the experimental section.
+The testing image is captured by a Nikon D800 camera when ISO is 3200.
+The "ground truth" image is also provided with which we can calculate objective measurements such as PSNR and SSIM \cite{ssim}.
 The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image.
-This proves that the above mentioned methods are not effective on denoising complex noise on real images.
 \begin{figure*}\label{fig1}
@@
 
-In this paper, we attempt to deal with complex noise in real images by intergrating the external and internal information.
-Since the real noise is signal dependent \cite{crosschannel2016,healey1994radiometric}, the prior information in external natural images can be employed to avoid the high correlation between noise and siganl in internal images.
-On the other hand, the internal prior is adaptive to the image and can recover better the latent clean image.
-Based on these observations, we make detailed study on internal and external information for real image denoising task.
-We made several observations.
-Firstly, we found that the Patch Group Prior learning based denoising method \cite{pgpd} learned on clean RGB images are enough to outperform the above mentioned denoising methods.
-Secondly, we also found that a fully internal PG prior based denoising method which achieve better performance than the fully external method.
-Most importantly, we found that the external PG prior guided internal method can achieve even better and faster performance on real image denoising.
-In fact, the external PG prior learning based model is employed to guide the clustering of internal PGs extracted from the input noisy images.
+The above mentioned methods can be categorized into external methods which learn priors from external images to recover noisy images, and internal ones which exploit priors of given images for denoising.
+The external priors in natural images are free of the high correlation between noise and siganls in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image.
+Combining the priors of external clean images and adaptivety of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images.
+Based on these observations, in this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising.
+The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary.
+Both of the two stages have closed-form solutions.
+Hence, our internal DL process is very efficient for online internal denoising.
+
+% In fact, the external PG prior learning based model is employed to guide the clustering of internal PGs extracted from the input noisy images.
 Then for each cluster of PGs, we perform subspace learning by PCA and denoising by weighted sparse coding.

### 2016-10-23 CVPR2017_Review_Unified.tex
ad

@@
 Hence, our internal DL process is very efficient for online internal denoising.
-
-% In fact, the external PG prior learning based model is employed to guide the clustering of internal PGs extracted from the input noisy images.
-Then for each cluster of PGs, we perform subspace learning by PCA and denoising by weighted sparse coding.
-We perform comprehensive experiments on real noisy images captured by different CMOS or CCS sensors.
-The results demonstrate that our method achieves comparable or even better performance on denoising real noisy images.
-An initial glimpse of our method is also listed in Figure \ref{fig1}.
-This reveals the potential advantages of combining external and internal information o natural images on robust and complex real noisy image denoising problem.
+Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising
 
@@
 \begin{itemize}
-\item We propose a noval method which combine the external and internal PG prior for real noisy image denoising problem;
-\item Our method doesn't need noise modeling and estimation, and the noise levels of real noisy images are automatically expresssed by the singular values of learned subspace;
-\item We achieve much better performance on visual quality, PSNR, SSIM, and speed, than other competing methods for real image denoising problem.
+\item We propose a noval dictionary learning method which employ the external prior guided the internal orthogonal dictionary learning for real image denoising.
+Both the external prior and internal prior are performed on patch groups instead of patches.
+\item The internal orthogonal dictionary learning are alternating iterative solved with closed-form solutions.
+The learned orthogonal dictionary are very efficient in both learning and denoising stages.
+\item We achieve much better performance on the real image denoising problem than other competing methods in terms of visual quality, PSNR, and SSIM.
 \end{itemize}
 
-The rest of this paper will be summerized as follows: in Section 2, we will introduce the related work close to our work; in Section 3, we will introduce our proposed external prior guided internal subspace learning framework for real image denoising; in Section 4, we will demonstrate the denoising experiments on several standard dataset; in Section 5, we will conclude our paper and give our future work.
+The rest of this paper will be summerized as follows: in Section 2, we will introduce the related work; in Section 3, we will introduce the proposed external prior guided internal orthogonal dictionary learning algorithm for real image denoising; in Section 4, we will demonstrate the extensive experiments on two standard dataset; we will conclude our paper and give our future work in Section 5.
 

### 2016-10-23 CVPR2017_Review_Unified.tex
aa

@@
 The PG prior largely reduces the space of images to be modeled when compared to the patch prior \cite{epll}.
-The better modeling on NSS is demonstrated via better image denoising performance on natural images.
-However, in \cite{pgpd}, only the PGs of clean natural images is utilized, while the PGs of noisy input images are ignored.
-In this paper, we aim at making use of both PGs from natural clean images and real noisy images for better denoising performance.
+In \cite{pgpd}, only the PGs of clean natural images is utilized, while the PGs of noisy input images are ignored.
+In this paper, we make use of PGs both from external clean images and internal given real noisy image for better denoising performance.
 

### 2016-10-23 CVPR2017_Review_Unified.tex
add

@@
 \subsection{Internal v.s. External Dictionary Learning}
-For natural images, the internal patch recurrence across multiple scales has been successfully applied in many image restoration problems \cite{Irani2009sr,Irani2013separating,Irani2014deblur,Irani2016dehazing}.
-These work demonstrate that internal information is enough for many ill-posed problems including denoising additive white Gaussian noise.
-The rationale is, since the AWGN noise is independent of the original clean images, it will be reduced if the image is scaled to a smaller size.
+There are two categories of dictionary learning methods in image denoising.
+One category of methods \cite{epll,pgpd} learns dictionary from external clean images to reconstruct the given noisy images, while the other category of methods \cite{ple,ncsr} directly learns adaptive dictionary from the given noisy image to recover the latent clean image.
+The two categories of methods are very successful in removing Gaussian noise.
 However, the noise in real images is generated mostly from the camera sensors, which is highly complex and signal dependent \cite{crosschannel2016}.
-Besides, according to the seminar workd of \cite{healey1994radiometric}, the noise in real images has fixed patterns from several main sources.
+Besides, the noise in real images has fixed patterns from several main sources \cite{healey1994radiometric}.
 Therefore, we can hardly seperate the complex noise from the signals without the help of external (correct) information of natural clean images.
-Only using the internal information may be not enough for real image denoising problem.
-On the other hand, the methods only using the external information may be not adaptive for real noisy images.
-Recently, the methods of \cite{mlp,csf,chen2015learning} had been proposed to learn, on both internal and external images, a process directly mapping the noisy patches to denoised ones.
-These discriminatice learning based methods are only effective on additive white Gaussian noise and ineffective on complex and signal dependent noise in real images.
-This has been shown in Figure \ref{fig1}.
-In this paper, our goal is to make use of external information to guide the subspace learning of internal PGs for image denoising task.
+In this paper, our goal is to employ the external patch group prior to guide the internal noisy PGs to be clustered into correct subspace, and the learning process of internal orthogonal dictionary.
+
+%For natural images, the internal patch recurrence across multiple scales has been successfully applied in many image restoration problems \cite{Irani2009sr,Irani2013separating,Irani2014deblur,Irani2016dehazing}.
 

### 2016-10-24 CVPR2017_Review_Unified.tex
add

@@
 
-%For natural images, the internal patch recurrence across multiple scales has been successfully applied in many image restoration problems \cite{Irani2009sr,Irani2013separating,Irani2014deblur,Irani2016dehazing}.
-
 \subsection{Real Image Denoising}
-To the best of our knowledge, the study of real image denoising can be dated back to the BLS-GSM model \cite{blsgsm}, in which Portilla et al.
+In the last decade, there are many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} proposed for real image denoising problem.
+In the seminar work of BLS-GSM \cite{blsgsm} for real image denoising, Portilla et al.
 proposed to use scale mixture of Gaussian in overcomplete oriented pyramids to estimate the latent clean images.
 In \cite{fullyblind}, Portilla proposed to use a correlated Gaussian model for noise estimation of each wavelet subband.
-Based on the robust statistics theory \cite{huber2011robust}, the work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers, which could be removed via Lorentzian robust estimator.
-In \cite{Liu2008}, Liu et al.
-proposed to use 'noise level function' (NLF) to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image.
-Recently, Gong et al.
-proposed an optimization based method \cite{almapg}, which models the data fitting term by weighted sum of $\ell_{1}$ and $\ell_{2}$ norms and the regularization term by sparsity prior in the wavelet transform domain.
+The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}.
+Liu et al.
+\cite{Liu2008} proposed to use 'noise level function' (NLF) to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image.
+Gong et al.
+\cite{almapg} models the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain.
 Later, Lebrun el al.
-proposed a multiscale denoising algorithm called 'Noise Clinic' \cite{noiseclinic} for real image denoising task.
-This method generalizes the NL-Bayes \cite{nlbayes} to deal with signal, scale, and frequency dependent noise.
+proposed a multiscale denoising algorithm called 'Noise Clinic' \cite{noiseclinic}.
+This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance.
 Recently, Zhu et al.
-proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates the noise via Mixture of Gaussian (MoG) model \cite{Bishop}.
-The clean image is recovered from the noisy image by the proposed Low Rank MoG filter (LR-MoG).
-In this paper, we proposed a noval denoising method achieving much better performance than previous real denoising methods.
+proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and remove the noise via Low-Rank Mixture of Gaussian (LR-MoG) model.
+The commercial software Neat Image \cite{neatimage} first estimate the parameters of noise via a large flat area and then filter the noise accordingly.
 

### 2016-10-24 CVPR2017_Review_Unified.tex
ad

@@
 The internal orthogonal dictionary learning process has closed-form solutions and hence very efficient for online denoising.
-The experiments on standard datasets demonstrate that, that the proposed method achieves much better denoising performance than the other state-of-the-art methods on real image denoising.
+The experiments on standard datasets demonstrate that, that the proposed method achieves better performance than other state-of-the-art methods on real image denoising.
 \end{abstract}
@@
 \end{minipage}
-}
+}\vspace{-3mm}
 \subfigure{
@@
 \end{minipage}
-}
-\caption{Denoised images of the real noisy image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
+}\vspace{-1mm}
+\caption{Denoised images of the real noisy image "Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} \vspace{-4mm}
 \end{figure*}

### 2016-10-24 CVPR2017_Review_Unified.tex
addd

@@
 \subsection{Internal v.s. External Dictionary Learning}
-There are two categories of dictionary learning methods in image denoising.
-One category of methods \cite{epll,pgpd} learns dictionary from external clean images to reconstruct the given noisy images, while the other category of methods \cite{ple,ncsr} directly learns adaptive dictionary from the given noisy image to recover the latent clean image.
-The two categories of methods are very successful in removing Gaussian noise.
-However, the noise in real images is generated mostly from the camera sensors, which is highly complex and signal dependent \cite{crosschannel2016}.
-Besides, the noise in real images has fixed patterns from several main sources \cite{healey1994radiometric}.
-Therefore, we can hardly seperate the complex noise from the signals without the help of external (correct) information of natural clean images.
-In this paper, our goal is to employ the external patch group prior to guide the internal noisy PGs to be clustered into correct subspace, and the learning process of internal orthogonal dictionary.
+Learning dictionaries to represent images has been successfully used in image modeling \cite{ksvd,ksvdtsp,epll,ple,ncsr,pgpd}.There are mainly two categories of DL methods: 1) External DL methods pre-learned dictionary from a set of clean image patches, and the learned dictionaries are used to encode the noisy image patches for denoising \cite{ksvdtsp,epll,pgpd}.
+2) Internal DL methods directly learned dictionary from the patches of given noisy image, and the image denoising is simultaneously done with the DL process \cite{ksvd,ple,ncsr}.
+The external DL methods is not adaptive to the noisy image, while the internal DL methods is adaptive to the degraded images but it ignores the information hidden in clean images.
+In this paper, our goal is to employ the external dictionary to guide the learning of internal orthogonal dictionary.
 
@@
 Recently, Zhu et al.
-proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and remove the noise via Low-Rank Mixture of Gaussian (LR-MoG) model.
-The commercial software Neat Image \cite{neatimage} first estimate the parameters of noise via a large flat area and then filter the noise accordingly.
+proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and remove the noise via Low-Rank Mixture of Gaussians (LR-MoG).
+The commercial software Neat Image \cite{neatimage} first estimates the parameters of noise via a large flat area and then filters the noise accordingly.
 

### 2016-10-26 CVPR2017_Review_Unified.tex
add

@@
 \section{External Patch Group Prior Guided Internal Orthogonal Dictionary Learning}
-In this section, we formulate the framework of external Patch Group prior guided internal subspace learning.
-We first introduce the patch group prior leaning on clean natural RGB images.
-Then we formulate the external guided internal subspace learning.
-Finally, we discuss the differences between external subspaces and the corresponding internal subspace.
+In this section, we formulate the framework of external patch group (PG) prior guided internal orthogonal dictionary learning.
+We first introduce the patch PG leaning on clean natural RGB images.
+Then we propose to exploy the external PG prior to guide the internal clustering and orthogonal dictionary learning (DL).
+The orthogonal DL has alternative closed-form solutions in term of updating sparse coefficients and dictionary.
+Finally, we discuss the advantages of our proposed external PG prior guided internal orthogonal dictionary learning algorithm.
 

### 2016-10-26 CVPR2017_Review_Unified.tex
add

@@
 \subsection{External Patch Group Prior Learning}
-Natural images often demonstrate repepitive patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm,pgpd} and restoration methods \cite{}.
-In \cite{pgpd}, the NSS property is directly learned as an external prior in a patch group manner.
-In this section, we formulate the Patch Group prior on natural color images.
-
-In \cite{pgpd}, the patch group (PG) is defined as a group of similar patches to the local patch.
+Natural images often demonstrate repepitive local patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm,pgpd}.
+In this section, we formulate the Patch Group prior learned on natural color images.
+Similar to \cite{pgpd}, the patch group (PG) is defined as a group of similar patches to the local patch.
 The patch group mean is destracted, and hence different groups patches can share similar PGs.
-Therefore the space to be modeled is largely reduced.
-In this work, we extract PGs from RGB images.
-Each patch is of size $p\times p \times 3$.
-For each local patch, we search its similar patches around it through the Euclidean distance in a local window of size $W\times W$.
-The PG is denoted by $\{\mathbf{x}_{m}\}_{m=1}^{M}$, where $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ is a color image patch vector.
-The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and $\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}$ is the group mean subtracted patch vector.
-The PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}\}, m=1,...,M$, and it represent the external NSS prior on color images.
-Assume we have extracted $N$ PGs from a given set of natural images, and the $n$-th PG is defined as $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.
-We employ the patch group based Gaussian Mixture Model (PG-GMM) for NSS prior learning.
-We aim to learn a set of $K$ Gaussians $\{\mathcal{N}(\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})\}$ from $N$ training PGs $\{\mathbf{\overline{X}}_{n}\}$, while requiring that all the $M$ patches $\{\mathbf{\overline{x}}_{n,m}\}$  in PG $\mathbf{\overline{X}}_{n}$ belong to the same Gaussian component and assume that the patches in the PG are independently sampled.
-Note that such an assumption is commonly used in patch based image modeling \cite{ksvd,lssc}.
-Then, the likelihood of $\{\mathbf{\overline{X}}_{n}\}$ can be calculated as
-\begin{equation}\label{equ1}
-P(\mathbf{\overline{X}}_{n})  = \sum\nolimits_{k=1}^{K}\pi_{k}\prod\nolimits_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k}).
+In this way, the space natural image patches to be modeled is largely reduced.
+In this work, each local patch extracted from RGB images is of size $p\times p \times 3$.
+Then we search the $M$ most similar patches $\{\mathbf{x}_{m}\}_{m=1}^{M}$ around each local patch through Euclidean distance, in a local window of size $W\times W$.
+The $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ is a patch vector formed by combining the 3 patch vectors (of size $p^{2}\times 1$) in R, G, B channels.
+The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}\}, m=1,...,M$.
+Assume we have extracted $N$ PGs from a set of external natural images, and the $n$-th PG is defined as $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.
+We employ the Gaussian Mixture Model (GMM) to learn the external patch group based NSS prior.
+In this model, the likelihood of the $n$-th PG $\{\mathbf{\overline{X}}_{n}\}$ can be calculated as
+\vspace{-2mm}
+\begin{equation}\label{equ1}\vspace{-2mm}
+P(\mathbf{\overline{X}}_{n})  = \sum\nolimits_{k=1}^{K}\pi_{k}\prod\nolimits_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k}),
 \end{equation}
+where $K$ is the number of Gaussians and the $k$-th Gaussian is $\{\mathcal{N}(\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})\}$.
 By assuming that all the PGs are independently sampled, the overall objective log-likelihood function is
-\begin{equation}\label{equ2}
+\vspace{-2mm}
+\begin{equation}\label{equ2}\vspace{-2mm}
 \begin{split}

### 2016-10-26 CVPR2017_Review_Unified.tex
addd

@@
 \end{equation}
-where $K$ is the number of Gaussians and the $k$-th Gaussian is $\{\mathcal{N}(\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})\}$.
+where $K$ is the number of Gaussians and the parameters $\pi_{k}$, $\boldsymbol{\upmu}_{k}$, $\mathbf{\Sigma}_{k}$ are mixture weight, mean vector, and covariance matrix of the $k$-th Gaussian, respectively.
 By assuming that all the PGs are independently sampled, the overall objective log-likelihood function is
@@
 \end{equation} 
-We maximize the above objective function for PG-GMM learning and  finally obtain the GMM model with learned parameters including mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}=\mathbf{0}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.
-Noted that the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
+We maximize the above objective function via EM algorithm \cite{em} and finally obtain the GMM model with learned parameters as the learned external PG prior.
 

### 2016-10-26 CVPR2017_Review_Unified.tex
add

@@
 %%%%%%%%% TITLE
-\title{External Patch Group Prior Guided Internal Orthogonal Dictionary Learning for Real Image Denoising}
+\title{External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising}
 
@@
 \section{Introduction}
+
 Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images.
@@
 \subsection{Our Contributions}
+
 The contributions of this paper are summarized as follows:
 \begin{itemize}
-\item We propose a noval dictionary learning method which employ the external prior guided the internal orthogonal dictionary learning for real image denoising.
-Both the external prior and internal prior are performed on patch groups instead of patches.
-\item The internal orthogonal dictionary learning are alternating iterative solved with closed-form solutions.
-The learned orthogonal dictionary are very efficient in both learning and denoising stages.
-\item We achieve much better performance on the real image denoising problem than other competing methods in terms of visual quality, PSNR, and SSIM.
+\item We propose a novel model to learn internal priors adaptive to given images.
+This model employs the external patch group (PG) prior learned from clean images to guide the internal PG prior learning of given images.
+The external prior benefits the internal learning on subspace selection and orthogonal dictionary learning.
+\item The proposed guided internal prior learning method is very efficient. The reason is that both the subspace selection and orthogonal dictionary learning have explicit solutions.
+\item For real image denoising problem, the proposed method achieves much better performance than other competing methods.
 \end{itemize}
 
-The rest of this paper will be summerized as follows: in Section 2, we will introduce the related work; in Section 3, we will introduce the proposed external prior guided internal orthogonal dictionary learning algorithm for real image denoising; in Section 4, we will demonstrate the extensive experiments on two standard dataset; we will conclude our paper and give our future work in Section 5.
+The rest of this paper will be summerized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model; in Section 4, we formulate the overall image denoising algorithm; in Section 4, we demonstrate extensive experiments on real image denoising probelm; in Section 5, we conclude our paper and give future work.
 
@@
 \subsection{Patch Group Prior of Natural Images}
+
 The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self similar (NSS) property of natural images.
@@
 
-\subsection{Internal v.s. External Dictionary Learning}
-Learning dictionaries to represent images has been successfully used in image modeling \cite{ksvd,ksvdtsp,epll,ple,ncsr,pgpd}.There are mainly two categories of DL methods: 1) External DL methods pre-learned dictionary from a set of clean image patches, and the learned dictionaries are used to encode the noisy image patches for denoising \cite{ksvdtsp,epll,pgpd}.
-2) Internal DL methods directly learned dictionary from the patches of given noisy image, and the image denoising is simultaneously done with the DL process \cite{ksvd,ple,ncsr}.
-The external DL methods is not adaptive to the noisy image, while the internal DL methods is adaptive to the degraded images but it ignores the information hidden in clean images.
-In this paper, our goal is to employ the external dictionary to guide the learning of internal orthogonal dictionary.
+\subsection{Internal v.s. External Prior Learning}
+
+Learning priors to represent images has been successfully used in image modeling \cite{ksvd,epll,pgpd,ple,ncsr}.
+There are mainly two categories of prior learning methods: 1) External methods pre-learned priors (e.g., dictionaries) from a set of clean images, and the learned priors are used to recover the noisy images \cite{epll,pgpd}.
+2) Internal methods directly learned priors from the given noisy image, and the image denoising is simultaneously done with the learning process \cite{ksvd,ple,ncsr}.
+Both the two categories of methods have limitations.
+The external methods is not adaptive to the noisy image, while the internal methods ignores the information hidden in clean images.
+In this paper, our goal is to employ the external prior to guide the internal prior learning.
 
 \subsection{Real Image Denoising}
+
 In the last decade, there are many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} proposed for real image denoising problem.
@@
 Liu et al.
-\cite{Liu2008} proposed to use 'noise level function' (NLF) to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image.
+\cite{Liu2008} proposed to use 'noise level function' to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image.
 Gong et al.
@@
 Recently, Zhu et al.
-proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and remove the noise via Low-Rank Mixture of Gaussians (LR-MoG).
-The commercial software Neat Image \cite{neatimage} first estimates the parameters of noise via a large flat area and then filters the noise accordingly.
+proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via Low-Rank Mixture of Gaussians.
 
-\section{External Patch Group Prior Guided Internal Orthogonal Dictionary Learning}
+\section{External Patch Group Prior Guided Internal Prior Learning}
+
 In this section, we formulate the framework of external patch group (PG) prior guided internal orthogonal dictionary learning.
@@
 \subsection{External Patch Group Prior Learning}
+
 Natural images often demonstrate repepitive local patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm,pgpd}.
@@
 
-\subsection{External Prior Guided Internal Orthogonal Dictionary Learning}
-Given a rael noisy image, we extract noisy PGs from it and save the mean vectors of each PG for recovering.
-The mean substracted PG is defined as $\mathbf{\overline{Y}}$.
-To project this PG into a most adaptive subspace, we select the most suitable Gaussian component to it from the PG-GMM trained in previous section.
-The selection can be done by checking the posterior probability that $\mathbf{\overline{Y}}$ belongs to the $k$th Gaussian component:
-\begin{equation}\label{equ3}
-P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})}.
+\subsection{External Prior Guided Internal Prior Learning}
+
+After the external patch group (PG) prior is learned, we can employ it to guide the internal PG prior learning for the given testing (real noisy) image.
+The guidance mainly comes from two aspects.
+One aspect is that the external prior can guide the internal noisy PGs to be assigned to most suitable Gaussians or subspaces.
+And for each subspace, the other aspect is to guide the orthogonal dictionary learning of internal noisy PGs.
+
+\vspace{-2mm}
+\subsubsection{Guided Internal Subspace Selection}
+
+Similar to the previous section, we extract noisy PGs from the given real noisy image and extract the mean substracted PG, which is defined as $\mathbf{\overline{Y}}$.
+Noted that, the mean vectors of external PGs are discarded in the external prior learning stage while the mean vectors of internal PGs are saved for recovering.
+For better adaptivity, we project the PG $\mathbf{\overline{Y}}$ into its most suitable Gaussian component (subspace) of the GMM trained by external PGs.
+The selection can be done by firstly calculating the posterior probability of "$\mathbf{\overline{Y}}$ belonging to the $k$th Gaussian component":
+\vspace{-2mm}
+\begin{equation}\label{equ3}\vspace{-2mm}
+P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})},
 \end{equation}
-Since the noise on real images are mostly small when compared to the signals, the covariance matrix of the $k$th component is still $\mathbf{\Sigma}_{k}$.
-Finally, the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}})$ is selected as the most suitable subspace for $\mathbf{\overline{Y}}$.
+and then selecting the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}})$ as the most suitable subspace for $\mathbf{\overline{Y}}$.
 
-Though each PG has been projected into its most suitable subspace, the pre-learned subspace is still too general to represent the noisy PG extracted from the real noisy image.
-That is, the noisy PGs projected into one cluster can still constisted a subspace which is of lower dimensions than the subspace pre-learned from the external PGs.
-This can be demonstrated by compare the distribution of external PGs and internal PGs in the same clusters.
-We randomly select one cluster, and collect the celan PGs extracted from external dataset (Kodak 24 images) and the niosy PGs from the testing image.
-Since the original PGs are of $3p^{2}$ dimensions, we apply PCA to project the PGs into 2 dimensions for better visualization.
-The results is shown in Figure \ref{fig}, from which we can see clearly that the projected PGs are mainly in a smaller region of the external PGs, which proves that the internal PGs are only consisted a subspace in a lower dimension than the PGs collected from external subspace.
+\vspace{-2mm}
+\subsubsection{Guided Internal Orthogonal Dictionary Learning}
+
 To better and adaptively charactering the internal PGs from the testing image, we need learn a more specific dictionary for noisy PGs assigned into each cluster.
@@
 
-\subsection{Optimization with Closed-form Solution}
 Similar to the K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem \ref{equ4}.
-In fact, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}$ and for $t=0, 1, ..., T-1$, alternatively do
+In fact, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}$ and for $t=0, 1, ..., T-1$, alternatively do:
 
@@
 
-\subsection{Discussion on External Prior and Internal Orthogonal Dictionary Learning}
+\subsection{Discussions on Learning External Priors and Internal Priors}
 Until now, we have divided the noisy PGs into multiple internal subspaces.
@@
 is a measure of quality of dictionary.
-
-The Internal PGs are in fact lying in the subspaces of external PG Spaces.
-To defend this argument, we compare the distribution of external PGs extracted from clean natural images and real noisy images.
-For better illumination, we randomly selected a cluster and project the original clean PGs $\mathbf{X}$ onto a 2-D plane.
-This could be done via $\mathbf{Xp}=\mathbf{U(:.1:2)}^{T}\mathbf{X}$, where $\mathbf{U}$ is the singular vector matrix of that cluster.
-The noisy PGs $\mathbf{Y}$ assigned in this cluster is also projected into 2-D via $\mathbf{Yp}=\mathbf{U(:.1:2)}^{T}\mathbf{Y}$.
-The Figure \ref{} reflects the distribution on the 2-D plane of the projected clean PGs from external natural images and the projected noisy PGs from internal image.
-We can see that the internal noisy PGs are indeed lying in a subspace of the external PGs.
-Hence, if we directly use the external prior learned from clean PGs, the learned subspaces would be too generative to be suitable for the testing data.
 
@@
 We also compare with three competing real image denoising methods such as Noise Clinic, Neat Image, and the CCNoise method proposed recently.
-The popular software NeatImage which is one of the best denoising software available.
+The commercial software Neat Image \cite{neatimage} first estimates the parameters of noise via a large flat area and then filters the noise accordingly.
 All these methods need noise estimation which is vary hard to perform if there is no uniform regions are available in the testing image.
@@
 Since this dataset contains repetitive contents across different images, we crop 60 small images of size $500\times500$ from these 17 images in \cite{crosschannel2016}.
-
 The PSNR and SSIM resluts are listed in Table \ref{tab1}.

### 2016-10-26 CVPR2017_Review_Unified.tex
add

@@
 We maximize the above objective function via EM algorithm \cite{em} and finally obtain the GMM model with learned parameters as the learned external PG prior.
+Similar to \cite{pgpd}, the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
 
@@
 \subsubsection{Guided Internal Subspace Selection}
+\vspace{-1mm}
 
-Similar to the previous section, we extract noisy PGs from the given real noisy image and extract the mean substracted PG, which is defined as $\mathbf{\overline{Y}}$.
-Noted that, the mean vectors of external PGs are discarded in the external prior learning stage while the mean vectors of internal PGs are saved for recovering.
-For better adaptivity, we project the PG $\mathbf{\overline{Y}}$ into its most suitable Gaussian component (subspace) of the GMM trained by external PGs.
-The selection can be done by firstly calculating the posterior probability of "$\mathbf{\overline{Y}}$ belonging to the $k$th Gaussian component":
-\vspace{-2mm}
+Given a real noisy image, we extract the noisy PGs and corresponding mean vectors.
+Each mean substracted PG is defined as $\mathbf{\overline{Y}}\triangleq \{\mathbf{\overline{x}}_{m}\}_{m=1}^{M}$.
+Noted that, different from the external PGs, the mean vectors of the internal noisy PGs are saved for recovering.
+For adaptivity, we project the PG $\mathbf{\overline{Y}}$ into its most suitable Gaussian component (subspace) of the GMM learned on external PGs.
+The subspace most suitable for $\mathbf{\overline{Y}}$ is selected by firstly calculating the posterior probability of "$\mathbf{\overline{Y}}$ belonging to the $k$th Gaussian component":
+\vspace{-3mm}
 \begin{equation}\label{equ3}\vspace{-2mm}
@@
 \end{equation}
-and then selecting the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}})$ as the most suitable subspace for $\mathbf{\overline{Y}}$.
+and then choosing the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}})$.
 
@@
 \subsubsection{Guided Internal Orthogonal Dictionary Learning}
+\vspace{-2mm}
 
-To better and adaptively charactering the internal PGs from the testing image, we need learn a more specific dictionary for noisy PGs assigned into each cluster.
-For notation simplicity, we ignore the index of subspace $k$.
-The internal PGs $\mathbf{Y}$ form a subspace which can be obtained by singular value decomposition (SVD),
+Now each internal noisy PG has been assigned to its most suitable Gaussian component $\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})$ (subspace).
+In order to recover the latent clean PG, we employ the sparse coding framework under which we need a suitable dictionary for coding.
+As we know, given a dictionary $\mathbf{D}$, its \emph{mutual incoherence} $\mu(\mathbf{D})$ \cite{donoho2003optimally}, which is difined as
+\vspace{-2mm}
 \begin{equation}\label{equ4}
+\vspace{-2mm}
+\mu(\mathbf{D})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}},
+\end{equation}
+is a measure of quality of dictionary. Since the \emph{mutual incoherence} of a orthogonal dictionary is $0$, its quality is often better than non-orthogonal dictionaries.
+
+external subspace through covariance matrix via singular value decomposition (SVD) 
+\begin{equation}\label{equ4}
+\mathbf{\Sigma}=\mathbf{U}_{e}\mathbf{S}_{e}\mathbf{V}_{e}^{T}.
+\end{equation}
+can learn for each subspace an internal orthogonal dictionary adaptive to the noisy PGs. For notation simplicity, we ignore the index of subspace $k$.
+
+\begin{equation}\label{equ5}
 \begin{split}
@@
 $\textbf{A}^{(t)}$ are obtained via solving
-\begin{equation}\label{equ5}
+\begin{equation}\label{equ6}
 \textbf{A}^{(t)}:=\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
@@
 $\textbf{A}^{(t)}$ are obtained via solving
-\begin{equation}\label{equ6} 
+\begin{equation}\label{equ7} 
 \begin{split}
@@
 This will bring better denoising performance than the methods only using the external information.
-The \emph{mutual incoherence} $\mu(\mathbf{U})$ \cite{donoho2003optimally}, which is difined as
-\begin{equation}\label{equ9}
-\mu(\mathbf{U})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}}
-\end{equation},
-is a measure of quality of dictionary.
 

### 2016-10-26 CVPR2017_Review_Unified.tex
add

@@
 In this way, the space natural image patches to be modeled is largely reduced.
+
 In this work, each local patch extracted from RGB images is of size $p\times p \times 3$.
@@
 \end{equation} 
-We maximize the above objective function via EM algorithm \cite{em} and finally obtain the GMM model with learned parameters as the learned external PG prior.
+We maximize the above objective function via EM algorithm \cite{em} and finally obtain the GMM model with learned parameters.
 Similar to \cite{pgpd}, the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
+
+Until now, we have clustered the PGs extracted from external clean images into $K$ subspaces (Gaussians).
+In order to better characterize each subspace, we perform singular value decomposition (SVD) on the covariance matrix of each subspace:
+\vspace{-1mm}
+\begin{equation}\label{equ3}\vspace{-2mm}
+\mathbf{\Sigma}=\mathbf{U}_{e}\mathbf{S}_{e}\mathbf{V}_{e}^{T},
+\end{equation}
+and the singular vectors in $\mathbf{U}_{e}$ are employed as the learned external orthogonal dictionary.
+Besides, the singular values are employed as weight prior which will be discussed in Section 4.
+The reason we use singular vectors $\mathbf{U}_{e}$ as external dictionary is, its \emph{mutual incoherence} $\mu(\mathbf{D})$ \cite{donoho2003optimally}, which is a measure of quality of dictionary (lower is better) and difined as
+\vspace{-2mm}
+\begin{equation}\label{equ4}
+\vspace{-2mm}
+\mu(\mathbf{D})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}},
+\end{equation}
+is naturally $0$.
 
@@
 
-Now each internal noisy PG has been assigned to its most suitable Gaussian component $\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})$ (subspace).
-In order to recover the latent clean PG, we employ the sparse coding framework under which we need a suitable dictionary for coding.
-As we know, given a dictionary $\mathbf{D}$, its \emph{mutual incoherence} $\mu(\mathbf{D})$ \cite{donoho2003optimally}, which is difined as
-\vspace{-2mm}
-\begin{equation}\label{equ4}
-\vspace{-2mm}
-\mu(\mathbf{D})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}},
-\end{equation}
-is a measure of quality of dictionary. Since the \emph{mutual incoherence} of a orthogonal dictionary is $0$, its quality is often better than non-orthogonal dictionaries.
+Now all internal noisy PGs have been assigned to their corresponding most suitable Gaussian components (subspaces) in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
+For the $k$-th subspace including internal noisy PGs, we employ the $k$-th Gaussian from external prior  internal prior learning framework to learn the internal orthogonal dictionary and the image denoising is simultaneously done with the learning process
 
-external subspace through covariance matrix via singular value decomposition (SVD) 
-\begin{equation}\label{equ4}
-\mathbf{\Sigma}=\mathbf{U}_{e}\mathbf{S}_{e}\mathbf{V}_{e}^{T}.
-\end{equation}
-can learn for each subspace an internal orthogonal dictionary adaptive to the noisy PGs. For notation simplicity, we ignore the index of subspace $k$.
+sparse coding 
+in order to recover the latent clean PGs, for under which we need a suitable dictionary for coding.
+
+can learn for each subspace an internal orthogonal dictionary adaptive to the noisy PGs.
 

### 2016-10-26 CVPR2017_Review_Unified.tex
add

--- 2016-10-26 CVPR2017_Review_Unified.tex
@@
 \end{equation} 
-We maximize the above objective function via EM algorithm \cite{em} and finally obtain the GMM model with learned parameters as the learned external PG prior.
+We maximize the above objective function via EM algorithm \cite{em} and finally obtain the GMM model with learned parameters.
 Similar to \cite{pgpd}, the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
+
+Now, we have clustered the PGs extracted from external clean images into $K$ Gaussians or subspaces.
+For notation simplicity, we ignore the index of subspace $k$.
+To better characterize each subspace, we perform singular value decomposition (SVD) on the covariance matrix:
+\vspace{-2mm}
+\begin{equation}\label{equ3}\vspace{-2mm}
+\mathbf{\Sigma}=\mathbf{U}_{e}\mathbf{S}_{e}\mathbf{V}_{e}^{T}.
+\end{equation}
+The singular vectors in $\mathbf{U}_{e}$ are employed as the external orthogonal dictionary to guide the internal orthogonal dictionary learning (the singular values are employed as prior weights for sparse coding which will be discussed in Section 4).
+For a dictionary $\mathbf{D}$, its \emph{mutual incoherence} $\mu(\mathbf{D})$ \cite{donoho2003optimally} difined by
+\vspace{-2mm}
+\begin{equation}\label{equ4}
+\vspace{-2mm}
+\mu(\mathbf{D})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}}
+\end{equation}
+is a measure of quality of dictionary (lower is better). The dictionary $\mathbf{U}_{e}$ always has $0$
+\emph{mutual incoherence} and hence better quality than non-orthogonal dictionaries.
 
@@
 The subspace most suitable for $\mathbf{\overline{Y}}$ is selected by firstly calculating the posterior probability of "$\mathbf{\overline{Y}}$ belonging to the $k$th Gaussian component":
-\vspace{-3mm}
-\begin{equation}\label{equ3}\vspace{-2mm}
+\vspace{-2mm}
+\begin{equation}\label{equ5}\vspace{-2mm}
 P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})},
@@
 
-Now each internal noisy PG has been assigned to its most suitable Gaussian component $\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})$ (subspace).
-In order to recover the latent clean PG, we employ the sparse coding framework under which we need a suitable dictionary for coding.
-As we know, given a dictionary $\mathbf{D}$, its \emph{mutual incoherence} $\mu(\mathbf{D})$ \cite{donoho2003optimally}, which is difined as
+Now all internal noisy PGs have been assigned to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
+For each subspace, we employ its external orthogonal dictionary $\mathbf{D}_{e}$ to guide the internal orthogonal dictionary learning.
+The learning is performed under the sparse coding framework (along with which the denoising of real noisy image is simultaneously done) as follows:
 \vspace{-2mm}
-\begin{equation}\label{equ4}
-\vspace{-2mm}
-\mu(\mathbf{D})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}},
-\end{equation}
-is a measure of quality of dictionary. Since the \emph{mutual incoherence} of a orthogonal dictionary is $0$, its quality is often better than non-orthogonal dictionaries.
-
-external subspace through covariance matrix via singular value decomposition (SVD) 
-\begin{equation}\label{equ4}
-\mathbf{\Sigma}=\mathbf{U}_{e}\mathbf{S}_{e}\mathbf{V}_{e}^{T}.
-\end{equation}
-can learn for each subspace an internal orthogonal dictionary adaptive to the noisy PGs. For notation simplicity, we ignore the index of subspace $k$.
-
-\begin{equation}\label{equ5}
+\begin{equation}\label{equ6}\vspace{-2mm}
 \begin{split}

### 2016-10-26 CVPR2017_Review_Unified.tex
add

@@
 \vspace{-2mm}
-\begin{equation}\label{equ5}\vspace{-2mm}
+\begin{equation}\label{equ5}\vspace{-1mm}
 P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})},
@@
 
-Now all internal noisy PGs have been assigned to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
-For each subspace, we employ its external orthogonal dictionary $\mathbf{D}_{e}$ to guide the internal orthogonal dictionary learning.
+Now we have assigned all internal noisy PGs to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
+For each subspace, we consider to use the external orthogonal dictionary to guide the learning of an orthogonal dictionary $\mathbf{D}:=[\mathbf{D}_{e}\ \mathbf{D}_{i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
+This dictionary has two parts: the external part $\mathbf{D}_{e}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is consisted of the first ($3p^2-r$) columns of the singular vector matrix $\mathbf{U}_{e}$ obtained from the external prior by Equ.
+(\ref{equ3}), and the internal part $\mathbf{D}_{i}$ is consisted of adaptive dictionary atoms learned from the internal noisy PGs.
 The learning is performed under the sparse coding framework (along with which the denoising of real noisy image is simultaneously done) as follows:
@@
 \end{equation}
-The singular vectors capture the statistical structures of NSS variations in natural images, while the singular values in $\mathbf{S}$ represent the significance of these singular vectors.
-Fig.\ 4 shows the singular vectors for one Gaussian component.
-
 Similar to the K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem \ref{equ4}.
@@
 
-\textbf{Updating Sparse Coefficients}: given the initialization orthogonal dictioanry $\textbf{D}_{i}^{(t)}$, the sparce coefficients 
-$\textbf{A}^{(t)}$ are obtained via solving
-\begin{equation}\label{equ6}
+\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{i}^{(t)}$, we update the sparce coefficients via solving
+\vspace{-2mm}
+\begin{equation}\label{equ7}\vspace{-2mm}
 \textbf{A}^{(t)}:=\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
@@
 
-\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(0)}$, the sparce coefficients 
-$\textbf{A}^{(t)}$ are obtained via solving
-\begin{equation}\label{equ7} 
+\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}$, we update the orthogonal dictionary via solving
+\vspace{-2mm}
+\begin{equation}\label{equ8} \vspace{-2mm}
 \begin{split}
@@
 \end{equation}
-Dividing the sparse coefficients $\mathbf{A}=[\mathbf{A}_{e}^{T}\ \mathbf{A}_{i}^{T}]^{T}$, where $\mathbf{A}_{e}$ and $\mathbf{A}_{i}$ denote the coefficients over external and internal dictionary $\mathbf{D}_{e}$ and $\mathbf{D}_{i}$.
+The sparse coefficients $\mathbf{A}=[\mathbf{A}_{e}^{T}\ \mathbf{A}_{i}^{T}]^{T}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively.
 According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ6})
@@
 the orthogonal matrices obtained by the following SVD
-\begin{equation}\label{equ7}
+\vspace{-2mm}
+\begin{equation}\label{equ9}\vspace{-2mm}
 (\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{T})\mathbf{Y}\mathbf{A}_{i}^{T}
@@
 With these solutions, the final obtained dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ are orthogonal ictionary. This can be proved by the following equation
-\begin{equation}\label{equ8}
+\vspace{-3mm}
+\begin{equation}\label{equ10}\vspace{-3mm}
 \mathbf{D}^{T}\mathbf{D} = 
-\left(\begin{array}{c}
+\left[\begin{array}{c}
 \mathbf{D}_{e}^{T}
@@
 \mathbf{D}_{i}^{T}
-\end{array}\right)
-(\mathbf{D}_{e}\ \mathbf{D}_{i})
+\end{array}\right]
+[\mathbf{D}_{e}\ \mathbf{D}_{i}]
 =
-\left(\begin{array}{cc}
+\left[\begin{array}{cc}
 \mathbf{D}_{e}^{T}\mathbf{D}_{e}\ \mathbf{D}_{e}^{T}\mathbf{D}_{i}
@@
 \mathbf{D}_{i}^{T}\mathbf{D}_{e}\ \mathbf{D}_{i}^{T}\mathbf{D}_{i}
-\end{array}\right)
+\end{array}\right]
 =
@@
 
-\subsection{Discussions on Learning External Priors and Internal Priors}
+\subsection{Discussions}
 Until now, we have divided the noisy PGs into multiple internal subspaces.

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 
-Now we have assigned all internal noisy PGs to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
-For each subspace, we consider to use the external orthogonal dictionary to guide the learning of an orthogonal dictionary $\mathbf{D}:=[\mathbf{D}_{e}\ \mathbf{D}_{i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
+Assume we have assigned all internal noisy PGs to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
+For each subspace, we consider to utilize the external orthogonal dictionary to guide the learning of an orthogonal dictionary $\mathbf{D}:=[\mathbf{D}_{e}\ \mathbf{D}_{i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
 This dictionary has two parts: the external part $\mathbf{D}_{e}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is consisted of the first ($3p^2-r$) columns of the singular vector matrix $\mathbf{U}_{e}$ obtained from the external prior by Equ.
@@
 \end{equation}
-Similar to the K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem \ref{equ4}.
-In fact, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}$ and for $t=0, 1, ..., T-1$, alternatively do:
-
-\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{i}^{(t)}$, we update the sparce coefficients via solving
+Noted that $\mathbf{D}_{e}=\emptyset$ if $r=3p^{2}$ and $\mathbf{D}_{e}=\mathbf{U}_{e}$ if $r=0$. The dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ is orthogonal by checking that:
 \vspace{-2mm}
-\begin{equation}\label{equ7}\vspace{-2mm}
-\textbf{A}^{(t)}:=\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
-\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}.
-\end{equation}
-This problem has closed-form solution by $\mathbf{A}^{*}=T_{\lambda}(\mathbf{\hat{D}}^{T}\mathbf{Y})$, 
-where $T_{\lambda}(\mathbf{A}) = \text{sgn}(\mathbf{A})\odot\max(\mathbf{A},\lambda)$ is a soft-thresholding function.
-
-\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}$, we update the orthogonal dictionary via solving
-\vspace{-2mm}
-\begin{equation}\label{equ8} \vspace{-2mm}
-\begin{split}
-\textbf{D}_{i}^{(t+1)}:=
-&
-\argmin_{\textbf{D}_{i}\in\mathbb{R}^{3p^2\times r}}
-\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}]\mathbf{A}^{(t)}\|_{F}^{2}
-\\
-&
-\text{s.t.}
-\quad
-\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
-\end{split}
-\end{equation}
-The sparse coefficients $\mathbf{A}=[\mathbf{A}_{e}^{T}\ \mathbf{A}_{i}^{T}]^{T}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively.
-According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ6})
-%\begin{equation}
-%\begin{split}
-%\min_{\textbf{D}_{i}\in\mathbb{R}^{3p^2\times r}}
-%&\|\mathbf{Y}-\mathbf{D}_{e}\mathbf{A}_{e}+\mathbf{D}_{i}\mathbf{A}_{i}\|_{F}^{2}
-%\\
-%&
-%\text{s.t.}
-%\quad
-%\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
-%\end{split}
-%\end{equation}
-has a closed-form solution $\mathbf{D}_{i}^{*}=\mathbf{U}\mathbf{V}^{T}$, where $\mathbf{U}$ and $\mathbf{V}$ are
-the orthogonal matrices obtained by the following SVD
-\vspace{-2mm}
-\begin{equation}\label{equ9}\vspace{-2mm}
-(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{T})\mathbf{Y}\mathbf{A}_{i}^{T}
-=
-\mathbf{U}\Sigma\mathbf{V}^{T}
-\end{equation}
-With these solutions, the final obtained dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ are orthogonal ictionary. This can be proved by the following equation
-\vspace{-3mm}
-\begin{equation}\label{equ10}\vspace{-3mm}
+\begin{equation}\label{equ7}\vspace{-1mm}
 \mathbf{D}^{T}\mathbf{D} = 
@@
 
+Similar to K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem (\ref{equ6}).
+Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{e}$ and for $t=0, 1, ..., T-1$, alternatively do:
+\\
+\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{i}^{(t)}$, we update the sparse coefficients via solving
+\vspace{-2mm}
+\begin{equation}\label{equ8}\vspace{-2mm}
+\textbf{A}^{(t)}:=\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
+\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}.
+\end{equation}
+Since dictionary $\mathbf{D}_{t}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problem (\ref{equ8}) has closed-form solution $\mathbf{A}^{(t)}=T_{\lambda}(\mathbf{D}_{t}^{T}\mathbf{Y})$, 
+where $T_{\lambda}(\mathbf{\bullet
+}) = \text{sgn}(\mathbf{\bullet
+})\odot\max(\mathbf{\bullet
+},\lambda)$ is soft-thresholding function and $\odot$ is element-wise product.
+\\
+\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}$, we update the orthogonal dictionary via solving
+\vspace{-2mm}
+\begin{equation}\label{equ9} \vspace{-2mm}
+\begin{split}
+\textbf{D}_{i}^{(t+1)}:=
+&
+\argmin_{\textbf{D}_{i}\in\mathbb{R}^{3p^2\times r}}
+\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}]\mathbf{A}^{(t)}\|_{F}^{2}
+\\
+&
+\text{s.t.}
+\quad
+\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+\end{split}
+\end{equation}
+Here we ignore the index ($t$) for notation simplicity.
+The sparse coefficient matrix $\mathbf{A}=[\mathbf{A}_{e}^{T}\ \mathbf{A}_{i}^{T}]^{T}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively.
+According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ9})
+has a closed-form solution $\mathbf{D}_{i}^{*}=\mathbf{U}_{i}\mathbf{V}_{i}^{T}$, where $\mathbf{U}_{i}$ and $\mathbf{V}_{i}$ are the orthogonal matrices obtained by the following SVD
+\vspace{-2mm}
+\begin{equation}\label{equ10}\vspace{-2mm}
+(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{T})\mathbf{Y}\mathbf{A}_{i}^{T}
+=
+\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{T}
+\end{equation}
+
 \subsection{Discussions}
-Until now, we have divided the noisy PGs into multiple internal subspaces.
 Here we take a deep analysis on how the external NSS prior guide the subspace learning of internal PGs.

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 \subsection{Discussions}
-Here we take a deep analysis on how the external NSS prior guide the subspace learning of internal PGs.
-The help are at least threefold.
-Firstly, through MAP in (\ref{equ3}), the external prior guides the noisy PGs to be clustered into the correct subspaces.
+
+Here we take a detailed analysis on how the external PG prior guide the internal prior learning of given real noisy images.
+The guidance comes from at least aspects.
+Firstly, through MAP in Equ.
+(\ref{equ5}), the external prior guides the noisy PGs to be clustered into the correct subspaces.
 If we cluster the noisy PGs in an automatical way, the subspaces we learned will be highly degraded by the signal dependent noise.
 Secondly, the guidance of external prior for internal clustering is more efficient than directly clustering the internal noisy PGs.
-It only needs to calculate the MAP probability via the equation (\ref{equ3}) while the internal clustering via GMM is time-consuming on EM algorithm \cite{em}.
+It only needs to calculate the MAP probability via the Equ.
+(\ref{equ5}) while the internal clustering via GMM is time-consuming on EM algorithm \cite{em}.
 Thirdly, due to the correct guidance of external prior, the structual decomposition via SVD of each subspace is more adaptive.
 This will bring better denoising performance than the methods only using the external information.
-
 Through SVD, the PGs in each internal subspace can be divided into singular vectors and singular values.
@@
 And the sigular values are adaptive parameters for internal noisy PGs.
-We can compare the singular values of one internal subspace and the corresponding space of external PGs.
-The result is shown in Figure \ref{}.
-From which we can see that the noisy subspace often have higher values than external space consisted of clean PGs.
-This gap is clearly made of the noise and can be used for image denoising in a natural way.
 
@@
 \subsection{Fast Patch Group Searching by Integral Image}
+
 The searching of patch groups in images is inefficient if we search non-local similar patches to each local patch.

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 
-Here we take a detailed analysis on how the external PG prior guide the internal prior learning of given real noisy images.
-The guidance comes from at least aspects.
-Firstly, through MAP in Equ.
-(\ref{equ5}), the external prior guides the noisy PGs to be clustered into the correct subspaces.
-If we cluster the noisy PGs in an automatical way, the subspaces we learned will be highly degraded by the signal dependent noise.
-Secondly, the guidance of external prior for internal clustering is more efficient than directly clustering the internal noisy PGs.
-It only needs to calculate the MAP probability via the Equ.
-(\ref{equ5}) while the internal clustering via GMM is time-consuming on EM algorithm \cite{em}.
-Thirdly, due to the correct guidance of external prior, the structual decomposition via SVD of each subspace is more adaptive.
-This will bring better denoising performance than the methods only using the external information.
-Through SVD, the PGs in each internal subspace can be divided into singular vectors and singular values.
-The singular vectors are the basis of the corresponding subspace while the singular values reflect the importance of these basis.
-The basis can be used as dictionary to code the noisy PGs.
-And the sigular values are adaptive parameters for internal noisy PGs.
+Here we take a detailed analysis on the guiance of the external patch group (PG) prior for the internal noisy PGs of given real noisy images.
+The guidance comes from at least three aspects: 1) the external prior guides the internal PGs to be clustered into suitable subspaces through MAP in Equ.
+(\ref{equ5}).
+The guided subspace clustering is more efficient than directly clustering the internal noisy PGs via k-means or Gaussian Mixture Model (GMM).
+The reason is, by guidance we only need calculate the probabilities via Equ.
+(\ref{equ5}) for all noisy PGs while by internal clustering via GMM we need perform EM algorithm \cite{em}.
+2) under the guidance of external orthogonal dictionary, the learned internal dictioary are also orthogonal and more adaptive to the given noisy images.
+This makes the learning process very efficient.
+Besides, the learned orthogonal dictionary can also makes the denoising process very efficient.
+3) the singular values obtained by SVD in Equ.
+(\ref{equ3}) reflect the prior importance of the atoms in learned dictionary and hence can be used as adaptive parameters in the sparse coding framework for real image denoising.
 

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 (\ref{equ5}) for all noisy PGs while by internal clustering via GMM we need perform EM algorithm \cite{em}.
-2) under the guidance of external orthogonal dictionary, the learned internal dictioary are also orthogonal and more adaptive to the given noisy images.
-This makes the learning process very efficient.
-Besides, the learned orthogonal dictionary can also makes the denoising process very efficient.
+2) the external dictionary guides the internal dictionary learning, and the obtained dictionary consisted of the two parts is orthogonal and more adaptive to the given noisy image.
+The learning process has closed-form solutions and hence is very efficient.
+Besides, the learned orthogonal dictionary also makes the denoising process very efficient under sparse coding framework.
 3) the singular values obtained by SVD in Equ.
-(\ref{equ3}) reflect the prior importance of the atoms in learned dictionary and hence can be used as adaptive parameters in the sparse coding framework for real image denoising.
+(\ref{equ3}) reflect the prior weights of the atoms in learned dictionary and can be used as adaptive parameters for real image denoising.
 

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 \section{The Denoising Algorithm}
-\subsection{Fast Patch Group Searching by Integral Image}
+\subsection{Fast Internal Patch Group Searching}
 
-The searching of patch groups in images is inefficient if we search non-local similar patches to each local patch.
-To speed up the searching process and make our proposed method faster, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching.
+Given a RGB image of size $256\times256\times3$, we can extract over 60 thousands local patches of size $6\times6\times3$.
+It is time-consumming to search patch groups (PG) for local patches one by one.
+To speed up the searching process, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching.
 The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size.
-That is to say, we do not need do distance measure for each patch.
-It was first proposed under the name of summed area table\cite{viola2004robust}
+Hence, we do not need do distance measure for each local patch.
 
 \subsection{Prior Weights for Sparse Coding}
+
 To remove the real noise, we employ the sparse coding framework.

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 \section{The Denoising Algorithm}
+
+In this work, we solve the real noisy image denoising problem by employing the sparse coding framework \cite{pgpd} in Equ.
+(\ref{equ6}).
+We utilize two strategies to gain better performance: one is the 'Summed Area Table' \cite{sat} for faster patch group (PG) searching and the other is that the prior weights in Equ.
+(\ref{equ3}) are used for better denoising effects.
+
 \subsection{Fast Internal Patch Group Searching}
@@
 \subsection{Prior Weights for Sparse Coding}
-
-To remove the real noise, we employ the sparse coding framework.
-And in order to be adaptive to the input image, we employ the internal learned $\mathbf{U}$ of each cluster as an adaptive dictioanry to represent the structural variations of the PGs in that cluster.
-Since the $\mathbf{U}$ is orthonormal, its \emph{mutual incoherence} is naturally $0$ and therefore better than other redundant dictionaries.
 
@@
 
+\begin{figure*}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_5dmark3_iso3200_1_real.png}}
+{\footnotesize (a) Noisy Image \\ (37.00dB/0.9345) }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
+{\footnotesize (b) CBM3D \\ (37.02dB/0.9351)}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_5dmark3_iso3200_1_real.png}}
+{\footnotesize (c) WNNM \\ (37.01dB/0.9347)}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_5dmark3_iso3200_1_real.png}}
+{\footnotesize (d) MLP \\ (33.90dB/0.9171) }
+\end{minipage}
+\centering
+\begin{minipage}[t]{0.195\textwidth}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
+{\footnotesize (e) TRD \\ (36.18dB/0.9454)   }
+\end{minipage}
+}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
+{\footnotesize (f) Noise Clinic \\ (38.76dB/0.9689) }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
+{\footnotesize (g) Neat Image \\ (37.68dB/0.9600) }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
+{\footnotesize (h) CCNoise \\ (38.37dB/0.9678) }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
+{\footnotesize (i) Guided \\ (\textbf{40.26}dB/\textbf{0.9800})}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_5dmark3_iso3200_1_real.png}}
+{\footnotesize (j) Mean Image}
+\end{minipage}
+}
+\caption{Denoised images of the image "Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
+\label{fig3}
+\end{figure*}
+
 \subsection{Comparison With other Competing Methods}
@@
 \subfigure{
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_5dmark3_iso3200_1_real.png}}
-{\footnotesize (a) Noisy Image \\ (37.00dB/0.9345) }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
-{\footnotesize (b) CBM3D \\ (37.02dB/0.9351)}
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_5dmark3_iso3200_1_real.png}}
-{\footnotesize (c) WNNM \\ (37.01dB/0.9347)}
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_5dmark3_iso3200_1_real.png}}
-{\footnotesize (d) MLP \\ (33.90dB/0.9171) }
-\end{minipage}
-\centering
-\begin{minipage}[t]{0.195\textwidth}
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
-{\footnotesize (e) TRD \\ (36.18dB/0.9454)   }
-\end{minipage}
-}
-\subfigure{
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
-{\footnotesize (f) Noise Clinic \\ (38.76dB/0.9689) }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
-{\footnotesize (g) Neat Image \\ (37.68dB/0.9600) }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
-{\footnotesize (h) CCNoise \\ (38.37dB/0.9678) }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
-{\footnotesize (i) Guided \\ (\textbf{40.26}dB/\textbf{0.9800})}
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_5dmark3_iso3200_1_real.png}}
-{\footnotesize (j) Mean Image}
-\end{minipage}
-}
-\caption{Denoised images of the image "Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
-\label{fig3}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\subfigure{
 \begin{minipage}[t]{0.244\textwidth}
@@
 
-\subsection{Discussion on Parameter $\lambda$}
-The proposed method only has a key parameter, namely the regularization paramters $\lambda$.
+%\subsection{Discussion on Parameter $\lambda$}
+%The proposed method only has a key parameter, namely the regularization paramters $\lambda$.
 To demonstrate that the proposed method is robust to the variance of $\lambda$, we vary the parameter $\lambda$ across a wide range and obtain the PSNR and SSIM results as a function of the parameter $\lambda$.
@@
 This shows that the proposed method is indeed robust to the chosen of the paramter $\lambda$.
-\begin{figure}
-\includegraphics[width=1\linewidth]{images/param.png}
-\caption{The PSNR/SSIM results as a function of the parameter $\lambda$.}
-\label{fig10}
-\end{figure}
+%\begin{figure}
+%\includegraphics[width=1\linewidth]{images/param.png}
+%\caption{The PSNR/SSIM results as a function of the parameter $\lambda$.}
+%\label{fig10}
+%\end{figure}
 

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 \begin{equation}\label{equ3}\vspace{-2mm}
-\mathbf{\Sigma}=\mathbf{U}_{e}\mathbf{S}_{e}\mathbf{V}_{e}^{T}.
+\mathbf{\Sigma}=\mathbf{U}_{e}\mathbf{S}_{e}\mathbf{U}_{e}^{T}.
 \end{equation}
@@
 \end{equation}
-Since dictionary $\mathbf{D}_{t}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problem (\ref{equ8}) has closed-form solution $\mathbf{A}^{(t)}=T_{\lambda}(\mathbf{D}_{t}^{T}\mathbf{Y})$, 
-where $T_{\lambda}(\mathbf{\bullet
-}) = \text{sgn}(\mathbf{\bullet
-})\odot\max(\mathbf{\bullet
-},\lambda)$ is soft-thresholding function and $\odot$ is element-wise product.
+Since dictionary $\mathbf{D}_{t}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problem (\ref{equ8}) has closed-form solution $\mathbf{A}^{(t)}=T_{\lambda}(\mathbf{D}_{t}^{T}\mathbf{Y})$, where $T_{\lambda}$ is the soft-thresholding function \cite{softthresholding} (we will give explicit solution in next section).
+%where $T_{\lambda}(\mathbf{\bullet
+%}) = \text{sgn}(\mathbf{\bullet
+%})\odot\max(\mathbf{\bullet
+%},\lambda)$ is soft-thresholding function and $\odot$ is element-wise product.
 \\
@@
 
-\subsection{Prior Weights for Sparse Coding}
+\subsection{Prior Weights for Weighted Sparse Coding}
 
-\begin{equation}\label{equ10}
-\min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{\overline{y}}_{m}-\mathbf{U}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{3p^{2}}\lambda_{i}|\boldsymbol{\upalpha}_{i}|.
+Under the sparse coding framework \cite{ksvd} in Equ.
+(\ref{equ6}), the dictionary atoms are treated equally for each subspace.
+This ignores the external weight prior learned from clean images.
+The singular values in the diagonal of $\mathbf{S}_{e}$ (Equ.
+(\ref{equ3})) reflect the significance of the singular vectors in $\mathbf{U}_{e}$.
+Therefore, similar to \cite{pgpd}, we employ a weighted sparse coding framework for real noisy image denoising problem.
+Given a real noisy image, we extract the internal PGs  from it and assign the noisy PGs into different subspaces via Equ.
+(\ref{equ5}).
+For each subspace, the learned orthogonal dictionary is denoted as $\mathbf{D}=[\mathbf{D}_{e}\ \mathbf{D}_{i}]$, and the PGs in this subspace is denoted as $\mathbf{Y}$.
+We employ the square root of singular values in $\mathbf{S}_{e}$ as the weight prior.
+For each column $\mathbf{y}$ of the noisy PG $\mathbf{Y}$, its sparse coefficients on dictionary $\mathbf{D}$ is obtained by solving
+\vspace{-2mm}
+\begin{equation}\label{equ11}\vspace{-2mm}
+\hat{\boldsymbol{\upalpha}}:=\arg\min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{y}-\mathbf{D}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{3p^{2}}\lambda_{i}|\boldsymbol{\upalpha}_{i}|,
 \end{equation}
-The $i$th entry of the regularization parameter $\lambda_{i}$ 
-\begin{equation}\label{equ11}
-\lambda_{i} = \lambda/(\mathbf{S}_{i}+\varepsilon),
+where $\lambda_{i}$ is the $i$th regularization parameter defined as
+\vspace{-2mm}
+\begin{equation}\label{equ12}\vspace{-2mm}
+\lambda_{i} = \lambda/(\sqrt{\mathbf{S}_{i}}+\varepsilon).
 \end{equation}
-where $\varepsilon$ is a small positive number to avoid dividing by zero.
-Since the dictionary $\mathbf{U}$ is orthonormal, it is not difficult to find out that (\ref{equ4}) has a closed-form solution (detailed derivation can be found in the supplementary material):
-\begin{equation}\label{equ12}
-\setlength{\abovedisplayskip}{3pt}
-\setlength{\belowdisplayskip}{4pt}
-\hat{\boldsymbol{\upalpha}}= \text{sgn}(\mathbf{U^{T}\overline{y}}_{m})\odot \text{max}(|\mathbf{U^{T}\overline{y}}_{m}|-\mathbf{\Lambda},\mathbf{0}),
+We add a small positive number $\varepsilon$ to avoid zero denominator. Since the learned dictionary $\mathbf{D}$ is orthonormal, the Equ. (\ref{equ11}) also has a closed-form solution \cite{pgpd} 
+\vspace{-2mm}
+\begin{equation}\label{equ13}\vspace{-2mm}
+\hat{\boldsymbol{\upalpha}}= \text{sgn}(\mathbf{D}^{T}\mathbf{y})\odot \text{max}(|\mathbf{D}^{T}\mathbf{y}|-\mathbf{\Lambda},\mathbf{0}),
 \end{equation}
-where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication, and $|\mathbf{U^{T}\overline{y}}_{m}|$ is the absolute value of each entry of vector $|\mathbf{U^{T}\overline{y}}_{m}|$.
-The closed-form solution makes our weighted sparse coding process very efficient.
-
-%\subsection{Effectively dealing with different noisy images}
-%For real image denoising, we can perform well on images which have similar noise levels with the training dataset.
-How can we deal with the real noisy images whose noise levels are higher than the training dataset?
-The answer is to remove the noise by more iterations.
-The input image of each iteration is the recovered image of previous iteration.
-This makes sense since we can still view the recovered image as a real noisy image.
-
-%This will also bring a second problem, that how we could automatically terminate the iteration.
-This can be solved by two methods.
-One way is to compare the images between two iterations and calculate their difference, the iteration can be terminated if the difference is smaller than a threshold.
-The other way is to estimate the noise level of the current image and terminate the iterations when the noise level is lower than a preset threshold.
-We employ the second way and set the threshold as 0.002 in our experiments.
-In fact, most of our testing images will be denoised well in one iteration.
-
-%\subsection{Efficient Model Selection by Gating Network}
-%In the Gaussian component selection procedure, if we employ the full posterior estimation, the speed is not fast. Our algorithm can be speeded up by introducing the Gating network model.
+where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication, and $|\mathbf{D}^{T}\mathbf{y}|$ is the absolute value of each entry of vector $|\mathbf{D}^{T}\mathbf{y}|$.
+The closed-form solution makes our denoising process very efficient.
 
 \subsection{The Overall Algorithm}
-With the solution $\hat{\boldsymbol{\upalpha}}$ in (\ref{equ7}), the clean patch in a PG can be estimated as $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$.
-Then the clean image $\hat{\mathbf{x}}$ can be reconstructed by aggregating all the estimated PGs.
-In practice, we could perform the above denoising procedures for several iterations for better denoising outputs.
-In iteration $t$, we use the iterative regularization strategy \cite{osher2005iterative} to add back to the recovered image $\hat{\mathbf{x}}^{(t-1)}$ some estimation residual in iteration $t-1$.
-The proposed denoising algorithm is summarized in Algorithm 1 (Alg.
-1).
+
+With the solution $\hat{\boldsymbol{\upalpha}}$ in (\ref{equ13}), each column of the PG $\mathbf{Y}$ can be estimated as $\hat{\mathbf{y}}=\mathbf{D}\hat{\boldsymbol{\upalpha}}$.
+Then we add back its PG mean denoted as $\boldsymbol{\upmu}_{y}$ and reconstruct the clean image $\hat{\mathbf{x}}$ by aggregating all the estimated PGs.
+Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs.
+But different from \cite{pgpd}, we do not employ the iterative regularization strategy \cite{osher2005iterative} since it is not effective in our method.
+The proposed denoising algorithm is summarized in Algorithm 1.
 \begin{table}
@@
 The second and third dataset do not have ground truth images.
-\begin{figure}[t]
-\centering
-\subfigure{
-\begin{minipage}{0.15\textwidth}
-\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Canon_EOS_5D_Mark3_ISO_3200_C3.png}
-\end{minipage}
-\begin{minipage}{0.15\textwidth}
-\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Nikon_D600_ISO_3200_C1.png}
-\end{minipage}
-\begin{minipage}{0.15\textwidth}
-\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Nikon_D800_ISO_1600_B2.png}
-\end{minipage}
-}\vspace{-0.14in}
-\subfigure{
-\begin{minipage}{0.15\textwidth}
-\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Nikon_D800_ISO_3200_A1.png}
-\end{minipage}
-\begin{minipage}{0.15\textwidth}
-\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Nikon_D800_ISO_3200_A5.png}
-\end{minipage}
-\begin{minipage}{0.15\textwidth}
-\includegraphics[width=1\textwidth]{images/resize_CC_Mean_Nikon_D800_ISO_6400_B1.png}
-\end{minipage}
-}
-\caption{Some testing images in the dataset \cite{crosschannel2016}.}
-\label{fig5}
-\end{figure}
 

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 \usepackage{color}
+\usepackage{bm}
 \DeclareMathOperator*{\argmin}{arg\,min}
@@
 Now, we have clustered the PGs extracted from external clean images into $K$ Gaussians or subspaces.
-For notation simplicity, we ignore the index of subspace $k$.
 To better characterize each subspace, we perform singular value decomposition (SVD) on the covariance matrix:
@@
 \begin{equation}\label{equ3}\vspace{-2mm}
-\mathbf{\Sigma}=\mathbf{U}_{e}\mathbf{S}_{e}\mathbf{U}_{e}^{T}.
+\mathbf{\Sigma}_{k}=\mathbf{U}_{k}\mathbf{S}_{k}\mathbf{U}_{k}^{T}.
 \end{equation}
-The singular vectors in $\mathbf{U}_{e}$ are employed as the external orthogonal dictionary to guide the internal orthogonal dictionary learning (the singular values are employed as prior weights for sparse coding which will be discussed in Section 4).
-For a dictionary $\mathbf{D}$, its \emph{mutual incoherence} $\mu(\mathbf{D})$ \cite{donoho2003optimally} difined by
-\vspace{-2mm}
-\begin{equation}\label{equ4}
-\vspace{-2mm}
-\mu(\mathbf{D})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}}
-\end{equation} 
-is a measure of quality of dictionary (lower is better). The dictionary $\mathbf{U}_{e}$ always has $0$
-\emph{mutual incoherence} and hence better quality than non-orthogonal dictionaries.
+The singular vector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ are employed as the external orthogonal dictionary to guide the internal dictionary learning.
+The singular values in the diagonal of $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$ and utilized as prior weights for weighted sparse coding which will be discussed in next section.
 
@@
 \vspace{-2mm}
-\begin{equation}\label{equ5}\vspace{-1mm}
+\begin{equation}\label{equ4}\vspace{-1mm}
 P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})},
@@
 Assume we have assigned all internal noisy PGs to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
-For each subspace, we consider to utilize the external orthogonal dictionary to guide the learning of an orthogonal dictionary $\mathbf{D}:=[\mathbf{D}_{e}\ \mathbf{D}_{i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
-This dictionary has two parts: the external part $\mathbf{D}_{e}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is consisted of the first ($3p^2-r$) columns of the singular vector matrix $\mathbf{U}_{e}$ obtained from the external prior by Equ.
-(\ref{equ3}), and the internal part $\mathbf{D}_{i}$ is consisted of adaptive dictionary atoms learned from the internal noisy PGs.
-The learning is performed under the sparse coding framework (along with which the denoising of real noisy image is simultaneously done) as follows:
+For noisy PGs $\mathbf{Y}=[\mathbf{y}_{1},...,\mathbf{y}_{N_{k}}]$ in the $k$-th subspace, we consider to utilize the external orthogonal dictionary to guide the learning of an orthogonal dictionary $\mathbf{D}_{k}:=[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
+This dictionary has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is obtained from the external prior by Equ.
+(\ref{equ3}), and the internal part $\mathbf{D}_{k,i}$ is consisted of adaptive dictionary atoms learned from the internal noisy PGs.
+The learning and denoising are simultaneously performed under the proposed reweighted sparse coding framework as f(for notation simplicity, we ignore the subspace index $k$):
 \vspace{-2mm}
-\begin{equation}\label{equ6}\vspace{-2mm}
+\begin{equation}\label{equ5}\vspace{-2mm}
 \begin{split}
-&\min_{\mathbf{D}_{i}\in \mathbb{R}^{3p^2\times r},\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
-\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}
+&\min_{\mathbf{D}_{i},\{\bm{\alpha}_{n}\}}
+\sum_{n=1}^{N}(\|\mathbf{y}_{n}-\mathbf{D}\bm{\alpha}_{n}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,j}|)
 \\
@@
 \quad
-\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+\mathbf{D}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
 \end{split}
 \end{equation}
-Noted that $\mathbf{D}_{e}=\emptyset$ if $r=3p^{2}$ and $\mathbf{D}_{e}=\mathbf{U}_{e}$ if $r=0$. The dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ is orthogonal by checking that:
+where $\lambda_{j}$ is the $j$-th regularization parameter defined as
+\vspace{-2mm}
+\begin{equation}\label{equ6}\vspace{-2mm}
+\lambda_{j} = \lambda/(\sqrt{\mathbf{S}_{j}}+\varepsilon).
+\end{equation}
+We employ square roots of the singular values in $\mathbf{S}$ (please refer Equ.
+(\ref{equ3})) as external prior weights and add a small positive number $\varepsilon$ to avoid zero denominator.
+Noted that $\mathbf{D}_{e}=\emptyset$ if $r=3p^{2}$ and $\mathbf{D}_{e}=\mathbf{U}_{k}$ if $r=0$.
+The dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ is orthogonal by checking that:
 \vspace{-2mm}
@@
 
-Similar to K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem (\ref{equ6}).
-Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{e}$ and for $t=0, 1, ..., T-1$, alternatively do:
+Similar to K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem (\ref{equ5}).
+Specifically, we initialize the orthogonal dictionary as $\mathbf{D}_{(0)}=\mathbf{U}_{k}$ and for $t=0, 1, ..., T-1$, alternatively do:
 \\
-\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{i}^{(t)}$, we update the sparse coefficients via solving
+\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{(t)}$, we update the sparse coefficients via solving
 \vspace{-2mm}
 \begin{equation}\label{equ8}\vspace{-2mm}
-\textbf{A}^{(t)}:=\argmin_{\textbf{A}\in\mathbb{R}^{3p^2\times MN}}
-\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}.
-\end{equation}
-Since dictionary $\mathbf{D}_{t}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problem (\ref{equ8}) has closed-form solution $\mathbf{A}^{(t)}=T_{\lambda}(\mathbf{D}_{t}^{T}\mathbf{Y})$, where $T_{\lambda}$ is the soft-thresholding function \cite{softthresholding} (we will give explicit solution in next section).
-%where $T_{\lambda}(\mathbf{\bullet
-%}) = \text{sgn}(\mathbf{\bullet
-%})\odot\max(\mathbf{\bullet
-%},\lambda)$ is soft-thresholding function and $\odot$ is element-wise product.
-\\
-\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}$, we update the orthogonal dictionary via solving
-\vspace{-2mm}
-\begin{equation}\label{equ9} \vspace{-2mm}
 \begin{split}
-\textbf{D}_{i}^{(t+1)}:=
-&
-\argmin_{\textbf{D}_{i}\in\mathbb{R}^{3p^2\times r}}
-\|\mathbf{Y}-[\mathbf{D}_{e}\ \mathbf{D}_{i}]\mathbf{A}^{(t)}\|_{F}^{2}
+&\bm{\alpha}_{n}^{(t)}:=\argmin_{\bm{\alpha}_{n}\in\mathbb{R}^{3p^2\times 1}}
+\|\mathbf{y}_{m}-\mathbf{D}_{(t)}\bm{\alpha}_{n}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,j}|
 \\
@@
 \quad
-\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
 \end{split}
 \end{equation}
-Here we ignore the index ($t$) for notation simplicity.
+Since dictionary $\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problems (\ref{equ8}) has a closed-form solution \cite{pgpd} 
+\vspace{-2mm}
+\begin{equation}\label{equ9}\vspace{-2mm}
+\hat{\bm{\alpha}}_{n}= \text{sgn}(\mathbf{D}_{(t)}^{T}\mathbf{y}_{n})\odot \text{max}(|\mathbf{D}_{(t)}^{T}\mathbf{y}_{n}|-\mathbf{\Lambda},\mathbf{0}),
+\end{equation}
+where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.
+\\
+\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}=[\bm{\alpha}_{1}^{(t)},...,\bm{\alpha}_{N}^{(t)}]$, we update the internal orthogonal dictionary via solving
+\vspace{-2mm}
+\begin{equation}\label{equ10} \vspace{-2mm}
+\begin{split}
+\textbf{D}_{i}^{(t+1)}
+:
+&
+=
+\argmin_{\textbf{D}_{i}}
+\sum_{n=1}^{N}(\|\mathbf{y}_{n}-\mathbf{D}\bm{\alpha}_{n}^{(t)}\|_{2}^{2})
+\\
+&
+=
+\argmin_{\textbf{D}_{i}}
+\|\mathbf{Y}-\mathbf{D}\mathbf{A}^{(t)}\|_{F}^{2}
+\\
+\text{s.t.}
+\quad
+\mathbf{D}
+&
+=
+[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+\end{split}
+\end{equation}
+Here we ignore the index $t$ for notation simplicity.
 The sparse coefficient matrix $\mathbf{A}=[\mathbf{A}_{e}^{T}\ \mathbf{A}_{i}^{T}]^{T}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively.
@@
 \vspace{-2mm}
-\begin{equation}\label{equ10}\vspace{-2mm}
+\begin{equation}\label{equ11}\vspace{-2mm}
 (\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{T})\mathbf{Y}\mathbf{A}_{i}^{T}
@@
 
-\subsection{Prior Weights for Weighted Sparse Coding}
-
-Under the sparse coding framework \cite{ksvd} in Equ.
-(\ref{equ6}), the dictionary atoms are treated equally for each subspace.
-This ignores the external weight prior learned from clean images.
-The singular values in the diagonal of $\mathbf{S}_{e}$ (Equ.
-(\ref{equ3})) reflect the significance of the singular vectors in $\mathbf{U}_{e}$.
-Therefore, similar to \cite{pgpd}, we employ a weighted sparse coding framework for real noisy image denoising problem.
-Given a real noisy image, we extract the internal PGs  from it and assign the noisy PGs into different subspaces via Equ.
-(\ref{equ5}).
-For each subspace, the learned orthogonal dictionary is denoted as $\mathbf{D}=[\mathbf{D}_{e}\ \mathbf{D}_{i}]$, and the PGs in this subspace is denoted as $\mathbf{Y}$.
-We employ the square root of singular values in $\mathbf{S}_{e}$ as the weight prior.
-For each column $\mathbf{y}$ of the noisy PG $\mathbf{Y}$, its sparse coefficients on dictionary $\mathbf{D}$ is obtained by solving
-\vspace{-2mm}
-\begin{equation}\label{equ11}\vspace{-2mm}
-\hat{\boldsymbol{\upalpha}}:=\arg\min\nolimits_{\boldsymbol{\upalpha}}\|\mathbf{y}-\mathbf{D}\boldsymbol{\upalpha}\|_{2}^{2}+\sum_{i=1}^{3p^{2}}\lambda_{i}|\boldsymbol{\upalpha}_{i}|,
-\end{equation}
-where $\lambda_{i}$ is the $i$th regularization parameter defined as
-\vspace{-2mm}
-\begin{equation}\label{equ12}\vspace{-2mm}
-\lambda_{i} = \lambda/(\sqrt{\mathbf{S}_{i}}+\varepsilon).
-\end{equation}
-We add a small positive number $\varepsilon$ to avoid zero denominator. Since the learned dictionary $\mathbf{D}$ is orthonormal, the Equ. (\ref{equ11}) also has a closed-form solution \cite{pgpd} 
-\vspace{-2mm}
-\begin{equation}\label{equ13}\vspace{-2mm}
-\hat{\boldsymbol{\upalpha}}= \text{sgn}(\mathbf{D}^{T}\mathbf{y})\odot \text{max}(|\mathbf{D}^{T}\mathbf{y}|-\mathbf{\Lambda},\mathbf{0}),
-\end{equation}
-where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication, and $|\mathbf{D}^{T}\mathbf{y}|$ is the absolute value of each entry of vector $|\mathbf{D}^{T}\mathbf{y}|$.
-The closed-form solution makes our denoising process very efficient.
-
 \subsection{The Overall Algorithm}
@@
 \hline
-\textbf{Alg. 1}: External Prior Guided Internal Orthogonal 
+\textbf{Alg. 1}: External PG Prior Guided Internal PG Prior
 \\
-\quad \quad \quad Dictionary Learning for Denoising
+\quad \quad \quad Learning for Real Image Denoising
 \\
 \hline
-\textbf{Input:} Noisy image $\mathbf{y}$, PG-GMM model
+\textbf{Input:} Noisy image $\mathbf{y}$, external prior GMM model
 \\
-1. Initialization: $\hat{\mathbf{x}}^{(0)}=\mathbf{y},\mathbf{y}^{(0)}=\mathbf{y}$;
+\textbf{Output:} The denoised image $\hat{\mathbf{x}}$.
+\\
+\textbf{Initialization:} $\hat{\mathbf{x}}^{(0)}=\mathbf{y}$;
 \\
@@
 \\
-\quad\textbf{for} each PG $\mathbf{Y}$ \textbf{do}
+\quad\textbf{for} each PG $\mathbf{Y}_{n}$ \textbf{do}
 \\
-2.\quad Calculate group mean $\boldsymbol{\upmu}_{y}$ and form PG $\mathbf{\overline{Y}}$;
+2.\quad Calculate group mean $\boldsymbol{\upmu}_{n}$ and form PG $\mathbf{\overline{Y}}_{n}$;
 \\
-3.\quad Gaussian component selection via (\ref{equ3});
+3.\quad Gaussian component selection via Equ. (\ref{equ5});
 \\
@@
 \\
-\textbf{Output:} The recovered image $\hat{\mathbf{x}}^{(IteNum)}$.\\
 \hline

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 
-The rest of this paper will be summerized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model; in Section 4, we formulate the overall image denoising algorithm; in Section 4, we demonstrate extensive experiments on real image denoising probelm; in Section 5, we conclude our paper and give future work.
+The rest of this paper will be summerized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model and formulate the overall image denoising algorithm; in Section 3, we demonstrate extensive experiments on real image denoising probelm; in Section 4, we conclude our paper and give future work.
 
 \section{Related Work}
+
+\begin{figure*}\label{fig2}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (a) Noisy Image \\ (34.66dB/0.9178)   }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (h) Offline \\ (34.97dB/0.9441) }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (i) Online \\ (36.86dB/0.9622) }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (j) Guided \\ (\textbf{37.09}dB/\textbf{0.9638})}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (h) Mean Image }
+\end{minipage}
+}
+\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
+\end{figure*}
+
 \subsection{Patch Group Prior of Natural Images}
@@
 
-\section{External Patch Group Prior Guided Internal Prior Learning}
+\section{External Patch Group Prior Guided Internal Prior Learning for Image Denoising}
 
-In this section, we formulate the framework of external patch group (PG) prior guided internal orthogonal dictionary learning.
-We first introduce the patch PG leaning on clean natural RGB images.
-Then we propose to exploy the external PG prior to guide the internal clustering and orthogonal dictionary learning (DL).
-The orthogonal DL has alternative closed-form solutions in term of updating sparse coefficients and dictionary.
-Finally, we discuss the advantages of our proposed external PG prior guided internal orthogonal dictionary learning algorithm.
+\begin{figure*}\label{fig3}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (a) Noisy Image \\ (36.15dB/0.9523)    }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (h) Offline \\ (37.12dB/0.9776) }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (i) Online \\ (35.70dB/0.9755)  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (j) Guided \\ (\textbf{37.94}dB/\textbf{0.9804})}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (h) Mean Image }
+\end{minipage}
+}
+\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
+\end{figure*}
+
+In this section, we formulate the framework of external patch group (PG) prior guided internal prior learning.
+We first introduce the external PG prior leaning on natural clean RGB images.
+Then we propose to employ the learned external PG prior to guide the internal prior (subspace selection and dictionary learning (DL)) learning of given degraded (such as noisy) images.
+Under the weighted sparse coding framework, the internal prior learning process has alternative closed-form solutions in term of updating sparse coefficients and orthogonal dictionary.
+Finally, we discuss in details how external prior learned from natural clean images guide the internal prior learning of given degraded (noisy) images.
 
@@
 \begin{equation}\label{equ3}\vspace{-2mm}
-\mathbf{\Sigma}_{k}=\mathbf{U}_{k}\mathbf{S}_{k}\mathbf{U}_{k}^{T}.
+\mathbf{\Sigma}_{k}=\mathbf{U}_{k}\mathbf{S}_{k}\mathbf{U}_{k}^{\top}.
 \end{equation}
@@
 
-Given a real noisy image, we extract the noisy PGs and corresponding mean vectors.
-Each mean substracted PG is defined as $\mathbf{\overline{Y}}\triangleq \{\mathbf{\overline{x}}_{m}\}_{m=1}^{M}$.
-Noted that, different from the external PGs, the mean vectors of the internal noisy PGs are saved for recovering.
-For adaptivity, we project the PG $\mathbf{\overline{Y}}$ into its most suitable Gaussian component (subspace) of the GMM learned on external PGs.
-The subspace most suitable for $\mathbf{\overline{Y}}$ is selected by firstly calculating the posterior probability of "$\mathbf{\overline{Y}}$ belonging to the $k$th Gaussian component":
+Given a real noisy image, assume we can totally extract $N$ local patches from it.
+Similar to the external prior learning stage, for the $n$-th local patch ($n=1,...,N$), we extract its similar patches around it to form a noisy PG denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.
+Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is calculated and subtracted from each patch, leading to the mean subtracted PG $\mathbf{\overline{Y}}_{n}$.
+Each mean substracted PG is defined as $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$ where $\mathbf{\overline{y}}_{n,m}=\mathbf{y}_{n,m}-\bm{\mu}_{n}$.
+For adaptivity, we project the PG $\mathbf{\overline{Y}}_{n}$ into its most suitable Gaussian component (subspace) of the GMM learned on external PGs.
+The subspace most suitable for $\mathbf{\overline{Y}}_{n}$ is selected by firstly calculating the posterior probability of "$\mathbf{\overline{Y}}_{n}$ belonging to the $k$th Gaussian component":
 \vspace{-2mm}
 \begin{equation}\label{equ4}\vspace{-1mm}
-P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})},
+P(k|\mathbf{\overline{Y}}_{n})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{l})},
 \end{equation}
-and then choosing the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}})$.
+and then choosing the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}}_{n})$.
 
@@
 
-Assume we have assigned all internal noisy PGs to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
-For noisy PGs $\mathbf{Y}=[\mathbf{y}_{1},...,\mathbf{y}_{N_{k}}]$ in the $k$-th subspace, we consider to utilize the external orthogonal dictionary to guide the learning of an orthogonal dictionary $\mathbf{D}_{k}:=[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
-This dictionary has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is obtained from the external prior by Equ.
-(\ref{equ3}), and the internal part $\mathbf{D}_{k,i}$ is consisted of adaptive dictionary atoms learned from the internal noisy PGs.
+Assume we have assigned all internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
+Assume $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ are the noisy PGs assigned to the $k$-th subspace, such that $\sum_{k=1}^{K}N_{k}=N$ and $\sum_{k=1}^{K}\sum_{n=1}^{N_{k}}k_{n}=NM$, we have that $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{y}_{k_{n},1},...,\mathbf{y}_{k_{n},M}]$.
+We consider to utilize the external orthogonal dictionary $\mathbf{U}_{k}$ to guide the learning of an orthogonal dictionary $\mathbf{D}_{k}:=[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
+This dictionary has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary in Equ.
+(\ref{equ3}), and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\mathbf{Y}_{k}$.
 The learning and denoising are simultaneously performed under the proposed reweighted sparse coding framework as f(for notation simplicity, we ignore the subspace index $k$):
@@
 \quad
-\mathbf{D}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+\mathbf{D}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
 \end{split}
@@
 \begin{equation}\label{equ7}\vspace{-1mm}
-\mathbf{D}^{T}\mathbf{D} = 
+\mathbf{D}^{\top}\mathbf{D} = 
 \left[\begin{array}{c}
-\mathbf{D}_{e}^{T}
+\mathbf{D}_{e}^{\top}
 \\
-\mathbf{D}_{i}^{T}
+\mathbf{D}_{i}^{\top}
 \end{array}\right]
@@
 \left[\begin{array}{cc}
-\mathbf{D}_{e}^{T}\mathbf{D}_{e}\ \mathbf{D}_{e}^{T}\mathbf{D}_{i}
+\mathbf{D}_{e}^{\top}\mathbf{D}_{e}\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i}
 \\
-\mathbf{D}_{i}^{T}\mathbf{D}_{e}\ \mathbf{D}_{i}^{T}\mathbf{D}_{i}
+\mathbf{D}_{i}^{\top}\mathbf{D}_{e}\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i}
 \end{array}\right]
@@
 &\bm{\alpha}_{n}^{(t)}:=\argmin_{\bm{\alpha}_{n}\in\mathbb{R}^{3p^2\times 1}}
-\|\mathbf{y}_{m}-\mathbf{D}_{(t)}\bm{\alpha}_{n}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,j}|
+\|\mathbf{y}_{n}-\mathbf{D}_{(t)}\bm{\alpha}_{n}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,j}|
 \\
@@
 \quad
-\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
 \end{split}
@@
 \begin{equation}\label{equ9}\vspace{-2mm}
-\hat{\bm{\alpha}}_{n}= \text{sgn}(\mathbf{D}_{(t)}^{T}\mathbf{y}_{n})\odot \text{max}(|\mathbf{D}_{(t)}^{T}\mathbf{y}_{n}|-\mathbf{\Lambda},\mathbf{0}),
+\hat{\bm{\alpha}}_{n}^{(t)}= \text{sgn}(\mathbf{D}_{(t)}^{\top}\mathbf{y}_{n})\odot \text{max}(|\mathbf{D}_{(t)}^{\top}\mathbf{y}_{n}|-\mathbf{\Lambda},\mathbf{0}),
 \end{equation}
@@
 =
-[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
+[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
 \end{split}
@@
 Here we ignore the index $t$ for notation simplicity.
-The sparse coefficient matrix $\mathbf{A}=[\mathbf{A}_{e}^{T}\ \mathbf{A}_{i}^{T}]^{T}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively.
+The sparse coefficient matrix $\mathbf{A}=[\mathbf{A}_{e}^{\top}\ \mathbf{A}_{i}^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively.
 According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ9})
-has a closed-form solution $\mathbf{D}_{i}^{*}=\mathbf{U}_{i}\mathbf{V}_{i}^{T}$, where $\mathbf{U}_{i}$ and $\mathbf{V}_{i}$ are the orthogonal matrices obtained by the following SVD
-\vspace{-2mm}
+has a closed-form solution $\mathbf{D}_{i}^{*}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}$ and $\mathbf{V}_{i}$ are the orthogonal matrices obtained by the following SVD
+\vspace{-1mm}
 \begin{equation}\label{equ11}\vspace{-2mm}
-(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{T})\mathbf{Y}\mathbf{A}_{i}^{T}
+(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}\mathbf{A}_{i}^{\top}
 =
-\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{T}
+\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{\top}
 \end{equation}
@@
 
-\section{The Denoising Algorithm}
+\subsection{The Denoising Algorithm}
 
-In this work, we solve the real noisy image denoising problem by employing the sparse coding framework \cite{pgpd} in Equ.
-(\ref{equ6}).
-We utilize two strategies to gain better performance: one is the 'Summed Area Table' \cite{sat} for faster patch group (PG) searching and the other is that the prior weights in Equ.
-(\ref{equ3}) are used for better denoising effects.
-
-\subsection{Fast Internal Patch Group Searching}
-
-Given a RGB image of size $256\times256\times3$, we can extract over 60 thousands local patches of size $6\times6\times3$.
-It is time-consumming to search patch groups (PG) for local patches one by one.
-To speed up the searching process, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching.
-The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size.
-Hence, we do not need do distance measure for each local patch.
-
-\subsection{The Overall Algorithm}
-
-With the solution $\hat{\boldsymbol{\upalpha}}$ in (\ref{equ13}), each column of the PG $\mathbf{Y}$ can be estimated as $\hat{\mathbf{y}}=\mathbf{D}\hat{\boldsymbol{\upalpha}}$.
-Then we add back its PG mean denoted as $\boldsymbol{\upmu}_{y}$ and reconstruct the clean image $\hat{\mathbf{x}}$ by aggregating all the estimated PGs.
+As discussed in previous section, the proposed framework employs the external prior learned from natural clean images to guide the internal prior learning for any given noisy image.
+The image denoising is simultaneously done with the learning process.
+In the denoising procedure, for each subspace (we ignore the indexes $k=1,...,K$ of subspaces for notation simplicity), the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of the internal noisy PGs $\{\mathbf{y}_{n}\}_{n=1}^{N}$ are saved for reconstruction.
+Until now, we obtain the solutions of sparse coefficients $\{\hat{\bm{\alpha}}_{n}^{T-1}\}$ in (\ref{equ9}) and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ.
+(\ref{equ10}).
+Then the latent clean PGs $\{\hat{\mathbf{y}}_{n}\}_{n=1}^{N}$ are recovered by $\hat{\mathbf{y}}_{n}=\mathbf{D}_{}^{}\hat{\boldsymbol{\upalpha}}$.
+We add back its PG mean denoted as $\boldsymbol{\upmu}_{y}$ and reconstruct the clean image $\hat{\mathbf{x}}$ by aggregating all the estimated PGs.
 Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs.
 But different from \cite{pgpd}, we do not employ the iterative regularization strategy \cite{osher2005iterative} since it is not effective in our method.
-The proposed denoising algorithm is summarized in Algorithm 1.
+The proposed denoising algorithm is summarized in Alg.
+1.
 \begin{table}
@@
 \textbf{for} $t = 1:IteNum$ \textbf{do}
+\\
+1. Extracting internal patch groups (PGs) from $\hat{\mathbf{x}}^{(0)}$;
 \\
@@
 \caption{Some cropped images of the dataset \cite{crosschannel2016}.}
-\label{fig5}
+\label{fig4}
 \end{figure}
-
-\subsection{Implementation Details}
-Our proposed method contains two stages, the external prior guided internal subspace learning stage and the adaptive denoising stage.
-In the learning stage, there are 4 parameters: the patch size $p$, the number of patches in a PG $M$, the window size $W$ for PG searching and the number of clusters $K$.
-We set $p = 6$ (hence the patch size is $6\times 6 \times 3$), $M=10$, $W = 31$, $K=32$.
-We extracted about 3.6 million PGs from the Kodak PhotoCD Dataset, which includes 24 high quality color images, to train the external prior via PG-GMM.
-In the denoising stage, the paramter $\lambda = 0.002$ is used to regularize the sparse term.
-The $\delta$ in iterative regularization is set as $\delta = 0.09$.
-
-\subsection{Comparison on External and Internal methods}
-In this subsection, we compared the proposed external prior guided internal subspace learning model on real image denoising.
-The three methods are evaluated on the dataset provided in \cite{crosschannel2016}.
-We calculate the PSNR, SSIM \cite{ssim} and visual quality of these three methods.
-We also compare the speed.
-The PSNR and SSIM results on 60 cropped images from \cite{crosschannel2016} are listed in Table 1.
-The images are cropped into size of $500\times 500$ for better illustration.
-We also compare the three methods on visual quality in Figure \ref{fig2}.
-Compare the denoised images listed in Figure \ref{fig2} and Figure \ref{fig2}, we can see that the Offline method is better at edges, smooth regions while the Online method is good at complex textures.
-The reason is two folds.
-Firstly, the Offline method is learned on clean images and hence is better at representing edges, structuals, and smooth area.
-The online method is influenced by the noise and hence some noise cannot be removed.
-Secondly, the Online method is better at recovering complex area sicne they could learn adaptive dictionaries for the specific area.
-The Offline method cannot recover the complex area since they did not learn the similar structures from the external natural clean images.
-
-\begin{table}\label{tab1}
-\caption{Average PSNR(dB)/SSIM results of external, internal, and guided methods on 60 cropped real noisy images in \cite{crosschannel2016}.}
-\label{tab1}
-\begin{center}
-\renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|}
-\hline
- & \textbf{Noisy} &\textbf{Offline} &\textbf{Online} &\textbf{Guided}  
-\\
-\hline
-PSNR & 34.51 & 38.19 & 38.07 & \textbf{38.55} 
-\\
-\hline
-SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9675}
-\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\begin{figure*}\label{fig2}
-\centering
-\subfigure{
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (a) Noisy Image \\ (34.66dB/0.9178)   }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (h) Offline \\ (34.97dB/0.9441) }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (i) Online \\ (36.86dB/0.9622) }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (j) Guided \\ (\textbf{37.09}dB/\textbf{0.9638})}
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (h) Mean Image }
-\end{minipage}
-}
-\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
-\end{figure*}
-
-\begin{figure*}\label{fig2}
-\centering
-\subfigure{
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (a) Noisy Image \\ (36.15dB/0.9523)    }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (h) Offline \\ (37.12dB/0.9776) }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (i) Online \\ (35.70dB/0.9755)  }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (j) Guided \\ (\textbf{37.94}dB/\textbf{0.9804})}
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (h) Mean Image }
-\end{minipage}
-}
-\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
-\end{figure*}
 
@@
 \caption{Denoised images of the image "Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
-\label{fig3}
+\label{fig5}
 \end{figure*}
 
-\subsection{Comparison With other Competing Methods}
-We compare with previous state-of-the-art Gaussian noise removal methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and the recently proposed TRD \cite{chen2015learning}.
-We also compare with three competing real image denoising methods such as Noise Clinic, Neat Image, and the CCNoise method proposed recently.
-The commercial software Neat Image \cite{neatimage} first estimates the parameters of noise via a large flat area and then filters the noise accordingly.
-All these methods need noise estimation which is vary hard to perform if there is no uniform regions are available in the testing image.
-The NeatImage will fail to perform automatical parameters settings if there is no uniform regions.
-\footnote{To compare with CCNoise, we first transform the denoised images into double format.}
+\subsection{Implementation Details}
+Our proposed method contains two stages, the external prior guided internal subspace learning stage and the adaptive denoising stage.
+In the learning stage, there are 4 parameters: the patch size $p$, the number of patches in a PG $M$, the window size $W$ for PG searching and the number of clusters $K$.
+We set $p = 6$ (hence the patch size is $6\times 6 \times 3$), $M=10$, $W = 31$, $K=32$.
+We extracted about 3.6 million PGs from the Kodak PhotoCD Dataset, which includes 24 high quality color images, to train the external prior via PG-GMM.
+In the denoising stage, the paramter $\lambda = 0.002$ is used to regularize the sparse term.
+The $\delta$ in iterative regularization is set as $\delta = 0.09$.
+Given a RGB image of size $256\times256\times3$, we can extract over 60 thousands local patches of size $6\times6\times3$.
+It is time-consumming to search patch groups (PG) for local patches one by one.
+To speed up the searching process, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching.
+The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size.
+Hence, we do not need do distance measure for each local patch.
 
-We the competing denoising methods from various research directions on two datasets.
-Both the two datasets comes from the \cite{crosschannel2016}.
-The first dataset contains 17 images of size over $7000\times5000$.
-Since this dataset contains repetitive contents across different images, we crop 60 small images of size $500\times500$ from these 17 images in \cite{crosschannel2016}.
-The PSNR and SSIM resluts are listed in Table \ref{tab1}.
-The number in red color and blue color means the best and second best results, respectively.
-From the Table \ref{tab1}, we can see that the external based method can already surpass largely the previous denoising methods.
-The improvement on PSNR over the second best method, i.e., TRD, is 0.44dB.
-The
+\subsection{Comparison on External and Internal methods}
+In this subsection, we compared the proposed external prior guided internal subspace learning model on real image denoising.
+The three methods are evaluated on the dataset provided in \cite{crosschannel2016}.
+We calculate the PSNR, SSIM \cite{ssim} and visual quality of these three methods.
+We also compare the speed.
+The PSNR and SSIM results on 60 cropped images from \cite{crosschannel2016} are listed in Table 1.
+The images are cropped into size of $500\times 500$ for better illustration.
+We also compare the three methods on visual quality in Figure \ref{fig2}.
+Compare the denoised images listed in Figure \ref{fig2} and Figure \ref{fig2}, we can see that the Offline method is better at edges, smooth regions while the Online method is good at complex textures.
+The reason is two folds.
+Firstly, the Offline method is learned on clean images and hence is better at representing edges, structuals, and smooth area.
+The online method is influenced by the noise and hence some noise cannot be removed.
+Secondly, the Online method is better at recovering complex area sicne they could learn adaptive dictionaries for the specific area.
+The Offline method cannot recover the complex area since they did not learn the similar structures from the external natural clean images.
+
+\begin{table}\label{tab1}
+\caption{Average PSNR(dB)/SSIM results of external, internal, and guided methods on 60 cropped real noisy images in \cite{crosschannel2016}.}
+\label{tab1}
+\begin{center}
+\renewcommand\arraystretch{1}
+\begin{tabular}{|c||c|c|c|c|}
+\hline
+ & \textbf{Noisy} &\textbf{Offline} &\textbf{Online} &\textbf{Guided}  
+\\
+\hline
+PSNR & 34.51 & 38.19 & 38.07 & \textbf{38.55} 
+\\
+\hline
+SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9675}
+\\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
 \begin{table*}\label{tab1}
@@
 \end{table*}
+
+\subsection{Comparison With other Competing Methods}
+We compare with previous state-of-the-art Gaussian noise removal methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and the recently proposed TRD \cite{chen2015learning}.
+We also compare with three competing real image denoising methods such as Noise Clinic, Neat Image, and the CCNoise method proposed recently.
+The commercial software Neat Image \cite{neatimage} first estimates the parameters of noise via a large flat area and then filters the noise accordingly.
+All these methods need noise estimation which is vary hard to perform if there is no uniform regions are available in the testing image.
+The NeatImage will fail to perform automatical parameters settings if there is no uniform regions.
+\footnote{To compare with CCNoise, we first transform the denoised images into double format.}
+
+We the competing denoising methods from various research directions on two datasets.
+Both the two datasets comes from the \cite{crosschannel2016}.
+The first dataset contains 17 images of size over $7000\times5000$.
+Since this dataset contains repetitive contents across different images, we crop 60 small images of size $500\times500$ from these 17 images in \cite{crosschannel2016}.
+The PSNR and SSIM resluts are listed in Table \ref{tab1}.
+The number in red color and blue color means the best and second best results, respectively.
+From the Table \ref{tab1}, we can see that the external based method can already surpass largely the previous denoising methods.
+The improvement on PSNR over the second best method, i.e., TRD, is 0.44dB.
+The
+
+\subsection{Discussion on Parameter $\lambda$}
+The proposed method only has a key parameter, namely the regularization paramters $\lambda$.
+To demonstrate that the proposed method is robust to the variance of $\lambda$, we vary the parameter $\lambda$ across a wide range and obtain the PSNR and SSIM results as a function of the parameter $\lambda$.
+The results is shown in Figure \ref{fig10}, from which we can see that the proposed method can achieve a PSNR (SSIM) over 38.5dB (0.9660) when $\lambda$ varies from $0.0015$ to $0.0025$.
+This shows that the proposed method is indeed robust to the chosen of the paramter $\lambda$.
+\begin{figure}
+\includegraphics[width=1\linewidth]{images/param.png}
+\caption{The PSNR/SSIM results as a function of the parameter $\lambda$.}
+\label{fig10}
+\end{figure}
 
@@
 
-%\subsection{Discussion on Parameter $\lambda$}
-%The proposed method only has a key parameter, namely the regularization paramters $\lambda$.
-To demonstrate that the proposed method is robust to the variance of $\lambda$, we vary the parameter $\lambda$ across a wide range and obtain the PSNR and SSIM results as a function of the parameter $\lambda$.
-The results is shown in Figure \ref{fig10}, from which we can see that the proposed method can achieve a PSNR (SSIM) over 38.5dB (0.9660) when $\lambda$ varies from $0.0015$ to $0.0025$.
-This shows that the proposed method is indeed robust to the chosen of the paramter $\lambda$.
-%\begin{figure}
-%\includegraphics[width=1\linewidth]{images/param.png}
-%\caption{The PSNR/SSIM results as a function of the parameter $\lambda$.}
-%\label{fig10}
-%\end{figure}
-
 \section{Conclusion and Future Work}

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 Assume we have assigned all internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
-Assume $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ are the noisy PGs assigned to the $k$-th subspace, such that $\sum_{k=1}^{K}N_{k}=N$ and $\sum_{k=1}^{K}\sum_{n=1}^{N_{k}}k_{n}=NM$, we have that $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{y}_{k_{n},1},...,\mathbf{y}_{k_{n},M}]$.
+Assume $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ are the noisy PGs assigned to the $k$-th subspace, such that $\sum_{k=1}^{K}N_{k}=N$ and $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$.
 We consider to utilize the external orthogonal dictionary $\mathbf{U}_{k}$ to guide the learning of an orthogonal dictionary $\mathbf{D}_{k}:=[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
 This dictionary has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary in Equ.
-(\ref{equ3}), and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\mathbf{Y}_{k}$.
-The learning and denoising are simultaneously performed under the proposed reweighted sparse coding framework as f(for notation simplicity, we ignore the subspace index $k$):
+(\ref{equ3}), and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\mathbf{Y}_{k}=\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
+For notation simplicity, we ignore the subspace index $k$ and denote as noisy PGs $\mathbf{Y}\triangleq\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N} = [\mathbf{\overline{y}}_{1,1},...,\mathbf{\overline{y}}_{1,M},...,\mathbf{\overline{y}}_{N,1},...,\mathbf{\overline{y}}_{N,M}]$.
+The learning and denoising are simultaneously performed under the weighted sparse coding framework proposed as follows:
 \vspace{-2mm}
@@
 \begin{split}
-&\min_{\mathbf{D}_{i},\{\bm{\alpha}_{n}\}}
-\sum_{n=1}^{N}(\|\mathbf{y}_{n}-\mathbf{D}\bm{\alpha}_{n}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,j}|)
+&\min_{\mathbf{D}_{i},\{\bm{\alpha}_{n,m}\}}
+\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|)
 \\
@@
 \end{equation}
-where $\lambda_{j}$ is the $j$-th regularization parameter defined as
+where $\bm{\alpha}_{n,m}$ is the sparse coefficients vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ of the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
+$\lambda_{j}$ is the $j$-th regularization parameter defined as
 \vspace{-2mm}
@@
 \begin{split}
-&\bm{\alpha}_{n}^{(t)}:=\argmin_{\bm{\alpha}_{n}\in\mathbb{R}^{3p^2\times 1}}
-\|\mathbf{y}_{n}-\mathbf{D}_{(t)}\bm{\alpha}_{n}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,j}|
+&\bm{\alpha}_{n,m}^{(t)}:=\argmin_{\bm{\alpha}_{n,m}}
+\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}_{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|
 \\
@@
 \begin{equation}\label{equ9}\vspace{-2mm}
-\hat{\bm{\alpha}}_{n}^{(t)}= \text{sgn}(\mathbf{D}_{(t)}^{\top}\mathbf{y}_{n})\odot \text{max}(|\mathbf{D}_{(t)}^{\top}\mathbf{y}_{n}|-\mathbf{\Lambda},\mathbf{0}),
+\bm{\alpha}_{n,m}^{(t)}= \text{sgn}(\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m}|-\mathbf{\Lambda},\mathbf{0}),
 \end{equation}
@@
 \\
-\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}=[\bm{\alpha}_{1}^{(t)},...,\bm{\alpha}_{N}^{(t)}]$, we update the internal orthogonal dictionary via solving
+\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$, we update the internal orthogonal dictionary via solving
 \vspace{-2mm}
@@
 \argmin_{\textbf{D}_{i}}
-\sum_{n=1}^{N}(\|\mathbf{y}_{n}-\mathbf{D}\bm{\alpha}_{n}^{(t)}\|_{2}^{2})
+\sum_{n=1}^{N}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
 \\
@@
 \end{equation}
-Here we ignore the index $t$ for notation simplicity.
-The sparse coefficient matrix $\mathbf{A}=[\mathbf{A}_{e}^{\top}\ \mathbf{A}_{i}^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}$ and the internal part $\mathbf{A}_{i}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}$, respectively.
-According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ9})
-has a closed-form solution $\mathbf{D}_{i}^{*}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}$ and $\mathbf{V}_{i}$ are the orthogonal matrices obtained by the following SVD
+The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}$ and the internal part $\mathbf{A}_{i}^{(t)}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively.
+According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ10})
+has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}$ and $\mathbf{V}_{i}$ are the orthogonal matrices obtained by the following SVD
 \vspace{-1mm}
 \begin{equation}\label{equ11}\vspace{-2mm}
-(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}\mathbf{A}_{i}^{\top}
+(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}(\mathbf{A}_{i}^{(t)})^{\top}
 =

### 2016-10-27 CVPR2017_Review_Unified.tex
add

@@
 \\
-\textbf{Updating Orthogonal Dictionary}: given the sparse coefficients $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$, we update the internal orthogonal dictionary via solving
+\textbf{Updating Internal Orthogonal Dictionary}: given the sparse coefficients vectors $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$, we update the internal orthogonal dictionary via solving
 \vspace{-2mm}
@@
 
-As discussed in previous section, the proposed framework employs the external prior learned from natural clean images to guide the internal prior learning for any given noisy image.
-The image denoising is simultaneously done with the learning process.
-In the denoising procedure, for each subspace (we ignore the indexes $k=1,...,K$ of subspaces for notation simplicity), the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of the internal noisy PGs $\{\mathbf{y}_{n}\}_{n=1}^{N}$ are saved for reconstruction.
-Until now, we obtain the solutions of sparse coefficients $\{\hat{\bm{\alpha}}_{n}^{T-1}\}$ in (\ref{equ9}) and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ.
+We evaluate the performance of the proposed framework on denoising real noisy images.
+The denoising is simultaneously done with the guided internal dictionary learning (DL) process.
+We ignore the index $k\in\{1,...,K\}$ of subspace for notation simplicity.
+In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean substracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction.
+Until now, we obtain the solutions of sparse coefficients vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ.
 (\ref{equ10}).
-Then the latent clean PGs $\{\hat{\mathbf{y}}_{n}\}_{n=1}^{N}$ are recovered by $\hat{\mathbf{y}}_{n}=\mathbf{D}_{}^{}\hat{\boldsymbol{\upalpha}}$.
-We add back its PG mean denoted as $\boldsymbol{\upmu}_{y}$ and reconstruct the clean image $\hat{\mathbf{x}}$ by aggregating all the estimated PGs.
-Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs.
-But different from \cite{pgpd}, we do not employ the iterative regularization strategy \cite{osher2005iterative} since it is not effective in our method.
-The proposed denoising algorithm is summarized in Alg.
-1.
+Then the $m$-th latent clean patch $\hat{\mathbf{y}}_{n,m}$ in the $n$-th PG $\mathbf{Y}_{n}$ is recovered by
+\vspace{-2mm}
+\begin{equation}\label{equ12}\vspace{-2mm}
+\hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
+\end{equation}
+where $n=1,...,N;m=1,...,M$.
+
 \begin{table}
@@
 \hline
-\textbf{Alg. 1}: External PG Prior Guided Internal PG Prior
+\textbf{Alg. 1}: External Patch Group (PG) Prior Guided Internal
 \\
-\quad \quad \quad Learning for Real Image Denoising
+\quad \quad \quad PG Prior Learning for Image Denoising
 \\
 \hline
-\textbf{Input:} Noisy image $\mathbf{y}$, external prior GMM model
+\textbf{Input:} Noisy image $\mathbf{y}$, external PG prior GMM model
 \\
@@
 \\
-\textbf{for} $t = 1:IteNum$ \textbf{do}
+\textbf{for} $Ite = 1:IteNum$ \textbf{do}
 \\
-1. Extracting internal patch groups (PGs) from $\hat{\mathbf{x}}^{(0)}$;
+1. Extracting internal PGs from $\hat{\mathbf{x}}^{(Ite-1)}$;
 \\
@@
 \\
-2.\quad Calculate group mean $\boldsymbol{\upmu}_{n}$ and form PG $\mathbf{\overline{Y}}_{n}$;
+2.\quad Calculate group mean vector $\boldsymbol{\upmu}_{n}$ and form 
 \\
-3.\quad Gaussian component selection via Equ. (\ref{equ5});
+\quad \ \ \ mean substracted PG $\mathbf{\overline{Y}}_{n}$;
+\\
+3.\quad Subspace selection via Equ. (\ref{equ4});
 \\
@@
 \\
-\quad\textbf{for} each Internal Subspace \textbf{do}
+\quad\textbf{for} the PGs in each Subspace \textbf{do}
 \\
-4.\quad Internal Subspace Learning by (\ref{equ4});
+4.\quad External PG prior Guided Internal Orthogonal
 \\
-5.\quad Recover each patch in all PGs via $\hat{\mathbf{x}}_{m}=\mathbf{D}\hat{\boldsymbol{\upalpha}}+\boldsymbol{\upmu}_{y}$;
+\quad \ \ \ Dictionary Learning by solving (\ref{equ5});
+\\
+5.\quad Recover each patch in all PGs via Equ. (\ref{equ12});
 \\
@@
 \\
-\quad the recovered image $\hat{\mathbf{x}}^{(t)}$;
+\quad the recovered image $\hat{\mathbf{x}}^{(Ite)}$;
 \\
@@
 \end{table}
+
+The latent clean image $\hat{\mathbf{x}}$ is reconstructed by aggregating all the estimated PGs.
+Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs.
+But different from \cite{pgpd}, we do not employ the iterative regularization strategy \cite{osher2005iterative} since it does no help to our proposed method.
+The proposed denoising algorithm is summarized in Alg.
+1.
 

### 2016-10-28 CVPR2017_Review_Unified.tex
add

@@
 Given a real noisy image, assume we can totally extract $N$ local patches from it.
-Similar to the external prior learning stage, for the $n$-th local patch ($n=1,...,N$), we extract its similar patches around it to form a noisy PG denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.
-Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is calculated and subtracted from each patch, leading to the mean subtracted PG $\mathbf{\overline{Y}}_{n}$.
-Each mean substracted PG is defined as $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$ where $\mathbf{\overline{y}}_{n,m}=\mathbf{y}_{n,m}-\bm{\mu}_{n}$.
+Similar to the external prior learning stage, for the $n$-th local patch ($n=1,...,N$), we extract its $M$ most similar patches around it to form a noisy PG denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.
+Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is calculated and subtracted from each patch by $\mathbf{\overline{y}}_{n,m}=\mathbf{y}_{n,m}-\bm{\mu}_{n}$, leading to the mean subtracted PG $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$.
 For adaptivity, we project the PG $\mathbf{\overline{Y}}_{n}$ into its most suitable Gaussian component (subspace) of the GMM learned on external PGs.
@@
 \begin{equation}\label{equ4}\vspace{-1mm}
-P(k|\mathbf{\overline{Y}}_{n})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{l})},
+P(k|\mathbf{\overline{Y}}_{n})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{l})}
 \end{equation}
-and then choosing the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}}_{n})$.
+for $k=1,...,K$, and then choosing the component with the maximum A-posteriori (MAP) probability $\max_{k}P(k|\mathbf{\overline{Y}}_{n})$.
 
@@
 Assume we have assigned all internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
-Assume $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ are the noisy PGs assigned to the $k$-th subspace, such that $\sum_{k=1}^{K}N_{k}=N$ and $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$.
-We consider to utilize the external orthogonal dictionary $\mathbf{U}_{k}$ to guide the learning of an orthogonal dictionary $\mathbf{D}_{k}:=[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
-This dictionary has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary in Equ.
-(\ref{equ3}), and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\mathbf{Y}_{k}=\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
-For notation simplicity, we ignore the subspace index $k$ and denote as noisy PGs $\mathbf{Y}\triangleq\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N} = [\mathbf{\overline{y}}_{1,1},...,\mathbf{\overline{y}}_{1,M},...,\mathbf{\overline{y}}_{N,1},...,\mathbf{\overline{y}}_{N,M}]$.
-The learning and denoising are simultaneously performed under the weighted sparse coding framework proposed as follows:
+For the $k$-th subspace, assume the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ such that $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.
+We consider to utilize the external orthogonal dictionary $\mathbf{U}_{k}$ (Equ.
+(\ref{equ3})) to guide the learning of an orthogonal dictionary defined as $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
+This dictionary has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary $\mathbf{U}_{k}$, and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
+Therefore, the dictionary $\mathbf{D}_{k}$ can adaptively characterize the internal PGs in the $k$-th subspace.
+For notation simplicity, we ignore the subspace index $k$ and denote the noisy PGs assigned to each subspace as $\mathbf{Y}\triangleq\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N} = [\mathbf{\overline{y}}_{1,1},...,\mathbf{\overline{y}}_{1,M},...,\mathbf{\overline{y}}_{N,1},...,\mathbf{\overline{y}}_{N,M}]$.
+The learning is performed under the weighted sparse coding framework proposed as follows:
 \vspace{-2mm}
@@
 \end{equation}
-where $\bm{\alpha}_{n,m}$ is the sparse coefficients vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ of the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
+where $\bm{\alpha}_{n,m}$ is the sparse coefficients vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
 $\lambda_{j}$ is the $j$-th regularization parameter defined as
@@
 We ignore the index $k\in\{1,...,K\}$ of subspace for notation simplicity.
-In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean substracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction.
+In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction.
 Until now, we obtain the solutions of sparse coefficients vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ.
@@
 where $n=1,...,N;m=1,...,M$.
-
 \begin{table}
@@
 \\
+%\textbf{Guided Internal Subspace Selection:}
+%\\
 \quad\textbf{for} each PG $\mathbf{Y}_{n}$ \textbf{do}
@@
 \\
-\quad \ \ \ mean substracted PG $\mathbf{\overline{Y}}_{n}$;
+\quad \ \ \ mean subtracted PG $\mathbf{\overline{Y}}_{n}$;
 \\
@@
 \\
+%\textbf{Guided Internal Orthogonal Dictionary Learning:}
+%\\
 \quad\textbf{for} the PGs in each Subspace \textbf{do}
@@
 \end{table}
-
 The latent clean image $\hat{\mathbf{x}}$ is reconstructed by aggregating all the estimated PGs.
 Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs.
-But different from \cite{pgpd}, we do not employ the iterative regularization strategy \cite{osher2005iterative} since it does no help to our proposed method.
 The proposed denoising algorithm is summarized in Alg.

### 2016-10-28 CVPR2017_Review_Unified.tex
add

@@
 }
-\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}\vspace{-4mm}
 \end{figure*}
@@
 }
-\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}\vspace{-4mm}
 \end{figure*}
@@
 For the $k$-th subspace, assume the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ such that $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.
-We consider to utilize the external orthogonal dictionary $\mathbf{U}_{k}$ (Equ.
-(\ref{equ3})) to guide the learning of an orthogonal dictionary defined as $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$.
-This dictionary has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary $\mathbf{U}_{k}$, and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
-Therefore, the dictionary $\mathbf{D}_{k}$ can adaptively characterize the internal PGs in the $k$-th subspace.
+We utilize the external orthogonal dictionary $\mathbf{U}_{k}$ (Equ.
+(\ref{equ3})) to guide the learning of an orthogonal dictionary for adaptively characterizing the internal PGs in the $k$-th subspace.
+The learned dictionary defined as $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$ has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary $\mathbf{U}_{k}$, and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
 For notation simplicity, we ignore the subspace index $k$ and denote the noisy PGs assigned to each subspace as $\mathbf{Y}\triangleq\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N} = [\mathbf{\overline{y}}_{1,1},...,\mathbf{\overline{y}}_{1,M},...,\mathbf{\overline{y}}_{N,1},...,\mathbf{\overline{y}}_{N,M}]$.
@@
 \vspace{-2mm}
-\begin{equation}\label{equ5}\vspace{-2mm}
+\begin{equation}\label{equ5}\vspace{-3mm}
 \begin{split}
@@
 \end{equation}
-where $\bm{\alpha}_{n,m}$ is the sparse coefficients vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
+where $\bm{\alpha}_{n,m}$ is the sparse coefficient vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
 $\lambda_{j}$ is the $j$-th regularization parameter defined as
-\vspace{-2mm}
-\begin{equation}\label{equ6}\vspace{-2mm}
+\vspace{-1mm}
+\begin{equation}\label{equ6}\vspace{-1mm}
 \lambda_{j} = \lambda/(\sqrt{\mathbf{S}_{j}}+\varepsilon).
 \end{equation}
-We employ square roots of the singular values in $\mathbf{S}$ (please refer Equ.
+We employ square roots of the singular values in $\mathbf{S}$ (please refer to Equ.
 (\ref{equ3})) as external prior weights and add a small positive number $\varepsilon$ to avoid zero denominator.
@@
 \\
-\textbf{Updating Sparse Coefficients}: given the orthogonal dictioanry $\textbf{D}_{(t)}$, we update the sparse coefficients via solving
-\vspace{-2mm}
-\begin{equation}\label{equ8}\vspace{-2mm}
+\textbf{Updating Sparse Coefficient}: given the orthogonal dictioanry $\textbf{D}_{(t)}$, we update the sparse coefficient vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ via solving
+\vspace{-3mm}
+\begin{equation}\label{equ8}\vspace{-3mm}
 \begin{split}
@@
 \\
-\textbf{Updating Internal Orthogonal Dictionary}: given the sparse coefficients vectors $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$, we update the internal orthogonal dictionary via solving
+\textbf{Updating Internal Dictionary}: given the sparse coefficient vectors $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$, we update the internal orthogonal dictionary via solving
 \vspace{-2mm}
@@
 \argmin_{\textbf{D}_{i}}
-\sum_{n=1}^{N}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
+\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
 \\
@@
 \end{equation}
-The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}$ and the internal part $\mathbf{A}_{i}^{(t)}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively.
-According to the Proposition 2.2 in \cite{bao2013fast}, the problem (\ref{equ10})
-has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}$ and $\mathbf{V}_{i}$ are the orthogonal matrices obtained by the following SVD
+The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{i}^{(t)}\in\mathbb{R}^{r\times NM}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively.
+According to the Theorem 4 in \cite{spca}, the problem (\ref{equ10})
+has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times 3p^2}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
 \vspace{-1mm}
@@
 =
-\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{\top}
+\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{\top}.
 \end{equation}
+The orthogonality of the dictionary $\mathbf{D}_{i}^{(t+1)}$ can be checked by 
+$(\mathbf{D}_{i}^{(t+1)})^{\top}(\mathbf{D}_{i}^{(t+1)})=\mathbf{V}_{i}\mathbf{U}_{i}^{\top}\mathbf{U}_{i}\mathbf{V}_{i}^{\top}=\mathbf{I}_{r}$.
 
@@
 In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction.
-Until now, we obtain the solutions of sparse coefficients vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ.
+Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ.
 (\ref{equ10}).

### 2016-10-28 CVPR2017_Review_Unified.tex
add

@@
 \end{equation}
-The orthogonality of the dictionary $\mathbf{D}_{i}^{(t+1)}$ can be checked by 
+The orthogonality of internal dictionary $\mathbf{D}_{i}^{(t+1)}$ can be checked by 
 $(\mathbf{D}_{i}^{(t+1)})^{\top}(\mathbf{D}_{i}^{(t+1)})=\mathbf{V}_{i}\mathbf{U}_{i}^{\top}\mathbf{U}_{i}\mathbf{V}_{i}^{\top}=\mathbf{I}_{r}$.
@@
 
-Here we take a detailed analysis on the guiance of the external patch group (PG) prior for the internal noisy PGs of given real noisy images.
+Here we take a detailed analysis on the guidance of the external patch group (PG) prior for the internal noisy PGs of given real noisy images.
 The guidance comes from at least three aspects: 1) the external prior guides the internal PGs to be clustered into suitable subspaces through MAP in Equ.
-(\ref{equ5}).
-The guided subspace clustering is more efficient than directly clustering the internal noisy PGs via k-means or Gaussian Mixture Model (GMM).
+(\ref{equ4}).
+The guided subspace selection is more efficient than directly clustering the internal noisy PGs via k-means or Gaussian Mixture Model (GMM).
 The reason is, by guidance we only need calculate the probabilities via Equ.
-(\ref{equ5}) for all noisy PGs while by internal clustering via GMM we need perform EM algorithm \cite{em}.
-2) the external dictionary guides the internal dictionary learning, and the obtained dictionary consisted of the two parts is orthogonal and more adaptive to the given noisy image.
-The learning process has closed-form solutions and hence is very efficient.
-Besides, the learned orthogonal dictionary also makes the denoising process very efficient under sparse coding framework.
-3) the singular values obtained by SVD in Equ.
-(\ref{equ3}) reflect the prior weights of the atoms in learned dictionary and can be used as adaptive parameters for real image denoising.
+(\ref{equ4}) for all noisy PGs while by internal clustering via GMM we have to perform time-consuming EM algorithm \cite{em}.
+2) the external clean dictionary guides the learning of orthogonal dictionaries more adaptive for internal noisy images.
+The learning process is very efficient because of closed-form solutions.
+Besides, the learned orthogonal dictionary also makes the denoising process very efficient under weighted sparse coding framework.
+3) the singular values learned by SVD in Equ.
+(\ref{equ3}) reflect the prior weights of the dictionary atoms and can be used as adaptive parameters for real image denoising.
 

### 2016-10-28 CVPR2017_Review_Unified.tex
add

@@
 \DeclareMathOperator*{\argmin}{arg\,min}
+\usepackage{arydshln}
 
@@
 
-For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN).
+For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN).
 In real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc.
@@
 \section{Experiments}
-In this section, we perform real image denoising experiments on three standard datasets.
+
+In this section, we evaluate the performance of the proposed algorithm on real image denoising.
+To evaluation the effectiveness of the proposed framework of external prior guided internal prior learning, we compare it with the methods with only external prior or only internal prior.
+This will be discussed in Section 4.2.
+We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,neatimage}.
+The evaluations are performed on two standard datasets.
 The first dataset is real noisy images with mean images as ground truths provided by \cite{crosschannel2016}, some samples are shown in Figure \ref{fig5}.
@@
 }
-\caption{Some cropped images of the dataset \cite{crosschannel2016}.}
+\caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
 \label{fig4}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_5dmark3_iso3200_1_real.png}}
-{\footnotesize (a) Noisy Image \\ (37.00dB/0.9345) }
+{\footnotesize (a) Noisy: 37.00dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
-{\footnotesize (b) CBM3D \\ (37.02dB/0.9351)}
+{\footnotesize (b) CBM3D: 37.02dB}
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_5dmark3_iso3200_1_real.png}}
-{\footnotesize (c) WNNM \\ (37.01dB/0.9347)}
+{\footnotesize (c) WNNM: 37.01dB}
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_5dmark3_iso3200_1_real.png}}
-{\footnotesize (d) MLP \\ (33.90dB/0.9171) }
+{\footnotesize (d) MLP: 33.90dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
-{\footnotesize (e) TRD \\ (36.18dB/0.9454)   }
+{\footnotesize (e) TRD: 36.18dB  }
 \end{minipage}
-}
+}\vspace{-2mm}
 \subfigure{
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
-{\footnotesize (f) Noise Clinic \\ (38.76dB/0.9689) }
+{\footnotesize (f) Noise Clinic: 38.76dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
-{\footnotesize (g) Neat Image \\ (37.68dB/0.9600) }
+{\footnotesize (g) Neat Image:37.68dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
-{\footnotesize (h) CCNoise \\ (38.37dB/0.9678) }
+{\footnotesize (h) CCNoise:38.37dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
-{\footnotesize (i) Guided \\ (\textbf{40.26}dB/\textbf{0.9800})}
+{\footnotesize (i) Guided: \textbf{40.26}dB}
 \end{minipage}
@@
 \begin{table}\label{tab1}
-\caption{Average PSNR(dB)/SSIM results of external, internal, and guided methods on 60 cropped real noisy images in \cite{crosschannel2016}.}
+\caption{Average PSNR(dB) results of External, Internal, and Guided methods on 60 cropped real noisy images in \cite{crosschannel2016}.}
 \label{tab1}
@@
 \hline
- & \textbf{Noisy} &\textbf{Offline} &\textbf{Online} &\textbf{Guided}  
+ & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Guided}  
 \\
@@
 \hline
-SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9675}
-\\
-\hline
+%SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9675}
+%\\
+%\hline
 \end{tabular}
@@
 \hline
-PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  \color{blue}{38.72} & \color{red}{ 38.90}
-\\
-\hline
-SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & \color{blue}{0.9694} & \color{red}{0.9702}
+PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  {\color{blue}{38.72}} & {\color{red}{ 38.90}}
+%\\
+%\hline
+%SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9694}} & {\color{red}{0.9702}}
 \\
@@
 \multirow{3}{*}{\small{Canon 5D Mark III}} 
-& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & \color{blue}{38.76} & 38.37 & \color{red}{40.50}
+& 37.00 & 37.08 & 37.09 & 33.92 & 35.68 & 36.20 & 37.68 & {\color{blue}{38.76}} & 38.37 & {\color{red}{40.50}}
 \\ 
-\cline{2-11} 
+\cdashline{2-11} 
 \multirow{3}{*}{ISO = 3200}   
-& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & \color{blue}{35.69} & 35.37 & \color{red}{37.22}
+& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & {\color{blue}{35.69}} & 35.37 & {\color{red}{37.22}}
 \\ 
-\cline{2-11}    
-& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & \color{blue}{35.54} & 34.91 & \color{red}{37.13}  
+\cdashline{2-11}    
+& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & {\color{blue}{35.54}} & 34.91 & {\color{red}{37.13}}  
 \\
@@
 \multirow{3}{*}{Nikon D600} 
-& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & \color{red}{35.57} & 34.98 & \color{blue}{35.34}
+& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & {\color{red}{35.57}} & 34.98 & {\color{blue}{35.34}}
 \\ 
-\cline{2-11} 
+\cdashline{2-11} 
 \multirow{3}{*}{ISO = 3200}   
-& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & \color{red}{36.70} & 35.95 & \color{blue}{36.69}
+& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & {\color{red}{36.70}} & 35.95 & {\color{blue}{36.69}}
 \\ 
-\cline{2-11}    
-& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & \color{blue}{40.51} & 38.68 & 39.28 & \color{red}{41.15} & 39.17
+\cdashline{2-11}    
+& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & {\color{blue}{40.51}} & 38.68 & 39.28 & {\color{red}{41.15}} & 39.17
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & \color{blue}{38.01} & 37.99 & \color{red}{38.82}
+& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & {\color{blue}{38.01}} & 37.99 & {\color{red}{38.82}}
 \\ 
-\cline{2-11} 
+\cdashline{2-11} 
 \multirow{3}{*}{ISO = 1600}   
-& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & \color{blue}{40.36} & \color{red}{40.98}
+& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & {\color{blue}{40.36}} & {\color{red}{40.98}}
 \\ 
-\cline{2-11}    
-& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & \color{blue}{38.30} & \color{red}{38.90}
+\cdashline{2-11}    
+& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & {\color{blue}{38.30}} & {\color{red}{38.90}}
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & \color{red}{39.01} & \color{blue}{38.69}
+& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & {\color{red}{39.01}} & {\color{blue}{38.69}}
 \\ 
-\cline{2-11} 
+\cdashline{2-11} 
 \multirow{3}{*}{ISO = 3200}   
-& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & \color{blue}{36.75} & \color{red}{36.82}
+& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & {\color{blue}{36.75}} & {\color{red}{36.82}}
 \\ 
-\cline{2-11}    
-& 32.91 & 32.98 & 32.96 & 38.54 & \color{blue}{40.05} & \color{red}{40.59} & 36.91 & 36.76 & 39.06 & 38.80
+\cdashline{2-11}    
+& 32.91 & 32.98 & 32.96 & 38.54 & {\color{blue}{40.05}} & {\color{red}{40.59}} & 36.91 & 36.76 & 39.06 & 38.80
 \\ 
@@
 \multirow{3}{*}{Nikon D800} 
-& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & \color{blue}{34.25} & 31.28 & 33.49 & \color{red}{34.61} & 33.31
+& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & {\color{blue}{34.25}} & 31.28 & 33.49 & {\color{red}{34.61}} & 33.31
 \\ 
-\cline{2-11} 
+\cdashline{2-11} 
 \multirow{3}{*}{ISO = 6400}   
-& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & \color{red}{33.21} & \color{blue}{33.18}
+& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & {\color{red}{33.21}} & {\color{blue}{33.18}}
 \\ 
-\cline{2-11}    
-& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & \color{blue}{33.22} & \color{red}{33.35}
+\cdashline{2-11}    
+& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & {\color{blue}{33.22}} & {\color{red}{33.35}}
 \\
 \hline
-Average PSNR & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & \color{blue}{36.88} & \color{red}{ 37.26}
+Average & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & {\color{blue}{36.88}} & {\color{red}{ 37.26}}
 \\
 \hline
-Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & \color{blue}{0.9481} & \color{red}{ 0.9505}
-\\
-\hline
+%Average SSIM & 0.8483 & 0.8511 & 0.8512 & 0.9113 & 0.9250 & 0.9280 & 0.9126 & 0.9364 & {\color{blue}{0.9481}} & {\color{red}{ 0.9505}}
+%\\
+%\hline
 \end{tabular}

### 2016-10-28 CVPR2017_Review_Unified.tex
a

@@
 
-In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} are developed to deal with real noisy images.
+In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} are developed to deal with real noisy images.
 Almost all these methods employ a two-stage framework: estimating the parameters of the assumed noise model (usually Gaussian) and performing denoising with the help of the noise modeling and estimation in the first stage.
@@
 The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image.
-\begin{figure*}\label{fig1}
+\begin{figure*}
 \centering
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.30dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (b) CBM3D \cite{cbm3d} \\ (33.33dB/0.8935)  }
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.33dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
+{\footnotesize (c) WNNM \cite{wnnm}: 33.30dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (d) MLP \cite{mlp}\\ (34.22dB/0.9603) }
+{\footnotesize (d) MLP \cite{mlp}: 34.22dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (e) CSF \cite{csf}\\ (35.39dB/0.9677) }
+{\footnotesize (e) CSF \cite{csf}: 35.39dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (f) TRD \cite{chen2015learning} \\ (35.97dB/0.9705)   }
+{\footnotesize (f) TRD \cite{chen2015learning}: 35.97dB   }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (g) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
+{\footnotesize (g) NoiseClinic \cite{noiseclinic}: 35.33dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (h) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
+{\footnotesize (h) Neat Image \cite{neatimage}: 34.39dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (i) Ours \\ (\textbf{37.28}dB/\textbf{0.9729})  }
+{\footnotesize (i) Ours: \textbf{37.28}dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (j) Mean Image }
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
 \end{minipage}
 }\vspace{-1mm}
-\caption{Denoised images of the real noisy image "Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} \vspace{-4mm}
+\caption{Denoised images of the real noisy image "Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
+\vspace{-4mm}
+\label{fig1}
 \end{figure*}
@@
 
-\begin{figure*}\label{fig2}
+\begin{figure*}
 \centering
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (a) Noisy Image \\ (34.66dB/0.9178)   }
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.66dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (h) Offline \\ (34.97dB/0.9441) }
+{\footnotesize (b) External: 34.97dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (i) Online \\ (36.86dB/0.9622) }
+{\footnotesize (c) Internal: 36.86dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (j) Guided \\ (\textbf{37.09}dB/\textbf{0.9638})}
+{\footnotesize (d) Guided: \textbf{37.09}dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (h) Mean Image }
+{\footnotesize (e) Mean Image \cite{crosschannel2016}}
 \end{minipage}
 }
-\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}\vspace{-4mm}
+\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
+\vspace{-4mm}
+\label{fig2}
 \end{figure*}
@@
 
-In the last decade, there are many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,Zhu_2016_CVPR,crosschannel2016} proposed for real image denoising problem.
+In the last decade, there are many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} proposed for real image denoising problem.
 In the seminar work of BLS-GSM \cite{blsgsm} for real image denoising, Portilla et al.
@@
 Later, Lebrun el al.
-proposed a multiscale denoising algorithm called 'Noise Clinic' \cite{noiseclinic}.
+proposed a multiscale denoising algorithm called 'Noise Clinic' \cite{noiseclinic,ncwebsite}.
 This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance.
@@
 
-\begin{figure*}\label{fig3}
+\begin{figure*}
 \centering
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (a) Noisy Image \\ (36.15dB/0.9523)    }
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 36.15dB   }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (h) Offline \\ (37.12dB/0.9776) }
+{\footnotesize (h) External: 37.12dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (i) Online \\ (35.70dB/0.9755)  }
+{\footnotesize (i) Internal: 35.70dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (j) Guided \\ (\textbf{37.94}dB/\textbf{0.9804})}
+{\footnotesize (j) Guided: \textbf{37.94}dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (h) Mean Image }
+{\footnotesize (h) Mean Image \cite{crosschannel2016} }
 \end{minipage}
@@
 \caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}\vspace{-4mm}
+\label{fig3}
 \end{figure*}
@@
 This will be discussed in Section 4.2.
-We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,neatimage}.
-The evaluations are performed on two standard datasets.
-The first dataset is real noisy images with mean images as ground truths provided by \cite{crosschannel2016}, some samples are shown in Figure \ref{fig5}.
-The second dataset is provided by the website of Noise Clinic \cite{noiseclinic}.
+We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage}.
+
+\subsection{The Testing Datasets}
+The comparisons are performed on three standard datasets, in which the images were captured by different types of cameras and camera settings under indoor and outdoor lighting conditions.
+The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images.
+The noisy images were collected under controlled indoor environment.
+Some samples can be found in \cite{crosschannel2016}.
+For each scene,  was shot 500 times (with same camera and camera setting).
+The mean image of the 500 shots is roughly taken as the “ground truth”, with which the PSNR can be computed.
+Since there are contents in different images, we cropped the 17 images into 60 smaller parts containing different contents.
+Some samples are shown in Figure \ref{fig4}.
+The second dataset provided in \cite{ncwebsite} includes about 15 real noisy images collected by the authors of Noise Clinic \cite{noiseclinic,ncwebsite}.
 The third dataset is provided by the Commercial software Neat Image \cite{neatimage}.
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_5dmark3_iso3200_1_real.png}}
-{\footnotesize (a) Noisy: 37.00dB }
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 37.00dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
-{\footnotesize (b) CBM3D: 37.02dB}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 37.02dB}
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_5dmark3_iso3200_1_real.png}}
-{\footnotesize (c) WNNM: 37.01dB}
+{\footnotesize (c) WNNM \cite{wnnm}: 37.01dB}
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_5dmark3_iso3200_1_real.png}}
-{\footnotesize (d) MLP: 33.90dB }
+{\footnotesize (d) MLP \cite{mlp}: 33.90dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
-{\footnotesize (e) TRD: 36.18dB  }
+{\footnotesize (e) TRD \cite{chen2015learning}: 36.18dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
-{\footnotesize (f) Noise Clinic: 38.76dB }
+{\footnotesize (f) NoiseClinic \cite{noiseclinic}: 38.76dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
-{\footnotesize (g) Neat Image:37.68dB  }
+{\footnotesize (g) Neat Image \cite{neatimage}: 37.68dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
-{\footnotesize (h) CCNoise:38.37dB }
+{\footnotesize (h) CCNoise \cite{crosschannel2016}: 38.37dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_5dmark3_iso3200_1_real.png}}
-{\footnotesize (j) Mean Image}
+{\footnotesize (j) Mean Image \cite{crosschannel2016}}
 \end{minipage}
@@
 This shows that the proposed method is indeed robust to the chosen of the paramter $\lambda$.
+
 \begin{figure}
 \includegraphics[width=1\linewidth]{images/param.png}
-\caption{The PSNR/SSIM results as a function of the parameter $\lambda$.}
-\label{fig10}
+\caption{The PSNR results as a function of the parameter $\lambda$.}
+\label{fig6}
 \end{figure}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_dog.png}}
-{\footnotesize (a) Noisy Image   }
+{\footnotesize (a) Noisy \cite{ncwebsite}   }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
-{\footnotesize (b) CBM3D}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
-{\footnotesize (c) WNNM    }
+{\footnotesize (c) WNNM \cite{wnnm}   }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
-{\footnotesize (d) MLP }
+{\footnotesize (d) MLP \cite{mlp}  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_dog.png}}
-{\footnotesize (e) TRD }
+{\footnotesize (e) TRD \cite{chen2015learning}}
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
-{\footnotesize (f) Noise Clinic   }
+{\footnotesize (f) Noise Clinic \cite{noiseclinic}  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
-{\footnotesize (g) Neat Image    }
+{\footnotesize (g) Neat Image \cite{neatimage}   }
 \end{minipage}
@@
 \caption{Denoised images of the image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
-\label{fig4}
+\label{fig7}
 \end{figure*}

### 2016-10-28 CVPR2017_Review_Unified.tex
ad

@@
 Some samples can be found in \cite{crosschannel2016}.
-For each scene,  was shot 500 times (with same camera and camera setting).
-The mean image of the 500 shots is roughly taken as the “ground truth”, with which the PSNR can be computed.
-Since there are contents in different images, we cropped the 17 images into 60 smaller parts containing different contents.
+For each image, the same scene was shot 500 times under the same camera and camera setting.
+The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed for comparison.
+Since there are many similar contents in these 17 images, we cropped the 17 images into 60 smaller parts including different contents.
 Some samples are shown in Figure \ref{fig4}.
-The second dataset provided in \cite{ncwebsite} includes about 15 real noisy images collected by the authors of Noise Clinic \cite{noiseclinic,ncwebsite}.
-The third dataset is provided by the Commercial software Neat Image \cite{neatimage}.
-The second and third dataset do not have ground truth images.
+The second dataset provided on \cite{ncwebsite} includes about 15 real noisy images collected by the authors of Noise Clinic \cite{noiseclinic}.
+The third dataset includes 18 color images provided by the website of Neat Image \cite{neatimage}, a commercial software embeded in PhotoShop .
+Different from the first dataset, the second and third datasets do not have ground truth images and hence the PSNR cannot be computed for comparison.
 

### 2016-10-28 CVPR2017_Review_Unified.tex
a

@@
 The testing image is captured by a Nikon D800 camera when ISO is 3200.
-The "ground truth" image is also provided with which we can calculate objective measurements such as PSNR and SSIM \cite{ssim}.
+The "ground truth" image is also provided with which we can calculate objective measurements such as PSNR.
 The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image.
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (d) Guided: \textbf{37.09}dB }
+{\footnotesize (d) Guided: \textbf{37.13}dB }
 \end{minipage}
@@
 
-In the last decade, there are many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} proposed for real image denoising problem.
-In the seminar work of BLS-GSM \cite{blsgsm} for real image denoising, Portilla et al.
-proposed to use scale mixture of Gaussian in overcomplete oriented pyramids to estimate the latent clean images.
-In \cite{fullyblind}, Portilla proposed to use a correlated Gaussian model for noise estimation of each wavelet subband.
+In the last decade, researchers proposed many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for real image denoising problem.
+In \cite{fullyblind}, Portilla proposed to use scale mixture of Gaussian to estimate the noise covariance matrix and latent clean images in wavelet domain.
 The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}.
@@
 The second dataset provided on \cite{ncwebsite} includes about 15 real noisy images collected by the authors of Noise Clinic \cite{noiseclinic}.
-The third dataset includes 18 color images provided by the website of Neat Image \cite{neatimage}, a commercial software embeded in PhotoShop .
-Different from the first dataset, the second and third datasets do not have ground truth images and hence the PSNR cannot be computed for comparison.
+The third dataset includes 18 color images provided by the website of Neat Image \cite{neatimage}, a commercial software embeded in Photoshop CC and Corel PaintShop Pro X9 \cite{neatimage}.
+Different from the first dataset, the second and third datasets do not have ground truth images and hence the PSNR cannot be computed.
 
@@
 \subsection{Implementation Details}
-Our proposed method contains two stages, the external prior guided internal subspace learning stage and the adaptive denoising stage.
-In the learning stage, there are 4 parameters: the patch size $p$, the number of patches in a PG $M$, the window size $W$ for PG searching and the number of clusters $K$.
+Our proposed method contains two learning stages, the external prior learning stage and the external prior guided internal learning stage.
+In the external stage, there are 4 parameters: the patch size $p$, the number of patches in a PG $M$, the window size $W$ for PG searching and the number of Gaussians or subspaces $K$ in Gaussian Mixture Model (GMM).
 We set $p = 6$ (hence the patch size is $6\times 6 \times 3$), $M=10$, $W = 31$, $K=32$.
@@
 The three methods are evaluated on the dataset provided in \cite{crosschannel2016}.
-We calculate the PSNR, SSIM \cite{ssim} and visual quality of these three methods.
+We compare the PSNR and visual quality of these three methods.
 We also compare the speed.
@@
 \hline
-PSNR & 34.51 & 38.19 & 38.07 & \textbf{38.55} 
+PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
 \\
 \hline
-%SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9675}
+%SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9691}
 %\\
@@
 \renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
 \hline
- & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Guided}  &\textbf{Guided2} 
+ & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Guided} 
 \\
 \hline
-PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & 37.75 & 36.53 & 37.57 &  {\color{blue}{38.72}} & {\color{red}{ 38.90}}
+PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
 %\\
 %\hline
-%SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9694}} & {\color{red}{0.9702}}
+%SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
 \\
@@
 \hline
-Camera Settings & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Guided2} 
+Camera Settings & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Guided} 
 \\
@@
 \multirow{3}{*}{ISO = 3200}   
-& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & {\color{blue}{35.69}} & 35.37 & {\color{red}{37.22}}
+& 33.88 & 33.94 & 33.93 & 33.24 & 34.03 & 34.35 & 34.87 & {\color{blue}{35.69}} & 35.37 & {\color{red}{37.05}}
 \\ 
 \cdashline{2-11}    
-& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & {\color{blue}{35.54}} & 34.91 & {\color{red}{37.13}}  
+& 33.83 & 33.88 & 33.90 & 32.37 & 32.63 & 33.10 & 34.77 & {\color{blue}{35.54}} & 34.91 & {\color{red}{36.11}}  
 \\
@@
 \multirow{3}{*}{Nikon D600} 
-& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & {\color{red}{35.57}} & 34.98 & {\color{blue}{35.34}}
+& 33.28 & 33.33 & 33.34 & 31.93 & 31.78 & 32.28 & 34.12 & {\color{red}{35.57}} & {\color{blue}{34.98}} & 34.88
 \\ 
@@
 \multirow{3}{*}{ISO = 3200}   
-& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & {\color{red}{36.70}} & 35.95 & {\color{blue}{36.69}}
+& 33.77 & 33.85 & 33.79 & 34.15 & 35.16 & 35.34 & 35.36 & {\color{red}{36.70}} & 35.95 & {\color{blue}{36.31}}
 \\ 
 \cdashline{2-11}    
-& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & {\color{blue}{40.51}} & 38.68 & 39.28 & {\color{red}{41.15}} & 39.17
+& 34.93 & 35.02 & 34.95 & 37.89 & 39.98 & {\color{blue}{40.51}} & 38.68 & 39.28 & {\color{red}{41.15}} & 39.23
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & {\color{blue}{38.01}} & 37.99 & {\color{red}{38.82}}
+& 35.47 & 35.54 & 35.57 & 33.77 & 34.84 & 35.09 & 37.34 & {\color{blue}{38.01}} & 37.99 & {\color{red}{38.40}}
 \\ 
@@
 \multirow{3}{*}{ISO = 1600}   
-& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & {\color{blue}{40.36}} & {\color{red}{40.98}}
+& 35.71 & 35.79 & 35.77 & 35.89 & 38.42 & 38.65 & 38.57 & 39.05 & {\color{blue}{40.36}} & {\color{red}{40.92}}
 \\ 
 \cdashline{2-11}    
-& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & {\color{blue}{38.30}} & {\color{red}{38.90}}
+& 34.81 & 34.92 & 34.95 & 34.25 & 35.79 & 35.85 & 37.87 & 38.20 & {\color{blue}{38.30}} & {\color{red}{38.97}}
 \\
@@
 \multirow{3}{*}{Nikon D800} 
-& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & {\color{red}{39.01}} & {\color{blue}{38.69}}
+& 33.26 & 33.34 & 33.31 & 37.42 & 38.36 & 38.56 & 36.95 & 38.07 & {\color{red}{39.01}} & {\color{blue}{38.66}}
 \\ 
@@
 \multirow{3}{*}{ISO = 3200}   
-& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & {\color{blue}{36.75}} & {\color{red}{36.82}}
+& 32.89 & 32.95 & 32.96 & 34.88 & 35.53 & 35.76 & 35.09 & 35.72 & {\color{blue}{36.75}} & {\color{red}{37.07}}
 \\ 
 \cdashline{2-11}    
-& 32.91 & 32.98 & 32.96 & 38.54 & {\color{blue}{40.05}} & {\color{red}{40.59}} & 36.91 & 36.76 & 39.06 & 38.80
+& 32.91 & 32.98 & 32.96 & 38.54 & {\color{blue}{40.05}} & {\color{red}{40.59}} & 36.91 & 36.76 & 39.06 & 38.52
 \\ 
@@
 \multirow{3}{*}{Nikon D800} 
-& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & {\color{blue}{34.25}} & 31.28 & 33.49 & {\color{red}{34.61}} & 33.31
+& 29.63 & 29.66 & 29.71 & 33.59 & 34.08 & {\color{blue}{34.25}} & 31.28 & 33.49 & {\color{red}{34.61}} & 33.76
 \\ 
@@
 \multirow{3}{*}{ISO = 6400}   
-& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & {\color{red}{33.21}} & {\color{blue}{33.18}}
+& 29.97 & 30.01 & 29.98 & 31.55 & 32.13 & 32.38 & 31.38 & 32.79 & {\color{blue}{33.21}} & {\color{red}{33.43}}
 \\ 
 \cdashline{2-11}    
-& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & {\color{blue}{33.22}} & {\color{red}{33.35}}
+& 29.87 & 29.90 & 29.95 & 31.42 & 31.52 & 31.76 & 31.40 & 32.86 & {\color{blue}{33.22}} & {\color{red}{33.58}}
 \\
 \hline
-Average & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & {\color{blue}{36.88}} & {\color{red}{ 37.26}}
+Average & 33.41 & 33.48 & 33.48 & 34.32 & 35.33 & 35.65 & 35.49 & 36.43 & {\color{blue}{36.88}} & {\color{red}{ 37.16}}
 \\
@@
 
-{\small
+{
+\small
 \bibliographystyle{unsrt}

### 2016-10-28 CVPR2017_Review_Unified.tex
add

@@
 To evaluation the effectiveness of the proposed framework of external prior guided internal prior learning, we compare it with the methods with only external prior or only internal prior.
-This will be discussed in Section 4.2.
-We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage}.
+This will be discussed in Section 4.3.
+We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage} in Section 4.4..
 
@@
 The third dataset includes 18 color images provided by the website of Neat Image \cite{neatimage}, a commercial software embeded in Photoshop CC and Corel PaintShop Pro X9 \cite{neatimage}.
-Different from the first dataset, the second and third datasets do not have ground truth images and hence the PSNR cannot be computed.
+Different from the first dataset, the second and third datasets do not have ground truth images and hence the PSNR cannot be computed  for comparison.
 
@@
 \caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
+\vspace{-4mm}
 \label{fig4}
@@
 We set $p = 6$ (hence the patch size is $6\times 6 \times 3$), $M=10$, $W = 31$, $K=32$.
-We extracted about 3.6 million PGs from the Kodak PhotoCD Dataset, which includes 24 high quality color images, to train the external prior via PG-GMM.
-In the denoising stage, the paramter $\lambda = 0.002$ is used to regularize the sparse term.
-The $\delta$ in iterative regularization is set as $\delta = 0.09$.
-Given a RGB image of size $256\times256\times3$, we can extract over 60 thousands local patches of size $6\times6\times3$.
-It is time-consumming to search patch groups (PG) for local patches one by one.
-To speed up the searching process, we employ the technique of 'Summed Area Table' \cite{sat} for efficient PG searching.
-The SAT permits to evaluate the sum of pixel values in rectangular regions of the image with four operations, regardless of the region size.
-Hence, we do not need do distance measure for each local patch.
+We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
 
-\subsection{Comparison on External and Internal methods}
+In the external prior guided internal learning stage, there are 4 parameters: $r$ is the number of internal atoms in the learned orthogonal dictionaries, $\lambda$ is the sparse regularization parameter, $T$ the number of iterations for alternative solving problem (\ref{equ5}), and $IteNum$ the number of iterations for denoising algorithm Alg.
+1.
+We set $r=3p^2/2=54$ to treat equally for external and internal priors.We set $\lambda=0.001$, $T=2$, and $IteNum=4$ for our experiments.
+
+\subsection{Comparison with External and Internal Priors}
 In this subsection, we compared the proposed external prior guided internal subspace learning model on real image denoising.
 The three methods are evaluated on the dataset provided in \cite{crosschannel2016}.
-We compare the PSNR and visual quality of these three methods.
+We compare the PSNR and visual quality of these three m ethods.
 We also compare the speed.
@@
 \caption{Average PSNR(dB) results of External, Internal, and Guided methods on 60 cropped real noisy images in \cite{crosschannel2016}.}
+\vspace{-2mm}
 \label{tab1}
@@
 \end{tabular}
-\end{center}
+\end{center}\vspace{-4mm}
 \end{table}
@@
 
-\subsection{Comparison With other Competing Methods}
+\subsection{Comparison with Other Denoising Methods}
 We compare with previous state-of-the-art Gaussian noise removal methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and the recently proposed TRD \cite{chen2015learning}.
@@
 
+\clearpage
 {

### 2016-10-28 CVPR2017_Review_Unified.tex
add

@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.66dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 36.15dB   }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (b) External: 34.97dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (h) External: 37.12dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (c) Internal: 36.86dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (i) Internal: 35.70dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (d) Guided: \textbf{37.13}dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (j) Guided: \textbf{37.94}dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (e) Mean Image \cite{crosschannel2016}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (h) Mean Image \cite{crosschannel2016} }
 \end{minipage}
 }
-\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
-\vspace{-4mm}
+\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}\vspace{-4mm}
 \label{fig2}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (a) Noisy \cite{crosschannel2016}: 36.15dB   }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.66dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (h) External: 37.12dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (b) External: 34.97dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (i) Internal: 35.70dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (c) Internal: 36.86dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (j) Guided: \textbf{37.94}dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (d) Guided: \textbf{37.13}dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (h) Mean Image \cite{crosschannel2016} }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+{\footnotesize (e) Mean Image \cite{crosschannel2016}}
 \end{minipage}
 }
-\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}\vspace{-4mm}
+\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
+\vspace{-4mm}
 \label{fig3}
@@
 The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed for comparison.
-Since there are many similar contents in these 17 images, we cropped the 17 images into 60 smaller parts including different contents.
+Since there are many similar contents in these 17 images, we cropped the 17 images into 60 smaller parts ($500\times 500$) including different contents.
 Some samples are shown in Figure \ref{fig4}.
 The second dataset provided on \cite{ncwebsite} includes about 15 real noisy images collected by the authors of Noise Clinic \cite{noiseclinic}.
-The third dataset includes 18 color images provided by the website of Neat Image \cite{neatimage}, a commercial software embeded in Photoshop CC and Corel PaintShop Pro X9 \cite{neatimage}.
-Different from the first dataset, the second and third datasets do not have ground truth images and hence the PSNR cannot be computed  for comparison.
+The third dataset includes 18 color images provided by the website of Neat Image \cite{neatimage}.
+Different from the first dataset, the other two datasets do not have "ground truth" images.
 
@@
 \end{minipage}
-}\vspace{-0.14in}
+}\vspace{-3mm}
 \subfigure{
@@
 \end{minipage}
-}\vspace{-2mm}
+}\vspace{-3mm}
 \subfigure{
@@
 \end{minipage}
-}
+}\vspace{-4mm}
 \caption{Denoised images of the image "Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
@@
 Our proposed method contains two learning stages, the external prior learning stage and the external prior guided internal learning stage.
-In the external stage, there are 4 parameters: the patch size $p$, the number of patches in a PG $M$, the window size $W$ for PG searching and the number of Gaussians or subspaces $K$ in Gaussian Mixture Model (GMM).
+In the external stage, there are 4 parameters: the patch size $p$, the number of patches in a patch group (PG) $M$, the window size $W$ for PG searching and the number of Gaussians or subspaces $K$ in Gaussian Mixture Model (GMM).
 We set $p = 6$ (hence the patch size is $6\times 6 \times 3$), $M=10$, $W = 31$, $K=32$.
 We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
-
-In the external prior guided internal learning stage, there are 4 parameters: $r$ is the number of internal atoms in the learned orthogonal dictionaries, $\lambda$ is the sparse regularization parameter, $T$ the number of iterations for alternative solving problem (\ref{equ5}), and $IteNum$ the number of iterations for denoising algorithm Alg.
+In the external prior guided internal learning stage, there are 4 parameters: $r$ is the number of internal atoms in the learned orthogonal dictionaries, $\lambda$ is the sparse regularization parameter, $T$ the number of iterations for alternative solving problem (\ref{equ5}), and $IteNum$ the number of iterations for the denoising algorithm Alg.
 1.
-We set $r=3p^2/2=54$ to treat equally for external and internal priors.We set $\lambda=0.001$, $T=2$, and $IteNum=4$ for our experiments.
+We set $r=3p^2/2=54$ to treat equally external and internal priors.
+We set $\lambda=0.001$, $T=2$, and $IteNum=4$.
 
 \subsection{Comparison with External and Internal Priors}
-In this subsection, we compared the proposed external prior guided internal subspace learning model on real image denoising.
-The three methods are evaluated on the dataset provided in \cite{crosschannel2016}.
-We compare the PSNR and visual quality of these three m ethods.
-We also compare the speed.
-The PSNR and SSIM results on 60 cropped images from \cite{crosschannel2016} are listed in Table 1.
-The images are cropped into size of $500\times 500$ for better illustration.
-We also compare the three methods on visual quality in Figure \ref{fig2}.
-Compare the denoised images listed in Figure \ref{fig2} and Figure \ref{fig2}, we can see that the Offline method is better at edges, smooth regions while the Online method is good at complex textures.
-The reason is two folds.
-Firstly, the Offline method is learned on clean images and hence is better at representing edges, structuals, and smooth area.
-The online method is influenced by the noise and hence some noise cannot be removed.
-Secondly, the Online method is better at recovering complex area sicne they could learn adaptive dictionaries for the specific area.
-The Offline method cannot recover the complex area since they did not learn the similar structures from the external natural clean images.
+In this section, we compare the proposed external prior guided internal prior learning framework with external prior method (denoted as "External") and internal prior method (denoted as "Internal") on real image denoising.
+Both methods perform real image denoising under the weighted sparse coding framework in Equ.
+(\ref{equ5}).
+The "External" method employs the external dictionaries (i.e., $r=0$ in Equ.
+(\ref{equ5})) to recover the latent clean images, while the "Internal" method directly utilizes the Gaussian Mixture Model to cluster the internal niosy PGs into multiple subspaces and perform denoising with internal dictionaries (i.e., $r=128$ in Equ.
+(\ref{equ5})).
 
-\begin{table}\label{tab1}
+We compare the "External" method, the "Internal" method, and the proposed method (denoted as "Guided") on the first dataset provided in \cite{crosschannel2016}.
+We compare the PSNR and visual quality of these three methods.
+The average PSNR results on 60 cropped images from \cite{crosschannel2016} are listed in Table \ref{tab1}.
+It can be seen that the proposed "Guided" method achieves higher PSNR results then the "External" and "Internal" methods.
+We also compare the visual qualities of denoised images listed in Figure \ref{fig2} and Figure \ref{fig3}.
+We can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering complex textures (Figure \ref{fig3}).
+And if we make use of both the external and internal priors, the proposed "Guided" method can recover well both the structures and complex textures.
+
+\begin{table}
 \caption{Average PSNR(dB) results of External, Internal, and Guided methods on 60 cropped real noisy images in \cite{crosschannel2016}.}
+\label{tab1}
 \vspace{-2mm}
-\label{tab1}
 \begin{center}
@@
 
-\begin{table*}\label{tab1}
+\begin{table*}
 \caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
-\label{tab1}
+\label{tab2}
 \begin{center}
@@
 \end{tabular}
-\end{center}
+\end{center}\vspace{-5mm}
 \end{table*}
@@
 We also compare with three competing real image denoising methods such as Noise Clinic, Neat Image, and the CCNoise method proposed recently.
-The commercial software Neat Image \cite{neatimage} first estimates the parameters of noise via a large flat area and then filters the noise accordingly.
+Neat Image \cite{neatimage} is a commercial software embeded in Photoshop CC and Corel PaintShop Pro X9 \cite{neatimage}.
+It first estimates the parameters of noise via a large flat area and then filters the noise accordingly.
 All these methods need noise estimation which is vary hard to perform if there is no uniform regions are available in the testing image.
@@
 
-\begin{figure}
+\begin{figure}\vspace{-3mm}
 \includegraphics[width=1\linewidth]{images/param.png}
+\vspace{-6mm}
 \caption{The PSNR results as a function of the parameter $\lambda$.}
+\vspace{-4mm}
 \label{fig6}
@@
 
-\begin{table*}\label{tab2}
+\begin{table*}
 \caption{Average PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
-\label{tab1}
+\label{tab3}
 \begin{center}

### 2016-10-28 CVPR2017_Review_Unified.tex
add

@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.33dB  }
+{\footnotesize (b) BM3D \cite{bm3d,cbm3d}: 33.33dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (h) External: 37.12dB }
+{\footnotesize (b) External: 37.12dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (i) Internal: 35.70dB  }
+{\footnotesize (c) Internal: 35.70dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (j) Guided: \textbf{37.94}dB  }
+{\footnotesize (d) Ours: \textbf{37.94}dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (h) Mean Image \cite{crosschannel2016} }
+{\footnotesize (e) Mean Image \cite{crosschannel2016} }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (d) Guided: \textbf{37.13}dB }
+{\footnotesize (d) Ours: \textbf{37.13}dB }
 \end{minipage}
@@
 \subsection{The Testing Datasets}
-The comparisons are performed on three standard datasets, in which the images were captured by different types of cameras and camera settings under indoor and outdoor lighting conditions.
-The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images.
+
+The comparisons are performed on two standard datasets in which the images were captured under indoor and outdoor lighting conditions by different types of cameras and camera settings.
+The first dataset is provided in \cite{crosschannel2016}.
+It includes 17 real noisy images and corresponding mean images.
 The noisy images were collected under controlled indoor environment.
@@
 For each image, the same scene was shot 500 times under the same camera and camera setting.
-The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed for comparison.
-Since there are many similar contents in these 17 images, we cropped the 17 images into 60 smaller parts ($500\times 500$) including different contents.
+The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed.
+Since there are many similar contents in these 17 images, we cropped thses images into 60 smaller images (of size $500\times 500$) including different contents.
 Some samples are shown in Figure \ref{fig4}.
-The second dataset provided on \cite{ncwebsite} includes about 15 real noisy images collected by the authors of Noise Clinic \cite{noiseclinic}.
-The third dataset includes 18 color images provided by the website of Neat Image \cite{neatimage}.
-Different from the first dataset, the other two datasets do not have "ground truth" images.
+The authors of \cite{crosschannel2016} also provided us the 15 images (of size $512\times 512$) used in \cite{crosschannel2016} and hence we can compare with the method of \cite{crosschannel2016}.
+Noted that the noise in the 15 images used in \cite{crosschannel2016} is different from the noise in the 60 images cropped from \cite{crosschannel2016} since they are taken in different shots.
+The second dataset is provided in \cite{ncwebsite} includes about 15 real noisy images collected under uncontrolled outdoor environment.
+This dataset do not have "ground truth" images.
 
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
-{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 37.02dB}
+{\footnotesize (b) BM3D \cite{bm3d,cbm3d}: 37.02dB}
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
-{\footnotesize (i) Guided: \textbf{40.26}dB}
+{\footnotesize (i) Ours: \textbf{40.26}dB}
 \end{minipage}
@@
 \subsection{Implementation Details}
-Our proposed method contains two learning stages, the external prior learning stage and the external prior guided internal learning stage.
+Our proposed denoising method contains two learning stages, the external prior learning stage and the external prior guided internal learning stage.
 In the external stage, there are 4 parameters: the patch size $p$, the number of patches in a patch group (PG) $M$, the window size $W$ for PG searching and the number of Gaussians or subspaces $K$ in Gaussian Mixture Model (GMM).
@@
 \subsection{Comparison with External and Internal Priors}
-In this section, we compare the proposed external prior guided internal prior learning framework with external prior method (denoted as "External") and internal prior method (denoted as "Internal") on real image denoising.
+In this section, we compare the proposed method with external prior method (denoted as "External") and internal prior method (denoted as "Internal") on real image denoising.
 Both methods perform real image denoising under the weighted sparse coding framework in Equ.
@@
 
-We compare the "External" method, the "Internal" method, and the proposed method (denoted as "Guided") on the first dataset provided in \cite{crosschannel2016}.
-We compare the PSNR and visual quality of these three methods.
-The average PSNR results on 60 cropped images from \cite{crosschannel2016} are listed in Table \ref{tab1}.
+We compare the PSNR and visual quality of the "External" method, the "Internal" method, and the proposed method (denoted as "Ours") on the first dataset provided in \cite{crosschannel2016}.
+The average PSNR results of these methods on 60 cropped images from \cite{crosschannel2016} are listed in Table \ref{tab1}.
 It can be seen that the proposed "Guided" method achieves higher PSNR results then the "External" and "Internal" methods.
@@
 We can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering complex textures (Figure \ref{fig3}).
-And if we make use of both the external and internal priors, the proposed "Guided" method can recover well both the structures and complex textures.
+And if we make use of both the external and internal priors, our proposed method can recover well both the structures and complex textures.
 
 \begin{table}
-\caption{Average PSNR(dB) results of External, Internal, and Guided methods on 60 cropped real noisy images in \cite{crosschannel2016}.}
+\caption{Average PSNR(dB) results of External, Internal, and our proposed methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
 \label{tab1}
@@
 \hline
- & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Guided}  
+ & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Ours}  
 \\
@@
 \begin{table*}
-\caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
+\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
 \label{tab2}
@@
 \hline
- & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Guided} 
+ & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
 \\
@@
 \subsection{Comparison with Other Denoising Methods}
-We compare with previous state-of-the-art Gaussian noise removal methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and the recently proposed TRD \cite{chen2015learning}.
-We also compare with three competing real image denoising methods such as Noise Clinic, Neat Image, and the CCNoise method proposed recently.
-Neat Image \cite{neatimage} is a commercial software embeded in Photoshop CC and Corel PaintShop Pro X9 \cite{neatimage}.
-It first estimates the parameters of noise via a large flat area and then filters the noise accordingly.
-All these methods need noise estimation which is vary hard to perform if there is no uniform regions are available in the testing image.
-The NeatImage will fail to perform automatical parameters settings if there is no uniform regions.
-\footnote{To compare with CCNoise, we first transform the denoised images into double format.}
+%For BM3D, we employ its color version \cite{cbm3d} which would have better performance on color images.
 
-We the competing denoising methods from various research directions on two datasets.
-Both the two datasets comes from the \cite{crosschannel2016}.
-The first dataset contains 17 images of size over $7000\times5000$.
-Since this dataset contains repetitive contents across different images, we crop 60 small images of size $500\times500$ from these 17 images in \cite{crosschannel2016}.
-The PSNR and SSIM resluts are listed in Table \ref{tab1}.
+In this section, we compare the proposed method  with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning}.
+These methods are designed for removing Gaussian noise.
+For BM3D and WNNM, the level $\sigma$ of Gaussian noise is very important and is estimated by the method \cite{noiselevel}.
+The other parameters are set as default.
+For the methods of MLP, CSF, and TRD, we employ their default paramters settings.
+Since these methods are designed for grayscale images, we utilize them to denoise the R, G, B channels seperately for color noisy images.
+We also compare with three other denoising methods \cite{noiseclinic,neatimage,crosschannel2016}.
+The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior for image denoising.
+The Neat Image (NI) is a commercial software on image denoising and is embeded into Photoshop CC and Corel PaintShop Pro X9 \cite{neatimage}.
+The recently proposed method Cross-Channel (CC) \cite{crosschannel2016} is a state-of-the-art method for real image denoising problem.
+The comparison is performed on the two datasets mentioned in Section 4.1.
+
+For the first dataset, the average PSNR values on the 60 images cropped from \cite{crosschannel2016} are listed in Table \ref{tab2}.
 The number in red color and blue color means the best and second best results, respectively.
-From the Table \ref{tab1}, we can see that the external based method can already surpass largely the previous denoising methods.
-The improvement on PSNR over the second best method, i.e., TRD, is 0.44dB.
-The
+It can be seen that our proposed method achieves the best PSNR results than other methods and the gap over the second best result (blue) is 1dB.
+Considering that the 60 cropped images contain different scenes with complex noise, the improvements of our proposed method is impressed.
+Besides, to compare with the recently proposed \cite{crosschannel2016}, we also perform experiments on the 15 images used in \cite{crosschannel2016}.
+The comparison  on PSNR values are listed in Table \ref{tab3}.
+As we can see, our proposed method obtains best PSNR values on most (9 out of 15) of the images captured by different camera settings.
+Noted that, though the method \cite{crosschannel2016} trains a specific model for each camera settng, our proposed general method still gains 0.28dB improvements over \cite{crosschannel2016}.
+We also compare the visual quality of the compared method.
+For example, Figure \ref{fig5} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO$=3200$.
+More visual comparisons can be found in the supplementary file.
+We can see that BM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts while MLP, TRD are likely to over-smooth the image.
+Our proposed method preserves edges and textures much better than other methods.
 
-\subsection{Discussion on Parameter $\lambda$}
-The proposed method only has a key parameter, namely the regularization paramters $\lambda$.
-To demonstrate that the proposed method is robust to the variance of $\lambda$, we vary the parameter $\lambda$ across a wide range and obtain the PSNR and SSIM results as a function of the parameter $\lambda$.
-The results is shown in Figure \ref{fig10}, from which we can see that the proposed method can achieve a PSNR (SSIM) over 38.5dB (0.9660) when $\lambda$ varies from $0.0015$ to $0.0025$.
-This shows that the proposed method is indeed robust to the chosen of the paramter $\lambda$.
+For the second dataset provided in \cite{ncwebsite}, we can only compare the visual quality of the images denoised by different methods.
+In Figure \ref{fig6}, we take the real noisy image "Dog" as an example and more visual comparisons can be found in the supplementary file.
+It can be seen that the methods of BM3D, WNNM would over-smooth the whole image while remain some noise in local areas.
+The methods of MLP, TRD also remain a lot of noise in the whole image.
+This demonstrates that the methods designed for Gaussian noise are not suitable for the complex noise in real noisy images.
+Even Noise Clinic and Neat Image, which are specifically developed for real noisy images, would sometimes fail to deal with the complex noise in real noisy images.
+However, we can see that the proposed algorithm recoveries more faithfully the fine structures of the eye area than the other competing methods.
 
-\begin{figure}\vspace{-3mm}
-\includegraphics[width=1\linewidth]{images/param.png}
-\vspace{-6mm}
-\caption{The PSNR results as a function of the parameter $\lambda$.}
-\vspace{-4mm}
-\label{fig6}
-\end{figure}
+In summary, our proposed external prior guided internal prior learning algorithm demonstrates impressing ability on dealing with the complex noise in real noisy images in terms of PSNR and visual quality.
 
@@
 \hline
-Camera Settings & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Guided} 
+Camera Settings & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Guided} 
 \\
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
-{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
+{\footnotesize (b) BM3D \cite{bm3d,cbm3d}  }
 \end{minipage}
@@
 \caption{Denoised images of the image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
-\label{fig7}
+\label{fig6}
 \end{figure*}
@@
 This will be our line of future work.
-
+In the future, we will evaluate the proposed method on other conputer vision tasks such as single image super-resolution, photo-sketch synthesis, and cross-domain image recognition.
+Our proposed method can be improved if we use better training images, fine tune the parameters via cross-validation.
 \clearpage

### 2016-10-28 CVPR2017_Review_Unified.tex
ad

@@
 \subsection{Implementation Details}
-Our proposed denoising method contains two learning stages, the external prior learning stage and the external prior guided internal learning stage.
-In the external stage, there are 4 parameters: the patch size $p$, the number of patches in a patch group (PG) $M$, the window size $W$ for PG searching and the number of Gaussians or subspaces $K$ in Gaussian Mixture Model (GMM).
-We set $p = 6$ (hence the patch size is $6\times 6 \times 3$), $M=10$, $W = 31$, $K=32$.
+Our proposed denoising method contains two stages, the external prior learning stage and the external prior guided internal learning stage.
+In the first stage, there are 4 parameters: the $p$ is set as $p = 6$ (hence the patch size is $6\times 6 \times 3$), the number of patches in a patch group (PG) is set as $M=10$, the window size for PG searching is set as $W=31$, and the number of Gaussians in Gaussian Mixture Model (GMM) is set as $K=32$.
 We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
-In the external prior guided internal learning stage, there are 4 parameters: $r$ is the number of internal atoms in the learned orthogonal dictionaries, $\lambda$ is the sparse regularization parameter, $T$ the number of iterations for alternative solving problem (\ref{equ5}), and $IteNum$ the number of iterations for the denoising algorithm Alg.
-1.
-We set $r=3p^2/2=54$ to treat equally external and internal priors.
-We set $\lambda=0.001$, $T=2$, and $IteNum=4$.
+In the second stage, there are 4 parameters: the number of internal atoms in the learned dictionaries is set as $r=3p^2/2=54$, the sparse regularization parameter is set as $\lambda=0.001$, the number of iterations for solving problem (\ref{equ5}) is set as $T=2$, and the number of iterations for the denoising algorithm is set as $IteNum=4$.
+Our proposed method needs about 60 seconds to denoise an image of size $512\times512\times3$ under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.
 
 \subsection{Comparison with External and Internal Priors}
-In this section, we compare the proposed method with external prior method (denoted as "External") and internal prior method (denoted as "Internal") on real image denoising.
-Both methods perform real image denoising under the weighted sparse coding framework in Equ.
+In this section, we compare our proposed method on real image denoising with external prior based method (denoted as "External") and internal prior based method (denoted as "Internal").
+All the three methods perform real image denoising under the weighted sparse coding framework in Equ.
 (\ref{equ5}).
 The "External" method employs the external dictionaries (i.e., $r=0$ in Equ.
-(\ref{equ5})) to recover the latent clean images, while the "Internal" method directly utilizes the Gaussian Mixture Model to cluster the internal niosy PGs into multiple subspaces and perform denoising with internal dictionaries (i.e., $r=128$ in Equ.
+(\ref{equ5})) to recover the latent clean images, while the "Internal" method directly learn the subspace structures from the internal PGs via GMM and perform denoising with internal dictionary learning (i.e., $r=128$ in Equ.
 (\ref{equ5})).
+All parameters are tuned to achieve the best performance.
 
-We compare the PSNR and visual quality of the "External" method, the "Internal" method, and the proposed method (denoted as "Ours") on the first dataset provided in \cite{crosschannel2016}.
-The average PSNR results of these methods on 60 cropped images from \cite{crosschannel2016} are listed in Table \ref{tab1}.
-It can be seen that the proposed "Guided" method achieves higher PSNR results then the "External" and "Internal" methods.
+We compare the three methods on the 60 cropped images from \cite{crosschannel2016}.
+The average PSNR results of these methods are listed in Table \ref{tab1}.
+It can be seen that our proposed method achieves higher PSNR results then the "External" and "Internal" methods.
 We also compare the visual qualities of denoised images listed in Figure \ref{fig2} and Figure \ref{fig3}.
 We can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering complex textures (Figure \ref{fig3}).
-And if we make use of both the external and internal priors, our proposed method can recover well both the structures and complex textures.
+And if we make use of both the external and internal priors, our proposed method can recover well both the structures and textures.
+
+In summary, the proposed algorithm achieves better performance on denoising real images than the external and internal prior based methods.
 
@@
 The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior for image denoising.
-The Neat Image (NI) is a commercial software on image denoising and is embeded into Photoshop CC and Corel PaintShop Pro X9 \cite{neatimage}.
+The Neat Image (NI) is a commercial software on image denoising and is embeded into Photoshop and Corel PaintShop Pro \cite{neatimage}.
 The recently proposed method Cross-Channel (CC) \cite{crosschannel2016} is a state-of-the-art method for real image denoising problem.
-The comparison is performed on the two datasets mentioned in Section 4.1.
+The comparison is performed on the two datasets mentioned above.
 
@@
 
-In summary, our proposed external prior guided internal prior learning algorithm demonstrates impressing ability on dealing with the complex noise in real noisy images in terms of PSNR and visual quality.
+In summary, our proposed algorithm demonstrates impressing ability on dealing with the complex noise in real noisy images in terms of PSNR and visual quality.
 
@@
 \end{tabular}
-\end{center}
+\end{center}\vspace{-3mm}
 \end{table*}
@@
 \caption{Denoised images of the image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
+\vspace{-2mm}
 \label{fig6}
@@
 
-In the future, we will evaluate the proposed method on other conputer vision tasks such as single image super-resolution, photo-sketch synthesis, and cross-domain image recognition.
-Our proposed method can be improved if we use better training images, fine tune the parameters via cross-validation.
-We believe that our framework can be useful not just for real image denoising, but for image super-resolution, image cross-style synthesis, and recognition tasks.
-This will be our line of future work.
-In the future, we will evaluate the proposed method on other conputer vision tasks such as single image super-resolution, photo-sketch synthesis, and cross-domain image recognition.
-Our proposed method can be improved if we use better training images, fine tune the parameters via cross-validation.
+The image priors are commonly used for image denoising problem.
+The external priors are general but not adaptive to specific images, while the internal priors are adaptive but would largely degraded by the complex noise in real noisy images.
+In this paper, we demonstrates that, we can unify the priors in external clean images and in internal noisy images to achieve better performance on real image denoising problem.
+This unify can be attempted by employing the external prior learned on natural images to guide the internal prior learning on given noisy images.
+The experiments on standard datasets have demonstrated the powerful ability of the proposed method.
+In the future, we will evaluate the proposed method on other conputer vision tasks such as image super-resolution, image deblurring, etc.
+
 \clearpage

### 2016-10-29 CVPR2017_Review_Unified.tex
a

@@
 Since dictionary $\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problems (\ref{equ8}) has a closed-form solution \cite{pgpd} 
-\vspace{-2mm}
-\begin{equation}\label{equ9}\vspace{-2mm}
+\vspace{-1mm}
+\begin{equation}\label{equ9}\vspace{-1mm}
 \bm{\alpha}_{n,m}^{(t)}= \text{sgn}(\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m}|-\mathbf{\Lambda},\mathbf{0}),
@@
 In this section, we evaluate the performance of the proposed algorithm on real image denoising.
-To evaluation the effectiveness of the proposed framework of external prior guided internal prior learning, we compare it with the methods with only external prior or only internal prior.
-This will be discussed in Section 4.3.
-We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage} in Section 4.4..
+To evaluation the effectiveness of the proposed framework of external prior guided internal prior learning, we compare it with the methods with only external prior or only internal prior (Section 4.3).
+We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage} (Section 4.4).
 
@@
 The comparisons are performed on two standard datasets in which the images were captured under indoor and outdoor lighting conditions by different types of cameras and camera settings.
-The first dataset is provided in \cite{crosschannel2016}.
-It includes 17 real noisy images and corresponding mean images.
+The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images.
 The noisy images were collected under controlled indoor environment.
@@
 The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed.
-Since there are many similar contents in these 17 images, we cropped thses images into 60 smaller images (of size $500\times 500$) including different contents.
+Since the 17 images share repetitive contents, we cropped these images into 60 smaller images (of size $500\times 500\times3$) including different contents.
 Some samples are shown in Figure \ref{fig4}.
-The authors of \cite{crosschannel2016} also provided us the 15 images (of size $512\times 512$) used in \cite{crosschannel2016} and hence we can compare with the method of \cite{crosschannel2016}.
+We also perform comparison on the 15 testing images (of size $512\times 521\times3$) used in \cite{crosschannel2016}.
 Noted that the noise in the 15 images used in \cite{crosschannel2016} is different from the noise in the 60 images cropped from \cite{crosschannel2016} since they are taken in different shots.
-The second dataset is provided in \cite{ncwebsite} includes about 15 real noisy images collected under uncontrolled outdoor environment.
-This dataset do not have "ground truth" images.
+The second dataset provided in \cite{ncwebsite} includes about 20 real noisy images collected under uncontrolled outdoor environment.
+These images do not have "ground truth" images.
 
@@
 }
-\caption{Denoised images of the image "$5dmark3 iso3200 3$" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the image "Dog" by different methods. The images are better to be zoomed in on screen.}
 \vspace{-2mm}

### 2016-10-29 CVPR2017_Review_Unified.tex
add

@@
 where $n=1,...,N;m=1,...,M$.
-\begin{table}
-\label{alg1}
+\begin{table}\label{alg1}
 \begin{tabular}{l}
@@
 
-The comparisons are performed on two standard datasets in which the images were captured under indoor and outdoor lighting conditions by different types of cameras and camera settings.
+The comparisons are performed on two standard datasets in which the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings.
 The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images.
@@
 The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed.
-Since the 17 images share repetitive contents, we cropped these images into 60 smaller images (of size $500\times 500\times3$) including different contents.
+Since the 17 images share repetitive contents, we cropped them into 60 smaller images (of size $500\times 500\times3$) including different contents.
 Some samples are shown in Figure \ref{fig4}.
-We also perform comparison on the 15 testing images (of size $512\times 521\times3$) used in \cite{crosschannel2016}.
+We also perform comparison on the 15 cropped images (of size $512\times 521\times3$) used in \cite{crosschannel2016}.
 Noted that the noise in the 15 images used in \cite{crosschannel2016} is different from the noise in the 60 images cropped from \cite{crosschannel2016} since they are taken in different shots.
 The second dataset provided in \cite{ncwebsite} includes about 20 real noisy images collected under uncontrolled outdoor environment.
-These images do not have "ground truth" images.
+This dataset does not have "ground truth" images.
 
@@
 \caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
-\vspace{-4mm}
+\vspace{-2mm}
 \label{fig4}
@@
 \subsection{Implementation Details}
-Our proposed denoising method contains two stages, the external prior learning stage and the external prior guided internal learning stage.
-In the first stage, there are 4 parameters: the $p$ is set as $p = 6$ (hence the patch size is $6\times 6 \times 3$), the number of patches in a patch group (PG) is set as $M=10$, the window size for PG searching is set as $W=31$, and the number of Gaussians in Gaussian Mixture Model (GMM) is set as $K=32$.
+Our proposed method contains two stages, the external prior learning stage and the external prior guided internal learning stage.
+In the first stage, we set $p = 6$ (so the patch size is $6\times 6 \times 3$), $M=10$ (the number of patches in a patch group (PG)), $W=31$ (so the window size for PG searching is $31\times31$, and $K=32$ (the number of Gaussians in Gaussian Mixture Model (GMM)).
 We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
-In the second stage, there are 4 parameters: the number of internal atoms in the learned dictionaries is set as $r=3p^2/2=54$, the sparse regularization parameter is set as $\lambda=0.001$, the number of iterations for solving problem (\ref{equ5}) is set as $T=2$, and the number of iterations for the denoising algorithm is set as $IteNum=4$.
+In the second stage, we set $r=54$ (the number of internal atoms in the learned dictionaries), $\lambda=0.001$ (the sparse regularization parameter), $T=2$ (the number of iterations for solving problem (\ref{equ5})), and $IteNum=4$ (the number of iterations for Alg.
+1).
 Our proposed method needs about 60 seconds to denoise an image of size $512\times512\times3$ under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.
@@
 The "External" method employs the external dictionaries (i.e., $r=0$ in Equ.
-(\ref{equ5})) to recover the latent clean images, while the "Internal" method directly learn the subspace structures from the internal PGs via GMM and perform denoising with internal dictionary learning (i.e., $r=128$ in Equ.
-(\ref{equ5})).
-All parameters are tuned to achieve the best performance.
+(\ref{equ5})) to recover the latent clean images, while the "Internal" method employ the GMM to directly cluster the internal noisy PGs into multiple subspaces, and perform denoising with internal dictionary learning (i.e., $r=128$ in Equ.
+(\ref{equ5})) for each subspace.
+All parameters of the three methods are tuned to achieve corresponding best performance.
 

### 2016-10-29 CVPR2017_Review_Unified.tex
a

@@
 The "External" method employs the external dictionaries (i.e., $r=0$ in Equ.
-(\ref{equ5})) to recover the latent clean images, while the "Internal" method employ the GMM to directly cluster the internal noisy PGs into multiple subspaces, and perform denoising with internal dictionary learning (i.e., $r=128$ in Equ.
+(\ref{equ5})) to recover the latent clean images, while the "Internal" method employ the GMM (with also $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and perform denoising with internal dictionary learning (i.e., $r=3p^{2}$ in Equ.
 (\ref{equ5})) for each subspace.
@@
 
-We compare the three methods on the 60 cropped images from \cite{crosschannel2016}.
+We compare the above mentioned three methods on the 60 cropped images from \cite{crosschannel2016}.
 The average PSNR results of these methods are listed in Table \ref{tab1}.
-It can be seen that our proposed method achieves higher PSNR results then the "External" and "Internal" methods.
-We also compare the visual qualities of denoised images listed in Figure \ref{fig2} and Figure \ref{fig3}.
-We can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering complex textures (Figure \ref{fig3}).
-And if we make use of both the external and internal priors, our proposed method can recover well both the structures and textures.
+It can be seen that our proposed method achieves higher PSNR results then the methods of "External" and "Internal".
+We also compare the visual quality of the images denoised by these methods.
+From the results listed in Figure \ref{fig2} and Figure \ref{fig3}, we can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering internal complex textures (Figure \ref{fig3}).
+And by making use of both the external and internal priors, our proposed method can recover well both the structures and textures.
 
-In summary, the proposed algorithm achieves better performance on denoising real images than the external and internal prior based methods.
+In summary, the proposed algorithm achieves better performance on denoising real noisy images than the external prior based method and internal prior based method.
 

### 2016-10-29 CVPR2017_Review_Unified.tex
add

@@
 \end{tabular}
-\end{center}\vspace{-5mm}
+\end{center}\vspace{-4mm}
 \end{table*}
@@
 
-In this section, we compare the proposed method  with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning}.
+In this section, we compare the proposed method with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}.
 These methods are designed for removing Gaussian noise.
@@
 Since these methods are designed for grayscale images, we utilize them to denoise the R, G, B channels seperately for color noisy images.
-We also compare with three other denoising methods \cite{noiseclinic,neatimage,crosschannel2016}.
-The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior for image denoising.
-The Neat Image (NI) is a commercial software on image denoising and is embeded into Photoshop and Corel PaintShop Pro \cite{neatimage}.
-The recently proposed method Cross-Channel (CC) \cite{crosschannel2016} is a state-of-the-art method for real image denoising problem.
-The comparison is performed on the two datasets mentioned above.
+The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior.
+The recently proposed Cross-Channel (CC) \cite{crosschannel2016} is a state-of-the-art method on real image denoising problem.
+We also compare with Neat Image (NI), a commercial software for image denoising.
+Due to its excellant performance, NI is embeded into Photoshop and Corel PaintShop Pro \cite{neatimage}.
 
-For the first dataset, the average PSNR values on the 60 images cropped from \cite{crosschannel2016} are listed in Table \ref{tab2}.
-The number in red color and blue color means the best and second best results, respectively.
-It can be seen that our proposed method achieves the best PSNR results than other methods and the gap over the second best result (blue) is 1dB.
-Considering that the 60 cropped images contain different scenes with complex noise, the improvements of our proposed method is impressed.
-Besides, to compare with the recently proposed \cite{crosschannel2016}, we also perform experiments on the 15 images used in \cite{crosschannel2016}.
-The comparison  on PSNR values are listed in Table \ref{tab3}.
-As we can see, our proposed method obtains best PSNR values on most (9 out of 15) of the images captured by different camera settings.
-Noted that, though the method \cite{crosschannel2016} trains a specific model for each camera settng, our proposed general method still gains 0.28dB improvements over \cite{crosschannel2016}.
-We also compare the visual quality of the compared method.
-For example, Figure \ref{fig5} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO$=3200$.
+The comparisons are performed on the two datasets mentioned before.
+For the first dataset \cite{crosschannel2016}, the average PSNR results on the 60 cropped images  are listed in Table \ref{tab2} (the code of \cite{crosschannel2016} is not available so that it is not compared).
+The numbers in red color and blue color are the best and second best results, respectively.
+It can be seen that our proposed method achieves much better PSNR results than the other methods.
+The improvement of our method over the second best method (\textbf{TRD}) is 1dB.
+To compare with \cite{crosschannel2016}, we also perform experiments on the 15 cropped images used in \cite{crosschannel2016}.
+The PSNR values are listed in Table \ref{tab3}.
+As we can see, on most (9 out of the 15) images captured by different cameras and camera settings, our proposed method obtains better PSNR values than the other methods.
+Noted that, though in \cite{crosschannel2016} a specific model is trained for each camera and camera setting, our proposed general method still gains 0.28dB improvements on PNSR over \cite{crosschannel2016}.
+We also compare the visual quality of the denoised images by the competing methods.
+Figure \ref{fig5} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO $=3200$ by the competing methods.
 More visual comparisons can be found in the supplementary file.
-We can see that BM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts while MLP, TRD are likely to over-smooth the image.
-Our proposed method preserves edges and textures much better than other methods.
+We can see that BM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TRD are likely to over-smooth the image.
+Owe to the unify of external and internal priors, our proposed method preserves edges and textures better than other methods.
 
-For the second dataset provided in \cite{ncwebsite}, we can only compare the visual quality of the images denoised by different methods.
-In Figure \ref{fig6}, we take the real noisy image "Dog" as an example and more visual comparisons can be found in the supplementary file.
-It can be seen that the methods of BM3D, WNNM would over-smooth the whole image while remain some noise in local areas.
-The methods of MLP, TRD also remain a lot of noise in the whole image.
-This demonstrates that the methods designed for Gaussian noise are not suitable for the complex noise in real noisy images.
-Even Noise Clinic and Neat Image, which are specifically developed for real noisy images, would sometimes fail to deal with the complex noise in real noisy images.
-However, we can see that the proposed algorithm recoveries more faithfully the fine structures of the eye area than the other competing methods.
+For the second dataset \cite{ncwebsite} with no "ground truth" images, we only compare the visual quality of the denoised images.
+Figure \ref{fig6} shows the denoised images of "Dog" by the competing methods.
+More visual comparisons can be found in the supplementary file.
+It can be seen that the methods of BM3D, WNNM tend to globally over-smooth the image while locally remain some noise, while the methods of MLP, TRD are likely to remain noise in the whole image.
+This demonstrates that the methods designed for Gaussian noise are not effective for removing the complex noise in real noisy images.
+Though Noise Clinic and Neat Image are specificly developed for removing complex noise, they would sometimes fail to recovery real noisy images.
+However, our proposed method recoveries more faithfully the structures and textures (such as the eye area) than the other competing methods.
 
-In summary, our proposed algorithm demonstrates impressing ability on dealing with the complex noise in real noisy images in terms of PSNR and visual quality.
+In summary, our proposed method demonstrates impressing ability on dealing with the complex noise in real noisy images in terms of PSNR and visual quality.
 

### 2016-10-29 CVPR2017_Review_Unified.tex
a

@@
 \begin{abstract}
-For image denoising problem, the external and internal priors are playing key roles in many different methdos.
+For image denoising problem, the external and internal priors are playing key roles in many different methods.
 External priors learn from external images to restore noisy images while internal ones exploit priors of given images for denoising.
-The external priors are more generative and efficient on recovering structures existing in most images while the internal priors are more adaptive on recovering detials existed in given noisy images.
+The external priors are more generative and efficient on recovering structures existing in most images while the internal priors are more adaptive on recovering details existed in given noisy images.
 In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising.
@@
 Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images.
-The camera sensors and outdoor low light conditions will unavoidly bring noise to the captured images.
+The camera sensors and outdoor low light conditions will unavoidably bring noise to the captured images.
 The impact is that the image details will be lost or hardly visible.
 As a result, image denoising is an essential procedure for the reliability of these vision systems.
-In the research ara, image denoising is also an ideal platform for testing natural image models and provides high-quality images for other conputer vision tasks such as image registration, segmentation, and pattern recognition, etc.
+In the research area, image denoising is also an ideal platform for testing natural image models and provides high-quality images for other computer vision tasks such as image registration, segmentation, and pattern recognition.
 
@@
 Therefore, the noise in real images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric}.
-It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc).
+It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc.).
 The models designed for AWGN would become much less effective on real noisy images.
@@
 Although the mixture of Gaussians (MoG) model is possible to approximate any noise distribution \cite{Bishop}, estimating its parameters is time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR}.
-To evaluate the performanec of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}.
+To evaluate the performance of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}.
 The testing image is captured by a Nikon D800 camera when ISO is 3200.
 The "ground truth" image is also provided with which we can calculate objective measurements such as PSNR.
-The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or oversmooth the complex details in real noisy image.
+The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or over-smooth the complex details in real noisy image.
 \begin{figure*}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (g) NoiseClinic \cite{noiseclinic}: 35.33dB  }
+{\footnotesize (g) NC \cite{noiseclinic}: 35.33dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (h) Neat Image \cite{neatimage}: 34.39dB  }
+{\footnotesize (h) NI \cite{neatimage}: 34.39dB  }
 \end{minipage}
@@
 \caption{Denoised images of the real noisy image "Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
-\vspace{-4mm}
+\vspace{-3mm}
 \label{fig1}
@@
 The above mentioned methods can be categorized into external methods which learn priors from external images to recover noisy images, and internal ones which exploit priors of given images for denoising.
-The external priors in natural images are free of the high correlation between noise and siganls in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image.
-Combining the priors of external clean images and adaptivety of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images.
+The external priors in natural images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image.
+Combining the priors of external clean images and priors of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images.
 Based on these observations, in this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising.
@@
 
-The rest of this paper will be summerized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model and formulate the overall image denoising algorithm; in Section 3, we demonstrate extensive experiments on real image denoising probelm; in Section 4, we conclude our paper and give future work.
+The rest of this paper will be summarized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model and formulate the overall image denoising algorithm; in Section 3, we demonstrate extensive experiments on real image denoising problem; in Section 4, we conclude our paper and give future work.
 
@@
 }
-\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}\vspace{-4mm}
+\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
+\vspace{-3mm}
 \label{fig2}
@@
 
-The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self similar (NSS) property of natural images.
+The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self-similarity (NSS) property of natural images.
 The NSS property is commonly used in image restoration tasks \cite{nlm,bm3d,lssc,wnnm,pgpd}.
@@
 In this paper, we make use of PGs both from external clean images and internal given real noisy image for better denoising performance.
-
-%In fact, we use the external Pacth Group prior to guide the structural clustering of internal patch groups in real noisy images.
-For each cluster of PGs, we propose to use PCA for subspace learning.
-The eigenvectors are the basis of this subspace and hence can be used as an orthonormal dictionary.
-The eigenvalues reflect the information describing the noise levels and hence can be used as parameters for image denoising.
-Noted that the dictionary and parameters are obtained via a fully unsupervised way by subspace learning.
-Therefore, our model is highly adaptive to the noisy input images.
 
@@
 \caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
-\vspace{-4mm}
+\vspace{-3mm}
 \label{fig3}
@@
 
-Natural images often demonstrate repepitive local patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm,pgpd}.
+Natural images often demonstrate repetitive local patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm,pgpd}.
 In this section, we formulate the Patch Group prior learned on natural color images.
 Similar to \cite{pgpd}, the patch group (PG) is defined as a group of similar patches to the local patch.
-The patch group mean is destracted, and hence different groups patches can share similar PGs.
+The patch group mean is subtracted, and hence different groups patches can share similar PGs.
 In this way, the space natural image patches to be modeled is largely reduced.
@@
 \\
-\textbf{Updating Sparse Coefficient}: given the orthogonal dictioanry $\textbf{D}_{(t)}$, we update the sparse coefficient vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ via solving
+\textbf{Updating Sparse Coefficient}: given the orthogonal dictionary $\textbf{D}_{(t)}$, we update the sparse coefficient vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ via solving
 \vspace{-3mm}
@@
 The reason is, by guidance we only need calculate the probabilities via Equ.
-(\ref{equ4}) for all noisy PGs while by internal clustering via GMM we have to perform time-consuming EM algorithm \cite{em}.
-2) the external clean dictionary guides the learning of orthogonal dictionaries more adaptive for internal noisy images.
+(\ref{equ4}) for all noisy PGs while by internal clustering via GMM we have to perform time-consuming EM algorithm \cite{em}; 2) the external clean dictionary guides the learning of orthogonal dictionaries more adaptive for internal noisy images.
 The learning process is very efficient because of closed-form solutions.
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
-{\footnotesize (f) NoiseClinic \cite{noiseclinic}: 38.76dB }
+{\footnotesize (f) NC \cite{noiseclinic}: 38.76dB }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
-{\footnotesize (g) Neat Image \cite{neatimage}: 37.68dB  }
+{\footnotesize (g) NI \cite{neatimage}: 37.68dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
-{\footnotesize (h) CCNoise \cite{crosschannel2016}: 38.37dB }
+{\footnotesize (h) CC \cite{crosschannel2016}: 38.37dB }
 \end{minipage}
@@
 \end{minipage}
-}\vspace{-4mm}
+}\vspace{-1mm}
 \caption{Denoised images of the image "Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
+%\vspace{-1mm}
 \label{fig5}
@@
 The other parameters are set as default.
-For the methods of MLP, CSF, and TRD, we employ their default paramters settings.
-Since these methods are designed for grayscale images, we utilize them to denoise the R, G, B channels seperately for color noisy images.
+For the methods of MLP, CSF, and TRD, we employ their default parameters settings.
+Since these methods are designed for grayscale images, we utilize them to denoise the R, G, B channels separately for color noisy images.
 The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior.
@@
 We also compare with Neat Image (NI), a commercial software for image denoising.
-Due to its excellant performance, NI is embeded into Photoshop and Corel PaintShop Pro \cite{neatimage}.
+Due to its excellent performance, NI is embedded into Photoshop and Corel PaintShop \cite{neatimage}.
 
@@
 It can be seen that our proposed method achieves much better PSNR results than the other methods.
-The improvement of our method over the second best method (\textbf{TRD}) is 1dB.
+The improvement of our method over the second best method (TRD) is 1dB.
 To compare with \cite{crosschannel2016}, we also perform experiments on the 15 cropped images used in \cite{crosschannel2016}.
@@
 This demonstrates that the methods designed for Gaussian noise are not effective for removing the complex noise in real noisy images.
-Though Noise Clinic and Neat Image are specificly developed for removing complex noise, they would sometimes fail to recovery real noisy images.
+Though Noise Clinic and Neat Image are specifically developed for removing complex noise, they would sometimes fail to recovery real noisy images.
 However, our proposed method recoveries more faithfully the structures and textures (such as the eye area) than the other competing methods.
@@
 \hline
-Camera Settings & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Guided} 
+Camera Settings & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Ours} 
 \\
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
-{\footnotesize (f) Noise Clinic \cite{noiseclinic}  }
+{\footnotesize (f) NC \cite{noiseclinic}  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
-{\footnotesize (g) Neat Image \cite{neatimage}   }
+{\footnotesize (g) NI \cite{neatimage}   }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_dog.png}}
-{\footnotesize (h) Guided  }
+{\footnotesize (h) Ours  }
 \end{minipage}
@@
 The experiments on standard datasets have demonstrated the powerful ability of the proposed method.
-In the future, we will evaluate the proposed method on other conputer vision tasks such as image super-resolution, image deblurring, etc.
+In the future, we will evaluate the proposed method on other computer vision tasks such as image super-resolution, image deblurring, etc.
 

### 2016-10-29 CVPR2017_Review_Unified.tex
add

@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (i) Ours: \textbf{37.28}dB  }
+{\footnotesize (i) Ours: \textbf{37.02}dB  }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
-{\footnotesize (i) Ours: \textbf{40.26}dB}
+{\footnotesize (i) Ours: \textbf{40.50}dB}
 \end{minipage}

### 2016-10-29 CVPR2017_Review_Unified.tex
a

@@
 In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising.
-The internal orthogonal dictionary learning process has closed-form solutions and hence very efficient for online denoising.
-The experiments on standard datasets demonstrate that, that the proposed method achieves better performance than other state-of-the-art methods on real image denoising.
+The internal orthogonal dictionary learning process has closed-form solutions and hence very efficient for image denoising.
+We perform extensive experiments on dozens of real noisy images captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions.
+The results demonstrate that the proposed method achieves better performance than other state-of-the-art methods on real image denoising.
 \end{abstract}

### 2016-10-29 CVPR2017_Review_Unified.tex
add

@@
 External priors learn from external images to restore noisy images while internal ones exploit priors of given images for denoising.
-The external priors are more generative and efficient on recovering structures existing in most images while the internal priors are more adaptive on recovering details existed in given noisy images.
+The external priors are more generative and efficient on recovering structure s existing in most images while the internal priors are more adaptive on recovering details existed in given noisy images.
 In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising.
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (a) Noisy \cite{crosschannel2016}: 36.15dB   }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (b) External: 37.12dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (b) External: 39.05dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (c) Internal: 35.70dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (c) Internal: 38.75dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (d) Ours: \textbf{37.94}dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (d) Ours: \textbf{39.39}dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
-{\footnotesize (e) Mean Image \cite{crosschannel2016} }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (e) Mean Image \cite{crosschannel2016}}
 \end{minipage}
 }
-\caption{Denoised images of the image "Canon EOS 5D Mark3 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the $96$-th cropped image from "Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \vspace{-3mm}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.66dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.55dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (b) External: 34.97dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (b) External: 36.09dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (c) Internal: 36.86dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (c) Internal: 37.11dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
-{\footnotesize (d) Ours: \textbf{37.13}dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (d) Ours: \textbf{37.39}dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_95.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
 {\footnotesize (e) Mean Image \cite{crosschannel2016}}
@@
 }
-\caption{Denoised images of the image "Nikon D600 ISO 3200 C1" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the $94$-th cropped image from "Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \vspace{-3mm}

### 2016-10-29 CVPR2017_Review_Unified.tex
add

@@
 \caption{Denoised images of the image "Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
-%\vspace{-1mm}
+\vspace{-1mm}
 \label{fig5}
@@
 In this section, we compare our proposed method on real image denoising with external prior based method (denoted as "External") and internal prior based method (denoted as "Internal").
-All the three methods perform real image denoising under the weighted sparse coding framework in Equ.
+The three methods perform denoising under the same framework as Equ.
 (\ref{equ5}).
 The "External" method employs the external dictionaries (i.e., $r=0$ in Equ.
-(\ref{equ5})) to recover the latent clean images, while the "Internal" method employ the GMM (with also $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and perform denoising with internal dictionary learning (i.e., $r=3p^{2}$ in Equ.
-(\ref{equ5})) for each subspace.
+(\ref{equ5})) for denoising, while the "Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with internal dictionary learning (i.e., $r=3p^{2}$ in Equ.
+(\ref{equ5})).
 All parameters of the three methods are tuned to achieve corresponding best performance.
@@
 And by making use of both the external and internal priors, our proposed method can recover well both the structures and textures.
+Noted that the noisy images in Figures \ref{fig2} and \ref{fig3} are cropped from the same image captured by Nikon D600 at ISO $=3200$ in \cite{crosschannel2016}.
+Therefore the differences on PSNR and visual quality among the three methods are not influenced by the noise, but by the contents of the cropped images.
 
@@
 \end{tabular}
-\end{center}\vspace{-4mm}
+\end{center}\vspace{-5mm}
 \end{table}
@@
 \end{tabular}
-\end{center}\vspace{-4mm}
+\end{center}\vspace{-5mm}
 \end{table*}

### 2016-10-30 CVPR2017_Review_Unified.tex
add

@@
 \caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
-\vspace{-2mm}
+\vspace{-3mm}
 \label{fig4}
@@
 1).
-Our proposed method needs about 60 seconds to denoise an image of size $512\times512\times3$ under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.
+All experiments are performed under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.
 
@@
 The "External" method employs the external dictionaries (i.e., $r=0$ in Equ.
-(\ref{equ5})) for denoising, while the "Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with internal dictionary learning (i.e., $r=3p^{2}$ in Equ.
+(\ref{equ5})) for denoising, while the "Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with fully learned dictionary (i.e., $r=3p^{2}$ in Equ.
 (\ref{equ5})).
-All parameters of the three methods are tuned to achieve corresponding best performance.
+All parameters of the three methods are tuned to achieve best performance.
 
-We compare the above mentioned three methods on the 60 cropped images from \cite{crosschannel2016}.
-The average PSNR results of these methods are listed in Table \ref{tab1}.
-It can be seen that our proposed method achieves higher PSNR results then the methods of "External" and "Internal".
-We also compare the visual quality of the images denoised by these methods.
+We compare the above mentioned methods on the 60 cropped images from \cite{crosschannel2016}.
+The average PSNR and speed of these methods are listed in Table \ref{tab1}.
+It can be seen that our proposed method achieves better PSNR results than the methods of "External" and "Internal".
+The speed of our proposed method is much faster than the "Internal" method while a little slower than the "External" method.
+We also compare the visual quality of the denoised images by these methods.
 From the results listed in Figure \ref{fig2} and Figure \ref{fig3}, we can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering internal complex textures (Figure \ref{fig3}).
-And by making use of both the external and internal priors, our proposed method can recover well both the structures and textures.
+And by utilizing both the external and internal priors, our proposed method can recover well both the structures and textures.
 Noted that the noisy images in Figures \ref{fig2} and \ref{fig3} are cropped from the same image captured by Nikon D600 at ISO $=3200$ in \cite{crosschannel2016}.
-Therefore the differences on PSNR and visual quality among the three methods are not influenced by the noise, but by the contents of the cropped images.
-
-In summary, the proposed algorithm achieves better performance on denoising real noisy images than the external prior based method and internal prior based method.
+Hence, the differences on PSNR and visual quality among these methods only depends on the contents of the cropped images.
 
 \begin{table}
-\caption{Average PSNR(dB) results of External, Internal, and our proposed methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
+\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
 \label{tab1}
-\vspace{-2mm}
+\vspace{-3mm}
 \begin{center}
@@
 \hline
-%SSIM & 0.8718 &  0.9663   & 0.9625 & \textbf{0.9691}
-%\\
-%\hline
+Time & | &  ?  & 706.63 & 58.47
+\\
+\hline
 \end{tabular}
-\end{center}\vspace{-5mm}
+\end{center}\vspace{-6mm}
 \end{table}
@@
 \end{tabular}
-\end{center}\vspace{-5mm}
+\end{center}\vspace{-6mm}
 \end{table*}
@@
 This demonstrates that the methods designed for Gaussian noise are not effective for removing the complex noise in real noisy images.
-Though Noise Clinic and Neat Image are specifically developed for removing complex noise, they would sometimes fail to recovery real noisy images.
+Though Noise Clinic and Neat Image are specifically developed for removing complex noise, they would sometimes fail to recover real noisy images.
 However, our proposed method recoveries more faithfully the structures and textures (such as the eye area) than the other competing methods.

### 2016-10-31 CVPR2017_Review_Unified.tex
add

@@
 \begin{abstract}
-For image denoising problem, the external and internal priors are playing key roles in many different methods.
-External priors learn from external images to restore noisy images while internal ones exploit priors of given images for denoising.
-The external priors are more generative and efficient on recovering structure s existing in most images while the internal priors are more adaptive on recovering details existed in given noisy images.
-In this paper, we propose to employ the external patch group prior of images to guide the clustering of internal patch groups, and develop an external dictionary guided internal orthogonal dictionary learning algorithm for real image denoising.
-The internal orthogonal dictionary learning process has closed-form solutions and hence very efficient for image denoising.
-We perform extensive experiments on dozens of real noisy images captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions.
-The results demonstrate that the proposed method achieves better performance than other state-of-the-art methods on real image denoising.
+Image priors (e.g., sparsity, self-similarity) are playing key roles in image denoising problem.
+External priors are priors learned from external (usually clean) images while internal priors are learned from the given noisy image.
+The external priors are more generative on recovering structures in images while the internal priors are more adaptive on recovering textures and details in given noisy image.
+In this paper, we propose an algorithm of external priors guided internal priors learning for real image denoising.
+Specifically, the external priors are learned on patch groups (PGs) from external images via Gaussian Mixture Model, and employed to guide the clustering and orthogonal dictionary learning of PGs from the given noisy image.
+The orthogonal dictionary learning has closed-form solutions and the image denoising is simultaneously performed with the learning process.
+We perform extensive experiments on real image denoising, in which the noisy images are captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions.
+The results on PSNR and visual quality demonstrate that the proposed method achieves better performance than other state-of-the-art denoising methods.
 \end{abstract}
@@
 It can be seen that our proposed method achieves better PSNR results than the methods of "External" and "Internal".
-The speed of our proposed method is much faster than the "Internal" method while a little slower than the "External" method.
+The speed of our proposed method is much faster than the "Internal" method while only a little slower than the "External" method.
 We also compare the visual quality of the denoised images by these methods.
@@
 \hline
-Time & | &  ?  & 706.63 & 58.47
+Time & | &  \textbf{56.39}  & 706.63 & 58.47
 \\

### 2016-10-31 CVPR2017_Review_Unified.tex
a

@@
 According to the Theorem 4 in \cite{spca}, the problem (\ref{equ10})
-has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times 3p^2}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
+has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
 \vspace{-1mm}
@@
 We evaluate the performance of the proposed framework on denoising real noisy images.
-The denoising is simultaneously done with the guided internal dictionary learning (DL) process.
+The denoising is simultaneously done with the guided internal dictionary learning process.
 We ignore the index $k\in\{1,...,K\}$ of subspace for notation simplicity.
@@
 \begin{table}
-\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
+\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
 \label{tab1}
@@
 \hline
-Time & | &  \textbf{56.39}  & 706.63 & 58.47
+Time & | &  \textbf{56.39}  & 667.36 & 58.47
 \\

### 2016-11-04 CVPR2017_Review_Unified.tex
AD

@@
 
-Learning priors to represent images has been successfully used in image modeling \cite{ksvd,epll,pgpd,ple,ncsr}.
+Learning priors to represent images has been successfully used in image modeling \cite{ksvd,epll,pgpd,ple}.
 There are mainly two categories of prior learning methods: 1) External methods pre-learned priors (e.g., dictionaries) from a set of clean images, and the learned priors are used to recover the noisy images \cite{epll,pgpd}.
-2) Internal methods directly learned priors from the given noisy image, and the image denoising is simultaneously done with the learning process \cite{ksvd,ple,ncsr}.
+2) Internal methods directly learned priors from the given noisy image, and the image denoising is simultaneously done with the learning process \cite{ksvd,ple}.
 Both the two categories of methods have limitations.
@@
 
-Natural images often demonstrate repetitive local patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,ncsr,wnnm,pgpd}.
+Natural images often demonstrate repetitive local patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,wnnm,pgpd}.
 In this section, we formulate the Patch Group prior learned on natural color images.
@@
 \caption{Denoised images of the image "Dog" by different methods. The images are better to be zoomed in on screen.}
-\vspace{-2mm}
+%\vspace{-2mm}
 \label{fig6}
@@
 
-The image priors are commonly used for image denoising problem.
+Image priors are commonly used for solving image denoising problems.
 The external priors are general but not adaptive to specific images, while the internal priors are adaptive but would largely degraded by the complex noise in real noisy images.

### 2016-11-04 CVPR2017_Review_Unified.tex
add

@@
 }\vspace{-1mm}
-\caption{Denoised images of the real noisy image "Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
+\caption{Denoised images of the real noisy image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \vspace{-3mm}
@@
 }
-\caption{Denoised images of the $96$-th cropped image from "Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the $96$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \vspace{-3mm}
@@
 }
-\caption{Denoised images of the $94$-th cropped image from "Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the $94$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \vspace{-3mm}
@@
 }\vspace{-1mm}
-\caption{Denoised images of the image "Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
 \vspace{-1mm}
@@
 }
-\caption{Denoised images of the image "Dog" by different methods. The images are better to be zoomed in on screen.}
-%\vspace{-2mm}
+\caption{Denoised images of the image ``Dog" by different methods. The images are better to be zoomed in on screen.}
+\vspace{-2mm}
 \label{fig6}
@@
 
-Image priors are commonly used for solving image denoising problems.
-The external priors are general but not adaptive to specific images, while the internal priors are adaptive but would largely degraded by the complex noise in real noisy images.
-In this paper, we demonstrates that, we can unify the priors in external clean images and in internal noisy images to achieve better performance on real image denoising problem.
-This unify can be attempted by employing the external prior learned on natural images to guide the internal prior learning on given noisy images.
-The experiments on standard datasets have demonstrated the powerful ability of the proposed method.
-In the future, we will evaluate the proposed method on other computer vision tasks such as image super-resolution, image deblurring, etc.
+Image priors are important for solving image denoising problems.
+The external priors learned from external clean images are generally effective to most images, while the internal priors learned directly from the noisy image are adaptive to the given image but would be biased by the complex noise in real noisy images.
+In this paper, we demonstrates that, once unifying both the priors in external clean images and internal noisy images, we can achieve much better while still efficient performance on real image denoising problem.
+Specifically, the external patch group (PG) priors learned on natural clean images can be used to guide the subspace selection and orthogonal dictionary learning of internal noisy PGs from given noisy images.
+The experiments on real image denoising problem have demonstrated the powerful ability of the proposed method.
+In the future, we will speed up the proposed algorithm and evaluate the proposed method on other computer vision tasks such as image super-resolution.
 

### 2016-11-04 CVPR2017_Review_Unified.tex
add

@@
 
-\subsection{Internal v.s. External Prior Learning}
+\subsection{Internal \textbf{\emph{vs.}} External Prior Learning}
 
@@
 Similar to \cite{pgpd}, the patch group (PG) is defined as a group of similar patches to the local patch.
-The patch group mean is subtracted, and hence different groups patches can share similar PGs.
+The patch group mean is subtracted, and hence different groups of patches can share similar PGs.
 In this way, the space natural image patches to be modeled is largely reduced.
@@
 For adaptivity, we project the PG $\mathbf{\overline{Y}}_{n}$ into its most suitable Gaussian component (subspace) of the GMM learned on external PGs.
-The subspace most suitable for $\mathbf{\overline{Y}}_{n}$ is selected by firstly calculating the posterior probability of "$\mathbf{\overline{Y}}_{n}$ belonging to the $k$th Gaussian component":
+The subspace most suitable for $\mathbf{\overline{Y}}_{n}$ is selected by firstly calculating the posterior probability of ``$\mathbf{\overline{Y}}_{n}$ belonging to the $k$-th Gaussian component":
 \vspace{-2mm}
@@
 &
-\text{s.t.}
+s.t.
 \quad
@@
 \\
-\text{s.t.}
+s.t.
 \quad
@@
 For each image, the same scene was shot 500 times under the same camera and camera setting.
-The mean image of the 500 shots is roughly taken as the "ground truth", with which the PSNR can be computed.
+The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.
 Since the 17 images share repetitive contents, we cropped them into 60 smaller images (of size $500\times 500\times3$) including different contents.
@@
 The second dataset provided in \cite{ncwebsite} includes about 20 real noisy images collected under uncontrolled outdoor environment.
-This dataset does not have "ground truth" images.
+This dataset does not have ``ground truth" images.
 
@@
 \subsection{Comparison with External and Internal Priors}
-In this section, we compare our proposed method on real image denoising with external prior based method (denoted as "External") and internal prior based method (denoted as "Internal").
+In this section, we compare our proposed method on real image denoising with external prior based method (denoted as ``External") and internal prior based method (denoted as ``Internal").
 The three methods perform denoising under the same framework as Equ.
 (\ref{equ5}).
-The "External" method employs the external dictionaries (i.e., $r=0$ in Equ.
-(\ref{equ5})) for denoising, while the "Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with fully learned dictionary (i.e., $r=3p^{2}$ in Equ.
+The ``External" method employs the external dictionaries (i.e., $r=0$ in Equ.
+(\ref{equ5})) for denoising, while the ``Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with fully learned dictionary (i.e., $r=3p^{2}$ in Equ.
 (\ref{equ5})).
@@
 The average PSNR and speed of these methods are listed in Table \ref{tab1}.
-It can be seen that our proposed method achieves better PSNR results than the methods of "External" and "Internal".
-The speed of our proposed method is much faster than the "Internal" method while only a little slower than the "External" method.
+It can be seen that our proposed method achieves better PSNR results than the methods of ``External" and ``Internal".
+The speed of our proposed method is much faster than the ``Internal" method while only a little slower than the ``External" method.
 We also compare the visual quality of the denoised images by these methods.
-From the results listed in Figure \ref{fig2} and Figure \ref{fig3}, we can see that the "External" method is good at recovering structures (Figure \ref{fig2}) while the "Internal" method is good at recovering internal complex textures (Figure \ref{fig3}).
+From the results listed in Figure \ref{fig2} and Figure \ref{fig3}, we can see that the ``External" method is good at recovering structures (Figure \ref{fig2}) while the ``Internal" method is good at recovering internal complex textures (Figure \ref{fig3}).
 And by utilizing both the external and internal priors, our proposed method can recover well both the structures and textures.
@@
 We can see that BM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TRD are likely to over-smooth the image.
-Owe to the unify of external and internal priors, our proposed method preserves edges and textures better than other methods.
+By combining the external and internal priors, our proposed method preserves edges and textures better than other methods.
 
-For the second dataset \cite{ncwebsite} with no "ground truth" images, we only compare the visual quality of the denoised images.
-Figure \ref{fig6} shows the denoised images of "Dog" by the competing methods.
+For the second dataset \cite{ncwebsite} with no ``ground truth" images, we only compare the visual quality of the denoised images.
+Figure \ref{fig6} shows the denoised images of ``Dog" by the competing methods.
 More visual comparisons can be found in the supplementary file.

### 2016-11-04 CVPR2017_Review_Unified.tex
add
a

@@
 
-In the last decade, the methods of \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} are developed to deal with real noisy images.
+In the last decade, the methods of \cite{crosschannel2016,fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR} are developed to deal with real noisy images.
 Almost all these methods employ a two-stage framework: estimating the parameters of the assumed noise model (usually Gaussian) and performing denoising with the help of the noise modeling and estimation in the first stage.

### 2016-11-05 CVPR2017_Review_Unified.tex
add

@@
 \begin{abstract}
-Image priors (e.g., sparsity, self-similarity) are playing key roles in image denoising problem.
+Image priors (e.g., sparsity, self-similarity) are playing key roles in image restoration problems such as denoising.
 External priors are priors learned from external (usually clean) images while internal priors are learned from the given noisy image.
@@
 As a result, image denoising is an essential procedure for the reliability of these vision systems.
-In the research area, image denoising is also an ideal platform for testing natural image models and provides high-quality images for other computer vision tasks such as image registration, segmentation, and pattern recognition.
+In the research area, image denoising is an ideal platform for testing natural image models and provides high-quality images for other computer vision tasks such as image registration, segmentation, and pattern recognition.
 

### 2016-11-06 CVPR2017_Review_Unified.tex
add

@@
 
-For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and all of them focus mainly on dealing with additive white Gaussian noise (AWGN).
+For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and most of them focus mainly on dealing with additive white Gaussian noise (AWGN).
 In real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc.

### 2016-11-07 CVPR2017_Review_Unified.tex
add

@@
 %%%%%%%%% TITLE
-\title{External Patch Group Prior Guided Internal Prior Learning for Real Image Denoising}
+\title{External Prior Guided Internal Prior Learning for Real Noisy Image Denoising}
 
@@
 For the $k$-th subspace, assume the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ such that $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.
-We utilize the external orthogonal dictionary $\mathbf{U}_{k}$ (Equ.
+We utilize the external orthogonal dictionary $\mathbf{U}_{k}$ (Eqn.
 (\ref{equ3})) to guide the learning of an orthogonal dictionary for adaptively characterizing the internal PGs in the $k$-th subspace.
@@
 \end{equation}
-We employ square roots of the singular values in $\mathbf{S}$ (please refer to Equ.
+We employ square roots of the singular values in $\mathbf{S}$ (please refer to Eqn.
 (\ref{equ3})) as external prior weights and add a small positive number $\varepsilon$ to avoid zero denominator.
@@
 Here we take a detailed analysis on the guidance of the external patch group (PG) prior for the internal noisy PGs of given real noisy images.
-The guidance comes from at least three aspects: 1) the external prior guides the internal PGs to be clustered into suitable subspaces through MAP in Equ.
+The guidance comes from at least three aspects: 1) the external prior guides the internal PGs to be clustered into suitable subspaces through MAP in Eqn.
 (\ref{equ4}).
 The guided subspace selection is more efficient than directly clustering the internal noisy PGs via k-means or Gaussian Mixture Model (GMM).
-The reason is, by guidance we only need calculate the probabilities via Equ.
+The reason is, by guidance we only need calculate the probabilities via Eqn.
 (\ref{equ4}) for all noisy PGs while by internal clustering via GMM we have to perform time-consuming EM algorithm \cite{em}; 2) the external clean dictionary guides the learning of orthogonal dictionaries more adaptive for internal noisy images.
@@
 Besides, the learned orthogonal dictionary also makes the denoising process very efficient under weighted sparse coding framework.
-3) the singular values learned by SVD in Equ.
+3) the singular values learned by SVD in Eqn.
 (\ref{equ3}) reflect the prior weights of the dictionary atoms and can be used as adaptive parameters for real image denoising.
@@
 In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction.
-Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Equ.
+Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Eqn.
 (\ref{equ10}).
@@
 \\
-3.\quad Subspace selection via Equ. (\ref{equ4});
+3.\quad Subspace selection via Eqn. (\ref{equ4});
 \\
@@
 \\
-5.\quad Recover each patch in all PGs via Equ. (\ref{equ12});
+5.\quad Recover each patch in all PGs via Eqn. (\ref{equ12});
 \\
@@
 In this section, we compare our proposed method on real image denoising with external prior based method (denoted as ``External") and internal prior based method (denoted as ``Internal").
-The three methods perform denoising under the same framework as Equ.
+The three methods perform denoising under the same framework as Eqn.
 (\ref{equ5}).
-The ``External" method employs the external dictionaries (i.e., $r=0$ in Equ.
-(\ref{equ5})) for denoising, while the ``Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with fully learned dictionary (i.e., $r=3p^{2}$ in Equ.
+The ``External" method employs the external dictionaries (i.e., $r=0$ in Eqn.
+(\ref{equ5})) for denoising, while the ``Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with fully learned dictionary (i.e., $r=3p^{2}$ in Eqn.
 (\ref{equ5})).

### 2016-11-08 CVPR2017_Review_Unified.tex
add

@@
 \begin{abstract}
-Image priors (e.g., sparsity, self-similarity) are playing key roles in image restoration problems such as denoising.
-External priors are priors learned from external (usually clean) images while internal priors are learned from the given noisy image.
-The external priors are more generative on recovering structures in images while the internal priors are more adaptive on recovering textures and details in given noisy image.
-In this paper, we propose an algorithm of external priors guided internal priors learning for real image denoising.
-Specifically, the external priors are learned on patch groups (PGs) from external images via Gaussian Mixture Model, and employed to guide the clustering and orthogonal dictionary learning of PGs from the given noisy image.
-The orthogonal dictionary learning has closed-form solutions and the image denoising is simultaneously performed with the learning process.
-We perform extensive experiments on real image denoising, in which the noisy images are captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions.
-The results on PSNR and visual quality demonstrate that the proposed method achieves better performance than other state-of-the-art denoising methods.
+Existing image denoising methods mainly focus on signal independent noise such as Gaussian noise.\ The related paper showed that the internal priors (e.g., self-similarity) are highly effective for removing Gaussian noise from synthetic noisy images.\ However, the noise in real noisy images is much more complex than Gaussian noise since it is signal dependent and from several main sources.\ Hence, the internal priors learned on real noisy images would largely degrade the performance of denoising methods.\ In this paper, we propose to avoid the degradation by employing the external priors to guide the learning of internal priors.\ Specifically, we firstly learn external priors via Gaussian Mixture Model on the patch groups (PGs) extracted from natural clean images, and then employ the external priors to guide the subspace selection and orthogonal dictionary learning of the PGs from given noisy image.\ The orthogonal dictionary learning has closed-form solutions and the image denoising is simultaneously performed with the learning process.\ Extensive experiments on real noisy image denoising demonstrate that the proposed method achieves better performance than other state-of-the-art denoising methods.
 \end{abstract}
+% in which the noisy images are captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions.
 %Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise.
@@
 Hence, our internal DL process is very efficient for online internal denoising.
-Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising
+Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising.
 
@@
 
-\subsection{Patch Group Prior of Natural Images}
-
-The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self-similarity (NSS) property of natural images.
+%The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self-similarity (NSS) property of natural images.
 The NSS property is commonly used in image restoration tasks \cite{nlm,bm3d,lssc,wnnm,pgpd}.

### 2016-11-08 CVPR2017_Review_Unified.tex
add

@@
 
-Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images.
+%Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images.
 The camera sensors and outdoor low light conditions will unavoidably bring noise to the captured images.
 The impact is that the image details will be lost or hardly visible.
-As a result, image denoising is an essential procedure for the reliability of these vision systems.
-In the research area, image denoising is an ideal platform for testing natural image models and provides high-quality images for other computer vision tasks such as image registration, segmentation, and pattern recognition.
+As a result,
 
-For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,wnnm,csf,pgpd,chen2015learning}, and most of them focus mainly on dealing with additive white Gaussian noise (AWGN).
-In real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc.
+Image denoising is an essential procedure for the reliability of many vision systems such as medical imaging and surveillance.
+It is also an ideal platform for testing computer vision models.
+Image denoising is to recover the latent clean image $\mathbf{x}$ from its noisy observation $\mathbf{y}=\mathbf{x}+\mathbf{n}$ where $\mathbf{n}$ is the additive noise.
+For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,ncsr,wnnm,csf,pgpd,chen2015learning}, and most of them focus on additive white Gaussian noise (AWGN).
+These methods exploited self-similarity \cite{nlm,epll,wnnm,pgpd}, structural sparsity \cite{ksvd,bm3d,cbm3d,lssc,ncsr}, neural network \cite{mlp}, or learned filters \cite{foe,csf,chen2015learning} for image denoising problem.
+
+However, in real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc.
 Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}.

### 2016-11-08 CVPR2017_Review_Unified.tex
ad

@@
 
-%Most vision systems, such as medical imaging and surveillance, need accurate feature extraction from high-quality images.
-The camera sensors and outdoor low light conditions will unavoidably bring noise to the captured images.
-The impact is that the image details will be lost or hardly visible.
-As a result,
-
-Image denoising is an essential procedure for the reliability of many vision systems such as medical imaging and surveillance.
-It is also an ideal platform for testing computer vision models.
-Image denoising is to recover the latent clean image $\mathbf{x}$ from its noisy observation $\mathbf{y}=\mathbf{x}+\mathbf{n}$ where $\mathbf{n}$ is the additive noise.
-For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,ncsr,wnnm,csf,pgpd,chen2015learning}, and most of them focus on additive white Gaussian noise (AWGN).
+Image denoising is an ideal platform for testing computer vision models and an essential procedure for the reliability of many vision systems such as medical imaging and surveillance.
+It aims to recover the latent clean image $\mathbf{x}$ from its noisy observation $\mathbf{y}=\mathbf{x}+\mathbf{n}$ where $\mathbf{n}$ is the additive noise.
+For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,ncsr,wnnm,csf,pgpd,chen2015learning} most of which focusing on additive white Gaussian noise (AWGN).
 These methods exploited self-similarity \cite{nlm,epll,wnnm,pgpd}, structural sparsity \cite{ksvd,bm3d,cbm3d,lssc,ncsr}, neural network \cite{mlp}, or learned filters \cite{foe,csf,chen2015learning} for image denoising problem.
 
-However, in real world, the cameras will undertake high ISO settings for high-speed shots on actions, long exposure for low light on night shots, etc.
-Under these situations, the noise is generated in a complex form and also been changed during the in-camera imaging pipeline \cite{NewInCamera,crosschannel2016}.
-Therefore, the noise in real images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric}.
-It depends on camera series, brands, as well as the settings (ISO, shutter speed, and aperture, etc.).
-The models designed for AWGN would become much less effective on real noisy images.
+However, the methods designed for synthetic Gaussian noise is much less effective for removing the noise in real noisy images.
+The reason is that the noise in real noisy images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).
+Besides, by the seminar work of \cite{healey1994radiometric}, the noise in the camera imaging process \cite{NewInCamera,crosschannel2016} are signal dependent and identified by five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
+This would largely limit the performance of these methods, which are designed for signal independent noise, on dealing with complex real noise.
+To prove our argument, we apply some representing methods of BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning} on a real noisy image provided in \cite{crosschannel2016}.
+The testing image is captured by a Nikon D800 camera when ISO is 3200.
+The ``ground truth" image is also provided with which we can calculate objective measurements such as PSNR.
+The denoised images of these methods are listed in Figure \ref{fig1} (from (b)$\sim$(f)).
+One can see that these methods either remove the noise or over-smooth the complex details in real noisy image.
 
-In the last decade, the methods of \cite{crosschannel2016,fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR} are developed to deal with real noisy images.
-Almost all these methods employ a two-stage framework: estimating the parameters of the assumed noise model (usually Gaussian) and performing denoising with the help of the noise modeling and estimation in the first stage.
-However, the Gaussian assumption is inflexible in describing the complex noise on real noisy images \cite{Liu2008}.
-Although the mixture of Gaussians (MoG) model is possible to approximate any noise distribution \cite{Bishop}, estimating its parameters is time consuming via nonparametric Bayesian techniques \cite{Zhu_2016_CVPR}.
-To evaluate the performance of these methods on dealing with complex real noise, we apply these methods, with corresponding default parameters, on a real noisy image provided in \cite{crosschannel2016}.
-The testing image is captured by a Nikon D800 camera when ISO is 3200.
-The "ground truth" image is also provided with which we can calculate objective measurements such as PSNR.
-The denoised images are listed in Figure \ref{fig1}, from which we can see that these methods either remove the noise or over-smooth the complex details in real noisy image.
+In the last decade, there are also several methods \cite{crosschannel2016,fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR} developed for real noisy image denoising.
+Almost all these methods employ a two-stage framework: firstly estimating the parameters of the assumed noise model (usually Gaussian distribution or mixture of Gaussians (MoG)) and then performing denoising with the help of the estimated noise model.
+However, the noise in real noisy images are very complex and hard to be modeled by explict distributions.
+Therefore, the denoising performance of these methods would be influenced by the error between the estimated noise model and the actual noise distribution.
+This can be validated by the   denoised results listed in Figure \ref{fig1} ((g) and (h)), in which we evaluate the state-of-the-art real noisy image denoising method Noise Clinic \cite{noiseclinic,ncwebsite} and a comercial denoising software Neat Image \cite{neatimage}.
+From the results, we can see that the two methods do not perform well on the testing noisy image.
+These methods only exploit internal priors (e.g., noise prior, self-similarity) for real noisy image denoising and ignore the information of external natural clean images.
 \begin{figure*}
@@
 
-The above mentioned methods can be categorized into external methods which learn priors from external images to recover noisy images, and internal ones which exploit priors of given images for denoising.
 The external priors in natural images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image.
 Combining the priors of external clean images and priors of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images.
-Based on these observations, in this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising.
+In this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising.
 The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary.
@@
 
-\subsection{Our Contributions}
-
-The contributions of this paper are summarized as follows:
-\begin{itemize}
-\item We propose a novel model to learn internal priors adaptive to given images.
-This model employs the external patch group (PG) prior learned from clean images to guide the internal PG prior learning of given images.
+%The contributions of this paper are summarized as follows:
+%\begin{itemize}
+%\item We propose a novel model to learn internal priors adaptive to given images.
+%This model employs the external patch group (PG) prior learned from clean images to guide the internal PG prior learning of given images.
 The external prior benefits the internal learning on subspace selection and orthogonal dictionary learning.
-\item The proposed guided internal prior learning method is very efficient. The reason is that both the subspace selection and orthogonal dictionary learning have explicit solutions.
-\item For real image denoising problem, the proposed method achieves much better performance than other competing methods.
-\end{itemize}
+%\item The proposed guided internal prior learning method is very efficient. The reason is that both the subspace selection and orthogonal dictionary learning have explicit solutions.
+%\item For real image denoising problem, the proposed method achieves much better performance than other competing methods.
+%\end{itemize}
 

### 2016-11-08 CVPR2017_Review_Unified.tex
add

@@
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{1047} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 Therefore, the denoising performance of these methods would be influenced by the error between the estimated noise model and the actual noise distribution.
-This can be validated by the   denoised results listed in Figure \ref{fig1} ((g) and (h)), in which we evaluate the state-of-the-art real noisy image denoising method Noise Clinic \cite{noiseclinic,ncwebsite} and a comercial denoising software Neat Image \cite{neatimage}.
+This can be validated by the   denoised results listed in Figure \ref{fig1} ((g) and (h)), in which we evaluate the state-of-the-art real noisy image denoising method Noise Clinic \cite{noiseclinic,ncwebsite} and a commercial denoising software Neat Image \cite{neatimage}.
 From the results, we can see that the two methods do not perform well on the testing noisy image.
@@
 
-The external priors in natural images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image.
-Combining the priors of external clean images and priors of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images.
-In this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising.
+The external priors in natural clean images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image.
+Combining the priors of external clean images and priors of internal.
+In this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups of given noisy image, and internal orthogonal dictionary learning (DL) for real image denoising.
 The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary.
@@
 
-%The contributions of this paper are summarized as follows:
-%\begin{itemize}
-%\item We propose a novel model to learn internal priors adaptive to given images.
-%This model employs the external patch group (PG) prior learned from clean images to guide the internal PG prior learning of given images.
-The external prior benefits the internal learning on subspace selection and orthogonal dictionary learning.
-%\item The proposed guided internal prior learning method is very efficient. The reason is that both the subspace selection and orthogonal dictionary learning have explicit solutions.
-%\item For real image denoising problem, the proposed method achieves much better performance than other competing methods.
-%\end{itemize}
-
 The rest of this paper will be summarized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model and formulate the overall image denoising algorithm; in Section 3, we demonstrate extensive experiments on real image denoising problem; in Section 4, we conclude our paper and give future work.
@@
 \section{Related Work}
-
-\begin{figure*}
-\centering
-\subfigure{
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
-{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB  }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
-{\footnotesize (b) External: 39.05dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
-{\footnotesize (c) Internal: 38.75dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
-{\footnotesize (d) Ours: \textbf{39.39}dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
-{\footnotesize (e) Mean Image \cite{crosschannel2016}}
-\end{minipage}
-}
-\caption{Denoised images of the $96$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
-\vspace{-3mm}
-\label{fig2}
-\end{figure*}
 
@@
 
-Learning priors to represent images has been successfully used in image modeling \cite{ksvd,epll,pgpd,ple}.
+Image priors are playing key factors in image denoising methods \cite{nlm,ksvd,epll,pgpd,Irani2013separating}.
 There are mainly two categories of prior learning methods: 1) External methods pre-learned priors (e.g., dictionaries) from a set of clean images, and the learned priors are used to recover the noisy images \cite{epll,pgpd}.
 2) Internal methods directly learned priors from the given noisy image, and the image denoising is simultaneously done with the learning process \cite{ksvd,ple}.
-Both the two categories of methods have limitations.
-The external methods is not adaptive to the noisy image, while the internal methods ignores the information hidden in clean images.
-In this paper, our goal is to employ the external prior to guide the internal prior learning.
+On one hand, the methods of \cite{epll,pgpd} demonstrated that the external priors learned from natural clean images are highly effctive and efficient for image denoising problem.
+On the other hand, the work of \cite{ncsr,Irani2013separating} showed that the internal priors are highly effective for removing the signal independent Gaussian noise.
+However, the actual noise in real noisy images are much more complex than Gaussian noise.
+Only using the internal information may be not enough for real image denoising problem.
+The methods using only the external priors are not adaptive to given real noisy images, while the methods exploiting only internal priors would be degraded by the complex noise.
+In this paper, we propose to combine both the external and internal priors to solve the real noisy image denoising problem.
 
@@
 The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}.
-Liu et al.
-\cite{Liu2008} proposed to use 'noise level function' to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image.
+Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image.
 Gong et al.
-\cite{almapg} models the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain.
+\cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain.
 Later, Lebrun el al.
@@
 proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via Low-Rank Mixture of Gaussians.
+Though these methods are , these methods In this paper, we proposed a noval denoising method achieving much better performance than previous real denoising methods.
 
-\section{External Patch Group Prior Guided Internal Prior Learning for Image Denoising}
-
-\begin{figure*}
-\centering
-\subfigure{
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.55dB  }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (b) External: 36.09dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (c) Internal: 37.11dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (d) Ours: \textbf{37.39}dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (e) Mean Image \cite{crosschannel2016}}
-\end{minipage}
-}
-\caption{Denoised images of the $94$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
-\vspace{-3mm}
-\label{fig3}
-\end{figure*}
+\section{External Prior Guided Internal Prior Learning}
 
@@
 
-\subsection{Discussions}
-
-Here we take a detailed analysis on the guidance of the external patch group (PG) prior for the internal noisy PGs of given real noisy images.
+%Here we take a detailed analysis on the guidance of the external patch group (PG) prior for the internal noisy PGs of given real noisy images.
 The guidance comes from at least three aspects: 1) the external prior guides the internal PGs to be clustered into suitable subspaces through MAP in Eqn.
@@
 This dataset does not have ``ground truth" images.
+
+\begin{figure*}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (b) External: 39.05dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (c) Internal: 38.75dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (d) Ours: \textbf{39.39}dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (e) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}
+\caption{Denoised images of the $96$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\vspace{-3mm}
+\label{fig2}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.55dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (b) External: 36.09dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (c) Internal: 37.11dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (d) Ours: \textbf{37.39}dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (e) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}
+\caption{Denoised images of the $94$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\vspace{-3mm}
+\label{fig3}
+\end{figure*}
 

### 2016-11-08 CVPR2017_Review_Unified.tex
ad

@@
 In the last decade, researchers proposed many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for real image denoising problem.
-In \cite{fullyblind}, Portilla proposed to use scale mixture of Gaussian to estimate the noise covariance matrix and latent clean images in wavelet domain.
+In \cite{fullyblind}, Portilla proposed to use scale mixture of Gaussians to estimate the noise covariance matrix and latent clean images in wavelet domain.
 The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}.
@@
 Later, Lebrun el al.
-proposed a multiscale denoising algorithm called 'Noise Clinic' \cite{noiseclinic,ncwebsite}.
+proposed a multiscale denoising algorithm called ``Noise Clinic" \cite{noiseclinic,ncwebsite}.
 This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance.
 Recently, Zhu et al.
-proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via Low-Rank Mixture of Gaussians.
-Though these methods are , these methods In this paper, we proposed a noval denoising method achieving much better performance than previous real denoising methods.
+proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians.
+However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explict distributions.
+Besides, the parametric estimation of the Gaussian or MoG distribution is time consumming.
 
@@
 
-\subsection{External Patch Group Prior Learning}
+\subsection{Learn External Patch Group Prior}
 
@@
 We employ the Gaussian Mixture Model (GMM) to learn the external patch group based NSS prior.
-In this model, the likelihood of the $n$-th PG $\{\mathbf{\overline{X}}_{n}\}$ can be calculated as
-\vspace{-2mm}
-\begin{equation}\label{equ1}\vspace{-2mm}
-P(\mathbf{\overline{X}}_{n})  = \sum\nolimits_{k=1}^{K}\pi_{k}\prod\nolimits_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k}),
-\end{equation}
-where $K$ is the number of Gaussians and the parameters $\pi_{k}$, $\boldsymbol{\upmu}_{k}$, $\mathbf{\Sigma}_{k}$ are mixture weight, mean vector, and covariance matrix of the $k$-th Gaussian, respectively.
-By assuming that all the PGs are independently sampled, the overall objective log-likelihood function is
-\vspace{-2mm}
-\begin{equation}\label{equ2}\vspace{-2mm}
+The overall objective log-likelihood function of GMM is
+\begin{equation}\label{equ2}
 \begin{split}
@@
 \end{equation}
-We maximize the above objective function via EM algorithm \cite{em} and finally obtain the GMM model with learned parameters.
+The learning process is similar to the learning stage of the PGPD method \cite{pgpd}.
+Please refer to \cite{pgpd} for more details.
+After the learning stage, we finally obtain a GMM model with $K$ Gaussian components.
+The learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.
 Similar to \cite{pgpd}, the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
@@
 \vspace{-2mm}
-\subsubsection{Guided Internal Subspace Selection}
+\subsubsection{Internal Subspace Selection}
 \vspace{-1mm}
@@
 \vspace{-2mm}
-\subsubsection{Guided Internal Orthogonal Dictionary Learning}
+\subsubsection{Internal Orthogonal Dictionary Learning}
 \vspace{-2mm}

### 2016-11-08 CVPR2017_Review_Unified.tex
add

@@
 The external priors in natural clean images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image.
-Combining the priors of external clean images and priors of internal.
-In this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups of given noisy image, and internal orthogonal dictionary learning (DL) for real image denoising.
+Combining the priors of external clean images and priors of internalwould naturally achieves better performance.
+In this paper, we propose to employ the external priors learned from natural clean images to guide the learning of internal priors of given noisy image.
+We learn the external priors of patch groups \cite{pgpd} since nonlocal self-similarity is successfully used in many denoising methods \cite{nlm,bm3d,wnnm,pgpd}.
+The learning of external priors is performed by Gaussian Mixture Model.
+The learning of internal priors includes Gaussian selection and orthogonal dictionary learning (DL).
 The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary.
+The real noisy image denoising is simultaneously done with the DL process.
 Both of the two stages have closed-form solutions.
-Hence, our internal DL process is very efficient for online internal denoising.
+Hence, our proposed denoising method is very efficient.
 Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising.
@@
 However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explict distributions.
-Besides, the parametric estimation of the Gaussian or MoG distribution is time consumming.
+Besides, the parametric estimation of the Gaussian or MoG distribution is often time consumming \cite{B}.
 
@@
 
-Natural images often demonstrate repetitive local patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,wnnm,pgpd}.
 In this section, we formulate the Patch Group prior learned on natural color images.
@@
 The comparisons are performed on two standard datasets in which the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings.
-The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images.
+The first dataset provided in \cite{ncwebsite} includes 20 real noisy images collected under uncontrolled outdoor environment.
+This dataset does not have ``ground truth" images and hence the objective measurements can not be performed.
+In order to evaluate the compared methods on quantitative measures, we perform experiments on the second dataset provided in \cite{crosschannel2016}.
+It includes 17 real noisy images and corresponding mean images.
 The noisy images were collected under controlled indoor environment.
@@
 The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.
-Since the 17 images share repetitive contents, we cropped them into 60 smaller images (of size $500\times 500\times3$) including different contents.
+Since the 17 images are too large (of size about $7000\times5000\times3$) and share repetitive contents, the authors in \cite{crosschannel2016} performed comparison on 15 cropped images (of size $512\times 521\times3$).
+To evaluate the compared methods on more samples, we cropped the 17 large images from \cite{crosschannel2016} into 60 smaller images (of size $500\times 500\times3$) including different contents.
 Some samples are shown in Figure \ref{fig4}.
-We also perform comparison on the 15 cropped images (of size $512\times 521\times3$) used in \cite{crosschannel2016}.
-Noted that the noise in the 15 images used in \cite{crosschannel2016} is different from the noise in the 60 images cropped from \cite{crosschannel2016} since they are taken in different shots.
-The second dataset provided in \cite{ncwebsite} includes about 20 real noisy images collected under uncontrolled outdoor environment.
-This dataset does not have ``ground truth" images.
+Note that the noise in our cropped 60 images used in \cite{crosschannel2016} are different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are taken in different shots.
 
@@
 
-\subsection{Comparison with External and Internal Priors}
+\subsection{Comparison among external, internal and external guided internal priors}
 In this section, we compare our proposed method on real image denoising with external prior based method (denoted as ``External") and internal prior based method (denoted as ``Internal").

### 2016-11-08 CVPR2017_Review_Unified.tex
a

@@
 \end{minipage}
-}\vspace{-3mm}
+}\vspace{-3.5mm}
 \subfigure{
@@
 Combining the priors of external clean images and priors of internalwould naturally achieves better performance.
-In this paper, we propose to employ the external priors learned from natural clean images to guide the learning of internal priors of given noisy image.
-We learn the external priors of patch groups \cite{pgpd} since nonlocal self-similarity is successfully used in many denoising methods \cite{nlm,bm3d,wnnm,pgpd}.
-The learning of external priors is performed by Gaussian Mixture Model.
-The learning of internal priors includes Gaussian selection and orthogonal dictionary learning (DL).
-The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary.
-The real noisy image denoising is simultaneously done with the DL process.
-Both of the two stages have closed-form solutions.
-Hence, our proposed denoising method is very efficient.
-Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising.
+Based on above considerations, in this paper, we propose to employ the external priors learned from natural clean images to guide the learning of internal priors of given noisy image.\ The flowchart of the proposed method is illustrated in Fig.\ \ref{fig2}.\ In the external stage, we learn the external priors of patch groups \cite{pgpd} since nonlocal self-similarity is successfully used in many denoising methods \cite{nlm,bm3d,wnnm,pgpd}.\ The learning of external priors is performed by Gaussian Mixture Model.
+In the internal stage, the learning of internal priors includes Gaussian selection and orthogonal dictionary learning (DL).\ The internal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary.
+The image denoising is simultaneously done with the DL process.\ Both of the two stages have closed-form solutions.\ Hence, our proposed denoising method is very efficient.\ Through extensive experiments on real noisy image denoising, we demonstrate that the proposed method achieves better performance on real image denoising.
 
-The rest of this paper will be summarized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model and formulate the overall image denoising algorithm; in Section 3, we demonstrate extensive experiments on real image denoising problem; in Section 4, we conclude our paper and give future work.
+The rest of this paper will be summarized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model and formulate the overall image denoising algorithm; in Section 3, we perform extensive experiments on real image denoising problem; in Section 4, we conclude our paper and give future work.
 
@@
 However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explict distributions.
-Besides, the parametric estimation of the Gaussian or MoG distribution is often time consumming \cite{B}.
+Besides, the parametric estimation of the Gaussian or MoG distribution is often time consumming.
 
@@
 The overall objective log-likelihood function of GMM is
-\begin{equation}\label{equ2}
+\begin{equation}\label{equ1}
 \begin{split}
@@
 \vspace{-2mm}
-\begin{equation}\label{equ3}\vspace{-2mm}
+\begin{equation}\label{equ2}\vspace{-2mm}
 \mathbf{\Sigma}_{k}=\mathbf{U}_{k}\mathbf{S}_{k}\mathbf{U}_{k}^{\top}.
@@
 The singular vector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ are employed as the external orthogonal dictionary to guide the internal dictionary learning.
-The singular values in the diagonal of $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$ and utilized as prior weights for weighted sparse coding which will be discussed in next section.
+In Figure \ref{fig3} (a) and (b), we illustrate an external clean image and one orthogonal dictionary learned via GMM on PGs of the external clean image.
+To better illustrate the dictionary The singular values in the diagonal of $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$ and utilized as prior weights for weighted sparse coding which will be discussed in next section.
 
@@
 \vspace{-2mm}
-\begin{equation}\label{equ4}\vspace{-1mm}
+\begin{equation}\label{equ3}\vspace{-1mm}
 P(k|\mathbf{\overline{Y}}_{n})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{l})}
@@
 For the $k$-th subspace, assume the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ such that $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.
-We utilize the external orthogonal dictionary $\mathbf{U}_{k}$ (Eqn.
-(\ref{equ3})) to guide the learning of an orthogonal dictionary for adaptively characterizing the internal PGs in the $k$-th subspace.
-The learned dictionary defined as $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$ has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary $\mathbf{U}_{k}$, and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
+We utilize the external orthogonal dictionary $\mathbf{U}_{k}$ (Eqn.\ (\ref{equ2})) to guide the learning of an orthogonal dictionary for adaptively characterizing the internal PGs in the $k$-th subspace.
+The reasons we aim to learn orthogonal dictionaries are two-fold: firstly, given an orthonormal dictionary  $\mathbf{D}$, its quality measure \emph{mutual incoherence} $\mu(\mathbf{D})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}}$
+is naturally $0$ and therefore better than other redundant dictionaries; secondly, the orthogonality of dictioanry can guarantee the dictionary learning stage has closed-form solutions (please refer to Eqn.\ (\ref{equ9})) and the closed-form solutions will make our proposed method efficient, which will be discussed in experimental section.
+
+The learned dictionary $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$ has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary $\mathbf{U}_{k}$, and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
 For notation simplicity, we ignore the subspace index $k$ and denote the noisy PGs assigned to each subspace as $\mathbf{Y}\triangleq\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N} = [\mathbf{\overline{y}}_{1,1},...,\mathbf{\overline{y}}_{1,M},...,\mathbf{\overline{y}}_{N,1},...,\mathbf{\overline{y}}_{N,M}]$.
@@
 \vspace{-2mm}
-\begin{equation}\label{equ5}\vspace{-3mm}
+\begin{equation}\label{equ4}\vspace{-3mm}
 \begin{split}
@@
 \vspace{-1mm}
-\begin{equation}\label{equ6}\vspace{-1mm}
+\begin{equation}\label{equ5}\vspace{-1mm}
 \lambda_{j} = \lambda/(\sqrt{\mathbf{S}_{j}}+\varepsilon).
@@
 We employ square roots of the singular values in $\mathbf{S}$ (please refer to Eqn.
-(\ref{equ3})) as external prior weights and add a small positive number $\varepsilon$ to avoid zero denominator.
+(\ref{equ2})) as external prior weights and add a small positive number $\varepsilon$ to avoid zero denominator.
 Noted that $\mathbf{D}_{e}=\emptyset$ if $r=3p^{2}$ and $\mathbf{D}_{e}=\mathbf{U}_{k}$ if $r=0$.
@@
 \vspace{-2mm}
-\begin{equation}\label{equ7}\vspace{-1mm}
+\begin{equation}\label{equ6}\vspace{-1mm}
 \mathbf{D}^{\top}\mathbf{D} = 
@@
 \vspace{-3mm}
-\begin{equation}\label{equ8}\vspace{-3mm}
+\begin{equation}\label{equ7}\vspace{-3mm}
 \begin{split}
@@
 \end{equation}
-Since dictionary $\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problems (\ref{equ8}) has a closed-form solution \cite{pgpd} 
+Since dictionary $\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problems (\ref{equ7}) has a closed-form solution \cite{pgpd} 
 \vspace{-1mm}
-\begin{equation}\label{equ9}\vspace{-1mm}
+\begin{equation}\label{equ8}\vspace{-1mm}
 \bm{\alpha}_{n,m}^{(t)}= \text{sgn}(\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m}|-\mathbf{\Lambda},\mathbf{0}),
@@
 \vspace{-2mm}
-\begin{equation}\label{equ10} \vspace{-2mm}
+\begin{equation}\label{equ9} \vspace{-2mm}
 \begin{split}
@@
 The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{i}^{(t)}\in\mathbb{R}^{r\times NM}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively.
-According to the Theorem 4 in \cite{spca}, the problem (\ref{equ10})
+According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9})
 has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
 \vspace{-1mm}
-\begin{equation}\label{equ11}\vspace{-2mm}
+\begin{equation}\label{equ10}\vspace{-2mm}
 (\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}(\mathbf{A}_{i}^{(t)})^{\top}
@@
 $(\mathbf{D}_{i}^{(t+1)})^{\top}(\mathbf{D}_{i}^{(t+1)})=\mathbf{V}_{i}\mathbf{U}_{i}^{\top}\mathbf{U}_{i}\mathbf{V}_{i}^{\top}=\mathbf{I}_{r}$.
+In Figure \ref{fig3} (c) and (d), we illustrate a denoised image by our proposed method and one internal orthogonal dictionary learned from PGs of the given noisy image.
 
@@
 (\ref{equ3}) reflect the prior weights of the dictionary atoms and can be used as adaptive parameters for real image denoising.
+When compared with Figure \ref{fig3} (b), we can see that the internal dictionary are more adaptive to the testing real noisy image.
 
@@
 In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction.
-Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in (\ref{equ9}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Eqn.
-(\ref{equ10}).
+Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eqn.\ (\ref{equ8}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Eqn.
+(\ref{equ9}).
 Then the $m$-th latent clean patch $\hat{\mathbf{y}}_{n,m}$ in the $n$-th PG $\mathbf{Y}_{n}$ is recovered by
 \vspace{-2mm}
-\begin{equation}\label{equ12}\vspace{-2mm}
+\begin{equation}\label{equ11}\vspace{-2mm}
 \hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
@@
 \\
-3.\quad Subspace selection via Eqn. (\ref{equ4});
+3.\quad Subspace selection via Eqn. (\ref{equ3});
 \\
@@
 \\
-\quad \ \ \ Dictionary Learning by solving (\ref{equ5});
+\quad \ \ \ Dictionary Learning by solving (\ref{equ4});
 \\
-5.\quad Recover each patch in all PGs via Eqn. (\ref{equ12});
+5.\quad Recover each patch in all PGs via Eqn. (\ref{equ11});
 \\
@@
 We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
-In the second stage, we set $r=54$ (the number of internal atoms in the learned dictionaries), $\lambda=0.001$ (the sparse regularization parameter), $T=2$ (the number of iterations for solving problem (\ref{equ5})), and $IteNum=4$ (the number of iterations for Alg.
+In the second stage, we set $r=54$ (the number of internal atoms in the learned dictionaries), $\lambda=0.001$ (the sparse regularization parameter), $T=2$ (the number of iterations for solving problem (\ref{equ4})), and $IteNum=4$ (the number of iterations for Alg.
 1).
@@
 \hline
-Time & | &  \textbf{56.39}  & 667.36 & 58.47
+Time & | &  \textbf{41.39}  & 667.36 & 44.06
 \\
@@
 
+In this section, we compare the proposed method with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}.
+The methods of BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning} are designed for removing Gaussian noise.
+For BM3D and WNNM, the level $\sigma$ of Gaussian noise is very important and is estimated by the method \cite{noiselevel}.
+The other parameters are set as default.
+For the methods of MLP, CSF, and TRD, we employ their default parameters settings.
+Since these methods are designed for grayscale images, we utilize them to denoise the R, G, B channels separately for color noisy images.
+The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior.
+We also compare with Neat Image (NI), a commercial software for image denoising.
+Due to its excellent performance, Neat Image (NI) is embedded into Photoshop and Corel PaintShop \cite{neatimage}.
+The comparisons are performed on the real noisy images from \cite{ncwebsite} and \cite{crosschannel2016}.
+
+\subsubsection{Comparison on the First Dataset \cite{ncwebsite}}
+
+The real noisy images in the first dataset \cite{ncwebsite} do not have ``ground truth" images. 
+We compare the proposed method with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}.
+
+For the second dataset \cite{ncwebsite} with no ``ground truth" images, we only compare the visual quality of the denoised images.
+Figure \ref{fig6} shows the denoised images of ``Dog" by the competing methods.
+More visual comparisons can be found in the supplementary file.
+It can be seen that the methods of BM3D, WNNM tend to globally over-smooth the image while locally remain some noise, while the methods of MLP, TRD are likely to remain noise in the whole image.
+This demonstrates that the methods designed for Gaussian noise are not effective for removing the complex noise in real noisy images.
+Though Noise Clinic and Neat Image are specifically developed for removing complex noise, they would sometimes fail to recover real noisy images.
+However, our proposed method recoveries more faithfully the structures and textures (such as the eye area) than the other competing methods.
+
+\subsubsection{Comparison on the Second Dataset \cite{crosschannel2016}}
+
+while those in the second dataset \cite{crosschannel2016} have corresponding ``ground truth" images.
+
 In this section, we compare the proposed method with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}.
@@
 
-The comparisons are performed on the two datasets mentioned before.
 For the first dataset \cite{crosschannel2016}, the average PSNR results on the 60 cropped images  are listed in Table \ref{tab2} (the code of \cite{crosschannel2016} is not available so that it is not compared).
@@
 By combining the external and internal priors, our proposed method preserves edges and textures better than other methods.
-
-For the second dataset \cite{ncwebsite} with no ``ground truth" images, we only compare the visual quality of the denoised images.
-Figure \ref{fig6} shows the denoised images of ``Dog" by the competing methods.
-More visual comparisons can be found in the supplementary file.
-It can be seen that the methods of BM3D, WNNM tend to globally over-smooth the image while locally remain some noise, while the methods of MLP, TRD are likely to remain noise in the whole image.
-This demonstrates that the methods designed for Gaussian noise are not effective for removing the complex noise in real noisy images.
-Though Noise Clinic and Neat Image are specifically developed for removing complex noise, they would sometimes fail to recover real noisy images.
-However, our proposed method recoveries more faithfully the structures and textures (such as the eye area) than the other competing methods.
 

### 2016-11-08 CVPR2017_Review_Unified.tex
add

@@
 In \cite{fullyblind}, Portilla proposed to use scale mixture of Gaussians to estimate the noise covariance matrix and latent clean images in wavelet domain.
-The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}.
+The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator.
 Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image.
@@
 \hline
-\textbf{Alg. 1}: External Patch Group (PG) Prior Guided Internal
+\textbf{Alg. 1}: External Prior Guided Internal Prior Learning
 \\
-\quad \quad \quad PG Prior Learning for Image Denoising
+\quad \quad \quad for Real Noisy Image Denoising
 \\
@@
 \subfigure{
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_5dmark3_iso3200_1_real.png}}
-{\footnotesize (a) Noisy  \cite{crosschannel2016}: 37.00dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_dog.png}}
+{\footnotesize (a) Noisy \cite{ncwebsite}   }
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
-{\footnotesize (b) BM3D \cite{bm3d,cbm3d}: 37.02dB}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
+{\footnotesize (b) BM3D \cite{bm3d,cbm3d}  }
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_5dmark3_iso3200_1_real.png}}
-{\footnotesize (c) WNNM \cite{wnnm}: 37.01dB}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
+{\footnotesize (c) WNNM \cite{wnnm}   }
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_5dmark3_iso3200_1_real.png}}
-{\footnotesize (d) MLP \cite{mlp}: 33.90dB }
-\end{minipage}
-\centering
-\begin{minipage}[t]{0.195\textwidth}
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
-{\footnotesize (e) TRD \cite{chen2015learning}: 36.18dB  } 
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
+{\footnotesize (d) MLP \cite{mlp}  }
 \end{minipage}
@@
 \subfigure{
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
-{\footnotesize (f) NC \cite{noiseclinic}: 38.76dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_dog.png}}
+{\footnotesize (e) TRD \cite{chen2015learning}}
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
-{\footnotesize (g) NI \cite{neatimage}: 37.68dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
+{\footnotesize (f) NC \cite{noiseclinic}  }
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
-{\footnotesize (h) CC \cite{crosschannel2016}: 38.37dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
+{\footnotesize (g) NI \cite{neatimage}   }
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
-{\footnotesize (i) Ours: \textbf{40.50}dB}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_dog.png}}
+{\footnotesize (h) Ours  }
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_5dmark3_iso3200_1_real.png}}
-{\footnotesize (j) Mean Image \cite{crosschannel2016}}
-\end{minipage}
-}\vspace{-1mm}
-\caption{Denoised images of the image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
-\vspace{-1mm}
+}
+\caption{Denoised images of the image ``Dog" by different methods. The images are better to be zoomed in on screen.}
+\vspace{-2mm}
 \label{fig5}
@@
 In this section, we compare our proposed method on real image denoising with external prior based method (denoted as ``External") and internal prior based method (denoted as ``Internal").
-The three methods perform denoising under the same framework as Eqn.
-(\ref{equ5}).
-The ``External" method employs the external dictionaries (i.e., $r=0$ in Eqn.
-(\ref{equ5})) for denoising, while the ``Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with fully learned dictionary (i.e., $r=3p^{2}$ in Eqn.
-(\ref{equ5})).
+For the ``External" method, we utilize the external dictionaries (i.e., $r=0$ in Eqn.
+(\ref{equ5})) for denoising.
+For the given noisy image, we extract the PGs and then do internal subspace selection via Eqn.\ \ref{equ3}.
+The denoising is performed via the weighted sparse coding framework proposed in \cite{pgpd}.
+For the ``Internal" method, the overall framework is similar to the method of \cite{ncsr}.
+We employ the GMM model (also with $K=32$ Gaussians) to cluster the noisy PGs extracted from given noisy image into multiple subspaces, and for each subspace, we utilize the internal orthogonal dictionary obtained via Eqn.\ (\ref{equ2}) by weighted sparse coding framework in \cite{pgpd}.
 All parameters of the three methods are tuned to achieve best performance.
 
-We compare the above mentioned methods on the 60 cropped images from \cite{crosschannel2016}.
+We compare the above mentioned methods on the 60 cropped images (of size $500\times 500\times3$) from \cite{crosschannel2016}.
 The average PSNR and speed of these methods are listed in Table \ref{tab1}.
@@
 
-\begin{table*}
-\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
-\label{tab2}
-\begin{center}
-\renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
-\hline
- & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
-\\
-\hline
-PSNR & 34.51 & 34.58 & 34.52 & 36.19 & 37.40 & {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
-%\\
-%\hline
-%SSIM & 0.8718  & 0.8748  & 0.8743 & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
-\\
-\hline
-\end{tabular}
-\end{center}\vspace{-6mm}
-\end{table*}
-
 \subsection{Comparison with Other Denoising Methods}
@@
 
-The real noisy images in the first dataset \cite{ncwebsite} do not have ``ground truth" images. 
-We compare the proposed method with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}.
-
-For the second dataset \cite{ncwebsite} with no ``ground truth" images, we only compare the visual quality of the denoised images.
-Figure \ref{fig6} shows the denoised images of ``Dog" by the competing methods.
+The real noisy images in the dataset \cite{ncwebsite} do not have ``ground truth" images.
+On this dataset, we compare the proposed method with the methods of BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, and Neat Image (NI) \cite{neatimage}.
+We only compare the visual quality of the denoised images.
+Figure \ref{fig5} shows the denoised images of ``Dog" by the competing methods.
 More visual comparisons can be found in the supplementary file.
@@
 
-while those in the second dataset \cite{crosschannel2016} have corresponding ``ground truth" images.
-
-In this section, we compare the proposed method with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}.
-These methods are designed for removing Gaussian noise.
-For BM3D and WNNM, the level $\sigma$ of Gaussian noise is very important and is estimated by the method \cite{noiselevel}.
-The other parameters are set as default.
-For the methods of MLP, CSF, and TRD, we employ their default parameters settings.
-Since these methods are designed for grayscale images, we utilize them to denoise the R, G, B channels separately for color noisy images.
-The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior.
-The recently proposed Cross-Channel (CC) \cite{crosschannel2016} is a state-of-the-art method on real image denoising problem.
-We also compare with Neat Image (NI), a commercial software for image denoising.
-Due to its excellent performance, NI is embedded into Photoshop and Corel PaintShop \cite{neatimage}.
-
-For the first dataset \cite{crosschannel2016}, the average PSNR results on the 60 cropped images  are listed in Table \ref{tab2} (the code of \cite{crosschannel2016} is not available so that it is not compared).
-The numbers in red color and blue color are the best and second best results, respectively.
-It can be seen that our proposed method achieves much better PSNR results than the other methods.
-The improvement of our method over the second best method (TRD) is 1dB.
-To compare with \cite{crosschannel2016}, we also perform experiments on the 15 cropped images used in \cite{crosschannel2016}.
-The PSNR values are listed in Table \ref{tab3}.
+The real noisy images in the second dataset \cite{crosschannel2016} have corresponding ``ground truth" images.
+On this dataset, we firstly perform comparison on the 15 cropped images used in \cite{crosschannel2016}.
+The compared method are BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, and Cross-Channel (CC) \cite{crosschannel2016}.
+The PSNR values are listed in Table \ref{tab2}.
 As we can see, on most (9 out of the 15) images captured by different cameras and camera settings, our proposed method obtains better PSNR values than the other methods.
@@
 We also compare the visual quality of the denoised images by the competing methods.
-Figure \ref{fig5} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO $=3200$ by the competing methods.
+Figure \ref{fig6} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO $=3200$ by the competing methods.
 More visual comparisons can be found in the supplementary file.
@@
 
-In summary, our proposed method demonstrates impressing ability on dealing with the complex noise in real noisy images in terms of PSNR and visual quality.
+To evaluate the compared methods on more samples, we then perform denoising experiments on the 60 smaller images cropped from the 17 images provided in \cite{crosschannel2016}.
+The average PSNR results are listed in Table \ref{tab3} (the code of \cite{crosschannel2016} is not available so that it is not compared).
+The numbers in red color and blue color are the best and second best results, respectively.
+It can be seen that our proposed method achieves much better PSNR results than the other methods.
+The improvement of our method over the second best method (TRD) is 1dB.
+Due to the spacial limitations, the visual comparisions are provided in the supplementary file.
 
@@
 \caption{Average PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
-\label{tab3}
+\label{tab2}
 \begin{center}
@@
 \subfigure{
-\begin{minipage}[t]{0.244\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_dog.png}}
-{\footnotesize (a) Noisy \cite{ncwebsite}   }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_5dmark3_iso3200_1_real.png}}
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 37.00dB }
 \end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
-{\footnotesize (b) BM3D \cite{bm3d,cbm3d}  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
+{\footnotesize (b) BM3D \cite{bm3d,cbm3d}: 37.02dB}
 \end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
-{\footnotesize (c) WNNM \cite{wnnm}   }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_5dmark3_iso3200_1_real.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 37.01dB}
 \end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
-{\footnotesize (d) MLP \cite{mlp}  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_5dmark3_iso3200_1_real.png}}
+{\footnotesize (d) MLP \cite{mlp}: 33.90dB }
+\end{minipage}
+\centering
+\begin{minipage}[t]{0.195\textwidth}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
+{\footnotesize (e) TRD \cite{chen2015learning}: 36.18dB  } 
 \end{minipage}
@@
 \subfigure{
-\begin{minipage}[t]{0.244\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_dog.png}}
-{\footnotesize (e) TRD \cite{chen2015learning}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
+{\footnotesize (f) NC \cite{noiseclinic}: 38.76dB }
 \end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
-{\footnotesize (f) NC \cite{noiseclinic}  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
+{\footnotesize (g) NI \cite{neatimage}: 37.68dB  }
 \end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
-{\footnotesize (g) NI \cite{neatimage}   }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
+{\footnotesize (h) CC \cite{crosschannel2016}: 38.37dB }
 \end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
+\begin{minipage}[t]{0.195\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_dog.png}}
-{\footnotesize (h) Ours  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
+{\footnotesize (i) Ours: \textbf{40.50}dB}
 \end{minipage}
-}
-\caption{Denoised images of the image ``Dog" by different methods. The images are better to be zoomed in on screen.}
-\vspace{-2mm}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_5dmark3_iso3200_1_real.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}\vspace{-1mm}
+\caption{Denoised images of the image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
+\vspace{-1mm}
 \label{fig6}
 \end{figure*}
+
+\begin{table}
+\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
+\vspace{-3mm}
+\label{tab3}
+\begin{center}
+\renewcommand\arraystretch{1}
+\begin{tabular}{|c||c|c|c|c|}
+\hline
+ Methods& \textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
+\\
+\hline
+PSNR &   34.58 & 34.52 & 36.19 & 37.40
+\\
+\hline
+Methods& \textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
+\\
+\hline
+PSNR &  {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
+%SSIM &   0.8748  & 0.8743 & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
+\\
+\hline
+\end{tabular}
+\end{center}\vspace{-8mm}
+\end{table}
 

### 2016-11-08 CVPR2017_Review_Unified.tex
add

@@
 Almost all these methods employ a two-stage framework: firstly estimating the parameters of the assumed noise model (usually Gaussian distribution or mixture of Gaussians (MoG)) and then performing denoising with the help of the estimated noise model.
-However, the noise in real noisy images are very complex and hard to be modeled by explict distributions.
+However, the noise in real noisy images are very complex and hard to be modeled by explicit distributions.
 Therefore, the denoising performance of these methods would be influenced by the error between the estimated noise model and the actual noise distribution.
@@
 proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians.
-However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explict distributions.
-Besides, the parametric estimation of the Gaussian or MoG distribution is often time consumming.
+However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explicit distributions.
+Besides, the parametric estimation of the Gaussian or MoG distribution is often time consuming.
 

### 2016-11-10 CVPR2017_Review_Unified.tex
add

@@
 \begin{abstract}
-Existing image denoising methods mainly focus on signal independent noise such as Gaussian noise.\ The related paper showed that the internal priors (e.g., self-similarity) are highly effective for removing Gaussian noise from synthetic noisy images.\ However, the noise in real noisy images is much more complex than Gaussian noise since it is signal dependent and from several main sources.\ Hence, the internal priors learned on real noisy images would largely degrade the performance of denoising methods.\ In this paper, we propose to avoid the degradation by employing the external priors to guide the learning of internal priors.\ Specifically, we firstly learn external priors via Gaussian Mixture Model on the patch groups (PGs) extracted from natural clean images, and then employ the external priors to guide the subspace selection and orthogonal dictionary learning of the PGs from given noisy image.\ The orthogonal dictionary learning has closed-form solutions and the image denoising is simultaneously performed with the learning process.\ Extensive experiments on real noisy image denoising demonstrate that the proposed method achieves better performance than other state-of-the-art denoising methods.
+Most of existing image denoising methods use some statistical models such as additive white Gaussian noise (AWGN) to model the noise, and learn image priors from either external data or the noisy image itself to remove noise.
+However, the noise in real-world noisy images is much more complex than AWGN, and it is hard to be modeled by simple analytical distributions.
+Therefore, many state-of-the-art denoising methods in literature become much less effective when applied to real noisy images.
+In this paper, we develop a robust denoiser for real noisy image denoising without explicit assumption on noise models.
+Specifically, we first learn external priors from a set of clean natural images, and then use the learned external priors to guide the learning of internal latent priors from the given noisy image.
+The proposed method is simple yet highly effective.
+Experiments on real noisy images demonstrate that it achieves much better denoising performance than state-of-the-art denoising methods, including those designed for real noisy images.
 \end{abstract}
-% in which the noisy images are captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions.
-%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise.
-Therefore, only exploiting the external or internal priors are not enough for real image denoising.
 
@@
 
-Image denoising is an ideal platform for testing computer vision models and an essential procedure for the reliability of many vision systems such as medical imaging and surveillance.
-It aims to recover the latent clean image $\mathbf{x}$ from its noisy observation $\mathbf{y}=\mathbf{x}+\mathbf{n}$ where $\mathbf{n}$ is the additive noise.
-For several decades, there emerge numerous image denoising methods \cite{nlm,foe,ksvd,bm3d,cbm3d,lssc,epll,mlp,ncsr,wnnm,csf,pgpd,chen2015learning} most of which focusing on additive white Gaussian noise (AWGN).
-These methods exploited self-similarity \cite{nlm,epll,wnnm,pgpd}, structural sparsity \cite{ksvd,bm3d,cbm3d,lssc,ncsr}, neural network \cite{mlp}, or learned filters \cite{foe,csf,chen2015learning} for image denoising problem.
+Image denoising is a crucial and indispensable step to improve image quality in digital imaging systems.
+In particular, with the decrease of size of CMOS/CCD sensors, noise is more easily to be corrupted and hence denoising is becoming increasingly important for high resolution imaging.
+In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise.
+Numerous image denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc}, nonlocal self-similarity based methods \cite{nlm,bm3d,cbm3d,ncsr,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.
 
-However, the methods designed for synthetic Gaussian noise is much less effective for removing the noise in real noisy images.
-The reason is that the noise in real noisy images are much more complex than Gaussian \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).
-Besides, by the seminar work of \cite{healey1994radiometric}, the noise in the camera imaging process \cite{NewInCamera,crosschannel2016} are signal dependent and identified by five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
-This would largely limit the performance of these methods, which are designed for signal independent noise, on dealing with complex real noise.
-To prove our argument, we apply some representing methods of BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning} on a real noisy image provided in \cite{crosschannel2016}.
-The testing image is captured by a Nikon D800 camera when ISO is 3200.
-The ``ground truth" image is also provided with which we can calculate objective measurements such as PSNR.
-The denoised images of these methods are listed in Figure \ref{fig1} (from (b)$\sim$(f)).
-One can see that these methods either remove the noise or over-smooth the complex details in real noisy image.
+Most of the existing denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise n to be additive white Gaussian noise (AWGN).
+Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).
+According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
+As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}.
+One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.
 
-In the last decade, there are also several methods \cite{crosschannel2016,fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR} developed for real noisy image denoising.
-Almost all these methods employ a two-stage framework: firstly estimating the parameters of the assumed noise model (usually Gaussian distribution or mixture of Gaussians (MoG)) and then performing denoising with the help of the estimated noise model.
-However, the noise in real noisy images are very complex and hard to be modeled by explicit distributions.
-Therefore, the denoising performance of these methods would be influenced by the error between the estimated noise model and the actual noise distribution.
-This can be validated by the   denoised results listed in Figure \ref{fig1} ((g) and (h)), in which we evaluate the state-of-the-art real noisy image denoising method Noise Clinic \cite{noiseclinic,ncwebsite} and a commercial denoising software Neat Image \cite{neatimage}.
-From the results, we can see that the two methods do not perform well on the testing noisy image.
-These methods only exploit internal priors (e.g., noise prior, self-similarity) for real noisy image denoising and ignore the information of external natural clean images.
+There have been a few methods \cite{Liu2008,almapg,Zhu_2016_CVPR,crosschannel2016,noiseclinic,ncwebsite,neatimage} developed for real noisy image denoising.
+Almost all of these methods follow a two-stage framework: first estimate the parameters of the assumed noise model (usually Gaussian  or mixture of Gaussians (MoG)), and then perform denoising with the estimated noise model.
+Again, the noise in real noisy images is very complex and hard to be modeled by explicit distributions such as Gaussian and MoG.\ Fig.\ \ref{fig1} also shows the denoised results of two state-of-the-art real noisy image denoising methods, Noise Clinic \cite{noiseclinic,ncwebsite} and Neat Image \cite{neatimage}.
+One can see that these two methods do not perform well on this noisy image either.
+
 \begin{figure*}
@@
 
-The external priors in natural clean images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image.
-Combining the priors of external clean images and priors of internalwould naturally achieves better performance.
-Based on above considerations, in this paper, we propose to employ the external priors learned from natural clean images to guide the learning of internal priors of given noisy image.\ The flowchart of the proposed method is illustrated in Fig.\ \ref{fig2}.\ In the external stage, we learn the external priors of patch groups \cite{pgpd} since nonlocal self-similarity is successfully used in many denoising methods \cite{nlm,bm3d,wnnm,pgpd}.\ The learning of external priors is performed by Gaussian Mixture Model.
-In the internal stage, the learning of internal priors includes Gaussian selection and orthogonal dictionary learning (DL).\ The internal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary.
-The image denoising is simultaneously done with the DL process.\ Both of the two stages have closed-form solutions.\ Hence, our proposed denoising method is very efficient.\ Through extensive experiments on real noisy image denoising, we demonstrate that the proposed method achieves better performance on real image denoising.
+\begin{figure}\vspace{-0.1in}
+\centering
+\includegraphics[width=0.9\linewidth]{Flowchart.png}
+\vspace{-0.1in}
+\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
+}
+\vspace{-0.2in}
+\label{fig2}
+\end{figure}
 
-The rest of this paper will be summarized as follows: in Section 2, we briefly introduce the related work; in Section 3, we develop the proposed external prior guided internal prior learning model and formulate the overall image denoising algorithm; in Section 3, we perform extensive experiments on real image denoising problem; in Section 4, we conclude our paper and give future work.
+This work aims to develop a robust solution for real noisy image denoising without explicitly assuming certain noise models.
+To achieve this goal, we propose to first learn image priors from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image.
+The flowchart of the proposed method is illustrated in\ Fig.\ \ref{fig2}.
+We first extract millions of patch groups from a set of high quality natural images, with which a Gaussian Mixture Model (GMM) is learned as the external prior.
+The learned GMM prior model is used to cluster the patch groups extracted from the given noisy image, and then a hybrid orthogonal dictionary (HOD) is learned as the internal prior for image denoising.
+Our proposed denoising method is simple and efficient, yet our extensive experiments on real noisy images clearly demonstrate its better denoising performance than the current state-of-the-arts.
 
@@
 
-In the last decade, researchers proposed many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for real image denoising problem.
-In \cite{fullyblind}, Portilla proposed to use scale mixture of Gaussians to estimate the noise covariance matrix and latent clean images in wavelet domain.
-The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator.
+In the last decade, researchers proposed many methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for blind image denoising problem.
 Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image.
@@
 \cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain.
-Later, Lebrun el al.
-proposed a multiscale denoising algorithm called ``Noise Clinic" \cite{noiseclinic,ncwebsite}.
-This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance.
 Recently, Zhu et al.
 proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians.
+The method of ``Noise Clinic" \cite{noiseclinic,ncwebsite} and the software of Neat Image \cite{neatimage} are developed specifically for real noisy image denoising.
+``Noise Clinic" \cite{noiseclinic,ncwebsite} generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance.
 However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explicit distributions.
@@
 \hline
-Time & | &  \textbf{41.39}  & 667.36 & 44.06
+Time & | &  \textbf{39.57}  & 667.36 & 43.77
 \\

### 2016-11-10 CVPR2017_Review_Unified.tex
add

@@
 In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise.
-Numerous image denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc}, nonlocal self-similarity based methods \cite{nlm,bm3d,cbm3d,ncsr,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.
+Numerous image denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc,ncsr}, nonlocal self-similarity based methods \cite{nlm,bm3d,cbm3d,ncsr,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.
 
@@
 \centering
-\includegraphics[width=0.9\linewidth]{Flowchart.png}
-\vspace{-0.1in}
+\includegraphics[width=1\linewidth]{Flowchart.png}
+\vspace{-0.25in}
 \caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
@@
 
-%The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self-similarity (NSS) property of natural images.
-The NSS property is commonly used in image restoration tasks \cite{nlm,bm3d,lssc,wnnm,pgpd}.
-The PG prior largely reduces the space of images to be modeled when compared to the patch prior \cite{epll}.
-In \cite{pgpd}, only the PGs of clean natural images is utilized, while the PGs of noisy input images are ignored.
-In this paper, we make use of PGs both from external clean images and internal given real noisy image for better denoising performance.
-
 \subsection{Internal \textbf{\emph{vs.}} External Prior Learning}
 
-Image priors are playing key factors in image denoising methods \cite{nlm,ksvd,epll,pgpd,Irani2013separating}.
-There are mainly two categories of prior learning methods: 1) External methods pre-learned priors (e.g., dictionaries) from a set of clean images, and the learned priors are used to recover the noisy images \cite{epll,pgpd}.
-2) Internal methods directly learned priors from the given noisy image, and the image denoising is simultaneously done with the learning process \cite{ksvd,ple}.
-On one hand, the methods of \cite{epll,pgpd} demonstrated that the external priors learned from natural clean images are highly effctive and efficient for image denoising problem.
-On the other hand, the work of \cite{ncsr,Irani2013separating} showed that the internal priors are highly effective for removing the signal independent Gaussian noise.
-However, the actual noise in real noisy images are much more complex than Gaussian noise.
-Only using the internal information may be not enough for real image denoising problem.
-The methods using only the external priors are not adaptive to given real noisy images, while the methods exploiting only internal priors would be degraded by the complex noise.
-In this paper, we propose to combine both the external and internal priors to solve the real noisy image denoising problem.
+Image priors are playing a key role in image denoising \cite{pgpd,epll,ksvd,ple,ncsr,iraniinternal}.
+There are mainly two categories of prior learning methods.
+1) External prior learning methods \cite{foe,pgpd,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images.
+2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and the image denoising is often done simultaneously with the prior learning process.
+It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.
+By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.
+In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images.
+In this paper, we use external priors to guide the internal prior learning.
+Our method is not only much faster than the traditional internal learning methods, but also very effective to denoise real noisy images.
 

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 
-\subsection{Real Image Denoising}
+\subsection{Real Noisy Image Denoising}
 
-In the last decade, researchers proposed many methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for blind image denoising problem.
+In the last decade, there are many methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for blind image denoising problem.
+These methods can be applied to real noisy image denoising directly.
 Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image.
@@
 
-In this section, we formulate the framework of external patch group (PG) prior guided internal prior learning.
-We first introduce the external PG prior leaning on natural clean RGB images.
-Then we propose to employ the learned external PG prior to guide the internal prior (subspace selection and dictionary learning (DL)) learning of given degraded (such as noisy) images.
-Under the weighted sparse coding framework, the internal prior learning process has alternative closed-form solutions in term of updating sparse coefficients and orthogonal dictionary.
-Finally, we discuss in details how external prior learned from natural clean images guide the internal prior learning of given degraded (noisy) images.
+In this section, we first describe the learning of external prior, and then describe in detail the guided internal prior learning.
+Finally, the denoising algorithm with the learned priors is presented.
 
@@
 \hline
-Time & | &  \textbf{39.57}  & 667.36 & 43.77
+Time & | &  \textbf{39.57}  & 667.36 & 41.89
 \\

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 
-\subsection{Learn External Patch Group Prior}
+\subsection{Learn External Patch Group Priors}
 
-In this section, we formulate the Patch Group prior learned on natural color images.
-Similar to \cite{pgpd}, the patch group (PG) is defined as a group of similar patches to the local patch.
-The patch group mean is subtracted, and hence different groups of patches can share similar PGs.
-In this way, the space natural image patches to be modeled is largely reduced.
+The nonlocal self-similarity based patch group (PG) \cite{pgpd} has proved to be a very effective unit for image prior learning.
+In this work, we also extract PGs from natural clean images to learn priors.
+A PG  is a group of similar patches to a local patch.
 
-In this work, each local patch extracted from RGB images is of size $p\times p \times 3$.
-Then we search the $M$ most similar patches $\{\mathbf{x}_{m}\}_{m=1}^{M}$ around each local patch through Euclidean distance, in a local window of size $W\times W$.
-The $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ is a patch vector formed by combining the 3 patch vectors (of size $p^{2}\times 1$) in R, G, B channels.
-The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}\}, m=1,...,M$.
-Assume we have extracted $N$ PGs from a set of external natural images, and the $n$-th PG is defined as $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.
-We employ the Gaussian Mixture Model (GMM) to learn the external patch group based NSS prior.
-The overall objective log-likelihood function of GMM is
-\begin{equation}\label{equ1}
+In our method, each local patch is extracted from a RGB image with patch size $p\times p \times 3$.
+We search the $M$ most similar patches to this local patch (including the local patch itself) in a $W\times W$ local region around it.
+Each patch is stretched to a patch vector $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ to form the PG $\{\mathbf{x}_{m}\}_{m=1}^{M}$.
+The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}\}$.
+
+Assume we extract a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.
+A Gaussian Mixture Model (GMM) is learned to model the PG prior.
+The overall log-likelihood function is
+\vspace{-2mm}
+\begin{equation}\label{equ1}\vspace{-2mm}
 \begin{split}
@@
 \end{equation}
-The learning process is similar to the learning stage of the PGPD method \cite{pgpd}.
-Please refer to \cite{pgpd} for more details.
-After the learning stage, we finally obtain a GMM model with $K$ Gaussian components.
-The learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.
-Similar to \cite{pgpd}, the mean vector of each cluster is natural zeros, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
+The learning process is similar to the GMM learning in \cite{pgpd,epll}.
+Finally, a GMM model with $K$ Gaussian components is learned, and the learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.
+Note that the mean vector of each cluster is naturally zero, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
 
-Now, we have clustered the PGs extracted from external clean images into $K$ Gaussians or subspaces.
-To better characterize each subspace, we perform singular value decomposition (SVD) on the covariance matrix:
+To better describe the subspace of each Gaussian component, we perform singular value decomposition (SVD) on the covariance matrix:
 \vspace{-2mm}
@@
 \end{equation}
-The singular vector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ are employed as the external orthogonal dictionary to guide the internal dictionary learning.
-In Figure \ref{fig3} (a) and (b), we illustrate an external clean image and one orthogonal dictionary learned via GMM on PGs of the external clean image.
-To better illustrate the dictionary The singular values in the diagonal of $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$ and utilized as prior weights for weighted sparse coding which will be discussed in next section.
+The eigenvector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ will be employed as the external orthogonal dictionary to guide the internal dictionary learning in next sub-section.
+In Fig.\ \ref{fig3} (a) and (b), we illustrate an external clean image and one orthogonal dictionary learned via GMM on PGs of the external clean image.
+The singular values in $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$.
+They  will also be utilized as prior weights for weighted sparse coding in our denoising algorithm.
 
@@
 \vspace{-2mm}
-\subsubsection{Internal Subspace Selection}
+\subsubsection{Internal Subspace Assignment}
 \vspace{-1mm}

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 
-\subsection{External Prior Guided Internal Prior Learning}
+\subsection{Guided Internal Prior Learning}
 
-After the external patch group (PG) prior is learned, we can employ it to guide the internal PG prior learning for the given testing (real noisy) image.
-The guidance mainly comes from two aspects.
-One aspect is that the external prior can guide the internal noisy PGs to be assigned to most suitable Gaussians or subspaces.
-And for each subspace, the other aspect is to guide the orthogonal dictionary learning of internal noisy PGs.
+After the external PG prior is learned, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ One is that the external prior can guide the subspace assignment of internal noisy PGs, while the other is that the external prior could guide the orthogonal dictionary learning of internal noisy PGs.
 
@@
 
-Given a real noisy image, assume we can totally extract $N$ local patches from it.
-Similar to the external prior learning stage, for the $n$-th local patch ($n=1,...,N$), we extract its $M$ most similar patches around it to form a noisy PG denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.
-Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is calculated and subtracted from each patch by $\mathbf{\overline{y}}_{n,m}=\mathbf{y}_{n,m}-\bm{\mu}_{n}$, leading to the mean subtracted PG $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$.
-For adaptivity, we project the PG $\mathbf{\overline{Y}}_{n}$ into its most suitable Gaussian component (subspace) of the GMM learned on external PGs.
-The subspace most suitable for $\mathbf{\overline{Y}}_{n}$ is selected by firstly calculating the posterior probability of ``$\mathbf{\overline{Y}}_{n}$ belonging to the $k$-th Gaussian component":
+Given a real noisy image, we extract $N$ (overlapped) local patches from it.
+Similar to the external prior learning stage, for the $n$-th local patch we search its $M$ most similar patches around it to form a noisy PG, denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.
+Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is subtracted from each patch by $\mathbf{\overline{y}}_{n,m}=\mathbf{y}_{n,m}-\bm{\mu}_{n}$, leading to the mean subtracted noisy PG $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$.
+
+The external GMM prior models $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$ basically characterize the subspaces of natural high quality PGs.
+Therefore, we project the noisy PG $\mathbf{\overline{Y}}_{n}$ into the subspaces of $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$ and assign it to the most suitable subspace based on the posterior probability:
 \vspace{-2mm}
-\begin{equation}\label{equ3}\vspace{-1mm}
+\begin{equation}\label{equ3}\vspace{-2mm}
 P(k|\mathbf{\overline{Y}}_{n})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{n,m}|\mathbf{0},\mathbf{\Sigma}_{l})}
 \end{equation}
-for $k=1,...,K$, and then choosing the component with the maximum A-posteriori (MAP) probability $\max_{k}P(k|\mathbf{\overline{Y}}_{n})$.
+for $k=1,...,K$.\ Then $\mathbf{\overline{Y}}_{n}$ is assigned to the component with the maximum A-posteriori (MAP) probability $\max_{k}P(k|\mathbf{\overline{Y}}_{n})$.
 
 \vspace{-2mm}
-\subsubsection{Internal Orthogonal Dictionary Learning}
+\subsubsection{Guided Orthogonal Dictionary Learning}
 \vspace{-2mm}

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 
-Assume we have assigned all internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable Gaussians or subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
-For the $k$-th subspace, assume the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ such that $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.
-We utilize the external orthogonal dictionary $\mathbf{U}_{k}$ (Eqn.\ (\ref{equ2})) to guide the learning of an orthogonal dictionary for adaptively characterizing the internal PGs in the $k$-th subspace.
-The reasons we aim to learn orthogonal dictionaries are two-fold: firstly, given an orthonormal dictionary  $\mathbf{D}$, its quality measure \emph{mutual incoherence} $\mu(\mathbf{D})=\max_{i~=j}\frac{|\mathbf{d}_{i}^{T}\mathbf{d}_{j}|}{\|\mathbf{d}_{i}\|_{2}\|\mathbf{d}_{j}\|_{2}}$
-is naturally $0$ and therefore better than other redundant dictionaries; secondly, the orthogonality of dictioanry can guarantee the dictionary learning stage has closed-form solutions (please refer to Eqn.\ (\ref{equ9})) and the closed-form solutions will make our proposed method efficient, which will be discussed in experimental section.
+Assume we have assigned all the internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
+For the $k$-th subspace, the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ where $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.
+We propose to learn an orthogonal dictionary $\mathbf{D}_{k}$ from each set of PGs $\mathbf{\overline{Y}}_{k_{n}}$ with the guidance of the corresponding external orthogonal dictionary $\mathbf{U}_{k}$ (Eqn.\ (\ref{equ2})) to characterize the internal PG prior.
+The reasons that we learn orthogonal dictionaries are two-fold.
+Firstly, the PGs $\mathbf{\overline{Y}}_{k_{n}}$ are in a subspace of the whole space of all PGs, therefore, there is no necessary to learn a redundant over-complete dictionary to characterize it, while an orthonormal dictionary has naturally zero \emph{mutual incoherence} \cite{donoho2001uncertainty}.
+Secondly, the orthogonality of dictionary can make the encoding in the testing stage very efficient, leading to an efficient denoising algorithm (please refer to sub-section 3.3 for details).
 
-The learned dictionary $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,e}\ \mathbf{D}_{k,i}]\in \mathbb{R}^{3p^2\times 3p^2}$ has two parts: the external part $\mathbf{D}_{k,e}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is directly obtained from the external dictionary $\mathbf{U}_{k}$, and the internal part $\mathbf{D}_{k,i}$ is consisted of dictionary atoms adaptively learned from the internal noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
-For notation simplicity, we ignore the subspace index $k$ and denote the noisy PGs assigned to each subspace as $\mathbf{Y}\triangleq\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N} = [\mathbf{\overline{y}}_{1,1},...,\mathbf{\overline{y}}_{1,M},...,\mathbf{\overline{y}}_{N,1},...,\mathbf{\overline{y}}_{N,M}]$.
-The learning is performed under the weighted sparse coding framework proposed as follows:
+We let the orthogonal dictionary $\mathbf{D}_{k}$ be $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,\text{E}}\ \mathbf{D}_{k,\text{I}}]\in \mathbb{R}^{3p^2\times 3p^2}$, where $\mathbf{D}_{k,\text{E}}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times r}$ is the external sub-dictionary and it includes the first $r$ most important eigenvectors of $\mathbf{U}_{k}$, and the internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ is to be adaptively learned from the noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
+The rationale to design $\mathbf{D}_{k}$ as a hybrid dictionary is as follows.
+The external sub-dictionary $\mathbf{D}_{k,\text{E}}$ is pre-trained from external clean data, and it represents the $k$-th latent subspace of natural images, which is helpful to reconstruct the common latent structures of images.
+However, $\mathbf{D}_{k,\text{E}}$ is general to all images and it is not adaptive to the given noisy image.
+Some fine-scale details specific to the given image may not be well characterized by $\mathbf{D}_{k,\text{E}}$.
+Therefore, we learn an internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ to supplement $\mathbf{D}_{k,\text{E}}$.
+In other words, $\mathbf{D}_{k,\text{I}}$ is to reveal the latent subspace adaptive to the input noisy image, which cannot be effectively represented by $\mathbf{D}_{k,\text{E}}$.
+
+For notation simplicity, in the following development we ignore the subspace index $k$ for $\mathbf{\overline{Y}}_{k_{n}}$ and $\mathbf{D}_{k}$, etc.
+The learning of hybrid orthogonal dictionary $\mathbf{D}$ is performed under the following weighted sparse coding
+framework:
 \vspace{-2mm}
@@
 \end{equation}
-where $\bm{\alpha}_{n,m}$ is the sparse coefficient vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
+where $\bm{\alpha}_{n,m}$ is the sparse coding vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
 $\lambda_{j}$ is the $j$-th regularization parameter defined as
@@
 \begin{equation}\label{equ5}\vspace{-1mm}
-\lambda_{j} = \lambda/(\sqrt{\mathbf{S}_{j}}+\varepsilon).
+\lambda_{j} = \lambda/(\sqrt{\mathbf{S}_{k}(j)}+\varepsilon),
 \end{equation}
-We employ square roots of the singular values in $\mathbf{S}$ (please refer to Eqn.
-(\ref{equ2})) as external prior weights and add a small positive number $\varepsilon$ to avoid zero denominator.
-Noted that $\mathbf{D}_{e}=\emptyset$ if $r=3p^{2}$ and $\mathbf{D}_{e}=\mathbf{U}_{k}$ if $r=0$.
-The dictionary $\mathbf{D} = [\mathbf{D}_{e}\ \mathbf{D}_{i}]$ is orthogonal by checking that:
+where $\mathbf{S}_{k}(j)$ is the $j$-th singular value of diagonal singular value matrix $\mathbf{S}_{k}$ (please refer to Eqn.
+(\ref{equ2})) and $\varepsilon$ is a small positive number to avoid zero denominator.
+Noted that $\mathbf{D}_{\text{E}}=\mathbf{U}_{k}$ if $r=3p^{2}$ and $\mathbf{D}_{\text{E}}=\emptyset$ if $r=0$.
+The dictionary $\mathbf{D} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}]$ is orthogonal by checking that:
 \vspace{-2mm}
@@
 
-Similar to K-SVD \cite{ksvd}, we employ an alternating iterative framework to solve the optimization problem (\ref{equ5}).
-Specifically, we initialize the orthogonal dictionary as $\mathbf{D}_{(0)}=\mathbf{U}_{k}$ and for $t=0, 1, ..., T-1$, alternatively do:
-\\
-\textbf{Updating Sparse Coefficient}: given the orthogonal dictionary $\textbf{D}_{(t)}$, we update the sparse coefficient vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ via solving
+We employ an alternating iterative approach to solve the optimization problem (\ref{equ4}).
+Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{k}$ and for $t=0,1, ...,T-1$, we alternatively update $\bm{\alpha}_{n,m}$ and $\mathbf{D}$ as follows:
+\vspace{2mm}\\
+\textbf{Updating Sparse Coefficient}: Given the orthogonal dictionary $\textbf{D}^{(t)}$, we update each sparse coding vector $\bm{\alpha}_{n,m}$ by solving
 \vspace{-3mm}

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 \begin{split}
-&\bm{\alpha}_{n,m}^{(t)}:=\argmin_{\bm{\alpha}_{n,m}}
-\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}_{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|
-\\
-&
-s.t.
-\quad
-\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
+\bm{\alpha}_{n,m}^{(t)}:=\argmin_{\bm{\alpha}_{n,m}}
+\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}^{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|
 \end{split}
 \end{equation}
-Since dictionary $\mathbf{D}_{(t)}=[\mathbf{D}_{e}\ \mathbf{D}_{i}^{(t)}]$ is orthogonal, the problems (\ref{equ7}) has a closed-form solution \cite{pgpd} 
-\vspace{-1mm}
-\begin{equation}\label{equ8}\vspace{-1mm}
-\bm{\alpha}_{n,m}^{(t)}= \text{sgn}(\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|\mathbf{D}_{(t)}^{\top}\mathbf{\overline{y}}_{n,m}|-\mathbf{\Lambda},\mathbf{0}),
+Since dictionary $\mathbf{D}^{(t)}$ is orthogonal, the problems (\ref{equ7}) has a closed-form solution
+\vspace{-2mm}
+\begin{equation}\label{equ8}\vspace{-2mm}
+\bm{\alpha}_{n,m}^{(t)}= \text{sgn}((\mathbf{D}^{(t)})^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|(\mathbf{D}^{(t)})^{\top}\mathbf{\overline{y}}_{n,m}|-\bm{\lambda},\mathbf{0}),
 \end{equation}
-where $\mathbf{\Lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.
-\\
-\textbf{Updating Internal Dictionary}: given the sparse coefficient vectors $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$, we update the internal orthogonal dictionary via solving
+where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.\ The detailed derivation of Eqn.
+(\ref{equ8}) can be found in the supplementary file.
+\vspace{2mm}\\
+\textbf{Updating Internal Sub-dictionary}: Given the sparse coding vectors $\bm{\alpha}_{n,m}^{(t)}$, we update the internal orthogonal dictionary via solving
 \vspace{-2mm}

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 \vspace{2mm}\\
-\textbf{Updating Internal Sub-dictionary}: Given the sparse coding vectors $\bm{\alpha}_{n,m}^{(t)}$, we update the internal orthogonal dictionary via solving
+\textbf{Updating Internal Sub-dictionary}: Given the sparse coding vectors $\bm{\alpha}_{n,m}^{(t)}$, we update the internal sub-dictionary by solving
 \vspace{-2mm}

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 \end{equation}
+where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$.
 The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{i}^{(t)}\in\mathbb{R}^{r\times NM}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively.

### 2016-11-11 CVPR2017_Review_Unified.tex
ad

@@
 \begin{split}
-\textbf{D}_{i}^{(t+1)}
+\textbf{D}_{\text{I}}^{(t+1)}
 :
@@
 =
-\argmin_{\textbf{D}_{i}}
+\argmin_{\textbf{D}_{\text{I}}}
 \sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
@@
 =
-\argmin_{\textbf{D}_{i}}
+\argmin_{\textbf{D}_{\text{I}}}
 \|\mathbf{Y}-\mathbf{D}\mathbf{A}^{(t)}\|_{F}^{2}
@@
 =
-[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
+[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}],\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{I}_{r},\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{0},
 \end{split}
@@
 where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$.
-The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{i}^{(t)}\in\mathbb{R}^{r\times NM}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively.
-According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9})
+The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{e}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{i}^{(t)}\in\mathbb{R}^{r\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary, respectively.
+
+ $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$ According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) 
 has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD

### 2016-11-11 CVPR2017_Review_Unified.tex
add

--- 2016-11-11 CVPR2017_Review_Unified.tex
@@
 where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$.
-The sparse coefficient matrix $\mathbf{A}^{(t)}=[(\mathbf{A}_{e}^{(t)})^{\top}\ (\mathbf{A}_{i}^{(t)})^{\top}]^{\top}$ also has two parts: the external part $\mathbf{A}_{e}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{i}^{(t)}\in\mathbb{R}^{r\times NM}$ denote the coefficients over external dictionary $\mathbf{D}_{e}$ and internal dictionary $\mathbf{D}_{i}^{(t)}$, respectively.
+The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{r\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.
 According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9})

### 2016-11-11 CVPR2017_Review_Unified.tex
ad
add

@@
 For the $k$-th subspace, the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ where $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.
-We propose to learn an orthogonal dictionary $\mathbf{D}_{k}$ from each set of PGs $\mathbf{\overline{Y}}_{k_{n}}$ with the guidance of the corresponding external orthogonal dictionary $\mathbf{U}_{k}$ (Eqn.\ (\ref{equ2})) to characterize the internal PG prior.
+We propose to learn an orthogonal dictionary $\mathbf{D}_{k}$ from each set of PGs $\mathbf{\overline{Y}}_{k_{n}}$ with the guidance of the corresponding external orthogonal dictionary $\mathbf{U}_{k}$ (Eq.\ (\ref{equ2})) to characterize the internal PG prior.
 The reasons that we learn orthogonal dictionaries are two-fold.
@@
 \end{equation}
-where $\mathbf{S}_{k}(j)$ is the $j$-th singular value of diagonal singular value matrix $\mathbf{S}_{k}$ (please refer to Eqn.
+where $\mathbf{S}_{k}(j)$ is the $j$-th singular value of diagonal singular value matrix $\mathbf{S}_{k}$ (please refer to Eq.
 (\ref{equ2})) and $\varepsilon$ is a small positive number to avoid zero denominator.
@@
 \end{equation}
-where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.\ The detailed derivation of Eqn.
+where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.\ The detailed derivation of Eq.
 (\ref{equ8}) can be found in the supplementary file.
@@
 The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{r\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.
-According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9})
-has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
+According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
 \vspace{-1mm}
@@
 
-%Here we take a detailed analysis on the guidance of the external patch group (PG) prior for the internal noisy PGs of given real noisy images.
-The guidance comes from at least three aspects: 1) the external prior guides the internal PGs to be clustered into suitable subspaces through MAP in Eqn.
-(\ref{equ4}).
-The guided subspace selection is more efficient than directly clustering the internal noisy PGs via k-means or Gaussian Mixture Model (GMM).
-The reason is, by guidance we only need calculate the probabilities via Eqn.
-(\ref{equ4}) for all noisy PGs while by internal clustering via GMM we have to perform time-consuming EM algorithm \cite{em}; 2) the external clean dictionary guides the learning of orthogonal dictionaries more adaptive for internal noisy images.
-The learning process is very efficient because of closed-form solutions.
-Besides, the learned orthogonal dictionary also makes the denoising process very efficient under weighted sparse coding framework.
-3) the singular values learned by SVD in Eqn.
-(\ref{equ3}) reflect the prior weights of the dictionary atoms and can be used as adaptive parameters for real image denoising.
-When compared with Figure \ref{fig3} (b), we can see that the internal dictionary are more adaptive to the testing real noisy image.
+\subsection{The Denoising Algorithm}
 
-\subsection{The Denoising Algorithm}
+The denoising of the given noisy image can be simultaneously done with the guided internal dictionary learning process.
+Once we obtain the solutions of sparse coding vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.\ (\ref{equ8}) and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{(T)}]$ in Eq.
+(\ref{equ9}), the latent clean patch of a noisy patch $\hat{\mathbf{y}}_{n,m}$ in PG $\mathbf{Y}_{n}$ is reconstructed as
+\vspace{-2mm}
+\begin{equation}\label{equ11}\vspace{-2mm}
+\hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
+\end{equation}
 
@@
 In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction.
-Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eqn.\ (\ref{equ8}) for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ in Eqn.
-(\ref{equ9}).
+Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.
+for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ .
 Then the $m$-th latent clean patch $\hat{\mathbf{y}}_{n,m}$ in the $n$-th PG $\mathbf{Y}_{n}$ is recovered by
-\vspace{-2mm}
-\begin{equation}\label{equ11}\vspace{-2mm}
-\hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
-\end{equation}
+
 where $n=1,...,N;m=1,...,M$.
@@
 \\
-3.\quad Subspace selection via Eqn. (\ref{equ3});
+3.\quad Subspace selection via Eq. (\ref{equ3});
 \\
@@
 \\
-5.\quad Recover each patch in all PGs via Eqn. (\ref{equ11});
+5.\quad Recover each patch in all PGs via Eq. (\ref{equ11});
 \\
@@
 In this section, we compare our proposed method on real image denoising with external prior based method (denoted as ``External") and internal prior based method (denoted as ``Internal").
-For the ``External" method, we utilize the external dictionaries (i.e., $r=0$ in Eqn.
+For the ``External" method, we utilize the external dictionaries (i.e., $r=0$ in Eq.
 (\ref{equ5})) for denoising.
-For the given noisy image, we extract the PGs and then do internal subspace selection via Eqn.\ \ref{equ3}.
+For the given noisy image, we extract the PGs and then do internal subspace selection via Eq.\ \ref{equ3}.
 The denoising is performed via the weighted sparse coding framework proposed in \cite{pgpd}.
 For the ``Internal" method, the overall framework is similar to the method of \cite{ncsr}.
-We employ the GMM model (also with $K=32$ Gaussians) to cluster the noisy PGs extracted from given noisy image into multiple subspaces, and for each subspace, we utilize the internal orthogonal dictionary obtained via Eqn.\ (\ref{equ2}) by weighted sparse coding framework in \cite{pgpd}.
+We employ the GMM model (also with $K=32$ Gaussians) to cluster the noisy PGs extracted from given noisy image into multiple subspaces, and for each subspace, we utilize the internal orthogonal dictionary obtained via Eq.\ (\ref{equ2}) by weighted sparse coding framework in \cite{pgpd}.
 All parameters of the three methods are tuned to achieve best performance.

### 2016-11-11 CVPR2017_Review_Unified.tex
ad
add

@@
 
-We let the orthogonal dictionary $\mathbf{D}_{k}$ be $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,\text{E}}\ \mathbf{D}_{k,\text{I}}]\in \mathbb{R}^{3p^2\times 3p^2}$, where $\mathbf{D}_{k,\text{E}}=\mathbf{U}_{k}(:,1:3p^2-r)\in\mathbb{R}^{3p^2\times r}$ is the external sub-dictionary and it includes the first $r$ most important eigenvectors of $\mathbf{U}_{k}$, and the internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ is to be adaptively learned from the noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
+We let the orthogonal dictionary $\mathbf{D}_{k}$ be $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,\text{E}}\ \mathbf{D}_{k,\text{I}}]\in \mathbb{R}^{3p^2\times 3p^2}$, where $\mathbf{D}_{k,\text{E}}=\mathbf{U}_{k}(:,1:r)\in\mathbb{R}^{3p^2\times r}$ is the external sub-dictionary and it includes the first $r$ most important eigenvectors of $\mathbf{U}_{k}$, and the internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ is to be adaptively learned from the noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
 The rationale to design $\mathbf{D}_{k}$ as a hybrid dictionary is as follows.
@@
 \end{equation}
+where $\bm{\mu}_{n}$ is the group mean of Yn.
+The latent clean image is then reconstructed by aggregating all the reconstructed patches in all PGs.
+We perform the above denoising procedures for several iterations for better denoising outputs.
+The proposed denoising algorithm is summarized in Alg.
+1.
 

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 
-\begin{figure}\vspace{-0.1in}
-\centering
-\includegraphics[width=1\linewidth]{Flowchart.png}
-\vspace{-0.25in}
-\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
-}
-\vspace{-0.2in}
-\label{fig2}
-\end{figure}
-
 This work aims to develop a robust solution for real noisy image denoising without explicitly assuming certain noise models.
@@
 Our proposed denoising method is simple and efficient, yet our extensive experiments on real noisy images clearly demonstrate its better denoising performance than the current state-of-the-arts.
+
+\begin{figure*}\vspace{-0.1in}
+\centering
+\includegraphics[width=0.8\linewidth]{Flowchart.png}
+\vspace{-3mm}
+\caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
+}
+\vspace{-3mm}
+\label{fig2}
+\end{figure*}
 
@@
 \end{equation}
-where $\bm{\mu}_{n}$ is the group mean of Yn.
+where $\bm{\mu}_{n}$ is the group mean of $\mathbf{Y}_{n}$.
 The latent clean image is then reconstructed by aggregating all the reconstructed patches in all PGs.
@@
 1.
-
-We evaluate the performance of the proposed framework on denoising real noisy images.
-The denoising is simultaneously done with the guided internal dictionary learning process.
-We ignore the index $k\in\{1,...,K\}$ of subspace for notation simplicity.
-In the denoising stage, for each subspace, the group mean vectors $\{\bm{\mu}_{n}\}_{n=1}^{N}$ of corresponding mean subtracted noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ are saved for reconstruction.
-Until now, we obtain the solutions of sparse coefficient vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.
-for $n=1,...,N;m=1,...,M$ and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{e}\ \mathbf{D}_{i}^{(T)}]$ .
-Then the $m$-th latent clean patch $\hat{\mathbf{y}}_{n,m}$ in the $n$-th PG $\mathbf{Y}_{n}$ is recovered by
-
-where $n=1,...,N;m=1,...,M$.
 \begin{table}\label{alg1}
@@
 
-In this section, we evaluate the performance of the proposed algorithm on real image denoising.
-To evaluation the effectiveness of the proposed framework of external prior guided internal prior learning, we compare it with the methods with only external prior or only internal prior (Section 4.3).
-We also compare the proposed algorithm with other state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage} (Section 4.4).
+We evaluate the performance of the proposed algorithm on real-world noisy images \cite{crosschannel2016,ncwebsite}  in comparison with  state-of-the-art denoising methods \cite{bm3d,cbm3d,mlp,wnnm,csf,chen2015learning,crosschannel2016,noiseclinic,ncwebsite,neatimage}.
+
+\subsection{Implementation Details}
+
+Our proposed method has two stages: the external prior learning stage and the external prior guided internal prior learning stage.
+In the first stage, we set $p = 6$ (the patch size), $M = 10$ (the number of similar patches in a PG), $W = 31$ (the window size for PG searching) and $K = 32$ (the number of Gaussian components in GMM.
+We learn the external GMM prior with 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
+
+In the second stage, we set $r = 54$ (the number of atoms in the external sub-dictionaries); that is, we let the external sub-dictionary have the same number of atoms as the internal sub-dictionary to be learned.
+Our experiments show that setting $r$ between 27 and 81 will lead to very similar results.
+For other parameters, we set $\lambda=0.001$ (the sparse regularization parameter), $T = 2$ (the number of iterations for solving problem (\ref{equ4})), and $IteNum = 4$ (the number of iterations for Alg.1).
+All parameters of our method are fixed to all experiments, which are run under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.
 
@@
 \end{figure*}
-
-\subsection{Implementation Details}
-Our proposed method contains two stages, the external prior learning stage and the external prior guided internal learning stage.
-In the first stage, we set $p = 6$ (so the patch size is $6\times 6 \times 3$), $M=10$ (the number of patches in a patch group (PG)), $W=31$ (so the window size for PG searching is $31\times31$, and $K=32$ (the number of Gaussians in Gaussian Mixture Model (GMM)).
-We learn the external prior via GMM on about 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
-In the second stage, we set $r=54$ (the number of internal atoms in the learned dictionaries), $\lambda=0.001$ (the sparse regularization parameter), $T=2$ (the number of iterations for solving problem (\ref{equ4})), and $IteNum=4$ (the number of iterations for Alg.
-1).
-All experiments are performed under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.
 

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 
-The comparisons are performed on two standard datasets in which the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings.
-The first dataset provided in \cite{ncwebsite} includes 20 real noisy images collected under uncontrolled outdoor environment.
-This dataset does not have ``ground truth" images and hence the objective measurements can not be performed.
-In order to evaluate the compared methods on quantitative measures, we perform experiments on the second dataset provided in \cite{crosschannel2016}.
-It includes 17 real noisy images and corresponding mean images.
+We evaluate the proposed method on two real noisy image datasets, where the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings.
+
+The first dataset is provided in \cite{ncwebsite}, which includes 20 real noisy images collected under uncontrolled outdoor environment.
+Since there is no ``ground truth" of the noisy images, the objective measures such as PSNR cannot be computed on this dataset.
+
+The second dataset is provided in \cite{crosschannel2016}, which includes noisy images of 17 static scenes.
 The noisy images were collected under controlled indoor environment.
-Some samples can be found in \cite{crosschannel2016}.
-For each image, the same scene was shot 500 times under the same camera and camera setting.
+Each scene was shot 500 times under the same camera and camera setting.
 The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.
-Since the 17 images are too large (of size about $7000\times5000\times3$) and share repetitive contents, the authors in \cite{crosschannel2016} performed comparison on 15 cropped images (of size $512\times 521\times3$).
-To evaluate the compared methods on more samples, we cropped the 17 large images from \cite{crosschannel2016} into 60 smaller images (of size $500\times 500\times3$) including different contents.
+Since the image size is very large (about $7000\times5000$) and the 17 scenes share repetitive contents, the authors of \cite{crosschannel2016} cropped 15 smaller images (of size $512\times512$) to perform experiments.
+To more comprehensively evaluate the proposed methods, we cropped 60 images of size $500\times500$ from the dataset for experiments.
 Some samples are shown in Figure \ref{fig4}.
-Note that the noise in our cropped 60 images used in \cite{crosschannel2016} are different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are taken in different shots.
+Note that the noise in our cropped 60 images is different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are from different shots.
 

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 \quad
-\mathbf{D}=[\mathbf{D}_{e}\ \mathbf{D}_{i}],\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i} = \mathbf{0},
+\mathbf{D}=[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}],\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{I}_{r},\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{0},
 \end{split}
@@
 \left[\begin{array}{c}
-\mathbf{D}_{e}^{\top}
+\mathbf{D}_{\text{E}}^{\top}
 \\
-\mathbf{D}_{i}^{\top}
+\mathbf{D}_{\text{I}}^{\top}
 \end{array}\right]
-[\mathbf{D}_{e}\ \mathbf{D}_{i}]
+[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}]
 =
 \left[\begin{array}{cc}
-\mathbf{D}_{e}^{\top}\mathbf{D}_{e}\ \mathbf{D}_{e}^{\top}\mathbf{D}_{i}
+\mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}}
 \\
-\mathbf{D}_{i}^{\top}\mathbf{D}_{e}\ \mathbf{D}_{i}^{\top}\mathbf{D}_{i}
+\mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}}
 \end{array}\right]
@@
 
-\subsection{Comparison among external, internal and external guided internal priors}
+\subsection{Comparison among external, internal and guided internal priors}
+
+To demonstrate the advantages of external prior guided internal priors, in this section we perform real noisy image denoising by using external priors (denoted by ``External"), internal priors (denoted by ``Internal"), and the proposed guided internal priors (denoted by ``Guided Internal"), respectively.
+For the ``External" method, we utilize the full external dictionaries (i.e., $r=108$ in Eq.
+(ref{equ4})) for denoising.
+For the “Internal” method, the overall framework is similar to the method of [9].
+A GMM model (with K = 32 Gaussians) is directly learned from the PGs extracted from the given noisy image without using any external data, and then the internal orthogonal dictionary is obtained via Eqn.
+(2) to perform denoising.
+All parameters of the
+
 In this section, we compare our proposed method on real image denoising with external prior based method (denoted as ``External") and internal prior based method (denoted as ``Internal").

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 $(\mathbf{D}_{i}^{(t+1)})^{\top}(\mathbf{D}_{i}^{(t+1)})=\mathbf{V}_{i}\mathbf{U}_{i}^{\top}\mathbf{U}_{i}\mathbf{V}_{i}^{\top}=\mathbf{I}_{r}$.
-In Figure \ref{fig3} (c) and (d), we illustrate a denoised image by our proposed method and one internal orthogonal dictionary learned from PGs of the given noisy image.
+In Fig.
+\ref{fig3} (c) and (d), we illustrate a denoised image by our proposed method and one internal orthogonal dictionary learned from PGs of the given noisy image.
 
@@
 To more comprehensively evaluate the proposed methods, we cropped 60 images of size $500\times500$ from the dataset for experiments.
-Some samples are shown in Figure \ref{fig4}.
+Some samples are shown in Fig.
+\ref{fig3}.
 Note that the noise in our cropped 60 images is different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are from different shots.
-
-\begin{figure*}
-\centering
-\subfigure{
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
-{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB  }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
-{\footnotesize (b) External: 39.05dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
-{\footnotesize (c) Internal: 38.75dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
-{\footnotesize (d) Ours: \textbf{39.39}dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
-{\footnotesize (e) Mean Image \cite{crosschannel2016}}
-\end{minipage}
-}
-\caption{Denoised images of the $96$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
-\vspace{-3mm}
-\label{fig2}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\subfigure{
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.55dB  }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (b) External: 36.09dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (c) Internal: 37.11dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (d) Ours: \textbf{37.39}dB }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (e) Mean Image \cite{crosschannel2016}}
-\end{minipage}
-}
-\caption{Denoised images of the $94$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
-\vspace{-3mm}
-\label{fig3}
-\end{figure*}
 
@@
 \vspace{-2mm}
+\label{fig3}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (b) External: 39.05dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (c) Internal: 38.75dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (d) Guided Internal: \textbf{39.39}dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (e) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}
+\caption{Denoised images of the $96$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\vspace{-3mm}
+\label{fig4}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.55dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (b) External: 36.09dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (c) Internal: 37.11dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (d) Guided Internal: \textbf{37.39}dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+{\footnotesize (e) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}
+\caption{Denoised images of the $94$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\vspace{-3mm}
 \label{fig5}
@@
 For the ``External" method, we utilize the full external dictionaries (i.e., $r=108$ in Eq.
-(ref{equ4})) for denoising.
-For the “Internal” method, the overall framework is similar to the method of [9].
-A GMM model (with K = 32 Gaussians) is directly learned from the PGs extracted from the given noisy image without using any external data, and then the internal orthogonal dictionary is obtained via Eqn.
-(2) to perform denoising.
-All parameters of the
+(\ref{equ4})) for denoising.
+For the ``Internal" method, the overall framework is similar to the method of \cite{ncsr}.
+A GMM model (with $K = 32$ Gaussians) is directly learned from the PGs extracted from the given noisy image without using any external data, and then the internal orthogonal dictionary is obtained via Eqn.
+(\ref{equ2}) to perform denoising.
+All parameters of the ``External" and ``Internal" methods are tuned to achieve their best performance.
 
-In this section, we compare our proposed method on real image denoising with external prior based method (denoted as ``External") and internal prior based method (denoted as ``Internal").
-For the ``External" method, we utilize the external dictionaries (i.e., $r=0$ in Eq.
-(\ref{equ5})) for denoising.
-For the given noisy image, we extract the PGs and then do internal subspace selection via Eq.\ \ref{equ3}.
-The denoising is performed via the weighted sparse coding framework proposed in \cite{pgpd}.
-For the ``Internal" method, the overall framework is similar to the method of \cite{ncsr}.
-We employ the GMM model (also with $K=32$ Gaussians) to cluster the noisy PGs extracted from given noisy image into multiple subspaces, and for each subspace, we utilize the internal orthogonal dictionary obtained via Eq.\ (\ref{equ2}) by weighted sparse coding framework in \cite{pgpd}.
-All parameters of the three methods are tuned to achieve best performance.
-
-We compare the above mentioned methods on the 60 cropped images (of size $500\times 500\times3$) from \cite{crosschannel2016}.
-The average PSNR and speed of these methods are listed in Table \ref{tab1}.
-It can be seen that our proposed method achieves better PSNR results than the methods of ``External" and ``Internal".
-The speed of our proposed method is much faster than the ``Internal" method while only a little slower than the ``External" method.
-We also compare the visual quality of the denoised images by these methods.
-From the results listed in Figure \ref{fig2} and Figure \ref{fig3}, we can see that the ``External" method is good at recovering structures (Figure \ref{fig2}) while the ``Internal" method is good at recovering internal complex textures (Figure \ref{fig3}).
-And by utilizing both the external and internal priors, our proposed method can recover well both the structures and textures.
-Noted that the noisy images in Figures \ref{fig2} and \ref{fig3} are cropped from the same image captured by Nikon D600 at ISO $=3200$ in \cite{crosschannel2016}.
-Hence, the differences on PSNR and visual quality among these methods only depends on the contents of the cropped images.
+We compare the three methods mentioned above on the 60 cropped images from \cite{crosschannel2016}.
+The average PSNR and run time  are listed in Table \ref{tab1}.
+It can be seen that ``Guided Internal" prior achieves better PSNR than both ``External" and ``Internal" priors.
+In addition, the ``Internal" method is very slow because it involves online GMM learning, while the ``Guided Internal" method is only a little slower than the ``External" method.
+Fig.
+\ref{fig4} and Fig.
+\ref{fig5} show the denoised images of two noisy image by the three methods.
+We can see that the ``External" method is good at recovering large-scale structures (see Fig.
+\ref{fig4}) while the ``Internal" method is good at recovering fine-scale textures (see Fig.
+\ref{fig5}).
+By utilizing external priors to guide the internal prior learning, our proposed method can effectively recover both the large-scale structures and fine-scale textures.
 
@@
 \label{tab1}
+\begin{small}
 \vspace{-3mm}
@@
 \hline
- & \textbf{Noisy} &\textbf{External} &\textbf{Internal} &\textbf{Ours}  
+ & \textbf{Noisy} & \textbf{External} & \textbf{Internal} & \textbf{Guided Internal}  
 \\
@@
 \end{center}\vspace{-6mm}
+\end{small}
 \end{table}
 
-\subsection{Comparison with Other Denoising Methods}
+\subsection{Comparison with State-of-the-Art Denoising Methods}
 %For BM3D, we employ its color version \cite{cbm3d} which would have better performance on color images.
@@
 We only compare the visual quality of the denoised images.
-Figure \ref{fig5} shows the denoised images of ``Dog" by the competing methods.
+Fig.
+\ref{fig5} shows the denoised images of ``Dog" by the competing methods.
 More visual comparisons can be found in the supplementary file.
@@
 We also compare the visual quality of the denoised images by the competing methods.
-Figure \ref{fig6} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO $=3200$ by the competing methods.
+Fig.
+\ref{fig6} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO $=3200$ by the competing methods.
 More visual comparisons can be found in the supplementary file.

### 2016-11-11 CVPR2017_Review_Unified.tex
ad

@@
 \subsection{Comparison with State-of-the-Art Denoising Methods}
-%For BM3D, we employ its color version \cite{cbm3d} which would have better performance on color images.
 
-In this section, we compare the proposed method with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}.
-The methods of BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning} are designed for removing Gaussian noise.
-For BM3D and WNNM, the level $\sigma$ of Gaussian noise is very important and is estimated by the method \cite{noiselevel}.
-The other parameters are set as default.
-For the methods of MLP, CSF, and TRD, we employ their default parameters settings.
-Since these methods are designed for grayscale images, we utilize them to denoise the R, G, B channels separately for color noisy images.
-The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior.
-We also compare with Neat Image (NI), a commercial software for image denoising.
-Due to its excellent performance, Neat Image (NI) is embedded into Photoshop and Corel PaintShop \cite{neatimage}.
-The comparisons are performed on the real noisy images from \cite{ncwebsite} and \cite{crosschannel2016}.
+We compare the proposed method with state-of-the-art image denoising methods, including CBM3D \cite{bm3d,cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}.
+Among them, CBM3D, WNNM, MLP, CSF and TNRD are designed based on Gaussian noise model, and they need to know the noise level for denoising.
+We use the method in \cite{noiselevel} to estimate the noise level for them.
+All the other parameters in these methods are set as the default ones.
+Since WNNM, MLP, CSF and TNRD are designed for grayscale images, we use them to denoise the R, G, B channels separately for color noisy images.
 
-\subsubsection{Comparison on the First Dataset \cite{ncwebsite}}
+Like our method, the NC is a blind image denoising method which does not need any noise prior.
+The NI is a commercial software for image denoising, which has been embedded into Photoshop and Corel PaintShop \cite{neatimage}.
+The code of CC is not released but its results on the 15 cropped images are available at \cite{crosschannel2016}.
+Therefore, we only compare with it on the 15 cropped images from \cite{crosschannel2016}.
+
+\subsubsection{Results on Dataset \cite{ncwebsite}}
 

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 \vspace{-3mm}
-\label{fig4}
+\label{fig3}
 \end{figure}
-
-\begin{figure*}
-\centering
-\subfigure{
-\begin{minipage}[t]{0.244\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_dog.png}}
-{\footnotesize (a) Noisy \cite{ncwebsite}   }
-\end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
-{\footnotesize (b) BM3D \cite{bm3d,cbm3d}  }
-\end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
-{\footnotesize (c) WNNM \cite{wnnm}   }
-\end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
-{\footnotesize (d) MLP \cite{mlp}  }
-\end{minipage}
-}\vspace{-3mm}
-\subfigure{
-\begin{minipage}[t]{0.244\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_dog.png}}
-{\footnotesize (e) TRD \cite{chen2015learning}}
-\end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
-{\footnotesize (f) NC \cite{noiseclinic}  }
-\end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
-{\footnotesize (g) NI \cite{neatimage}   }
-\end{minipage}
-\begin{minipage}[t]{0.244\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_dog.png}}
-{\footnotesize (h) Ours  }
-\end{minipage}
-}
-\caption{Denoised images of the image ``Dog" by different methods. The images are better to be zoomed in on screen.}
-\vspace{-2mm}
-\label{fig3}
-\end{figure*}
 
@@
 
-The real noisy images in the dataset \cite{ncwebsite} do not have ``ground truth" images.
-On this dataset, we compare the proposed method with the methods of BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, and Neat Image (NI) \cite{neatimage}.
-We only compare the visual quality of the denoised images.
-Fig.
-\ref{fig5} shows the denoised images of ``Dog" by the competing methods.
-More visual comparisons can be found in the supplementary file.
-It can be seen that the methods of BM3D, WNNM tend to globally over-smooth the image while locally remain some noise, while the methods of MLP, TRD are likely to remain noise in the whole image.
-This demonstrates that the methods designed for Gaussian noise are not effective for removing the complex noise in real noisy images.
-Though Noise Clinic and Neat Image are specifically developed for removing complex noise, they would sometimes fail to recover real noisy images.
-However, our proposed method recoveries more faithfully the structures and textures (such as the eye area) than the other competing methods.
+Since there is no ``ground truth" for the real noisy images in  dataset \cite{ncwebsite}, we only compare the visual quality of the denoised images by different methods.
+(Note that method CC \cite{crosschannel2016} is not compared since its code is not available.) Fig.
+\ref{fig6} shows the denoised images of ``Dog".
+It can be seen that CBM3D and WNNM tend to over-smooth much the image while remaining some noise caused color artifacts.
+MLP and TNRD are likely to remain many noise-caused color artifacts across the whole image.
+These results demonstrate that the methods designed with Gaussian noise model are not effective for real noise removal.
+Though NC and NI methods are specifically developed for real noisy images, their performance on noise removal is not very satisfactory.
+In comparison, our proposed method recovers much better the structures and textures (such as the eye area) than the other competing methods.
+More visual comparisons on dataset \cite{ncwebsite} can be found in the supplementary file.
+
+\begin{figure*}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_dog.png}}
+{\footnotesize (a) Noisy \cite{ncwebsite}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
+{\footnotesize (b) BM3D \cite{bm3d,cbm3d}  }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_dog.png}}
+{\footnotesize (c) WNNM \cite{wnnm}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_dog.png}}
+{\footnotesize (d) MLP \cite{mlp}  }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_dog.png}}
+{\footnotesize (e) TRD \cite{chen2015learning}}
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
+{\footnotesize (f) NC \cite{noiseclinic}  }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
+{\footnotesize (g) NI \cite{neatimage}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_dog.png}}
+{\footnotesize (h) Ours  }
+\end{minipage}
+}
+\caption{Denoised images of the image ``Dog" by different methods. The images are better to be zoomed in on screen.}
+\vspace{-2mm}
+\label{fig6}
+\end{figure*}
 

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 
-\subsubsection{Comparison on the Second Dataset \cite{crosschannel2016}}
+\subsubsection{Comparison on Dataset \cite{crosschannel2016}}
+
+As described in section 4.2, there is a mean image for each of the 17 scenes used in dataset \cite{crosschannel2016}, and those mean images can be roughly taken as ``ground truth" images for quantitative evaluation of denoising algorithms.
+We firstly perform quantitative comparison on the 15 cropped images used in \cite{crosschannel2016}.
+The PSNR results of CBM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, NC \cite{noiseclinic} and
+CC \cite{crosschannel2016} are listed in Table \ref{tab2}.
+(The results of CC are copied from the original paper \cite{crosschannel2016}.) The best PSNR result of each image is highlighted in bold.
+One can see that on 9 out of the 15 images, our method achieves the best PSNR values.
+CC achieves the best PSNR on 3 of the 15 images.
+It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images.
+On average, our proposed method has 0.28dB PSNR improvements over [14] and much higher PSNR gains over other competing methods.
+Fig.
+6 shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.
+We can see that CBM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image.
+By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs.
+More visual comparisons can be found in the supplementary file.
 

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images.
-On average, our proposed method has 0.28dB PSNR improvements over [14] and much higher PSNR gains over other competing methods.
+On average, our proposed method has 0.28dB PSNR improvements over \cite{crosschannel2016} and much higher PSNR gains over other competing methods.
 Fig.
-6 shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.
+\ref{fig7} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.
 We can see that CBM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image.
@@
 
-The real noisy images in the second dataset \cite{crosschannel2016} have corresponding ``ground truth" images.
-On this dataset, we firstly perform comparison on the 15 cropped images used in \cite{crosschannel2016}.
-The compared method are BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, and Cross-Channel (CC) \cite{crosschannel2016}.
-The PSNR values are listed in Table \ref{tab2}.
-As we can see, on most (9 out of the 15) images captured by different cameras and camera settings, our proposed method obtains better PSNR values than the other methods.
-Noted that, though in \cite{crosschannel2016} a specific model is trained for each camera and camera setting, our proposed general method still gains 0.28dB improvements on PNSR over \cite{crosschannel2016}.
-We also compare the visual quality of the denoised images by the competing methods.
-Fig.
-\ref{fig6} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO $=3200$ by the competing methods.
-More visual comparisons can be found in the supplementary file.
-We can see that BM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TRD are likely to over-smooth the image.
-By combining the external and internal priors, our proposed method preserves edges and textures better than other methods.
-
-To evaluate the compared methods on more samples, we then perform denoising experiments on the 60 smaller images cropped from the 17 images provided in \cite{crosschannel2016}.
-The average PSNR results are listed in Table \ref{tab3} (the code of \cite{crosschannel2016} is not available so that it is not compared).
-The numbers in red color and blue color are the best and second best results, respectively.
-It can be seen that our proposed method achieves much better PSNR results than the other methods.
-The improvement of our method over the second best method (TRD) is 1dB.
-Due to the spacial limitations, the visual comparisions are provided in the supplementary file.
+We then perform denoising experiments on the 60 images we cropped from \cite{crosschannel2016}.
+The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available).
+Again, our proposed method achieves much better PSNR results than the other methods.
+The improvement of our method over the second best method (TNRD) is about 1dB.
+Due to the space limitations, the visual comparisons are provided in the supplementary file.
 

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 \centering
-\includegraphics[width=0.8\linewidth]{Flowchart.png}
+\includegraphics[width=0.7\linewidth]{Flowchart.png}
 \vspace{-3mm}
@@
 The eigenvector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ will be employed as the external orthogonal dictionary to guide the internal dictionary learning in next sub-section.
-In Fig.\ \ref{fig3} (a) and (b), we illustrate an external clean image and one orthogonal dictionary learned via GMM on PGs of the external clean image.
 The singular values in $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$.
 They  will also be utilized as prior weights for weighted sparse coding in our denoising algorithm.
+
+%In Fig.\ \ref{fig3} (a) and (b), we illustrate an external clean image and one orthogonal dictionary learned via GMM on PGs of the external clean image.
 
@@
 $(\mathbf{D}_{i}^{(t+1)})^{\top}(\mathbf{D}_{i}^{(t+1)})=\mathbf{V}_{i}\mathbf{U}_{i}^{\top}\mathbf{U}_{i}\mathbf{V}_{i}^{\top}=\mathbf{I}_{r}$.
-In Fig.
-\ref{fig3} (c) and (d), we illustrate a denoised image by our proposed method and one internal orthogonal dictionary learned from PGs of the given noisy image.
+
+%In Fig. \ref{fig3} (c) and (d), we illustrate a denoised image by our proposed method and one internal orthogonal dictionary learned from PGs of the given noisy image.
 
@@
 %------------------------------------------------------------------------
-\section{Experiments}
+\vspace{-1mm}
+\section{Experiments}\vspace{-1mm}
 
@@
 
-\subsection{Implementation Details}
+\vspace{-1mm}
+\subsection{Implementation Details}\vspace{-1mm}
 
@@
 
-\subsection{The Testing Datasets}
+\vspace{-1mm}
+\subsection{The Testing Datasets}\vspace{-1mm}
 
@@
 
-\begin{figure*}
+\begin{figure*}\vspace{-1mm}
 \centering
@@
 \end{minipage}
-}
+}\vspace{-1mm}
 \caption{Denoised images of the $96$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
@@
 \end{figure*}
-
-\begin{figure*}
+\begin{figure*}\vspace{-1mm}
 \centering
@@
 \end{minipage}
-}
+}\vspace{-1mm}
 \caption{Denoised images of the $94$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
@@
 
+\vspace{-1mm}
 \subsection{Comparison among external, internal and guided internal priors}
@@
 
+\vspace{-1mm}
 \subsection{Comparison with State-of-the-Art Denoising Methods}
@@
 
+\vspace{-1mm}
 \subsubsection{Results on Dataset \cite{ncwebsite}}
@@
 Due to the space limitations, the visual comparisons are provided in the supplementary file.
+
+\begin{table}
+\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
+\vspace{-2mm}
+\label{tab3}
+\begin{center}
+\renewcommand\arraystretch{1}
+\begin{tabular}{|c||c|c|c|c|}
+\hline
+ Methods& \textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
+\\
+\hline
+PSNR &   34.58 & 34.52 & 36.19 & 37.40
+\\
+\hline
+Methods& \textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
+\\
+\hline
+PSNR &  {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
+%SSIM &   0.8748  & 0.8743 & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
+\\
+\hline
+\end{tabular}
+\end{center}\vspace{-8mm}
+\end{table}
 
@@
 
-\begin{table}
-\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
-\vspace{-3mm}
-\label{tab3}
-\begin{center}
-\renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|}
-\hline
- Methods& \textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
-\\
-\hline
-PSNR &   34.58 & 34.52 & 36.19 & 37.40
-\\
-\hline
-Methods& \textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
-\\
-\hline
-PSNR &  {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
-%SSIM &   0.8748  & 0.8743 & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
-\\
-\hline
-\end{tabular}
-\end{center}\vspace{-8mm}
-\end{table}
-
 \section{Conclusion and Future Work}
@@
 
-\clearpage
 {

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 
-Most of the existing denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise n to be additive white Gaussian noise (AWGN).
+Most of the existing denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN).
 Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).
@@
 
-In the last decade, there are many methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for blind image denoising problem.
-These methods can be applied to real noisy image denoising directly.
-Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image.
-Gong et al.
-\cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain.
-Recently, Zhu et al.
-proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians.
-The method of ``Noise Clinic" \cite{noiseclinic,ncwebsite} and the software of Neat Image \cite{neatimage} are developed specifically for real noisy image denoising.
-``Noise Clinic" \cite{noiseclinic,ncwebsite} generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance.
-However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explicit distributions.
-Besides, the parametric estimation of the Gaussian or MoG distribution is often time consuming.
+Recently, several denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} are proposed to remove unknown noise in noisy images.
+These methods can be directly applied to denoise real noisy images.
+Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimated the noise by a multivariate Gaussian and remove the noise by a generalized version of nonlocal Bayesian model \cite{nlbayes}.
+Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank MoG model.
+There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.
+The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.
+The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.
+Almost all these methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} use Gaussian or mixture of Gaussians (MoG) to model the noise in real noisy images.
+However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
 
@@
 
-\section{Conclusion and Future Work}
+\section{Conclusion}
 
-Image priors are important for solving image denoising problems.
-The external priors learned from external clean images are generally effective to most images, while the internal priors learned directly from the noisy image are adaptive to the given image but would be biased by the complex noise in real noisy images.
-In this paper, we demonstrates that, once unifying both the priors in external clean images and internal noisy images, we can achieve much better while still efficient performance on real image denoising problem.
-Specifically, the external patch group (PG) priors learned on natural clean images can be used to guide the subspace selection and orthogonal dictionary learning of internal noisy PGs from given noisy images.
-The experiments on real image denoising problem have demonstrated the powerful ability of the proposed method.
-In the future, we will speed up the proposed algorithm and evaluate the proposed method on other computer vision tasks such as image super-resolution.
+In the literature of real noisy image denoising, most denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016,neatimage} use explicit statistical models, such as Gaussian or mixture of Gaussians to model the noise, and learn image priors from either external data or the noisy image itself to remove noise.
+However, the noise in real-world noisy images is much more complex and hard to be modeled by simple analytical distributions.
+In this paper, we proposed a simple yet effective solution for real noisy image denoising without explicitly assuming certain noise models.
+Specifically, we firstly learned image priors of Gausian Mixture Model from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image.
+The learned hybrid orthogonal dictionary are simutaneously utilized in real noisy image denoising.
+Experiments on two real noisy image datasets demonstrate that our proposed method achieved much better performance than state-of-the-art image denoising methods.
 

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 
-In the literature of real noisy image denoising, most denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016,neatimage} use explicit statistical models, such as Gaussian or mixture of Gaussians to model the noise, and learn image priors from either external data or the noisy image itself to remove noise.
+Most image denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} are proposed for additive white Gaussian noise (AWGN).
+However, the noise in real noisy images is much more complex than AWGN.
+Even in the literature of real noisy image denoising, most methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016,neatimage} use explicit statistical models, such as Gaussian or mixture of Gaussians to model the noise, and learn image priors from either external data or the noisy image itself to remove noise.
 However, the noise in real-world noisy images is much more complex and hard to be modeled by simple analytical distributions.

### 2016-11-11 CVPR2017_Review_Unified.tex
add

--- 2016-11-11 CVPR2017_Review_Unified.tex
@@
 
-In the literature of real noisy image denoising, most denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016,neatimage} use explicit statistical models, such as Gaussian or mixture of Gaussians to model the noise, and learn image priors from either external data or the noisy image itself to remove noise.
+Most image denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} are proposed for additive white Gaussian noise (AWGN), which is the noise in real noisy images much more complex than AWGN.
+.
+Even in the literature of real noisy image denoising, most methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016,neatimage} use explicit statistical models (Gaussian or mixture of Gaussians) to model the noise, and remove noise by image priors from either external data or the noisy image itself to remove noise.
 However, the noise in real-world noisy images is much more complex and hard to be modeled by simple analytical distributions.

### 2016-11-11 CVPR2017_Review_Unified.tex
add

--- 2016-11-11 CVPR2017_Review_Unified.tex
@@
 \centering
-\includegraphics[width=0.7\linewidth]{Flowchart.png}
+\includegraphics[width=0.35\linewidth]{Flowchart.png}
 \vspace{-3mm}
@@
 
-\vspace{-1mm}
-\subsection{Comparison with State-of-the-Art Denoising Methods}
-
-We compare the proposed method with state-of-the-art image denoising methods, including CBM3D \cite{bm3d,cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}.
-Among them, CBM3D, WNNM, MLP, CSF and TNRD are designed based on Gaussian noise model, and they need to know the noise level for denoising.
-We use the method in \cite{noiselevel} to estimate the noise level for them.
-All the other parameters in these methods are set as the default ones.
-Since WNNM, MLP, CSF and TNRD are designed for grayscale images, we use them to denoise the R, G, B channels separately for color noisy images.
-
-Like our method, the NC is a blind image denoising method which does not need any noise prior.
-The NI is a commercial software for image denoising, which has been embedded into Photoshop and Corel PaintShop \cite{neatimage}.
-The code of CC is not released but its results on the 15 cropped images are available at \cite{crosschannel2016}.
-Therefore, we only compare with it on the 15 cropped images from \cite{crosschannel2016}.
-
-\vspace{-1mm}
-\subsubsection{Results on Dataset \cite{ncwebsite}}
-
-Since there is no ``ground truth" for the real noisy images in  dataset \cite{ncwebsite}, we only compare the visual quality of the denoised images by different methods.
-(Note that method CC \cite{crosschannel2016} is not compared since its code is not available.) Fig.
-\ref{fig6} shows the denoised images of ``Dog".
-It can be seen that CBM3D and WNNM tend to over-smooth much the image while remaining some noise caused color artifacts.
-MLP and TNRD are likely to remain many noise-caused color artifacts across the whole image.
-These results demonstrate that the methods designed with Gaussian noise model are not effective for real noise removal.
-Though NC and NI methods are specifically developed for real noisy images, their performance on noise removal is not very satisfactory.
-In comparison, our proposed method recovers much better the structures and textures (such as the eye area) than the other competing methods.
-More visual comparisons on dataset \cite{ncwebsite} can be found in the supplementary file.
-
 \begin{figure*}
@@
 \end{figure*}
+
+\vspace{-1mm}
+\subsection{Comparison with State-of-the-Art Denoising Methods}
+
+We compare the proposed method with state-of-the-art image denoising methods, including CBM3D \cite{bm3d,cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}.
+Among them, CBM3D, WNNM, MLP, CSF and TNRD are designed based on Gaussian noise model, and they need to know the noise level for denoising.
+We use the method in \cite{noiselevel} to estimate the noise level for them.
+All the other parameters in these methods are set as the default ones.
+Since WNNM, MLP, CSF and TNRD are designed for grayscale images, we use them to denoise the R, G, B channels separately for color noisy images.
+
+Like our method, the NC is a blind image denoising method which does not need any noise prior.
+The NI is a commercial software for image denoising, which has been embedded into Photoshop and Corel PaintShop \cite{neatimage}.
+The code of CC is not released but its results on the 15 cropped images are available at \cite{crosschannel2016}.
+Therefore, we only compare with it on the 15 cropped images from \cite{crosschannel2016}.
+
+\vspace{-1mm}
+\subsubsection{Results on Dataset \cite{ncwebsite}}
+
+Since there is no ``ground truth" for the real noisy images in  dataset \cite{ncwebsite}, we only compare the visual quality of the denoised images by different methods.
+(Note that method CC \cite{crosschannel2016} is not compared since its code is not available.) Fig.
+\ref{fig6} shows the denoised images of ``Dog".
+It can be seen that CBM3D and WNNM tend to over-smooth much the image while remaining some noise caused color artifacts.
+MLP and TNRD are likely to remain many noise-caused color artifacts across the whole image.
+These results demonstrate that the methods designed with Gaussian noise model are not effective for real noise removal.
+Though NC and NI methods are specifically developed for real noisy images, their performance on noise removal is not very satisfactory.
+In comparison, our proposed method recovers much better the structures and textures (such as the eye area) than the other competing methods.
+More visual comparisons on dataset \cite{ncwebsite} can be found in the supplementary file.
 
@@
 
-In the literature of real noisy image denoising, most denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016,neatimage} use explicit statistical models, such as Gaussian or mixture of Gaussians to model the noise, and learn image priors from either external data or the noisy image itself to remove noise.
-However, the noise in real-world noisy images is much more complex and hard to be modeled by simple analytical distributions.
+The noise in real-world noisy images is much more complex than additive white Gaussian noise and hard to be modeled by simple analytical distributions such as Gaussian or mixture of Gaussians.
 In this paper, we proposed a simple yet effective solution for real noisy image denoising without explicitly assuming certain noise models.

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 \centering
-\includegraphics[width=0.35\linewidth]{Flowchart.png}
-\vspace{-3mm}
+\includegraphics[width=0.85\linewidth]{Flowchart2.png}
+\vspace{-2mm}
 \caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
 }
-\vspace{-3mm}
+\vspace{-1mm}
 \label{fig2}
@@
 
-\vspace{-2mm}
 \subsubsection{Internal Subspace Assignment}
-\vspace{-1mm}
 
@@
 
-\vspace{-2mm}
 \subsubsection{Guided Orthogonal Dictionary Learning}
-\vspace{-2mm}
 
@@
 %------------------------------------------------------------------------
-\vspace{-1mm}
+
 \section{Experiments}\vspace{-1mm}
@@
 
-\vspace{-1mm}
 \subsection{Implementation Details}\vspace{-1mm}
@@
 \caption{Denoised images of the $96$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
-\vspace{-3mm}
+\vspace{-1mm}
 \label{fig4}
@@
 \caption{Denoised images of the $94$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
-\vspace{-3mm}
+\vspace{-2mm}
 \label{fig5}
@@
 \begin{small}
-\vspace{-3mm}
+\vspace{-1mm}
 \begin{center}
@@
 \end{tabular}
-\end{center}\vspace{-6mm}
+\end{center}\vspace{-4mm}
 \end{small}
@@
 \caption{Denoised images of the image ``Dog" by different methods. The images are better to be zoomed in on screen.}
-\vspace{-2mm}
+\vspace{-1mm}
 \label{fig6}
@@
 \caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
-\vspace{-2mm}
+\vspace{-1mm}
 \label{tab3}
@@
 \end{tabular}
-\end{center}\vspace{-3mm}
+\end{center}\vspace{-1mm}
 \end{table*}
@@
 The learned hybrid orthogonal dictionary are simutaneously utilized in real noisy image denoising.
-Experiments on two real noisy image datasets demonstrate that our proposed method achieved much better performance than state-of-the-art image denoising methods.
+Experiments on two real noisy image datasets, where the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings, demonstrate that our proposed method achieved much better performance than state-of-the-art image denoising methods.
 

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 \centering  
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.55dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.02dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (b) External: 36.09dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (b) External: 35.58dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (c) Internal: 37.11dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (c) Internal: 36.74dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
-{\footnotesize (d) Guided Internal: \textbf{37.39}dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (d) Guided Internal: \textbf{37.87}dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_94.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
 {\footnotesize (e) Mean Image \cite{crosschannel2016}}
@@
 }\vspace{-1mm}
-\caption{Denoised images of the $94$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the $111$-th cropped image from ``Nikon D800 ISO 3200 A1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \vspace{-2mm}

### 2016-11-11 CVPR2017_Review_Unified.tex
add

@@
 \centering
-\includegraphics[width=0.85\linewidth]{Flowchart2.png}
+\includegraphics[width=0.85\linewidth]{Flowchart3.png}
 \vspace{-2mm}
@@
 }
-\vspace{-1mm}
+\vspace{-3mm}
 \label{fig2}
@@
 The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{r\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.
-According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) has a closed-form solution $\mathbf{D}_{i}^{(t+1)}=\mathbf{U}_{i}\mathbf{V}_{i}^{\top}$, where $\mathbf{U}_{i}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{i}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
+According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
 \vspace{-1mm}
 \begin{equation}\label{equ10}\vspace{-2mm}
-(\mathbf{I}-\mathbf{D}_{e}\mathbf{D}_{e}^{\top})\mathbf{Y}(\mathbf{A}_{i}^{(t)})^{\top}
+(\mathbf{I}-\mathbf{D}_{\text{E}}\mathbf{D}_{\text{E}}^{\top})\mathbf{Y}(\mathbf{A}_{\text{I}}^{(t)})^{\top}
 =
-\mathbf{U}_{i}\mathbf{S}_{i}\mathbf{V}_{i}^{\top}.
+\mathbf{U}_{\text{I}}\mathbf{S}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}.
 \end{equation}
-The orthogonality of internal dictionary $\mathbf{D}_{i}^{(t+1)}$ can be checked by 
-$(\mathbf{D}_{i}^{(t+1)})^{\top}(\mathbf{D}_{i}^{(t+1)})=\mathbf{V}_{i}\mathbf{U}_{i}^{\top}\mathbf{U}_{i}\mathbf{V}_{i}^{\top}=\mathbf{I}_{r}$.
+The orthogonality of internal dictionary $\mathbf{D}_{\text{I}}^{(t+1)}$ can be checked by 
+$(\mathbf{D}_{\text{I}}^{(t+1)})^{\top}(\mathbf{D}_{\text{I}}^{(t+1)})=\mathbf{V}_{\text{I}}\mathbf{U}_{\text{I}}^{\top}\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}=\mathbf{I}_{r}$.
 

### 2016-11-12 CVPR2017_Review_Unified.tex
add

@@
 \centering
-\includegraphics[width=0.85\linewidth]{Flowchart3.png}
+\includegraphics[width=0.8\linewidth]{Flowchart3.png}
 \vspace{-2mm}
@@
 \centering  
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
-{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.02dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_94b.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.77dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
-{\footnotesize (b) External: 35.58dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Offline_CC_Noisy_Nikon_D600_ISO_3200_C1_94b.png}}
+{\footnotesize (b) External: 36.97dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
-{\footnotesize (c) Internal: 36.74dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Online_CC_Noisy_Nikon_D600_ISO_3200_C1_94b.png}}
+{\footnotesize (c) Internal: 37.40dB }
 \end{minipage} 
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
-{\footnotesize (d) Guided Internal: \textbf{37.87}dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_94b.png}}
+{\footnotesize (d) Guided Internal: \textbf{38.01}dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_94b.png}}
 {\footnotesize (e) Mean Image \cite{crosschannel2016}}
@@
 \hline
-Time & | &  \textbf{39.57}  & 667.36 & 41.89
+Time & | &  \textbf{39.57}  & 587.36 & 41.89
 \\

### 2016-11-12 CVPR2017_Review_Unified.tex
add

@@
 }\vspace{-1mm}
-\caption{Denoised images of the real noisy image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
+\caption{Denoised images of a noisy image cropped from the image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \vspace{-3mm}
@@
 }\vspace{-1mm}
-\caption{Denoised images of the $96$-th cropped image from ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a noisy image cropped from the image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \vspace{-1mm}
@@
 }\vspace{-1mm}
-\caption{Denoised images of the $111$-th cropped image from ``Nikon D800 ISO 3200 A1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a noisy image cropped from the image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \vspace{-2mm}
@@
 }
-\caption{Denoised images of the image ``Dog" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of the real noisy image ``Dog" by different methods. The images are better to be zoomed in on screen.}
 \vspace{-1mm}
@@
 }\vspace{-1mm}
-\caption{Denoised images of the image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a noisy image cropped from the image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
 \vspace{-1mm}

### 2016-11-12 CVPR2017_Review_Unified.tex
add

@@
 \begin{abstract}
-Most of existing image denoising methods use some statistical models such as additive white Gaussian noise (AWGN) to model the noise, and learn image priors from either external data or the noisy image itself to remove noise.
-However, the noise in real-world noisy images is much more complex than AWGN, and it is hard to be modeled by simple analytical distributions.
-Therefore, many state-of-the-art denoising methods in literature become much less effective when applied to real noisy images.
-In this paper, we develop a robust denoiser for real noisy image denoising without explicit assumption on noise models.
-Specifically, we first learn external priors from a set of clean natural images, and then use the learned external priors to guide the learning of internal latent priors from the given noisy image.
-The proposed method is simple yet highly effective.
-Experiments on real noisy images demonstrate that it achieves much better denoising performance than state-of-the-art denoising methods, including those designed for real noisy images.
+Most of existing image denoising methods use some statistical models such as additive white Gaussian noise (AWGN) to model the noise, and learn image priors from either external data or the noisy image itself to remove noise.\ However, the noise in real-world noisy images is much more complex than AWGN, and it is hard to be modeled by simple analytical distributions.\ Therefore, many state-of-the-art denoising methods in literature become much less effective when applied to real noisy images.\ In this paper, we develop a robust denoiser for real noisy image denoising without explicit assumption on noise models.\ Specifically, we first learn external priors from a set of clean natural images, and then use the learned external priors to guide the learning of internal latent priors from the given noisy image.\ The proposed method is simple yet highly effective.\ Experiments on real noisy images demonstrate that it achieves much better denoising performance than state-of-the-art denoising methods, including those designed for real noisy images.
 \end{abstract}
@@
 
-Most of the existing denoising methods \cite{ksvd,lssc,nlm,bm3d,cbm3d,ncsr,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN).
+Most of the existing denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN).
 Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).
 According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
-As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}.
-One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.
+As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}.\ One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.
 
-There have been a few methods \cite{Liu2008,almapg,Zhu_2016_CVPR,crosschannel2016,noiseclinic,ncwebsite,neatimage} developed for real noisy image denoising.
+There have been a few methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite,neatimage} developed for real noisy image denoising.
 Almost all of these methods follow a two-stage framework: first estimate the parameters of the assumed noise model (usually Gaussian  or mixture of Gaussians (MoG)), and then perform denoising with the estimated noise model.
-Again, the noise in real noisy images is very complex and hard to be modeled by explicit distributions such as Gaussian and MoG.\ Fig.\ \ref{fig1} also shows the denoised results of two state-of-the-art real noisy image denoising methods, Noise Clinic \cite{noiseclinic,ncwebsite} and Neat Image \cite{neatimage}.
-One can see that these two methods do not perform well on this noisy image either.
+Again, the noise in real noisy images is very complex and hard to be modeled by explicit distributions such as Gaussian and MoG.\ Fig.\ \ref{fig1} also shows the denoised results of two state-of-the-art real noisy image denoising methods, Noise Clinic \cite{noiseclinic,ncwebsite} and Neat Image \cite{neatimage}.\ One can see that these two methods do not perform well on this noisy image either.
 
@@
 \end{minipage}
-}\vspace{-1mm}
+}\vspace{-2mm}
 \caption{Denoised images of a noisy image cropped from the image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
@@
 
-This work aims to develop a robust solution for real noisy image denoising without explicitly assuming certain noise models.
-To achieve this goal, we propose to first learn image priors from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image.
-The flowchart of the proposed method is illustrated in\ Fig.\ \ref{fig2}.
-We first extract millions of patch groups from a set of high quality natural images, with which a Gaussian Mixture Model (GMM) is learned as the external prior.
-The learned GMM prior model is used to cluster the patch groups extracted from the given noisy image, and then a hybrid orthogonal dictionary (HOD) is learned as the internal prior for image denoising.
+This work aims to develop a robust solution for real noisy image denoising without explicitly assuming certain noise models.\ To achieve this goal, we propose to first learn image priors from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image.\ The flowchart of the proposed method is illustrated in\ Fig.\ \ref{fig2}.\ We first extract millions of patch groups from a set of high quality natural images, with which a Gaussian Mixture Model (GMM) is learned as the external prior.\ The learned GMM prior model is used to cluster the patch groups extracted from the given noisy image, and then a hybrid orthogonal dictionary (HOD) is learned as the internal prior for image denoising.
 Our proposed denoising method is simple and efficient, yet our extensive experiments on real noisy images clearly demonstrate its better denoising performance than the current state-of-the-arts.
@@
 
+\vspace{-1mm}
 \subsection{Internal \textbf{\emph{vs.}} External Prior Learning}
 
-Image priors are playing a key role in image denoising \cite{pgpd,epll,ksvd,ple,ncsr,iraniinternal}.
-There are mainly two categories of prior learning methods.
-1) External prior learning methods \cite{foe,pgpd,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images.
-2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and the image denoising is often done simultaneously with the prior learning process.
-It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.
-By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.
-In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images.
-In this paper, we use external priors to guide the internal prior learning.
-Our method is not only much faster than the traditional internal learning methods, but also very effective to denoise real noisy images.
+Image priors are playing a key role in image denoising \cite{pgpd,epll,ksvd,ple,ncsr,iraniinternal}.\ There are mainly two categories of prior learning methods.\ 1) External prior learning methods \cite{foe,pgpd,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images.\ 2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and the image denoising is often done simultaneously with the prior learning process.\ It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.\ By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.\ In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images.
+In this paper, we use external priors to guide the internal prior learning.\ Our method is not only much faster than the traditional internal learning methods, but also very effective to denoise real noisy images.
 
+\vspace{-1mm}
 \subsection{Real Noisy Image Denoising}
 
-Recently, several denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} are proposed to remove unknown noise in noisy images.
-These methods can be directly applied to denoise real noisy images.
-Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimated the noise by a multivariate Gaussian and remove the noise by a generalized version of nonlocal Bayesian model \cite{nlbayes}.
-Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank MoG model.
-There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.
-The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.
-The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.
-Almost all these methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} use Gaussian or mixture of Gaussians (MoG) to model the noise in real noisy images.
-However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
+Recently, several image denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} are proposed to remove unknown noise.\ These methods can be directly applied to denoise real noisy images.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimated the noise by a multivariate Gaussian and remove the noise by a generalized version of nonlocal Bayesian model \cite{nlbayes}.
+Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank MoG model.\ There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.\ Almost all these methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} use Gaussian or mixture of Gaussians (MoG) to model the noise in real noisy images.\ However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
 
@@
 
-In our method, each local patch is extracted from a RGB image with patch size $p\times p \times 3$.
-We search the $M$ most similar patches to this local patch (including the local patch itself) in a $W\times W$ local region around it.
+In our method, each local patch is extracted from a RGB image with patch size $p\times p \times 3$.\ We search the $M$ most similar patches to this local patch (including the local patch itself) in a $W\times W$ local region around it.
 Each patch is stretched to a patch vector $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ to form the PG $\{\mathbf{x}_{m}\}_{m=1}^{M}$.
@@
 
-Assume we extract a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.
-A Gaussian Mixture Model (GMM) is learned to model the PG prior.
+Assume we extract a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.\ A Gaussian Mixture Model (GMM) is learned to model the PG prior.
 The overall log-likelihood function is
@@
 
-After the external PG prior is learned, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ One is that the external prior can guide the subspace assignment of internal noisy PGs, while the other is that the external prior could guide the orthogonal dictionary learning of internal noisy PGs.
+After the external PG prior is learned, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ One is that the external prior can guide the subspace assignment of internal noisy PGs, while the other is that the external prior can guide the orthogonal dictionary learning of internal noisy PGs.
 
@@
 \textbf{Updating Sparse Coefficient}: Given the orthogonal dictionary $\textbf{D}^{(t)}$, we update each sparse coding vector $\bm{\alpha}_{n,m}$ by solving
-\vspace{-3mm}
-\begin{equation}\label{equ7}\vspace{-3mm}
+\vspace{-4mm}
+\begin{equation}\label{equ7}\vspace{-4mm}
 \begin{split}
@@
 
-\vspace{-1mm}
 \subsection{The Testing Datasets}\vspace{-1mm}
@@
 
-\vspace{-1mm}
 \subsection{Comparison among external, internal and guided internal priors}
@@
 
-\vspace{-1mm}
 \subsection{Comparison with State-of-the-Art Denoising Methods}
@@
 
+\vspace{-1mm}
 \subsubsection{Comparison on Dataset \cite{crosschannel2016}}
@@
 \end{tabular}
-\end{center}\vspace{-8mm}
+\end{center}\vspace{-6mm}
 \end{table}

### 2016-11-12 CVPR2017_Review_Unified.tex
add

@@
 
-Assume we extract a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.\ A Gaussian Mixture Model (GMM) is learned to model the PG prior.
-The overall log-likelihood function is
+Assume we extract a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.\ A Gaussian Mixture Model (GMM) is learned to model the PG prior.\ The overall log-likelihood function is
 \vspace{-2mm}
@@
 \end{equation}
-The learning process is similar to the GMM learning in \cite{pgpd,epll}.
-Finally, a GMM model with $K$ Gaussian components is learned, and the learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.
-Note that the mean vector of each cluster is naturally zero, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
+The learning process is similar to the GMM learning in \cite{pgpd,epll}.\ Finally, a GMM model with $K$ Gaussian components is learned, and the learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.\ Note that the mean vector of each cluster is naturally zero, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
 
@@
 \end{equation}
-The eigenvector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ will be employed as the external orthogonal dictionary to guide the internal dictionary learning in next sub-section.
-The singular values in $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$.
-They  will also be utilized as prior weights for weighted sparse coding in our denoising algorithm.
+The eigenvector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ will be employed as the external orthogonal dictionary to guide the internal dictionary learning in next sub-section.\ The singular values in $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$.\ They  will also be utilized as prior weights for weighted sparse coding in our denoising algorithm.
 
@@
 
-After the external PG prior is learned, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ One is that the external prior can guide the subspace assignment of internal noisy PGs, while the other is that the external prior can guide the orthogonal dictionary learning of internal noisy PGs.
+After the external PG prior is learned, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ One is that the external prior can guide the subspace assignment of internal noisy PGs, while the other is that the external prior could guide the orthogonal dictionary learning of internal noisy PGs.
 
@@
 
-Given a real noisy image, we extract $N$ (overlapped) local patches from it.
-Similar to the external prior learning stage, for the $n$-th local patch we search its $M$ most similar patches around it to form a noisy PG, denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.
-Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is subtracted from each patch by $\mathbf{\overline{y}}_{n,m}=\mathbf{y}_{n,m}-\bm{\mu}_{n}$, leading to the mean subtracted noisy PG $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$.
+Given a real noisy image $\mathbf{y}$, we extract $N$ (overlapped) local patches from it.\ Similar to the external prior learning stage, for the $n$-th local patch we search its $M$ most similar patches around it to form a noisy PG, denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.\ Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is subtracted from each patch by $\mathbf{\overline{y}}_{n,m}=\mathbf{y}_{n,m}-\bm{\mu}_{n}$, leading to the mean subtracted noisy PG $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$.
 
@@
 Assume we have assigned all the internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
-For the $k$-th subspace, the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ where $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.
-We propose to learn an orthogonal dictionary $\mathbf{D}_{k}$ from each set of PGs $\mathbf{\overline{Y}}_{k_{n}}$ with the guidance of the corresponding external orthogonal dictionary $\mathbf{U}_{k}$ (Eq.\ (\ref{equ2})) to characterize the internal PG prior.
-The reasons that we learn orthogonal dictionaries are two-fold.
-Firstly, the PGs $\mathbf{\overline{Y}}_{k_{n}}$ are in a subspace of the whole space of all PGs, therefore, there is no necessary to learn a redundant over-complete dictionary to characterize it, while an orthonormal dictionary has naturally zero \emph{mutual incoherence} \cite{donoho2001uncertainty}.
+For the $k$-th subspace, the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ where $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.\ We propose to learn an orthogonal dictionary $\mathbf{D}_{k}$ from each set of PGs $\mathbf{\overline{Y}}_{k_{n}}$ to characterize the internal PG prior with the guidance of the corresponding external orthogonal dictionary $\mathbf{U}_{k}$ (Eq.\ (\ref{equ2})).
+The reasons that we learn orthogonal dictionaries are two-fold.\ Firstly, the PGs $\mathbf{\overline{Y}}_{k_{n}}$ are in a subspace of the whole space of all PGs, therefore, there is no necessary to learn a redundant over-complete dictionary to characterize it, while an orthonormal dictionary has naturally zero \emph{mutual incoherence} \cite{donoho2001uncertainty}.
 Secondly, the orthogonality of dictionary can make the encoding in the testing stage very efficient, leading to an efficient denoising algorithm (please refer to sub-section 3.3 for details).
 
-We let the orthogonal dictionary $\mathbf{D}_{k}$ be $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,\text{E}}\ \mathbf{D}_{k,\text{I}}]\in \mathbb{R}^{3p^2\times 3p^2}$, where $\mathbf{D}_{k,\text{E}}=\mathbf{U}_{k}(:,1:r)\in\mathbb{R}^{3p^2\times r}$ is the external sub-dictionary and it includes the first $r$ most important eigenvectors of $\mathbf{U}_{k}$, and the internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ is to be adaptively learned from the noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.
-The rationale to design $\mathbf{D}_{k}$ as a hybrid dictionary is as follows.
-The external sub-dictionary $\mathbf{D}_{k,\text{E}}$ is pre-trained from external clean data, and it represents the $k$-th latent subspace of natural images, which is helpful to reconstruct the common latent structures of images.
-However, $\mathbf{D}_{k,\text{E}}$ is general to all images and it is not adaptive to the given noisy image.
-Some fine-scale details specific to the given image may not be well characterized by $\mathbf{D}_{k,\text{E}}$.
-Therefore, we learn an internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ to supplement $\mathbf{D}_{k,\text{E}}$.
-In other words, $\mathbf{D}_{k,\text{I}}$ is to reveal the latent subspace adaptive to the input noisy image, which cannot be effectively represented by $\mathbf{D}_{k,\text{E}}$.
+We let the orthogonal dictionary $\mathbf{D}_{k}$ be $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,\text{E}}\ \mathbf{D}_{k,\text{I}}]\in \mathbb{R}^{3p^2\times 3p^2}$, where $\mathbf{D}_{k,\text{E}}=\mathbf{U}_{k}(:,1:r)\in\mathbb{R}^{3p^2\times r}$ is the external sub-dictionary and it includes the first $r$ most important eigenvectors of $\mathbf{U}_{k}$, and the internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ is to be adaptively learned from the noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.\ The rationale to design $\mathbf{D}_{k}$ as a hybrid dictionary is as follows.\ The external sub-dictionary $\mathbf{D}_{k,\text{E}}$ is pre-trained from external clean data, and it represents the $k$-th latent subspace of natural images, which is helpful to reconstruct the common latent structures of images.
+However, $\mathbf{D}_{k,\text{E}}$ is general to all images and it is not adaptive to the given noisy image.\ Some fine-scale details specific to the given image may not be well characterized by $\mathbf{D}_{k,\text{E}}$.
+Therefore, we learn an internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ to supplement $\mathbf{D}_{k,\text{E}}$.\ In other words, $\mathbf{D}_{k,\text{I}}$ is to reveal the latent subspace adaptive to the input noisy image, which cannot be effectively represented by $\mathbf{D}_{k,\text{E}}$.
 
-For notation simplicity, in the following development we ignore the subspace index $k$ for $\mathbf{\overline{Y}}_{k_{n}}$ and $\mathbf{D}_{k}$, etc.
-The learning of hybrid orthogonal dictionary $\mathbf{D}$ is performed under the following weighted sparse coding
+For notation simplicity, in the following development we ignore the subspace index $k$ for $\mathbf{\overline{Y}}_{k_{n}}$ and $\mathbf{D}_{k}$, etc.\ The learning of hybrid orthogonal dictionary $\mathbf{D}$ is performed under the following weighted sparse coding
 framework:
@@
 \begin{split}
-&\min_{\mathbf{D}_{i},\{\bm{\alpha}_{n,m}\}}
+&\min_{\mathbf{D}_{\text{I}},\{\bm{\alpha}_{n,m}\}}
 \sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|)
@@
 \end{equation}
-where $\mathbf{S}_{k}(j)$ is the $j$-th singular value of diagonal singular value matrix $\mathbf{S}_{k}$ (please refer to Eq.
-(\ref{equ2})) and $\varepsilon$ is a small positive number to avoid zero denominator.
-Noted that $\mathbf{D}_{\text{E}}=\mathbf{U}_{k}$ if $r=3p^{2}$ and $\mathbf{D}_{\text{E}}=\emptyset$ if $r=0$.
-The dictionary $\mathbf{D} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}]$ is orthogonal by checking that:
+where $\mathbf{S}_{k}(j)$ is the $j$-th singular value of diagonal singular value matrix $\mathbf{S}_{k}$ (please refer to Eq.\ (\ref{equ2})) and $\varepsilon$ is a small positive number to avoid zero denominator.\ Noted that $\mathbf{D}_{\text{E}}=\mathbf{U}_{k}$ if $r=3p^{2}$ and $\mathbf{D}_{\text{E}}=\emptyset$ if $r=0$.\ The dictionary $\mathbf{D} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}]$ is orthogonal by checking that:
 \vspace{-2mm}
@@
 \vspace{2mm}\\
-\textbf{Updating Internal Sub-dictionary}: Given the sparse coding vectors $\bm{\alpha}_{n,m}^{(t)}$, we update the internal sub-dictionary by solving
+\textbf{Updating Internal Sub-dictionary}: Given the sparse coding vectors $\{\bm{\alpha}_{n,m}^{(t)}\}$, we update the internal sub-dictionary by solving
 \vspace{-2mm}
@@
 where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$.
-The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{r\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.
+The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.
 According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
@@
 
-The denoising of the given noisy image can be simultaneously done with the guided internal dictionary learning process.
-Once we obtain the solutions of sparse coding vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.\ (\ref{equ8}) and the orthogonal dictionary $\mathbf{D}_{(T)} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{(T)}]$ in Eq.
+The denoising of the given noisy image $\mathbf{y}$ can be simultaneously done with the guided internal dictionary learning process.
+Once we obtain the solutions of sparse coding vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.\ (\ref{equ8}) and the orthogonal dictionary $\mathbf{D}^{(T)} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{(T)}]$ in Eq.
 (\ref{equ9}), the latent clean patch of a noisy patch $\hat{\mathbf{y}}_{n,m}$ in PG $\mathbf{Y}_{n}$ is reconstructed as
@@
 \begin{equation}\label{equ11}\vspace{-2mm}
-\hat{\mathbf{y}}_{n,m}=\mathbf{D}_{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
+\hat{\mathbf{y}}_{n,m}=\mathbf{D}^{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
 \end{equation}
 where $\bm{\mu}_{n}$ is the group mean of $\mathbf{Y}_{n}$.
-The latent clean image is then reconstructed by aggregating all the reconstructed patches in all PGs.
-We perform the above denoising procedures for several iterations for better denoising outputs.
-The proposed denoising algorithm is summarized in Alg.
+The latent clean image is then reconstructed by aggregating all the reconstructed patches in all PGs.\ We perform the above denoising procedures for several iterations for better denoising outputs.\ The proposed denoising algorithm is summarized in Alg.
 1.
@@
 \\
-%\textbf{Guided Internal Subspace Selection:}
+%\textbf{Guided Internal Subspace Assignment:}
 %\\
@@
 \\
-2.\quad Calculate group mean vector $\boldsymbol{\upmu}_{n}$ and form 
+2.\quad Calculate group mean vector $\bm{\mu}_{n}$ and form 
 \\
@@
 \\
-3.\quad Subspace selection via Eq. (\ref{equ3});
+3.\quad Subspace assignment via Eq. (\ref{equ3});
 \\

### 2016-11-12 CVPR2017_Review_Unified.tex
add

@@
 
-Our proposed method has two stages: the external prior learning stage and the external prior guided internal prior learning stage.
-In the first stage, we set $p = 6$ (the patch size), $M = 10$ (the number of similar patches in a PG), $W = 31$ (the window size for PG searching) and $K = 32$ (the number of Gaussian components in GMM.
-We learn the external GMM prior with 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
+Our proposed method has two stages: the external prior learning stage and the external prior guided internal prior learning stage.\ In the first stage, we set $p = 6$ (the patch size), $M = 10$ (the number of similar patches in a PG), $W = 31$ (the window size for PG searching) and $K = 32$ (the number of Gaussian components in GMM.\ We learn the external GMM prior with 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
 
@@
 
-The first dataset is provided in \cite{ncwebsite}, which includes 20 real noisy images collected under uncontrolled outdoor environment.
-Since there is no ``ground truth" of the noisy images, the objective measures such as PSNR cannot be computed on this dataset.
+The first dataset is provided in \cite{ncwebsite}, which includes 20 real noisy images collected under uncontrolled outdoor environment.\ Since there is no ``ground truth" of the noisy images, the objective measures such as PSNR cannot be computed on this dataset.
 
-The second dataset is provided in \cite{crosschannel2016}, which includes noisy images of 17 static scenes.
-The noisy images were collected under controlled indoor environment.
-Each scene was shot 500 times under the same camera and camera setting.
-The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.
-Since the image size is very large (about $7000\times5000$) and the 17 scenes share repetitive contents, the authors of \cite{crosschannel2016} cropped 15 smaller images (of size $512\times512$) to perform experiments.
-To more comprehensively evaluate the proposed methods, we cropped 60 images of size $500\times500$ from the dataset for experiments.
-Some samples are shown in Fig.
-\ref{fig3}.
-Note that the noise in our cropped 60 images is different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are from different shots.
+The second dataset is provided in \cite{crosschannel2016}, which includes noisy images of 17 static scenes.\ The noisy images were collected under controlled indoor environment.\ Each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.
+Since the image size is very large (about $7000\times5000$) and the 17 scenes share repetitive contents, the authors of \cite{crosschannel2016} cropped 15 smaller images (of size $512\times512$) to perform experiments.\ To more comprehensively evaluate the proposed methods, we cropped 60 images of size $500\times500$ from the dataset for experiments.
+Some samples are shown in Fig.\ \ref{fig3}.\ Note that the noise in our cropped 60 images is different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are from different shots.
 

### 2016-11-12 CVPR2017_Review_Unified.tex
ADD

@@
 According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
-As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}.\ One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.
+As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TNRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}.\ One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.
 
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (f) TRD \cite{chen2015learning}: 35.97dB   }
+{\footnotesize (f) TNRD \cite{chen2015learning}: 35.97dB   }
 \end{minipage}
@@
 \centering
-\includegraphics[width=0.8\linewidth]{Flowchart3.png}
-\vspace{-2mm}
+\includegraphics[width=0.79\linewidth]{Flowchart3.png}
+\vspace{-1.5mm}
 \caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
@@
 
-To demonstrate the advantages of external prior guided internal priors, in this section we perform real noisy image denoising by using external priors (denoted by ``External"), internal priors (denoted by ``Internal"), and the proposed guided internal priors (denoted by ``Guided Internal"), respectively.
-For the ``External" method, we utilize the full external dictionaries (i.e., $r=108$ in Eq.
-(\ref{equ4})) for denoising.
-For the ``Internal" method, the overall framework is similar to the method of \cite{ncsr}.
-A GMM model (with $K = 32$ Gaussians) is directly learned from the PGs extracted from the given noisy image without using any external data, and then the internal orthogonal dictionary is obtained via Eqn.
-(\ref{equ2}) to perform denoising.
-All parameters of the ``External" and ``Internal" methods are tuned to achieve their best performance.
+To demonstrate the advantages of external prior guided internal priors, in this section we perform real noisy image denoising by using external priors (denoted by ``External"), internal priors (denoted by ``Internal"), and the proposed guided internal priors (denoted by ``Guided Internal"), respectively.\ For the ``External" method, we utilize the full external dictionaries (i.e., $r=108$ in Eq.\ (\ref{equ4})) for denoising.\ For the ``Internal" method, the overall framework is similar to the method of \cite{ncsr}.\ A GMM model (with $K = 32$ Gaussians) is directly learned from the PGs extracted from the given noisy image without using any external data, and then the internal orthogonal dictionary is obtained via Eq.\ (\ref{equ2}) to perform denoising.\ All parameters of the ``External" and ``Internal" methods are tuned to achieve their best performance.
 
-We compare the three methods mentioned above on the 60 cropped images from \cite{crosschannel2016}.
-The average PSNR and run time  are listed in Table \ref{tab1}.
+We compare the three methods mentioned above on the 60 cropped images from \cite{crosschannel2016}.\ The average PSNR and run time  are listed in Table \ref{tab1}.
 It can be seen that ``Guided Internal" prior achieves better PSNR than both ``External" and ``Internal" priors.
-In addition, the ``Internal" method is very slow because it involves online GMM learning, while the ``Guided Internal" method is only a little slower than the ``External" method.
-Fig.
-\ref{fig4} and Fig.
-\ref{fig5} show the denoised images of two noisy image by the three methods.
-We can see that the ``External" method is good at recovering large-scale structures (see Fig.
-\ref{fig4}) while the ``Internal" method is good at recovering fine-scale textures (see Fig.
-\ref{fig5}).
-By utilizing external priors to guide the internal prior learning, our proposed method can effectively recover both the large-scale structures and fine-scale textures.
+In addition, the ``Internal" method is very slow because it involves online GMM learning, while the ``Guided Internal" method is only a little slower than the ``External" method.\ Fig.\ \ref{fig4} and Fig.\ \ref{fig5} show the denoised images of two noisy image by the three methods.\ We can see that the ``External" method is good at recovering large-scale structures (see Fig.\ \ref{fig4}) while the ``Internal" method is good at recovering fine-scale textures (see Fig.\ \ref{fig5}).\ By utilizing external priors to guide the internal prior learning, our proposed method can effectively recover both the large-scale structures and fine-scale textures.
 
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_dog.png}}
-{\footnotesize (e) TRD \cite{chen2015learning}}
+{\footnotesize (e) TNRD \cite{chen2015learning}}
 \end{minipage}
@@
 
-We compare the proposed method with state-of-the-art image denoising methods, including CBM3D \cite{bm3d,cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}.
-Among them, CBM3D, WNNM, MLP, CSF and TNRD are designed based on Gaussian noise model, and they need to know the noise level for denoising.
-We use the method in \cite{noiselevel} to estimate the noise level for them.
-All the other parameters in these methods are set as the default ones.
-Since WNNM, MLP, CSF and TNRD are designed for grayscale images, we use them to denoise the R, G, B channels separately for color noisy images.
+We compare the proposed method with state-of-the-art image denoising methods, including CBM3D \cite{bm3d,cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}.\ Among them, CBM3D, WNNM, MLP, CSF and TNRD are designed based on Gaussian noise model, and they need to know the noise level for denoising.\ We use the method in \cite{noiselevel} to estimate the noise level for them.\ All the other parameters in these methods are set as the default ones.\ Since WNNM, MLP, CSF and TNRD are designed for grayscale images, we use them to denoise the R, G, B channels separately for color noisy images.
 
-Like our method, the NC is a blind image denoising method which does not need any noise prior.
-The NI is a commercial software for image denoising, which has been embedded into Photoshop and Corel PaintShop \cite{neatimage}.
+Like our method, the NC is a blind image denoising method which does not need any noise prior.\ The NI is a commercial software for image denoising, which has been embedded into Photoshop and Corel PaintShop \cite{neatimage}.
 The code of CC is not released but its results on the 15 cropped images are available at \cite{crosschannel2016}.
@@
 \hline
-Methods& \textbf{TRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
+Methods& \textbf{TNRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
 \\
@@
 \hline
-Camera Settings & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Ours} 
+Camera Settings & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TNRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Ours} 
 \\
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
-{\footnotesize (e) TRD \cite{chen2015learning}: 36.18dB  } 
+{\footnotesize (e) TNRD \cite{chen2015learning}: 36.18dB  } 
 \end{minipage}

### 2016-11-12 CVPR2017_Review_Unified.tex
add

@@
 }\vspace{-2mm}
-\caption{Denoised images of a noisy image cropped from the image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
+\caption{Denoised images of a part cropped from the real noisy image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
 \vspace{-3mm}
@@
 }\vspace{-1mm}
-\caption{Denoised images of a noisy image cropped from the image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a part cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \vspace{-1mm}
@@
 }\vspace{-1mm}
-\caption{Denoised images of a noisy image cropped from the image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a part cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \vspace{-2mm}
@@
 \begin{table}
-\caption{Average PSNR (dB) results and Run Time (seconds) of the External, the Internal, and our proposed methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
+\caption{Average PSNR (dB) results and Run Time (seconds) of the ``External", the ``Internal", and the ``Guided Internal" methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
 \label{tab1}
@@
 Since there is no ``ground truth" for the real noisy images in  dataset \cite{ncwebsite}, we only compare the visual quality of the denoised images by different methods.
-(Note that method CC \cite{crosschannel2016} is not compared since its code is not available.) Fig.
-\ref{fig6} shows the denoised images of ``Dog".
-It can be seen that CBM3D and WNNM tend to over-smooth much the image while remaining some noise caused color artifacts.
-MLP and TNRD are likely to remain many noise-caused color artifacts across the whole image.
-These results demonstrate that the methods designed with Gaussian noise model are not effective for real noise removal.
-Though NC and NI methods are specifically developed for real noisy images, their performance on noise removal is not very satisfactory.
+(Note that method CC \cite{crosschannel2016} is not compared since its code is not available.) Fig.\ \ref{fig6} shows the denoised images of ``Dog".
+It can be seen that CBM3D and WNNM tend to over-smooth much the image while remaining some noise caused color artifacts.\ MLP and TNRD are likely to remain many noise-caused color artifacts across the whole image.
+These results demonstrate that the methods designed with Gaussian noise model are not effective for real noise removal.\ Though NC and NI methods are specifically developed for real noisy images, their performance on noise removal is not very satisfactory.
 In comparison, our proposed method recovers much better the structures and textures (such as the eye area) than the other competing methods.
@@
 (The results of CC are copied from the original paper \cite{crosschannel2016}.) The best PSNR result of each image is highlighted in bold.
-One can see that on 9 out of the 15 images, our method achieves the best PSNR values.
-CC achieves the best PSNR on 3 of the 15 images.
-It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images.
-On average, our proposed method has 0.28dB PSNR improvements over \cite{crosschannel2016} and much higher PSNR gains over other competing methods.
-Fig.
-\ref{fig7} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.
-We can see that CBM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image.
-By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs.
-More visual comparisons can be found in the supplementary file.
+One can see that on 9 out of the 15 images, our method achieves the best PSNR values.\ CC achieves the best PSNR on 3 of the 15 images.\ It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images.\ On average, our proposed method has 0.28dB PSNR improvements over \cite{crosschannel2016} and much higher PSNR gains over other competing methods.\ Fig.\ \ref{fig7} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.\ We can see that CBM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image.\ By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs.\ More visual comparisons can be found in the supplementary file.
 
@@
 The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available).
-Again, our proposed method achieves much better PSNR results than the other methods.
-The improvement of our method over the second best method (TNRD) is about 1dB.
+Again, our proposed method achieves much better PSNR results than the other methods.\ The improvement of our method over the second best method (TNRD) is about 1dB.
 Due to the space limitations, the visual comparisons are provided in the supplementary file.
@@
 }\vspace{-1mm}
-\caption{Denoised images of a noisy image cropped from the image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a part cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
 \vspace{-1mm}
-\label{fig6}
+\label{fig7}
 \end{figure*}
@@
 
-The noise in real-world noisy images is much more complex than additive white Gaussian noise and hard to be modeled by simple analytical distributions such as Gaussian or mixture of Gaussians.
-In this paper, we proposed a simple yet effective solution for real noisy image denoising without explicitly assuming certain noise models.
-Specifically, we firstly learned image priors of Gausian Mixture Model from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image.
-The learned hybrid orthogonal dictionary are simutaneously utilized in real noisy image denoising.
-Experiments on two real noisy image datasets, where the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings, demonstrate that our proposed method achieved much better performance than state-of-the-art image denoising methods.
+The noise in real-world noisy images is much more complex than additive white Gaussian noise and hard to be modeled by simple analytical distributions such as Gaussian or mixture of Gaussians.\ In this paper, we proposed a simple yet effective solution for real noisy image denoising without explicitly assuming certain noise models.\ Specifically, we firstly learned image priors of Gausian Mixture Model from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image.\ The learned hybrid orthogonal dictionary are simutaneously utilized in real noisy image denoising.\ Experiments on two real noisy image datasets, where the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings, demonstrate that our proposed method achieved much better performance than state-of-the-art image denoising methods.
 

### 2016-11-12 CVPR2017_Review_Unified.tex
add

@@
 Each patch is stretched to a patch vector $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ to form the PG $\{\mathbf{x}_{m}\}_{m=1}^{M}$.
-The mean vector of this PG is $\boldsymbol{\upmu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\boldsymbol{\upmu}\}$.
+The mean vector of this PG is $\bm{\mu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\bm{\mu}\}$.
 
@@
 \begin{split}
-\ln\mathcal{L}=\sum_{n=1}^{N} \ln(\sum_{k=1}^{K}\pi_{k}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\boldsymbol{\upmu}_{k},\mathbf{\Sigma}_{k})).
+\ln\mathcal{L}=\sum_{n=1}^{N} \ln(\sum_{k=1}^{K}\pi_{k}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{x}}_{n,m}|\bm{\mu}_{k},\mathbf{\Sigma}_{k})).
 \end{split}
 \end{equation}
-The learning process is similar to the GMM learning in \cite{pgpd,epll}.\ Finally, a GMM model with $K$ Gaussian components is learned, and the learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\boldsymbol{\upmu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.\ Note that the mean vector of each cluster is naturally zero, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
+The learning process is similar to the GMM learning in \cite{pgpd,epll}.\ Finally, a GMM model with $K$ Gaussian components is learned, and the learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\bm{\mu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.\ Note that the mean vector of each cluster is naturally zero, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
 
@@
 
-\vspace{-1mm}
+\vspace{-2mm}
 \subsubsection{Comparison on Dataset \cite{crosschannel2016}}

### 2016-11-12 CVPR2017_Review_Unified.tex
a
add

@@
 Most of the existing denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN).
-Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).
-According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
-As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TNRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}.\ One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.
+Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).\ According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
+As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TNRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}.
+One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.
 
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (b) BM3D \cite{bm3d,cbm3d}: 33.33dB  }
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.33dB  }
 \end{minipage}
@@
 \end{minipage}
-}\vspace{-2mm}
-\caption{Denoised images of a part cropped from the real noisy image ``Nikon D800 ISO 3200 A3" from \cite{crosschannel2016} by different methods.
-The images are better viewed by zooming in on screen.}
+}\vspace{-1mm}
+\caption{Denoised images of a cropped part from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \vspace{-3mm}
@@
 
-\begin{figure*}\vspace{-0.1in}
+\begin{figure*}\vspace{-2mm}
 \centering
-\includegraphics[width=0.79\linewidth]{Flowchart3.png}
-\vspace{-1.5mm}
+\includegraphics[width=0.79\linewidth]{Flowchart.pdf}
+\vspace{-28mm}
 \caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
 }
-\vspace{-3mm}
+\vspace{-2mm}
 \label{fig2}
@@
 Recently, several image denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} are proposed to remove unknown noise.\ These methods can be directly applied to denoise real noisy images.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimated the noise by a multivariate Gaussian and remove the noise by a generalized version of nonlocal Bayesian model \cite{nlbayes}.
-Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank MoG model.\ There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.\ Almost all these methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} use Gaussian or mixture of Gaussians (MoG) to model the noise in real noisy images.\ However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
+Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.\ Almost all these methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} use Gaussian or MoG to model the noise in real noisy images.\ However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
 
@@
 \end{equation}
-The learning process is similar to the GMM learning in \cite{pgpd,epll}.\ Finally, a GMM model with $K$ Gaussian components is learned, and the learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\bm{\mu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.\ Note that the mean vector of each cluster is naturally zero, i.e., $\boldsymbol{\upmu}_{k}=\mathbf{0}$.
+The learning process is similar to the GMM learning in \cite{pgpd,epll}.\ Finally, a GMM model with $K$ Gaussian components is learned, and the learned parameters include mixture weights $\{\pi_{k}\}_{k=1}^{K}$, mean vectors $\{\bm{\mu}_{k}\}_{k=1}^{K}$, and covariance matrices $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$.\ Note that the mean vector of each cluster is naturally zero, i.e., $\bm{\mu}_{k}=\mathbf{0}$.
 
@@
 
-After the external PG prior is learned, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ One is that the external prior can guide the subspace assignment of internal noisy PGs, while the other is that the external prior could guide the orthogonal dictionary learning of internal noisy PGs.
+After the external PG prior is learned, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ One is that the external prior can guide the subspace assignments of internal noisy PGs, while the other is that the external prior could guide the orthogonal dictionary learning of internal noisy PGs.
 
@@
 
-The external GMM prior models $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$ basically characterize the subspaces of natural high quality PGs.
-Therefore, we project the noisy PG $\mathbf{\overline{Y}}_{n}$ into the subspaces of $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$ and assign it to the most suitable subspace based on the posterior probability:
+The external GMM prior models $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$ basically characterize the subspaces of natural high quality PGs.\ Therefore, we project the noisy PG $\mathbf{\overline{Y}}_{n}$ into the subspaces of $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$ and assign it to the most suitable subspace based on the posterior probability:
 \vspace{-2mm}
@@
 \caption{Some samples cropped from real noisy images of \cite{crosschannel2016}.}
-\vspace{-3mm}
 \label{fig3}
+\vspace{-2mm}
 \end{figure}
@@
 \end{minipage}
-}\vspace{-1mm}
-\caption{Denoised images of a part cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+}
+\vspace{-2mm}
+\caption{Denoised images of a cropped part from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The 
+\vspace{-0.5mm}
+images are better to be zoomed in on screen.}
 \vspace{-1mm}
@@
 \end{minipage}
-}\vspace{-1mm}
-\caption{Denoised images of a part cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+}
 \vspace{-2mm}
+\caption{Denoised images of a cropped part from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The 
+\vspace{-0.5mm}
+images are better to be zoomed in on screen.}
+\vspace{-1mm}
 \label{fig5}
@@
 In addition, the ``Internal" method is very slow because it involves online GMM learning, while the ``Guided Internal" method is only a little slower than the ``External" method.\ Fig.\ \ref{fig4} and Fig.\ \ref{fig5} show the denoised images of two noisy image by the three methods.\ We can see that the ``External" method is good at recovering large-scale structures (see Fig.\ \ref{fig4}) while the ``Internal" method is good at recovering fine-scale textures (see Fig.\ \ref{fig5}).\ By utilizing external priors to guide the internal prior learning, our proposed method can effectively recover both the large-scale structures and fine-scale textures.
-
-\begin{table}
-\caption{Average PSNR (dB) results and Run Time (seconds) of the ``External", the ``Internal", and the ``Guided Internal" methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
-\label{tab1}
-\begin{small}
-\vspace{-1mm}
-\begin{center}
-\renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|}
-\hline
- & \textbf{Noisy} & \textbf{External} & \textbf{Internal} & \textbf{Guided Internal}  
-\\
-\hline
-PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
-\\
-\hline
-Time & | &  \textbf{39.57}  & 587.36 & 41.89
-\\
-\hline
-\end{tabular}
-\end{center}\vspace{-4mm}
-\end{small}
-\end{table}
 
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_BM3D_dog.png}}
-{\footnotesize (b) BM3D \cite{bm3d,cbm3d}  }
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
 \end{minipage}
@@
 }
-\caption{Denoised images of the real noisy image ``Dog" by different methods. The images are better to be zoomed in on screen.}
+\vspace{-3mm}
+\caption{Denoised images of the real noisy image ``Dog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
 \vspace{-1mm}
@@
 Therefore, we only compare with it on the 15 cropped images from \cite{crosschannel2016}.
+
+\begin{table}
+\caption{Average PSNR (dB) results and Run Time (seconds) of the ``External", the ``Internal", and the ``Guided Internal" methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
+\label{tab1}
+\begin{small}
+\vspace{-3mm}
+\begin{center}
+\renewcommand\arraystretch{1}
+\begin{tabular}{|c||c|c|c|c|}
+\hline
+ & \textbf{Noisy} & \textbf{External} & \textbf{Internal} & \textbf{Guided Internal}  
+\\
+\hline
+PSNR & 34.51 & 38.21 & 38.07 & \textbf{38.75} 
+\\
+\hline
+Time & | &  \textbf{39.57}  & 587.36 & 41.89
+\\
+\hline
+\end{tabular}
+\end{center}\vspace{-4mm}
+\end{small}
+\end{table}
 
@@
 \caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
-\vspace{-1mm}
+\vspace{-3mm}
 \label{tab3}
@@
 \hline
- Methods& \textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
+ Methods& \textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
 \\
@@
 \hline
-Camera Settings & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TNRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Ours} 
+Camera Settings & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}&\textbf{TNRD}& \textbf{NI}& \textbf{NC}& \textbf{CC} &\textbf{Ours} 
 \\
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
-{\footnotesize (b) BM3D \cite{bm3d,cbm3d}: 37.02dB}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 37.02dB}
 \end{minipage}
@@
 }\vspace{-1mm}
-\caption{Denoised images of a part cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a part cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images 
+\vspace{-0.5mm}
+are better to be zoomed in on screen.}
 \vspace{-1mm}

### 2016-11-12 CVPR2017_Review_Unified.tex
add

@@
 In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise.
-Numerous image denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc,ncsr}, nonlocal self-similarity based methods \cite{nlm,bm3d,cbm3d,ncsr,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.
+Numerous image denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc,ncsr}, nonlocal self-similarity based methods \cite{ncsr,nlm,bm3d,cbm3d,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.
 
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (g) NC \cite{noiseclinic}: 35.33dB  }
+{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}: 35.33dB  }
 \end{minipage}
@@
 
-Image priors are playing a key role in image denoising \cite{pgpd,epll,ksvd,ple,ncsr,iraniinternal}.\ There are mainly two categories of prior learning methods.\ 1) External prior learning methods \cite{foe,pgpd,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images.\ 2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and the image denoising is often done simultaneously with the prior learning process.\ It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.\ By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.\ In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images.
+Image priors are playing a key role in image denoising \cite{ksvd,ncsr,pgpd,epll,ple,iraniinternal}.\ There are mainly two categories of prior learning methods.\ 1) External prior learning methods \cite{pgpd,foe,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images.\ 2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and the image denoising is often done simultaneously with the prior learning process.\ It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.\ By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.\ In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images.
 In this paper, we use external priors to guide the internal prior learning.\ Our method is not only much faster than the traditional internal learning methods, but also very effective to denoise real noisy images.
@@
 
-Recently, several image denoising methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} are proposed to remove unknown noise.\ These methods can be directly applied to denoise real noisy images.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimated the noise by a multivariate Gaussian and remove the noise by a generalized version of nonlocal Bayesian model \cite{nlbayes}.
-Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.\ Almost all these methods \cite{Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} use Gaussian or MoG to model the noise in real noisy images.\ However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
+Recently, several image denoising methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} are proposed to remove unknown noise.\ These methods can be directly applied to denoise real noisy images.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimated the noise by a multivariate Gaussian and remove the noise by a generalized version of nonlocal Bayesian model \cite{nlbayes}.
+Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.\ Almost all these methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} use Gaussian or MoG to model the noise in real noisy images.\ However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
 
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
-{\footnotesize (f) NC \cite{noiseclinic}  }
+{\footnotesize (f) NC \cite{noiseclinic,ncwebsite}  }
 \end{minipage}
@@
 
-We compare the proposed method with state-of-the-art image denoising methods, including CBM3D \cite{bm3d,cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}.\ Among them, CBM3D, WNNM, MLP, CSF and TNRD are designed based on Gaussian noise model, and they need to know the noise level for denoising.\ We use the method in \cite{noiselevel} to estimate the noise level for them.\ All the other parameters in these methods are set as the default ones.\ Since WNNM, MLP, CSF and TNRD are designed for grayscale images, we use them to denoise the R, G, B channels separately for color noisy images.
+We compare the proposed method with state-of-the-art image denoising methods, including CBM3D \cite{bm3d,cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic,ncwebsite}, Neat Image (NI) \cite{neatimage}, and Cross-Channel (CC) \cite{crosschannel2016}.\ Among them, CBM3D, WNNM, MLP, CSF and TNRD are designed based on Gaussian noise model, and they need to know the noise level for denoising.\ We use the method in \cite{noiselevel} to estimate the noise level for them.\ All the other parameters in these methods are set as the default ones.\ Since WNNM, MLP, CSF and TNRD are designed for grayscale images, we use them to denoise the R, G, B channels separately for color noisy images.
 
@@
 \vspace{-2mm}
-\subsubsection{Comparison on Dataset \cite{crosschannel2016}}
+\subsubsection{Results on Dataset \cite{crosschannel2016}}
 
@@
 We firstly perform quantitative comparison on the 15 cropped images used in \cite{crosschannel2016}.
-The PSNR results of CBM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, NC \cite{noiseclinic} and
+The PSNR results of CBM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, NC \cite{noiseclinic,ncwebsite}, NI \cite{neatimage} and
 CC \cite{crosschannel2016} are listed in Table \ref{tab2}.
@@
 \hline
-Methods& \textbf{TNRD}& \textbf{NI}& \textbf{NC} &\textbf{Ours} 
+Methods& \textbf{TNRD}& \textbf{NC} & \textbf{NI} &\textbf{Ours} 
 \\
 \hline
-PSNR &  {\color{blue}{37.75}} & 36.53 & 37.57  & {\color{red}{ 38.75}}
-%SSIM &   0.8748  & 0.8743 & 0.9470 & 0.9598 &  0.9617 & 0.9241  &  0.9514  & {\color{blue}{0.9685}} & {\color{red}{0.9691}}
+PSNR &  {\color{blue}{37.75}} & 37.57  & 36.53 & {\color{red}{ 38.75}}
 \\
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
-{\footnotesize (f) NC \cite{noiseclinic}: 38.76dB }
+{\footnotesize (f) NC \cite{noiseclinic,ncwebsite}: 38.76dB }
 \end{minipage}

### 2016-11-12 CVPR2017_Review_Unified.tex
add

@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}: 35.33dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (g) NI \cite{neatimage}: 34.39dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (h) NI \cite{neatimage}: 34.39dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
+{\footnotesize (h) NC \cite{noiseclinic,ncwebsite}: 35.33dB   }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
-{\footnotesize (f) NC \cite{noiseclinic,ncwebsite}  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
+{\footnotesize (f) NI \cite{neatimage}  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_dog.png}}
-{\footnotesize (g) NI \cite{neatimage}   }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_dog.png}}
+{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}   }
 \end{minipage}
@@
 \hline
-Methods& \textbf{TNRD}& \textbf{NC} & \textbf{NI} &\textbf{Ours} 
+Methods& \textbf{TNRD} & \textbf{NI} & \textbf{NC} &\textbf{Ours} 
 \\
 \hline
-PSNR &  {\color{blue}{37.75}} & 37.57  & 36.53 & {\color{red}{ 38.75}}
+PSNR &  {\color{blue}{37.75}}  & 36.53 & 37.57 & {\color{red}{ 38.75}}
 \\
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
-{\footnotesize (f) NC \cite{noiseclinic,ncwebsite}: 38.76dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
+{\footnotesize (f) NI \cite{neatimage}: 37.68dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
-{\footnotesize (g) NI \cite{neatimage}: 37.68dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
+{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}: 38.76dB  }
 \end{minipage}

### 2016-11-13 CVPR2017_Review_Unified.tex
add

@@
 Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.\ Almost all these methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} use Gaussian or MoG to model the noise in real noisy images.\ However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
+In this paper, we propose a simple yet effective denoising method for real noisy image denoising without explicitly assuming certain noise models.
 
@@
 
-After the external PG prior is learned, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ One is that the external prior can guide the subspace assignments of internal noisy PGs, while the other is that the external prior could guide the orthogonal dictionary learning of internal noisy PGs.
+After the external PG prior is learned on external natural clean images, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ One is that the external prior can guide the subspace assignments of internal noisy PGs, while the other is that the external prior could guide the orthogonal dictionary learning of internal noisy PGs.
 
@@
 The reasons that we learn orthogonal dictionaries are two-fold.\ Firstly, the PGs $\mathbf{\overline{Y}}_{k_{n}}$ are in a subspace of the whole space of all PGs, therefore, there is no necessary to learn a redundant over-complete dictionary to characterize it, while an orthonormal dictionary has naturally zero \emph{mutual incoherence} \cite{donoho2001uncertainty}.
-Secondly, the orthogonality of dictionary can make the encoding in the testing stage very efficient, leading to an efficient denoising algorithm (please refer to sub-section 3.3 for details).
+Secondly, the orthogonality of dictionary can make the encoding in the testing stage very efficient, leading to an efficient denoising algorithm (please refer to sub-section 3.3 for more details).
 
@@
 \end{table}
-The latent clean image $\hat{\mathbf{x}}$ is reconstructed by aggregating all the estimated PGs.
-Similar to \cite{pgpd}, we perform the above denoising procedures for several iterations for better denoising outputs.
-The proposed denoising algorithm is summarized in Alg.
-1.
 
@@
 
-To demonstrate the advantages of external prior guided internal priors, in this section we perform real noisy image denoising by using external priors (denoted by ``External"), internal priors (denoted by ``Internal"), and the proposed guided internal priors (denoted by ``Guided Internal"), respectively.\ For the ``External" method, we utilize the full external dictionaries (i.e., $r=108$ in Eq.\ (\ref{equ4})) for denoising.\ For the ``Internal" method, the overall framework is similar to the method of \cite{ncsr}.\ A GMM model (with $K = 32$ Gaussians) is directly learned from the PGs extracted from the given noisy image without using any external data, and then the internal orthogonal dictionary is obtained via Eq.\ (\ref{equ2}) to perform denoising.\ All parameters of the ``External" and ``Internal" methods are tuned to achieve their best performance.
+To demonstrate the advantages of external prior guided internal priors, in this section we perform real noisy image denoising by using external priors (denoted by ``External"), internal priors (denoted by ``Internal"), and the proposed guided internal priors (denoted by ``Guided Internal"), respectively.\ For the ``External" method, we utilize the full external dictionaries (i.e., $r=108$ in Eq.\ (\ref{equ4})) for denoising.\ For the ``Internal" method, the overall framework is similar to the method of \cite{ncsr}.\ A GMM model (with $K = 32$ Gaussians) is directly learned from the PGs extracted from the given noisy image without using any external data, and then the internal orthogonal dictionary is obtained via Eq.\ (\ref{equ2}) to perform denoising.\ All parameters of the ``External" and ``Internal" methods are tuned to achieve their corresponding best performance.
 

### 2016-11-13 CVPR2017_Review_Unified.tex
add
a

@@
 \begin{abstract}
-Most of existing image denoising methods use some statistical models such as additive white Gaussian noise (AWGN) to model the noise, and learn image priors from either external data or the noisy image itself to remove noise.\ However, the noise in real-world noisy images is much more complex than AWGN, and it is hard to be modeled by simple analytical distributions.\ Therefore, many state-of-the-art denoising methods in literature become much less effective when applied to real noisy images.\ In this paper, we develop a robust denoiser for real noisy image denoising without explicit assumption on noise models.\ Specifically, we first learn external priors from a set of clean natural images, and then use the learned external priors to guide the learning of internal latent priors from the given noisy image.\ The proposed method is simple yet highly effective.\ Experiments on real noisy images demonstrate that it achieves much better denoising performance than state-of-the-art denoising methods, including those designed for real noisy images.
+Most of existing image denoising methods use some statistical models such as additive white Gaussian noise (AWGN) to model the noise, and learn image priors from either external data or the noisy image itself to remove noise.\ However, the noise in real-world noisy images is much more complex than AWGN, and it is hard to be modeled by simple analytical distributions.\ Therefore, many state-of-the-art denoising methods in literature become much less effective when applied to real noisy images.\ In this paper, we develop a robust denoiser for real noisy image denoising without explicit assumption on noise models.\ Specifically, we first learn external priors from a set of clean natural images, and then use the learned external priors to guide the learning of internal priors from the given noisy image for latent clean image recovery.\ The proposed method is simple yet highly effective.\ Experiments on real noisy images demonstrate that it achieves much better denoising performance than state-of-the-art denoising methods, including those designed for real noisy images.
 \end{abstract}

### 2016-11-13 CVPR2017_Review_Unified.tex
add

@@
 \usepackage{arydshln}
+
+\usepackage{cite}
 
@@
 
-Most of the existing denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN).
+Most of the denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN).
 Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).\ According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
@@
 \small
-\bibliographystyle{unsrt}
+\bibliographystyle{plain}
 \bibliography{egbib}

### 2016-11-13 CVPR2017_Review_Unified.tex
add

@@
 Most of the denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN).
-Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).\ According to \cite{healey1994radiometric}, the noise corrupted in the imaging process [is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
-As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TNRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}.
+Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).\ According to \cite{healey1994radiometric}, the noise corrupted in the imaging process is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
+As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf} and TNRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}.
 One can see that these methods either remain the noise or over-smooth the image details on this real noisy image.
@@
 Almost all of these methods follow a two-stage framework: first estimate the parameters of the assumed noise model (usually Gaussian  or mixture of Gaussians (MoG)), and then perform denoising with the estimated noise model.
-Again, the noise in real noisy images is very complex and hard to be modeled by explicit distributions such as Gaussian and MoG.\ Fig.\ \ref{fig1} also shows the denoised results of two state-of-the-art real noisy image denoising methods, Noise Clinic \cite{noiseclinic,ncwebsite} and Neat Image \cite{neatimage}.\ One can see that these two methods do not perform well on this noisy image either.
+Again, the noise in real noisy images is very complex and hard to be modeled by explicit distributions such as Gaussian and MoG.\ Fig.\ \ref{fig1} also shows the denoising results of two state-of-the-art real noisy image denoising methods, Noise Clinic \cite{noiseclinic,ncwebsite} and Neat Image \cite{neatimage}.\ One can see that these two methods do not perform well on this noisy image either.
 
@@
 }\vspace{-1mm}
-\caption{Denoised images of a cropped part from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \vspace{-3mm}
@@
 
-This work aims to develop a robust solution for real noisy image denoising without explicitly assuming certain noise models.\ To achieve this goal, we propose to first learn image priors from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image.\ The flowchart of the proposed method is illustrated in\ Fig.\ \ref{fig2}.\ We first extract millions of patch groups from a set of high quality natural images, with which a Gaussian Mixture Model (GMM) is learned as the external prior.\ The learned GMM prior model is used to cluster the patch groups extracted from the given noisy image, and then a hybrid orthogonal dictionary (HOD) is learned as the internal prior for image denoising.
+This work aims to develop a robust denoiser for real noisy image denoising without explicitly assuming certain noise models.\ To achieve this goal, we propose to first learn image priors from external clean images, and then employ the learned external priors to guide the learning of internal priors from the given noisy image.\ The flowchart of the proposed method is illustrated in\ Fig.\ \ref{fig2}.\ We first extract millions of patch groups from a set of high quality natural images, with which a Gaussian Mixture Model (GMM) is learned as the external prior.\ The learned GMM prior model is used to cluster the patch groups extracted from the given noisy image, and then an external-internal hybrid orthogonal dictionary is learned as the final prior for image denoising.
 Our proposed denoising method is simple and efficient, yet our extensive experiments on real noisy images clearly demonstrate its better denoising performance than the current state-of-the-arts.

### 2016-11-13 CVPR2017_Review_Unified.tex
add

@@
 }\vspace{-1mm}
-\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods.
+The mean image of 500 shots of the static scene (with the same camera and camera setting) is roughly taken as the ``ground truth".
+The images are better viewed by zooming in on screen.}
 \vspace{-3mm}
@@
 
-Image priors are playing a key role in image denoising \cite{ksvd,ncsr,pgpd,epll,ple,iraniinternal}.\ There are mainly two categories of prior learning methods.\ 1) External prior learning methods \cite{pgpd,foe,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images.\ 2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and the image denoising is often done simultaneously with the prior learning process.\ It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.\ By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.\ In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images.
+Image priors are playing a key role in image denoising \cite{ksvd,ncsr,pgpd,epll,ple,iraniinternal}.\ There are mainly two categories of prior learning methods.\ 1) External prior learning methods \cite{pgpd,foe,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images.\ 2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and image denoising is often done simultaneously with the prior learning process.\ It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.\ By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.\ In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images.
 In this paper, we use external priors to guide the internal prior learning.\ Our method is not only much faster than the traditional internal learning methods, but also very effective to denoise real noisy images.
@@
 
-Recently, several image denoising methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} are proposed to remove unknown noise.\ These methods can be directly applied to denoise real noisy images.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimated the noise by a multivariate Gaussian and remove the noise by a generalized version of nonlocal Bayesian model \cite{nlbayes}.
-Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods developed specifically for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The \cite{crosschannel2016} modeled the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimated the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.\ Almost all these methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} use Gaussian or MoG to model the noise in real noisy images.\ However, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
+Recently, several denoising methods have been proposed to remove unknown noise from images \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite}.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimates the noise distribution by using a multivariate Gaussian model and removes the noise by using a generalized version of nonlocal Bayesian model \cite{nlbayes}.
+Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods specifically designed for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The method in \cite{crosschannel2016} models the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimates the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.
+Almost all the methods mentioned above \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} use Gaussian or MoG to model the noise in real noisy images.
+Nonetheless, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
 In this paper, we propose a simple yet effective denoising method for real noisy image denoising without explicitly assuming certain noise models.
@@
 
-The nonlocal self-similarity based patch group (PG) \cite{pgpd} has proved to be a very effective unit for image prior learning.
-In this work, we also extract PGs from natural clean images to learn priors.
-A PG is a group of similar patches to a local patch.
-
-In our method, each local patch is extracted from a RGB image with patch size $p\times p \times 3$.\ We search the $M$ most similar patches to this local patch (including the local patch itself) in a $W\times W$ local region around it.
+The nonlocal self-similarity based patch group (PG) \cite{pgpd} has proved to be a very effective unit for image prior learning.\ In this work, we extract PGs from natural clean images to learn priors.
+A PG is a group of similar patches to a local patch.\ In our method, each local patch is extracted from a RGB image with patch size $p\times p \times 3$.\ We search the $M$ most similar patches to this local patch (including the local patch itself) in a $W\times W$ local region around it.
 Each patch is stretched to a patch vector $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ to form the PG $\{\mathbf{x}_{m}\}_{m=1}^{M}$.
@@
 
-Assume we extract a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.\ A Gaussian Mixture Model (GMM) is learned to model the PG prior.\ The overall log-likelihood function is
+Assume that we extract a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.\ A Gaussian Mixture Model (GMM) is learned to model the PG prior.\ The overall log-likelihood function is
 \vspace{-2mm}
@@
 
-After the external PG prior is learned on external natural clean images, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ One is that the external prior can guide the subspace assignments of internal noisy PGs, while the other is that the external prior could guide the orthogonal dictionary learning of internal noisy PGs.
+After the external PG prior is learned on external natural clean images, we employ it to guide the internal PG prior learning for a given real noisy image.\ The guidance lies in two aspects.\ First, the external prior will guide the subspace assignments of internal noisy PGs.\ Second, the external prior will guide the orthogonal dictionary learning of internal noisy PGs.
 
@@
 \end{equation}
-for $k=1,...,K$.\ Then $\mathbf{\overline{Y}}_{n}$ is assigned to the component with the maximum A-posteriori (MAP) probability $\max_{k}P(k|\mathbf{\overline{Y}}_{n})$.
+for $k=1,...,K$.\ Then $\mathbf{\overline{Y}}_{n}$ is assigned to the component with the maximum \emph{a}-posteriori (MAP) probability $\max_{k}P(k|\mathbf{\overline{Y}}_{n})$.
 
@@
 For the $k$-th subspace, the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ where $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.\ We propose to learn an orthogonal dictionary $\mathbf{D}_{k}$ from each set of PGs $\mathbf{\overline{Y}}_{k_{n}}$ to characterize the internal PG prior with the guidance of the corresponding external orthogonal dictionary $\mathbf{U}_{k}$ (Eq.\ (\ref{equ2})).
-The reasons that we learn orthogonal dictionaries are two-fold.\ Firstly, the PGs $\mathbf{\overline{Y}}_{k_{n}}$ are in a subspace of the whole space of all PGs, therefore, there is no necessary to learn a redundant over-complete dictionary to characterize it, while an orthonormal dictionary has naturally zero \emph{mutual incoherence} \cite{donoho2001uncertainty}.
+The reasons that we learn orthogonal dictionaries are two-fold.\ Firstly, the PGs $\mathbf{\overline{Y}}_{k_{n}}$ are in a subspace of the whole space of all PGs; therefore, there is no necessary to learn a redundant over-complete dictionary to characterize it, while an orthonormal dictionary has naturally zero \emph{mutual incoherence} \cite{donoho2001uncertainty}.
 Secondly, the orthogonality of dictionary can make the encoding in the testing stage very efficient, leading to an efficient denoising algorithm (please refer to sub-section 3.3 for more details).
@@
 \quad
-\mathbf{D}=[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}],\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{I}_{r},\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{0},
+\mathbf{D}=[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}],\ \mathbf{D}^{\top}\mathbf{D} = \mathbf{I},
 \end{split}
 \end{equation}
-where $\bm{\alpha}_{n,m}$ is the sparse coding vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
+where $\mathbf{I}$ is the $3p^{2}$ dimensional identity matrix and $\bm{\alpha}_{n,m}$ is the sparse coding vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
 $\lambda_{j}$ is the $j$-th regularization parameter defined as
@@
 \end{equation}
-where $\mathbf{S}_{k}(j)$ is the $j$-th singular value of diagonal singular value matrix $\mathbf{S}_{k}$ (please refer to Eq.\ (\ref{equ2})) and $\varepsilon$ is a small positive number to avoid zero denominator.\ Noted that $\mathbf{D}_{\text{E}}=\mathbf{U}_{k}$ if $r=3p^{2}$ and $\mathbf{D}_{\text{E}}=\emptyset$ if $r=0$.\ The dictionary $\mathbf{D} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}]$ is orthogonal by checking that:
-\vspace{-2mm}
-\begin{equation}\label{equ6}\vspace{-1mm}
-\mathbf{D}^{\top}\mathbf{D} = 
-\left[\begin{array}{c}
-\mathbf{D}_{\text{E}}^{\top}
-\\
-\mathbf{D}_{\text{I}}^{\top}
-\end{array}\right]
-[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}]
-=
-\left[\begin{array}{cc}
-\mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}}
-\\
-\mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}}
-\end{array}\right]
-=
-\mathbf{I}
-\end{equation}
+where $\mathbf{S}_{k}(j)$ is the $j$-th singular value of diagonal singular value matrix $\mathbf{S}_{k}$ (please refer to Eq.\ (\ref{equ2})) and $\varepsilon$ is a small positive number to avoid zero denominator.\ Noted that $\mathbf{D}_{\text{E}}=\mathbf{U}_{k}$ if $r=3p^{2}$ and $\mathbf{D}_{\text{E}}=\emptyset$ if $r=0$.
+
+%The dictionary $\mathbf{D} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}]$ is orthogonal by checking that:
+%\vspace{-2mm}
+%\begin{equation}\label{equ6}\vspace{-1mm}
+%\mathbf{D}^{\top}\mathbf{D} = 
+%\left[\begin{array}{c}
+%\mathbf{D}_{\text{E}}^{\top}
+%\\
+%\mathbf{D}_{\text{I}}^{\top}
+%\end{array}\right]
+%[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}]
+%=
+%\left[\begin{array}{cc}
+%\mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}}
+%\\
+%\mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}}
+%\end{array}\right]
+%=
+%\mathbf{I}
+%\end{equation}
 
 We employ an alternating iterative approach to solve the optimization problem (\ref{equ4}).
-Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{k}$ and for $t=0,1, ...,T-1$, we alternatively update $\bm{\alpha}_{n,m}$ and $\mathbf{D}$ as follows:
+Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{k}$ and for $t=0,1, ...,T-1$, we alternatively update $\bm{\alpha}_{n,m}$ and $\mathbf{D}$ as follows.
 \vspace{2mm}\\
-\textbf{Updating Sparse Coefficient}: Given the orthogonal dictionary $\textbf{D}^{(t)}$, we update each sparse coding vector $\bm{\alpha}_{n,m}$ by solving
+\textbf{Updating Sparse Coding Coefficients}: Given the orthogonal dictionary $\textbf{D}^{(t)}$, we update each sparse coding vector $\bm{\alpha}_{n,m}$ by solving
 \vspace{-4mm}
@@
 \end{equation}
-where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$.
-The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.
+where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$ and $\mathbf{I}_{r}$ is the $r$ dimensional identity matrix.\ The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.
 According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
@@
 
-The noise in real-world noisy images is much more complex than additive white Gaussian noise and hard to be modeled by simple analytical distributions such as Gaussian or mixture of Gaussians.\ In this paper, we proposed a simple yet effective solution for real noisy image denoising without explicitly assuming certain noise models.\ Specifically, we firstly learned image priors of Gausian Mixture Model from external clean images, and then employ the learned external priors to guide the learning of internal latent priors from the given noisy image.\ The learned hybrid orthogonal dictionary are simutaneously utilized in real noisy image denoising.\ Experiments on two real noisy image datasets, where the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings, demonstrate that our proposed method achieved much better performance than state-of-the-art image denoising methods.
+The noise in real-world noisy images is much more complex than additive white Gaussian noise and hard to be modeled by simple analytical distributions such as Gaussian or mixture of Gaussians, making the real noisy image denoising problem very challenging.\ In this paper, we proposed a simple yet effective solution for real noisy image denoising without explicitly assuming certain noise models.\ Specifically, we firstly learned image priors from external clean images, and then employed the learned external priors to guide the learning of internal priors from the given noisy image.\ The learned hybrid priors are utilized for real noisy image denoising.\ Experiments on two real noisy image datasets, where the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings, demonstrated that our proposed method achieved much better performance than state-of-the-art image denoising methods.
 

### 2016-11-13 CVPR2017_Review_Unified.tex
add

@@
 
-Our proposed method has two stages: the external prior learning stage and the external prior guided internal prior learning stage.\ In the first stage, we set $p = 6$ (the patch size), $M = 10$ (the number of similar patches in a PG), $W = 31$ (the window size for PG searching) and $K = 32$ (the number of Gaussian components in GMM.\ We learn the external GMM prior with 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
+Our proposed method has two stages: the external prior learning stage and the external prior guided internal prior learning stage.\ In the first stage, we set $p = 6$ (the patch size), $M = 10$ (the number of similar patches in a PG), $W = 31$ (the window size for PG searching) and $K = 32$ (the number of Gaussian components in GMM).\ We learn the external GMM prior with 3.6 million PGs extracted from the Kodak PhotoCD Dataset (\url{http://r0k.us/graphics/kodak/}), which includes 24 high quality color images.
 
@@
 \vspace{-2mm}
-\caption{Denoised images of a cropped part from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The 
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The 
 \vspace{-0.5mm}
@@
 \vspace{-2mm}  
-\caption{Denoised images of a cropped part from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The 
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The 
 \vspace{-0.5mm}

### 2016-11-13 CVPR2017_Review_Unified.tex
a

@@
 Most of the denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} mentioned above assume noise $\mathbf{n}$ to be additive white Gaussian noise (AWGN).
-Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).\ According to \cite{healey1994radiometric}, the noise corrupted in the imaging process is signal dependent and comes from five main sources: photon shot, fixed pattern, dark current, readout, and quantization noise.
+Unfortunately, this assumption is too ideal to be true for real-world noisy images, where the noise is much more complex than AWGN \cite{crosschannel2016,healey1994radiometric} and varies by different cameras and camera settings (ISO, shutter speed, and aperture, etc.).\ According to \cite{healey1994radiometric}, the noise corrupted in the imaging process is signal dependent and comes from five main sources:\ photon shot, fixed pattern, dark current, readout, and quantization noise.
 As a result, many advanced denoising methods in literature becomes much less effective when applied to real-world noisy images.\ Fig.\ \ref{fig1} shows an example, where we apply some representative and state-of-the-art denoising methods, including CBM3D \cite{cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf} and TNRD \cite{chen2015learning}, to a real noisy image (captured by a Nikon D800 camera with ISO is 3200) provided in \cite{crosschannel2016}.
@@
 \end{minipage}
-}\vspace{-3.5mm}
+}\vspace{-3mm}
 \subfigure{
@@
 The images are better viewed by zooming in on screen.}
-\vspace{-3mm}
+\vspace{-1mm}
 \label{fig1}
@@
 \centering
-\includegraphics[width=0.79\linewidth]{Flowchart.pdf}
-\vspace{-28mm}
+\includegraphics[width=0.91\linewidth]{Flowchart.pdf}
+\vspace{-27mm}
 \caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
@@
 
-\vspace{-1mm}
 \subsection{Internal \textbf{\emph{vs.}} External Prior Learning}
@@
 
-\section{External Prior Guided Internal Prior Learning}
+\section{External Prior Guided Internal Prior Learn\\ing}
 
@@
 \begin{table}
-\caption{Average PSNR (dB) results and Run Time (seconds) of the ``External", the ``Internal", and the ``Guided Internal" methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
+\caption{Average PSNR (dB) and Run Time (seconds) of the ``External", ``Internal", and ``Guided Internal" methods on 60 real noisy images (of size $500\times500\times3$) cropped from \cite{crosschannel2016}.}
 \label{tab1}
@@
 
-\vspace{-1mm}
 \subsubsection{Results on Dataset \cite{ncwebsite}}
@@
 
-\vspace{-2mm}
 \subsubsection{Results on Dataset \cite{crosschannel2016}}
@@
 
-We then perform denoising experiments on the 60 images we cropped from \cite{crosschannel2016}.
-The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available).
-Again, our proposed method achieves much better PSNR results than the other methods.\ The improvement of our method over the second best method (TNRD) is about 1dB.
+We then perform denoising experiments on the 60 images we cropped from \cite{crosschannel2016}.\ The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available).\ Again, our proposed method achieves much better PSNR results than the other methods.\ The improvement of our method over the second best method (TNRD) is about 1dB.
 Due to the space limitations, the visual comparisons are provided in the supplementary file.
@@
 \vspace{-3mm}
-\label{tab3}
+\label{tab2}
 \begin{center}
@@
 \begin{table*}
-\caption{Average PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
-\label{tab2}
+\caption{PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
+\label{tab3}
 \begin{center}
@@
 }\vspace{-1mm}
-\caption{Denoised images of a part cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images 
+\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images 
 \vspace{-0.5mm}

### 2016-11-13 CVPR2017_Review_Unified.tex
add
ad

@@
 }\vspace{-1mm}
-\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods.
-The mean image of 500 shots of the static scene (with the same camera and camera setting) is roughly taken as the ``ground truth".
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods.\ The static scene was shot 500 times with the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR index can be computed.
 The images are better viewed by zooming in on screen.}
-\vspace{-1mm}
+%\vspace{-1mm}
 \label{fig1}
@@
 \centering
-\includegraphics[width=0.91\linewidth]{Flowchart.pdf}
-\vspace{-27mm}
+\includegraphics[width=0.95\linewidth]{Flowchart.pdf}
+\vspace{-32mm}
 \caption{Flowchart of the proposed external prior guided internal prior learning and real noisy image denoising framework.
 }
-\vspace{-2mm}
+\vspace{-1mm}
 \label{fig2}
@@
 
-\vspace{-1mm}
 \subsection{Real Noisy Image Denoising}
@@
 Recently, several denoising methods have been proposed to remove unknown noise from images \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite}.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimates the noise distribution by using a multivariate Gaussian model and removes the noise by using a generalized version of nonlocal Bayesian model \cite{nlbayes}.
-Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods specifically designed for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The method in \cite{crosschannel2016} models the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimates the noise parameters from a flat region of the given noisy image and filtered the noise correspondingly.
-Almost all the methods mentioned above \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} use Gaussian or MoG to model the noise in real noisy images.
-Nonetheless, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.
-In this paper, we propose a simple yet effective denoising method for real noisy image denoising without explicitly assuming certain noise models.
+Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods specifically designed for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The method in \cite{crosschannel2016} models the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimates the noise parameters from a flat region of the given noisy image and filters the noise correspondingly.\ Almost all the methods mentioned above \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} use Gaussian or MoG to model the noise in real noisy images.\ Nonetheless, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.\ In this paper, we propose a simple yet effective denoising method for real noisy image denoising without explicitly assuming certain noise models.
 
-\section{External Prior Guided Internal Prior Learn\\ing}
+\section{External Prior Guided Internal Prior Learning}
 
@@
 framework:
-\vspace{-2mm}
+\vspace{-3mm}
 \begin{equation}\label{equ4}\vspace{-3mm}
 \begin{split}
-&\min_{\mathbf{D}_{\text{I}},\{\bm{\alpha}_{n,m}\}}
-\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|)
+\min_{\mathbf{D}_{\text{I}},\{\bm{\alpha}_{n,m}\}}
+&\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|)
 \\
@@
 \end{equation}
-where $\mathbf{S}_{k}(j)$ is the $j$-th singular value of diagonal singular value matrix $\mathbf{S}_{k}$ (please refer to Eq.\ (\ref{equ2})) and $\varepsilon$ is a small positive number to avoid zero denominator.\ Noted that $\mathbf{D}_{\text{E}}=\mathbf{U}_{k}$ if $r=3p^{2}$ and $\mathbf{D}_{\text{E}}=\emptyset$ if $r=0$.
+where $\mathbf{S}_{k}(j)$ is the $j$-th singular value of diagonal singular value matrix $\mathbf{S}_{k}$ (please refer to Eq.\ (\ref{equ2})) and $\varepsilon$ is a small positive number to avoid zero denominator.\ Note that $\mathbf{D}_{\text{E}}=\mathbf{U}_{k}$ if $r=3p^{2}$ and $\mathbf{D}_{\text{E}}=\emptyset$ if $r=0$.
 
@@
 \vspace{-4mm}
-\begin{equation}\label{equ7}\vspace{-4mm}
+\begin{equation}\label{equ6}\vspace{-2mm}
 \begin{split}
@@
 \end{equation}
-Since dictionary $\mathbf{D}^{(t)}$ is orthogonal, the problems (\ref{equ7}) has a closed-form solution
-\vspace{-2mm}
-\begin{equation}\label{equ8}\vspace{-2mm}
+Since dictionary $\mathbf{D}^{(t)}$ is orthogonal, the problems (\ref{equ6}) has a closed-form solution
+\vspace{-1mm}
+\begin{equation}\label{equ7}\vspace{-0mm}
 \bm{\alpha}_{n,m}^{(t)}= \text{sgn}((\mathbf{D}^{(t)})^{\top}\mathbf{\overline{y}}_{n,m})\odot \text{max}(|(\mathbf{D}^{(t)})^{\top}\mathbf{\overline{y}}_{n,m}|-\bm{\lambda},\mathbf{0}),
@@
 where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.\ The detailed derivation of Eq.
-(\ref{equ8}) can be found in the supplementary file.
+(\ref{equ7}) can be found in the supplementary file.
 \vspace{2mm}\\
@@
 \vspace{-2mm}
-\begin{equation}\label{equ9} \vspace{-2mm}
+\begin{equation}\label{equ8} \vspace{-2mm}
 \begin{split}
@@
 \end{equation}
-where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$ and $\mathbf{I}_{r}$ is the $r$ dimensional identity matrix.\ The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.
-According to the Theorem 4 in \cite{spca}, the problem (\ref{equ9}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
+where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$ and $\mathbf{I}_{r}$ is the $r$ dimensional identity matrix.\ The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.\ According to the Theorem 4 in \cite{spca}, the problem (\ref{equ8}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
 \vspace{-1mm}
-\begin{equation}\label{equ10}\vspace{-2mm}
+\begin{equation}\label{equ9}\vspace{-1mm}
 (\mathbf{I}-\mathbf{D}_{\text{E}}\mathbf{D}_{\text{E}}^{\top})\mathbf{Y}(\mathbf{A}_{\text{I}}^{(t)})^{\top}
@@
 The denoising of the given noisy image $\mathbf{y}$ can be simultaneously done with the guided internal dictionary learning process.
-Once we obtain the solutions of sparse coding vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.\ (\ref{equ8}) and the orthogonal dictionary $\mathbf{D}^{(T)} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{(T)}]$ in Eq.
-(\ref{equ9}), the latent clean patch of a noisy patch $\hat{\mathbf{y}}_{n,m}$ in PG $\mathbf{Y}_{n}$ is reconstructed as
+Once we obtain the solutions of sparse coding vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.\ (\ref{equ7}) and the orthogonal dictionary $\mathbf{D}^{(T)} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{(T)}]$ in Eq.
+(\ref{equ8}), the latent clean patch of a noisy patch $\hat{\mathbf{y}}_{n,m}$ in PG $\mathbf{Y}_{n}$ is reconstructed as
 \vspace{-2mm}
-\begin{equation}\label{equ11}\vspace{-2mm}
+\begin{equation}\label{equ10}\vspace{-2mm}
 \hat{\mathbf{y}}_{n,m}=\mathbf{D}^{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
@@
 \\
-5.\quad Recover each patch in all PGs via Eq. (\ref{equ11});
+5.\quad Recover each patch in all PGs via Eq. (\ref{equ10});
 \\
@@
 \label{tab1}
-\begin{small}
+%\begin{small}
 \vspace{-3mm}
@@
 \hline
- & \textbf{Noisy} & \textbf{External} & \textbf{Internal} & \textbf{Guided Internal}  
+ & \small\textbf{Noisy} &\small \textbf{External} & \small\textbf{Internal} & \small\textbf{Guided Internal}  
 \\
@@
 \end{tabular}
-\end{center}\vspace{-4mm}
-\end{small}
+\end{center}\vspace{-3mm}
+%\end{small}
 \end{table}
@@
 In comparison, our proposed method recovers much better the structures and textures (such as the eye area) than the other competing methods.
-More visual comparisons on dataset \cite{ncwebsite} can be found in the supplementary file.
+More visual comparisons on this dataset \cite{ncwebsite} can be found in the supplementary file.
 
@@
 (The results of CC are copied from the original paper \cite{crosschannel2016}.) The best PSNR result of each image is highlighted in bold.
-One can see that on 9 out of the 15 images, our method achieves the best PSNR values.\ CC achieves the best PSNR on 3 of the 15 images.\ It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images.\ On average, our proposed method has 0.28dB PSNR improvements over \cite{crosschannel2016} and much higher PSNR gains over other competing methods.\ Fig.\ \ref{fig7} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.\ We can see that CBM3D, WNNM, NC, NI, and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image.\ By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs.\ More visual comparisons can be found in the supplementary file.
+One can see that on 9 out of the 15 images, our method achieves the best PSNR values.\ CC achieves the best PSNR on 3 of the 15 images.\ It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images.\ On average, our proposed method has 0.28dB PSNR improvements over \cite{crosschannel2016} and much higher PSNR gains over other competing methods.\ Fig.\ \ref{fig7} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.\ We can see that CBM3D, WNNM, NC, NI and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image.\ By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs.\ More visual comparisons on this dataset \cite{crosschannel2016} can be found in the supplementary file.
 
@@
 
-\begin{table*}
+\begin{table*}\vspace{2mm}
 \caption{PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
+\vspace{1mm}
 \label{tab3}
@@
 \end{tabular}
-\end{center}\vspace{-1mm}
+\end{center}
 \end{table*}
 
-\begin{figure*}
+\begin{figure*}\vspace{1mm}
 \centering
@@
 }\vspace{-1mm}
-\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images 
-\vspace{-0.5mm}
-are better to be zoomed in on screen.}
-\vspace{-1mm}
+\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
 \label{fig7}

### 2016-11-13 CVPR2017_Review_Unified.tex
add

@@
 images are better to be zoomed in on screen.}
-\vspace{-1mm}
+\vspace{-2mm}
 \label{fig4}
@@
 images are better to be zoomed in on screen.}
-\vspace{-1mm}
+\vspace{-3mm}
 \label{fig5}
@@
 
-We compare the three methods mentioned above on the 60 cropped images from \cite{crosschannel2016}.\ The average PSNR and run time  are listed in Table \ref{tab1}.
-It can be seen that ``Guided Internal" prior achieves better PSNR than both ``External" and ``Internal" priors.
+We compare the three methods mentioned above on the 60 cropped images from \cite{crosschannel2016}.\ The average PSNR and run time are listed in Table \ref{tab1}.\ The best results are highlighted in bold.\ It can be seen that ``Guided Internal" prior achieves better PSNR than both ``External" and ``Internal" priors.
 In addition, the ``Internal" method is very slow because it involves online GMM learning, while the ``Guided Internal" method is only a little slower than the ``External" method.\ Fig.\ \ref{fig4} and Fig.\ \ref{fig5} show the denoised images of two noisy image by the three methods.\ We can see that the  ``External" method is good at recovering large-scale structures (see Fig.\ \ref{fig4}) while the ``Internal" method is good at recovering fine-scale textures (see Fig.\ \ref{fig5}).\ By utilizing external priors to guide the internal prior learning, our proposed method can effectively recover both the large-scale structures and fine-scale textures.
@@
 \caption{Denoised images of the real noisy image ``Dog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
-\vspace{-1mm}
+%\vspace{-1mm}
 \label{fig6}
@@
 
-Like our method, the NC is a blind image denoising method which does not need any noise prior.\ The NI is a commercial software for image denoising, which has been embedded into Photoshop and Corel PaintShop \cite{neatimage}.
-The code of CC is not released but its results on the 15 cropped images are available at \cite{crosschannel2016}.
+Like our method, the NC is a blind image denoising method which does not need any noise prior.\ The NI is a commercial software for image denoising, which has been embedded into Photoshop and Corel PaintShop \cite{neatimage}.\ The code of CC is not released but its results on the 15 cropped images are available at \cite{crosschannel2016}.
 Therefore, we only compare with it on the 15 cropped images from \cite{crosschannel2016}.
@@
 \end{tabular}
-\end{center}\vspace{-3mm}
+\end{center}\vspace{-2mm}
 %\end{small}
@@
 
-\subsubsection{Results on Dataset \cite{crosschannel2016}}
-
-As described in section 4.2, there is a mean image for each of the 17 scenes used in dataset \cite{crosschannel2016}, and those mean images can be roughly taken as ``ground truth" images for quantitative evaluation of denoising algorithms.
-We firstly perform quantitative comparison on the 15 cropped images used in \cite{crosschannel2016}.
-The PSNR results of CBM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, NC \cite{noiseclinic,ncwebsite}, NI \cite{neatimage} and
-CC \cite{crosschannel2016} are listed in Table \ref{tab2}.
-(The results of CC are copied from the original paper \cite{crosschannel2016}.) The best PSNR result of each image is highlighted in bold.
-One can see that on 9 out of the 15 images, our method achieves the best PSNR values.\ CC achieves the best PSNR on 3 of the 15 images.\ It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images.\ On average, our proposed method has 0.28dB PSNR improvements over \cite{crosschannel2016} and much higher PSNR gains over other competing methods.\ Fig.\ \ref{fig7} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.\ We can see that CBM3D, WNNM, NC, NI and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image.\ By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs.\ More visual comparisons on this dataset \cite{crosschannel2016} can be found in the supplementary file.
-
-We then perform denoising experiments on the 60 images we cropped from \cite{crosschannel2016}.\ The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available).\ Again, our proposed method achieves much better PSNR results than the other methods.\ The improvement of our method over the second best method (TNRD) is about 1dB.
-Due to the space limitations, the visual comparisons are provided in the supplementary file.
-
-\begin{table}
-\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
-\vspace{-3mm}
-\label{tab2}
-\begin{center}
-\renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|}
-\hline
- Methods& \textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
-\\
-\hline
-PSNR &   34.58 & 34.52 & 36.19 & 37.40
-\\
-\hline
-Methods& \textbf{TNRD} & \textbf{NI} & \textbf{NC} &\textbf{Ours} 
-\\
-\hline
-PSNR &  {\color{blue}{37.75}}  & 36.53 & 37.57 & {\color{red}{ 38.75}}
-\\
-\hline
-\end{tabular}
-\end{center}\vspace{-6mm}
-\end{table}
-
 \begin{table*}\vspace{2mm}
 \caption{PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
-\vspace{1mm}
-\label{tab3}
+\label{tab2}
 \begin{center}
@@
 \end{center}
+\vspace{1mm}
 \end{table*}
+
+\subsubsection{Results on Dataset \cite{crosschannel2016}}
+
+As described in section 4.2, there is a mean image for each of the 17 scenes used in dataset \cite{crosschannel2016}, and those mean images can be roughly taken as ``ground truth" images for quantitative evaluation of denoising algorithms.
+We firstly perform quantitative comparison on the 15 cropped images used in \cite{crosschannel2016}.
+The PSNR results of CBM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, NC \cite{noiseclinic,ncwebsite}, NI \cite{neatimage} and
+CC \cite{crosschannel2016} are listed in Table \ref{tab2} (The results of CC are copied from the original paper \cite{crosschannel2016}).\ The best and second best PSNR results of each image are highlighted in red and blue, respectively.\ One can see that on 9 out of the 15 images, our method achieves the best PSNR values.\ CC achieves the best PSNR on 3 of the 15 images.\ It should be noted that in the CC method, a specific model is trained for each camera and camera setting, while our method uses the same model for all images.\ On average, our proposed method has 0.28dB PSNR improvements over \cite{crosschannel2016} and much higher PSNR gains over other competing methods.\ Fig.\ \ref{fig7} shows the denoised images of a scene captured by Canon 5D Mark 3 at ISO = 3200.\ We can see that CBM3D, WNNM, NC, NI and CC would either remain noise or generate artifacts, while MLP, TNRD over-smooth much the image.\ By using the external prior guided internal priors, our proposed method preserves edges and textures better than other methods, leading to visually pleasant outputs.\ More visual comparisons can be found in the supplementary file.
+
+We then perform denoising experiments on the 60 images we cropped from \cite{crosschannel2016}.\ The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available).\ The best PSNR result is highlighted in bold.\ Again, our proposed method achieves much better PSNR results than the other methods.\ The improvement of our method over the second best method (TNRD) is about 1dB.
+Due to the space limitations, the visual comparisons are provided in the supplementary file.
+
+\begin{table}
+\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
+\vspace{-3mm}
+\label{tab3}
+\begin{center}
+\renewcommand\arraystretch{1}
+\begin{tabular}{|c||c|c|c|c|}
+\hline
+ Methods& \textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
+\\
+\hline
+PSNR &   34.58 & 34.52 & 36.19 & 37.40
+\\
+\hline
+Methods& \textbf{TNRD} & \textbf{NI} & \textbf{NC} &\textbf{Ours} 
+\\
+\hline
+PSNR & 37.75  & 36.53 & 37.57 & {\textbf{{ 38.75}}}
+\\
+\hline
+\end{tabular}
+\end{center}\vspace{-2mm}
+\end{table}
 
@@
 \label{fig7}
+\vspace{1mm}
 \end{figure*}

### 2016-11-13 CVPR2017_Review_Unified.tex
add
a

@@
 \usepackage{arydshln}
+\usepackage{cite}
 
-\usepackage{cite}
+%\usepackage{sectsty}
+%\sectionfont{\fontsize{12}{11}\selectfont\leftskip=0pt\vspace{-2mm}}
+%\subsectionfont{\fontsize{11}{10}\selectfont\leftskip=0pt\vspace{-1mm}}
+%\subsubsectionfont{\fontsize{10}{10}\selectfont\leftskip=0pt\vspace{-1mm}}
 
@@
 
-\section{External Prior Guided Internal Prior Learning}
+\section{External Prior Guided Internal Prior Learning and Denoising}
 
@@
 
-We then perform denoising experiments on the 60 images we cropped from \cite{crosschannel2016}.\ The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available).\ The best PSNR result is highlighted in bold.\ Again, our proposed method achieves much better PSNR results than the other methods.\ The improvement of our method over the second best method (TNRD) is about 1dB.
+We then perform denoising experiments on the 60 images we cropped from \cite{crosschannel2016}.\ The average PSNR results are listed in Table \ref{tab3} (CC is not compared since the code of \cite{crosschannel2016} is not available).\ The best result is highlighted in bold.\ Again, our proposed method achieves much better PSNR results than the other methods.\ The improvement of our method over the second best method (TNRD) is about 1dB.
 Due to the space limitations, the visual comparisons are provided in the supplementary file.

### 2016-11-13 CVPR2017_Review_Unified.tex
ad
add

@@
 Image denoising is a crucial and indispensable step to improve image quality in digital imaging systems.
-In particular, with the decrease of size of CMOS/CCD sensors, noise is more easily to be corrupted and hence denoising is becoming increasingly important for high resolution imaging.
+In particular, with the decrease of size of CMOS/CCD sensors, image is more easily to be corrupted and hence denoising is becoming increasingly important for high resolution imaging.
 In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise.
@@
 
-\section{External Prior Guided Internal Prior Learning and Denoising}
+\section{External Prior Guided Internal Prior Learning and Image Denoising}
 

### 2016-11-13 CVPR2017_Review_Unified.tex
add

@@
 
-Image denoising is a crucial and indispensable step to improve image quality in digital imaging systems.
-In particular, with the decrease of size of CMOS/CCD sensors, image is more easily to be corrupted and hence denoising is becoming increasingly important for high resolution imaging.
-In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise.
-Numerous image denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc,ncsr}, nonlocal self-similarity based methods \cite{ncsr,nlm,bm3d,cbm3d,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.
+Image denoising is a crucial and indispensable step to improve image quality in digital imaging systems.\ In particular, with the decrease of size of CMOS/CCD sensors, image is more easily to be corrupted by noise and hence denoising is becoming increasingly important for high resolution imaging.\ In literature of image denoising, the observed noisy image is usually modeled as $\mathbf{y}=\mathbf{x}+\mathbf{n}$, where $\mathbf{x}$ is the latent clean image and $\mathbf{n}$ is the corrupted noise.\ Numerous image denoising methods \cite{ksvd,lssc,ncsr,nlm,bm3d,cbm3d,pgpd,wnnm,mlp,csf,chen2015learning,foe,epll} have been proposed in the past decades, including sparse representation and dictionary learning based methods \cite{ksvd,lssc,ncsr}, nonlocal self-similarity based methods \cite{ncsr,nlm,bm3d,cbm3d,pgpd}, low-rank based methods \cite{wnnm}, neural network based methods \cite{mlp}, and discriminative learning based methods \cite{csf,chen2015learning}.
 

### 2016-11-13 CVPR2017_Review_Unified.tex
add

@@
 
-Assume that we extract a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.\ A Gaussian Mixture Model (GMM) is learned to model the PG prior.\ The overall log-likelihood function is
-\vspace{-2mm}
+Assume that we have extracted a number of $N$ PGs from a set of external natural images, and the $n$-th PG is $\mathbf{\overline{X}}_{n}\triangleq \{\mathbf{\overline{x}}_{n,m}\}_{m=1}^{M}, n=1,...,N$.\ A Gaussian Mixture Model (GMM) is learned to model the PG prior.\ The overall log-likelihood function is
+\vspace{-3mm}
 \begin{equation}\label{equ1}\vspace{-2mm}
@@
 
-Assume we have assigned all the internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
+Assume that we have assigned all the internal noisy PGs $\{\mathbf{\overline{Y}}_{n}\}_{n=1}^{N}$ to their corresponding most suitable subspaces in $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$.
 For the $k$-th subspace, the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ where $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.\ We propose to learn an orthogonal dictionary $\mathbf{D}_{k}$ from each set of PGs $\mathbf{\overline{Y}}_{k_{n}}$ to characterize the internal PG prior with the guidance of the corresponding external orthogonal dictionary $\mathbf{U}_{k}$ (Eq.\ (\ref{equ2})).
@@
 \end{tabular}
-\end{center}\vspace{-2mm}
+\end{center}\vspace{-4mm}
 \end{table}

### 2016-11-14 CVPR2017_Review_Unified.tex
a

@@
 }\vspace{-1mm}
-\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods.\ The static scene was shot 500 times with the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR index can be computed.
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods.\ The scene was shot 500 times with the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR index can be computed.
 The images are better viewed by zooming in on screen.}
@@
 
-Image priors are playing a key role in image denoising \cite{ksvd,ncsr,pgpd,epll,ple,iraniinternal}.\ There are mainly two categories of prior learning methods.\ 1) External prior learning methods \cite{pgpd,foe,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from noisy images.\ 2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and image denoising is often done simultaneously with the prior learning process.\ It has been demonstrated \cite{pgpd,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.\ By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.\ In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images.
+Image priors are playing a key role in image denoising \cite{ksvd,ncsr,pgpd,foe,epll,ple,iraniinternal}.\ There are mainly two categories of prior learning methods.\ 1) External prior learning methods \cite{pgpd,foe,epll} learn priors (e.g., dictionaries) from a set of external clean images, and the learned priors are used to recover the latent clean image from the given noisy image.\ 2) Internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} directly learn priors from the given noisy image, and image denoising is often done simultaneously with the prior learning process.\ It has been demonstrated \cite{pgpd,foe,epll} that the external priors learned from natural clean images are effective and efficient for image denoising problem, but they are not adaptive to the given noisy image so that some fine-scale image structures may not be well recovered.\ By contrast, the internal priors are adaptive to content of the given image, but the learning processing are usually slow.\ In addition, most of the internal prior learning methods \cite{ksvd,ncsr,ple,iraniinternal} assume AWGN noise, making the learned priors less robust for real noisy images.
 In this paper, we use external priors to guide the internal prior learning.\ Our method is not only much faster than the traditional internal learning methods, but also very effective to denoise real noisy images.
@@
 
-Recently, several denoising methods have been proposed to remove unknown noise from images \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite}.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimates the noise distribution by using a multivariate Gaussian model and removes the noise by using a generalized version of nonlocal Bayesian model \cite{nlbayes}.
-Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods specifically designed for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The method in \cite{crosschannel2016} models the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by Bayesian nonlocal means.\ The commercial software Neat Image \cite{neatimage} estimates the noise parameters from a flat region of the given noisy image and filters the noise correspondingly.\ Almost all the methods mentioned above \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} use Gaussian or MoG to model the noise in real noisy images.\ Nonetheless, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.\ In this paper, we propose a simple yet effective denoising method for real noisy image denoising without explicitly assuming certain noise models.
+Recently, several denoising methods have been proposed to remove unknown noise from images \cite{Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite}.\ Among them, the ``Noise Clinic" \cite{noiseclinic,ncwebsite} estimates the noise distribution by using a multivariate Gaussian model and removes the noise by using a generalized version of nonlocal Bayesian model \cite{nlbayes}.
+Zhu \etal proposed a Bayesian method \cite{Zhu_2016_CVPR} to approximate and remove the noise via a low-rank mixture of Gaussians (MoG) model.\ There are also several methods specifically designed for real noisy image denoising \cite{crosschannel2016,neatimage}.\ The method in \cite{crosschannel2016} models the cross-channel noise in real noisy image as a multivariate Gaussian and the noise is removed by the Bayesian nonlocal means filter \cite{kervrann2007bayesian}.\ The commercial software Neat Image \cite{neatimage} estimates the noise parameters from a flat region of the given noisy image and filters the noise correspondingly.\ Almost all the methods \cite{crosschannel2016,Liu2008,almapg,Zhu_2016_CVPR,noiseclinic,ncwebsite} mentioned above use Gaussian or MoG to model the noise in real noisy images.\ Nonetheless, the noise in real noisy images is very complex and hard to be modeled by explicit distributions.\ In this paper, we propose a simple yet effective method for real noisy image denoising without explicitly assuming certain noise models.
 
@@
 
+\vspace{2mm}
 \subsection{Guided Internal Prior Learning}
@@
 
+\vspace{-2mm}
 \subsubsection{Internal Subspace Assignment}
 
-Given a real noisy image $\mathbf{y}$, we extract $N$ (overlapped) local patches from it.\ Similar to the external prior learning stage, for the $n$-th local patch we search its $M$ most similar patches around it to form a noisy PG, denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.\ Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is subtracted from each patch by $\mathbf{\overline{y}}_{n,m}=\mathbf{y}_{n,m}-\bm{\mu}_{n}$, leading to the mean subtracted noisy PG $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$.
+Given a real noisy image $\mathbf{y}$, we extract $N$ (overlapped) local patches from it.\ Similar to the external prior learning stage, for the $n$-th local patch we search its $M$ most similar patches around it to form a noisy PG, denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.\ Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is subtracted from each patch by $\mathbf{\overline{y}}_{n,m}\triangleq\mathbf{y}_{n,m}-\bm{\mu}_{n}$, leading to the mean subtracted noisy PG $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$.
 
 The external GMM prior models $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$ basically characterize the subspaces of natural high quality PGs.\ Therefore, we project the noisy PG $\mathbf{\overline{Y}}_{n}$ into the subspaces of $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$ and assign it to the most suitable subspace based on the posterior probability:
-\vspace{-2mm}
+\vspace{-3mm}
 \begin{equation}\label{equ3}\vspace{-2mm}
@@
 \end{equation}
-for $k=1,...,K$.\ Then $\mathbf{\overline{Y}}_{n}$ is assigned to the component with the maximum \emph{a}-posteriori (MAP) probability $\max_{k}P(k|\mathbf{\overline{Y}}_{n})$.
+for $k=1,...,K$.\ Then $\mathbf{\overline{Y}}_{n}$ is assigned to the subspace with the maximum \emph{a}-posteriori (MAP) probability $\max_{k}P(k|\mathbf{\overline{Y}}_{n})$.
 
+\vspace{-2mm}
 \subsubsection{Guided Orthogonal Dictionary Learning}
@@
 framework:
-\vspace{-3mm}
-\begin{equation}\label{equ4}\vspace{-3mm}
+\vspace{-2mm}
+\begin{equation}\label{equ4}\vspace{-2mm}
 \begin{split}
@@
 \end{equation}
-where $\mathbf{I}$ is the $3p^{2}$ dimensional identity matrix and $\bm{\alpha}_{n,m}$ is the sparse coding vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
+where $\mathbf{I}$ is the $3p^{2}$ dimensional identity matrix, $\bm{\alpha}_{n,m}$ is the sparse coding vector of the $m$-th patch $\mathbf{\overline{y}}_{n,m}$ in the $n$-th PG $\mathbf{\overline{Y}}_{n}$ and $\bm{\alpha}_{n,m,j}$ is the $j$-th element of $\bm{\alpha}_{n,m}$.
 $\lambda_{j}$ is the $j$-th regularization parameter defined as
-\vspace{-1mm}
-\begin{equation}\label{equ5}\vspace{-1mm}
+\vspace{-2mm}
+\begin{equation}\label{equ5}\vspace{-2mm}
 \lambda_{j} = \lambda/(\sqrt{\mathbf{S}_{k}(j)}+\varepsilon),
@@
 %\vspace{-2mm}
-%\begin{equation}\label{equ6}\vspace{-1mm}
+%\begin{equation}\label{equ6}\vspace{-2mm}
 %\mathbf{D}^{\top}\mathbf{D} = 
@@
 \end{equation}
-where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\text{sgn}(\bullet)$ is the sign function, $\odot$ means element-wise multiplication.\ The detailed derivation of Eq.
+where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter, $\text{sgn}(\bullet)$ is the sign function and $\odot$ means element-wise multiplication.\ The detailed derivation of Eq.
 (\ref{equ7}) can be found in the supplementary file.
@@
 \textbf{Updating Internal Sub-dictionary}: Given the sparse coding vectors $\{\bm{\alpha}_{n,m}^{(t)}\}$, we update the internal sub-dictionary by solving
-\vspace{-2mm}
+\vspace{-4mm}
 \begin{equation}\label{equ8} \vspace{-2mm}
@@
 \argmin_{\textbf{D}_{\text{I}}}
-\sum_{n=1}^{N}\sum_{m=1}^{M}(\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2})
+\sum_{n=1}^{N}\sum_{m=1}^{M}\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}\bm{\alpha}_{n,m}^{(t)}\|_{2}^{2}
 \\
@@
 \end{equation}
-where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$ and $\mathbf{I}_{r}$ is the $r$ dimensional identity matrix.\ The sparse coefficient matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.\ According to the Theorem 4 in \cite{spca}, the problem (\ref{equ8}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times r}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{r\times r}$ are the orthogonal matrices obtained by the following SVD
-\vspace{-1mm}
-\begin{equation}\label{equ9}\vspace{-1mm}
+where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$ and $\mathbf{I}_{r}$ is the $r$ dimensional identity matrix.\ The sparse coefficients matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.\ According to the Theorem 4 in \cite{spca}, the problem (\ref{equ8}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{(3p^2-r)\times (3p^2-r)}$ are the orthogonal matrices obtained by the following SVD
+\vspace{-2mm}
+\begin{equation}\label{equ9}\vspace{-2mm}
 (\mathbf{I}-\mathbf{D}_{\text{E}}\mathbf{D}_{\text{E}}^{\top})\mathbf{Y}(\mathbf{A}_{\text{I}}^{(t)})^{\top}
@@
 The orthogonality of internal dictionary $\mathbf{D}_{\text{I}}^{(t+1)}$ can be checked by 
-$(\mathbf{D}_{\text{I}}^{(t+1)})^{\top}(\mathbf{D}_{\text{I}}^{(t+1)})=\mathbf{V}_{\text{I}}\mathbf{U}_{\text{I}}^{\top}\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}=\mathbf{I}_{r}$.
+$(\mathbf{D}_{\text{I}}^{(t+1)})^{\top}(\mathbf{D}_{\text{I}}^{(t+1)})=\mathbf{V}_{\text{I}}\mathbf{U}_{\text{I}}^{\top}\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}=\mathbf{I}_{(3p^2-r)}$ where $\mathbf{I}_{(3p^2-r)}$ is the $3p^2-r$ dimensional identity matrix.
 
@@
 The denoising of the given noisy image $\mathbf{y}$ can be simultaneously done with the guided internal dictionary learning process.
-Once we obtain the solutions of sparse coding vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.\ (\ref{equ7}) and the orthogonal dictionary $\mathbf{D}^{(T)} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{(T)}]$ in Eq.
-(\ref{equ8}), the latent clean patch of a noisy patch $\hat{\mathbf{y}}_{n,m}$ in PG $\mathbf{Y}_{n}$ is reconstructed as
+Once we obtain the solutions of sparse coding vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.\ (\ref{equ7}) and the orthogonal dictionary $\mathbf{D}^{(T)} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{(T)}]$ in Eq.\ (\ref{equ8}), the latent clean patch $\hat{\mathbf{y}}_{n,m}$ of the $m$-th noisy patch in PG $\mathbf{Y}_{n}$ is reconstructed as
 \vspace{-2mm}
@@
 \\
-1. Extracting internal PGs from $\hat{\mathbf{x}}^{(Ite-1)}$;
+1. Extracting internal PGs $\{\mathbf{Y}_{n}\}_{n=1}^{N}$ from $\hat{\mathbf{x}}^{(Ite-1)}$;
 \\
@@
 We compare the three methods mentioned above on the 60 cropped images from \cite{crosschannel2016}.\ The average PSNR and run time are listed in Table \ref{tab1}.\ The best results are highlighted in bold.\ It can be seen that ``Guided Internal" prior achieves better PSNR than both ``External" and ``Internal" priors.
-In addition, the ``Internal" method is very slow because it involves online GMM learning, while the ``Guided Internal" method is only a little slower than the ``External" method.\ Fig.\ \ref{fig4} and Fig.\ \ref{fig5} show the denoised images of two noisy image by the three methods.\ We can see that the  ``External" method is good at recovering large-scale structures (see Fig.\ \ref{fig4}) while the ``Internal" method is good at recovering fine-scale textures (see Fig.\ \ref{fig5}).\ By utilizing external priors to guide the internal prior learning, our proposed method can effectively recover both the large-scale structures and fine-scale textures.
+In addition, the ``Internal" method is very slow because it involves online GMM learning, while the ``Guided Internal" method is only a little slower than the ``External" method.\ Fig.\ \ref{fig4} and Fig.\ \ref{fig5} show the denoised images of two noisy images by the three methods.\ We can see that the  ``External" method is good at recovering large-scale structures (see Fig.\ \ref{fig4}) while the ``Internal" method is good at recovering fine-scale textures (see Fig.\ \ref{fig5}).\ By utilizing external priors to guide the internal prior learning, our proposed method can effectively recover both the large-scale structures and fine-scale textures.
 
@@
 }\vspace{-1mm}
-\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \label{fig7}
@@
 \small
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{egbib}

### 2016-11-14 CVPR2017_Review_Unified.tex
add

@@
 Each patch is stretched to a patch vector $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ to form the PG $\{\mathbf{x}_{m}\}_{m=1}^{M}$.
-The mean vector of this PG is $\bm{\mu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\bm{\mu}\}$.
+The mean vector of this PG is $\bm{\mu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\bm{\mu}\}_{m=1}^{M}$.
 
@@
 \end{equation}
-The eigenvector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ will be employed as the external orthogonal dictionary to guide the internal dictionary learning in next sub-section.\ The singular values in $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$.\ They  will also be utilized as prior weights for weighted sparse coding in our denoising algorithm.
+The eigenvector matrices $\{\mathbf{U}_{k}\}_{k=1}^{K}$ will be employed as the external orthogonal dictionary to guide the internal sub-dictionary learning in next sub-section.\ The singular values in $\mathbf{S}_{k}$ reflect the significance of the singular vectors in $\mathbf{U}_{k}$.\ They  will also be utilized as prior weights for weighted sparse coding in our denoising algorithm.
 
@@
 
-The external GMM prior models $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$ basically characterize the subspaces of natural high quality PGs.\ Therefore, we project the noisy PG $\mathbf{\overline{Y}}_{n}$ into the subspaces of $\{\mathbf{\Sigma}_{k}\}_{k=1}^{K}$ and assign it to the most suitable subspace based on the posterior probability:
+The external GMM prior models $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$ basically characterize the subspaces of natural high quality PGs.\ Therefore, we project the noisy PG $\mathbf{\overline{Y}}_{n}$ into the subspaces of $\{\mathcal{N}(\mathbf{0},\mathbf{\Sigma}_{k})\}_{k=1}^{K}$ and assign it to the most suitable subspace based on the posterior probability:
 \vspace{-3mm}
@@
 For the $k$-th subspace, the noisy PGs assigned to it are $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ where $\mathbf{\overline{Y}}_{k_{n}}=[\mathbf{\overline{y}}_{k_{n},1},...,\mathbf{\overline{y}}_{k_{n},M}]$ and $\sum_{k=1}^{K}N_{k}=N$.\ We propose to learn an orthogonal dictionary $\mathbf{D}_{k}$ from each set of PGs $\mathbf{\overline{Y}}_{k_{n}}$ to characterize the internal PG prior with the guidance of the corresponding external orthogonal dictionary $\mathbf{U}_{k}$ (Eq.\ (\ref{equ2})).
-The reasons that we learn orthogonal dictionaries are two-fold.\ Firstly, the PGs $\mathbf{\overline{Y}}_{k_{n}}$ are in a subspace of the whole space of all PGs; therefore, there is no necessary to learn a redundant over-complete dictionary to characterize it, while an orthonormal dictionary has naturally zero \emph{mutual incoherence} \cite{donoho2001uncertainty}.
+The reasons that we learn orthogonal dictionaries are two-fold.\ Firstly, the PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$ are in a subspace of the whole space of all PGs; therefore, there is no necessary to learn a redundant over-complete dictionary to characterize it, while an orthonormal dictionary has naturally zero \emph{mutual incoherence} \cite{donoho2001uncertainty}.
 Secondly, the orthogonality of dictionary can make the encoding in the testing stage very efficient, leading to an efficient denoising algorithm (please refer to sub-section 3.3 for more details).
@@
 We employ an alternating iterative approach to solve the optimization problem (\ref{equ4}).
-Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{k}$ and for $t=0,1, ...,T-1$, we alternatively update $\bm{\alpha}_{n,m}$ and $\mathbf{D}$ as follows.
+Specifically, we initialize the orthogonal dictionary as $\mathbf{D}^{(0)}=\mathbf{U}_{k}$ and for $t=0,1, ...,T-1$, we alternatively update $\bm{\alpha}_{n,m}$ and $\mathbf{D}_{\text{I}}$ as follows.
 \vspace{2mm}\\
@@
 \end{equation}
-where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$ and $\mathbf{I}_{r}$ is the $r$ dimensional identity matrix.\ The sparse coefficients matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}$, respectively.\ According to the Theorem 4 in \cite{spca}, the problem (\ref{equ8}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{(3p^2-r)\times (3p^2-r)}$ are the orthogonal matrices obtained by the following SVD
+where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$ and $\mathbf{I}_{r}$ is the $r$ dimensional identity matrix.\ The sparse coefficients matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}^{(t)}$, respectively.\ According to the Theorem 4 in \cite{spca}, the problem (\ref{equ8}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{(3p^2-r)\times (3p^2-r)}$ are the orthogonal matrices obtained by the following SVD
 \vspace{-2mm}
@@
 \end{equation}
-The orthogonality of internal dictionary $\mathbf{D}_{\text{I}}^{(t+1)}$ can be checked by 
+The orthogonality of internal sub-dictionary $\mathbf{D}_{\text{I}}^{(t+1)}$ can be checked by 
 $(\mathbf{D}_{\text{I}}^{(t+1)})^{\top}(\mathbf{D}_{\text{I}}^{(t+1)})=\mathbf{V}_{\text{I}}\mathbf{U}_{\text{I}}^{\top}\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}=\mathbf{I}_{(3p^2-r)}$ where $\mathbf{I}_{(3p^2-r)}$ is the $3p^2-r$ dimensional identity matrix.
@@
 
-The denoising of the given noisy image $\mathbf{y}$ can be simultaneously done with the guided internal dictionary learning process.
+The denoising of the given noisy image $\mathbf{y}$ can be simultaneously done with the guided internal sub-dictionary learning process.
 Once we obtain the solutions of sparse coding vectors $\{\hat{\bm{\alpha}}_{n,m}^{(T-1)}\}$ in Eq.\ (\ref{equ7}) and the orthogonal dictionary $\mathbf{D}^{(T)} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{(T)}]$ in Eq.\ (\ref{equ8}), the latent clean patch $\hat{\mathbf{y}}_{n,m}$ of the $m$-th noisy patch in PG $\mathbf{Y}_{n}$ is reconstructed as
@@
 \begin{equation}\label{equ10}\vspace{-2mm}
-\hat{\mathbf{y}}_{n,m}=\mathbf{D}^{(T)}\hat{\bm{\alpha}}_{n,m}+\bm{\mu}_{n},
+\hat{\mathbf{y}}_{n,m}=\mathbf{D}^{(T)}\hat{\bm{\alpha}}_{n,m}^{(T-1)}+\bm{\mu}_{n},
 \end{equation}
@@
 %\\
-\quad\textbf{for} the PGs in each Subspace \textbf{do}
+\quad\textbf{for} the PGs in each subspace \textbf{do}
 \\
-4.\quad External PG prior Guided Internal Orthogonal
+4.\quad External PG prior guided internal orthogonal
 \\
-\quad \ \ \ Dictionary Learning by solving (\ref{equ4});
+\quad \ \ \ dictionary learning by solving (\ref{equ4});
 \\
@@
 
-In the second stage, we set $r = 54$ (the number of atoms in the external sub-dictionaries); that is, we let the external sub-dictionary have the same number of atoms as the internal sub-dictionary to be learned.
+In the second stage, we set $r = 54$ (the number of atoms in the external sub-dictionaries); that is, we let the external sub-dictionaries have the same number of atoms as the internal sub-dictionaries to be learned.
 Our experiments show that setting $r$ between 27 and 81 will lead to very similar results.
@@
 
-To demonstrate the advantages of external prior guided internal priors, in this section we perform real noisy image denoising by using external priors (denoted by ``External"), internal priors (denoted by ``Internal"), and the proposed guided internal priors (denoted by ``Guided Internal"), respectively.\ For the ``External" method, we utilize the full external dictionaries (i.e., $r=108$ in Eq.\ (\ref{equ4})) for denoising.\ For the ``Internal" method, the overall framework is similar to the method of \cite{ncsr}.\ A GMM model (with $K = 32$ Gaussians) is directly learned from the PGs extracted from the given noisy image without using any external data, and then the internal orthogonal dictionary is obtained via Eq.\ (\ref{equ2}) to perform denoising.\ All parameters of the ``External" and ``Internal" methods are tuned to achieve their corresponding best performance.
+To demonstrate the advantages of external prior guided internal prior learning, in this section we perform real noisy image denoising by methods using external priors (denoted by ``External"), internal priors (denoted by ``Internal"), and the proposed guided internal priors (denoted by ``Guided Internal"), respectively.\ For the ``External" method, we utilize the full external dictionaries (i.e., $r=108$ in Eq.\ (\ref{equ4})) for denoising.\ For the ``Internal" method, the overall framework is similar to the method of \cite{ncsr}.\ A GMM model (with $K = 32$ Gaussians) is directly learned from the PGs extracted from the given noisy image without using any external data, and then the internal orthogonal dictionaries are obtained via Eq.\ (\ref{equ2}) to perform denoising.\ All parameters of the ``External" and ``Internal" methods are tuned to achieve their corresponding best performance.
 
-We compare the three methods mentioned above on the 60 cropped images from \cite{crosschannel2016}.\ The average PSNR and run time are listed in Table \ref{tab1}.\ The best results are highlighted in bold.\ It can be seen that ``Guided Internal" prior achieves better PSNR than both ``External" and ``Internal" priors.
+We compare the three methods mentioned above on the 60 cropped images from \cite{crosschannel2016}.\ The average PSNR and run time are listed in Table \ref{tab1}.\ The best results are highlighted in bold.\ It can be seen that ``Guided Internal" method achieves better PSNR than both ``External" and ``Internal" methods.
 In addition, the ``Internal" method is very slow because it involves online GMM learning, while the ``Guided Internal" method is only a little slower than the ``External" method.\ Fig.\ \ref{fig4} and Fig.\ \ref{fig5} show the denoised images of two noisy images by the three methods.\ We can see that the  ``External" method is good at recovering large-scale structures (see Fig.\ \ref{fig4}) while the ``Internal" method is good at recovering fine-scale textures (see Fig.\ \ref{fig5}).\ By utilizing external priors to guide the internal prior learning, our proposed method can effectively recover both the large-scale structures and fine-scale textures.

### 2016-11-14 1047_sp.tex
add

\documentclass[10pt,onecolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{upgreek}
\usepackage{multirow}
\usepackage{color}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{1047} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi

\begin{document}

%%%%%%%%% TITLE
\title{Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle

%%%%%%%%% BODY TEXT
In this supplementary material, we provide:\vspace{-0.1in}
\begin{enumerate}
\item The closed-form solution of the proposed weighted sparse coding model in the main paper.\vspace{-0.1in}
\item Comparison of the \textsl{Patch Prior based Denoising} (PPD) method and the proposed \textsl{Patch Group Prior based Denoising} (PGPD) method.\vspace{-0.1in}
\item More denoising results on the 20 widely used natural images. \vspace{-0.1in}
\item The denoising results of the competing methods on the Berkeley Segmentation Data Set \cite{bsds}.
\end{enumerate}
\section{Closed-Form Solution of the Weighted Sparse Coding Problem}
The weighted sparse coding problem in the main paper is:
\begin{equation}\label{equ1}
\setlength{\abovedisplayskip}{1pt}
\setlength{\belowdisplayskip}{1pt}
\min_{\boldsymbol{\alpha}}\|\mathbf{y}-\mathbf{D}\boldsymbol{\alpha}\|_{2}^{2}+\|\mathbf{w}^{T}\boldsymbol{\alpha}\|_{1}.
\end{equation}
Since $\mathbf{D}$ is an orthonormal matrix, problem (\ref{equ1}) is equivalent to 
\begin{equation}\label{equ2}
\setlength{\abovedisplayskip}{1pt}
\setlength{\belowdisplayskip}{1pt}
\min_{\boldsymbol{\alpha}}\|\mathbf{D}^{T}\mathbf{y}-\boldsymbol{\alpha}\|_{2}^{2}+\|\mathbf{w}^{T}\boldsymbol{\alpha}\|_{1}.
\end{equation}
For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$. Since $\mathbf{w}_{i}=c*2\sqrt{2}\sigma^{2}/(\mathbf{\Lambda}_{i}+\varepsilon)$ is positive (please refer to Eq. (18) in the main paper), problem (\ref{equ2}) can be written as
\begin{equation}\label{equ3}
\setlength{\abovedisplayskip}{0.01pt}
\setlength{\belowdisplayskip}{0.01pt}
\min_{\boldsymbol{\alpha}}\sum_{i=1}^{p^{2}}((\mathbf{z}_{i}-\boldsymbol{\alpha}_{i})^{2}+\mathbf{w}_{i}|\boldsymbol{\alpha}_{i}|).
\end{equation}
The problem (\ref{equ3}) is separable w.r.t. $\boldsymbol{\alpha}_{i}$ and can be simplified to $p^{2}$ scalar minimization problems
\begin{equation}\label{equ4}
\setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{1pt}
\min_{\boldsymbol{\alpha}_{i}}(\mathbf{z}_{i}-\boldsymbol{\alpha}_{i})^{2}+\mathbf{w}_{i}|\boldsymbol{\alpha}_{i}|,
\end{equation}
where $i=1,...,p^{2}$. Taking derivative of $\boldsymbol{\alpha}_{i}$ in problem (\ref{equ4}) and setting the derivative to be zero. There are two cases for the solution.

(a) If $\boldsymbol{\alpha}_{i}\ge 0$, we have
\begin{equation}\label{equ5}
\setlength{\abovedisplayskip}{0.1pt}
\setlength{\belowdisplayskip}{0.11pt}
2(\boldsymbol{\alpha}_{i}-\mathbf{z}_{i})+\mathbf{w}_{i}=0.
\end{equation}
\qquad\ \  The solution is
\begin{equation}\label{equ6}
\setlength{\abovedisplayskip}{0.1pt}
\setlength{\belowdisplayskip}{0.1pt}
\hat{\boldsymbol{\alpha}}_{i}=\mathbf{z}_{i}-\frac{\mathbf{w}_{i}}{2} \ge 0.
\end{equation}
\qquad\ \  So $\mathbf{z}_{i}\ge\frac{\mathbf{w}_{i}}{2}> 0$, and the solution $\hat{\boldsymbol{\alpha}}_{i}$ can be written as
\begin{equation}\label{equ7}
\setlength{\abovedisplayskip}{0.1pt}
\setlength{\belowdisplayskip}{0.1pt}
\hat{\boldsymbol{\alpha}}_{i}=\text{sgn}(\mathbf{z}_{i})*(|\mathbf{z}_{i}|-\frac{\mathbf{w}_{i}}{2}),
\end{equation}
\qquad\ \  where $\text{sgn}(\bullet)$ is the sign function.

(b) If $\boldsymbol{\alpha}_{i}< 0$, we have
\begin{equation}\label{equ8}
\setlength{\abovedisplayskip}{0.1pt}
\setlength{\belowdisplayskip}{0.1pt}
2(\boldsymbol{\alpha}_{i}-\mathbf{z}_{i})-\mathbf{w}_{i}=0.
\end{equation}
\qquad\ \  The solution is
\begin{equation}\label{equ9}
\setlength{\abovedisplayskip}{0.1pt}
\setlength{\belowdisplayskip}{0.1pt}
\hat{\boldsymbol{\alpha}}_{i}=\mathbf{z}_{i}+\frac{\mathbf{w}_{i}}{2} < 0.
\end{equation}
\qquad\ \  So $\mathbf{z}_{i}<-\frac{\mathbf{w}_{i}}{2}< 0$, and the solution $\hat{\boldsymbol{\alpha}}_{i}$ can be written as
\begin{equation}\label{equ10}
\setlength{\abovedisplayskip}{1pt}
\setlength{\belowdisplayskip}{1pt}
\hat{\boldsymbol{\alpha}}_{i}=\text{sgn}(\mathbf{z}_{i})*(-\mathbf{z}_{i}-\frac{\mathbf{w}_{i}}{2})=\text{sgn}(\mathbf{z}_{i})*(|\mathbf{z}_{i}|-\frac{\mathbf{w}_{i}}{2}).
\end{equation}

In summary, we have the final solution of the weighted sparse coding problem (\ref{equ1}) as
\begin{equation}\label{equ11}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}
\hat{\boldsymbol{\alpha}}= \text{sgn}(\mathbf{D^{T}y})\odot \text{max}(|\mathbf{D^{T}y}|-\mathbf{w}/2,0),
\end{equation}
where $\odot$ means element-wise multiplication and $|\mathbf{D^{T}y}|$ is the absolute value of each entry of the vector $\mathbf{D^{T}y}$.

\begin{figure}\label{fig1}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (b) CBM3D \cite{cbm3d} \\ (33.33dB/0.8935)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (d) MLP \cite{mlp}\\ (34.22dB/0.9603) }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (e) CSF \cite{csf}\\ (35.39dB/0.9677) }
\end{minipage}
}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (f) TRD \cite{chen2015learning} \\ (35.97dB/0.9705)   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (g) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (h) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (i) Ours \\ (\textbf{37.28}dB/\textbf{0.9729})  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
{\footnotesize (j) Mean Image }
\end{minipage}
}
\caption{Denoised images of the real noisy image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
\end{figure}

{\small
\bibliographystyle{unsrt}
\bibliography{egbib}
}

\end{document}

### 2016-11-15 CVPR2017_Review_Unified.tex
add

@@
 \textbf{Updating Internal Sub-dictionary}: Given the sparse coding vectors $\{\bm{\alpha}_{n,m}^{(t)}\}$, we update the internal sub-dictionary by solving
-\vspace{-4mm}
+\vspace{-3mm}
 \begin{equation}\label{equ8} \vspace{-2mm}
@@
 =
-[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}],\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{I}_{r},\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{0},
+[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}],\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{I}_{(3p^2-r)},\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}} = \mathbf{0},
 \end{split}
 \end{equation}
-where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$ and $\mathbf{I}_{r}$ is the $r$ dimensional identity matrix.\ The sparse coefficients matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}^{(t)}$, respectively.\ According to the Theorem 4 in \cite{spca}, the problem (\ref{equ8}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{(3p^2-r)\times (3p^2-r)}$ are the orthogonal matrices obtained by the following SVD
+where $\textbf{A}^{(t)}=[\bm{\alpha}_{1,1}^{(t)},...,\bm{\alpha}_{1,M}^{(t)},...,\bm{\alpha}_{N,1}^{(t)},...,\bm{\alpha}_{N,M}^{(t)}]$ and $\mathbf{I}_{(3p^2-r)}$ is the $(3p^2-r)$ dimensional identity matrix.\ The sparse coefficients matrix can be written as $\mathbf{A}^{(t)}=[(\mathbf{A}_{\text{E}}^{(t)})^{\top}\ (\mathbf{A}_{\text{I}}^{(t)})^{\top}]^{\top}$ where the external part $\mathbf{A}_{\text{E}}^{(t)}\in\mathbb{R}^{r\times NM}$ and the internal part $\mathbf{A}_{\text{I}}^{(t)}\in\mathbb{R}^{(3p^2-r)\times NM}$ represent the coding coefficients of $\mathbf{Y}$ over external sub-dictionary $\mathbf{D}_{\text{E}}$ and internal sub-dictionary $\mathbf{D}_{\text{I}}^{(t)}$, respectively.\ According to the Theorem 4 in \cite{spca}, the problem (\ref{equ8}) has a closed-form solution $\mathbf{D}_{\text{I}}^{(t+1)}=\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}$, where $\mathbf{U}_{\text{I}}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ and $\mathbf{V}_{\text{I}}\in\mathbb{R}^{(3p^2-r)\times (3p^2-r)}$ are the orthogonal matrices obtained by the following SVD
 \vspace{-2mm}
@@
 The orthogonality of internal sub-dictionary $\mathbf{D}_{\text{I}}^{(t+1)}$ can be checked by 
-$(\mathbf{D}_{\text{I}}^{(t+1)})^{\top}(\mathbf{D}_{\text{I}}^{(t+1)})=\mathbf{V}_{\text{I}}\mathbf{U}_{\text{I}}^{\top}\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}=\mathbf{I}_{(3p^2-r)}$ where $\mathbf{I}_{(3p^2-r)}$ is the $3p^2-r$ dimensional identity matrix.
-
+$(\mathbf{D}_{\text{I}}^{(t+1)})^{\top}(\mathbf{D}_{\text{I}}^{(t+1)})=\mathbf{V}_{\text{I}}\mathbf{U}_{\text{I}}^{\top}\mathbf{U}_{\text{I}}\mathbf{V}_{\text{I}}^{\top}=\mathbf{I}_{(3p^2-r)}$.
 %In Fig. \ref{fig3} (c) and (d), we illustrate a denoised image by our proposed method and one internal orthogonal dictionary learned from PGs of the given noisy image.

### 2016-11-15 CVPR2017_Review_Unified.tex
add

@@
 
-In the second stage, we set $r = 54$ (the number of atoms in the external sub-dictionaries); that is, we let the external sub-dictionaries have the same number of atoms as the internal sub-dictionaries to be learned.
-Our experiments show that setting $r$ between 27 and 81 will lead to very similar results.
-For other parameters, we set $\lambda=0.001$ (the sparse regularization parameter), $T = 2$ (the number of iterations for solving problem (\ref{equ4})), and $IteNum = 4$ (the number of iterations for Alg.1).
-All parameters of our method are fixed to all experiments, which are run under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.
+In the second stage, we set $r = 54$ (the number of atoms in the external sub-dictionaries); that is, we let the external sub-dictionaries have the same number of atoms as the internal sub-dictionaries to be learned.\ Our experiments show that setting $r$ between 27 and 81 will lead to very similar results.\ For other parameters, we set $\lambda=0.001$ (the sparse regularization parameter), $T = 2$ (the number of iterations for solving problem (\ref{equ4})), and $IteNum = 4$ (the number of iterations for Alg.1).\ All parameters of our method are fixed to all experiments, which are run under the Matlab2014b environment on a machine with Intel(R) Core(TM) i7-5930K CPU of 3.5GHz and 32GB RAM.
 
@@
 
-Like our method, the NC is a blind image denoising method which does not need any noise prior.\ The NI is a commercial software for image denoising, which has been embedded into Photoshop and Corel PaintShop \cite{neatimage}.\ The code of CC is not released but its results on the 15 cropped images are available at \cite{crosschannel2016}.
-Therefore, we only compare with it on the 15 cropped images from \cite{crosschannel2016}.
+Like our method, the NC is a blind image denoising method which does not need any noise prior.\ The NI is a commercial software for image denoising, which has been embedded into Photoshop and Corel PaintShop \cite{neatimage}.\ The code of CC is not released but its results on the 15 cropped images are available at \cite{crosschannel2016}.\ Therefore, we only compare with it on the 15 cropped images from \cite{crosschannel2016}.
 
@@
 It can be seen that CBM3D and WNNM tend to over-smooth much the image while remaining some noise caused color artifacts.\ MLP and TNRD are likely to remain many noise-caused color artifacts across the whole image.
-These results demonstrate that the methods designed with Gaussian noise model are not effective for real noise removal.\ Though NC and NI methods are specifically developed for real noisy images, their performance on noise removal is not very satisfactory.
-In comparison, our proposed method recovers much better the structures and textures (such as the eye area) than the other competing methods.
-More visual comparisons on this dataset \cite{ncwebsite} can be found in the supplementary file.
+These results demonstrate that the methods designed with Gaussian noise model are not effective for real noise removal.\ Though NC and NI methods are specifically developed for real noisy images, their performance on noise removal is not very satisfactory.\ In comparison, our proposed method recovers much better the structures and textures (such as the eye area) than the other competing methods.\ More visual comparisons on this dataset \cite{ncwebsite} can be found in the supplementary file.
 

### 2016-11-15 CVPR2017_Review_Unified.tex
add

@@
 
-Given a real noisy image $\mathbf{y}$, we extract $N$ (overlapped) local patches from it.\ Similar to the external prior learning stage, for the $n$-th local patch we search its $M$ most similar patches around it to form a noisy PG, denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.\ Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is subtracted from each patch by $\mathbf{\overline{y}}_{n,m}\triangleq\mathbf{y}_{n,m}-\bm{\mu}_{n}$, leading to the mean subtracted noisy PG $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$.
+Given a real noisy image $\mathbf{y}$, we extract $N$ (overlapped) local patches from it.\ Similar to the external prior learning stage, for the $n$-th ($n=1,...,N$) local patch we search its $M$ most similar patches around it to form a noisy PG, denoted by $\mathbf{Y}_{n} = \{\mathbf{y}_{n,1},...,\mathbf{y}_{n,M}\}$.\ Then the group mean of $\mathbf{Y}_{n}$, denoted by $\bm{\mu}_{n}$, is subtracted from each patch by $\mathbf{\overline{y}}_{n,m}\triangleq\mathbf{y}_{n,m}-\bm{\mu}_{n}$, leading to the mean subtracted noisy PG $\mathbf{\overline{Y}}_{n}\triangleq \{\mathbf{\overline{y}}_{n,m}\}_{m=1}^{M}$.
 

### 2016-11-15 CVPR2017_Review_Unified.tex
a

@@
 
-\vspace{-2mm}
+\vspace{-3mm}
 \subsubsection{Guided Orthogonal Dictionary Learning}
@@
 
-We let the orthogonal dictionary $\mathbf{D}_{k}$ be $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,\text{E}}\ \mathbf{D}_{k,\text{I}}]\in \mathbb{R}^{3p^2\times 3p^2}$, where $\mathbf{D}_{k,\text{E}}=\mathbf{U}_{k}(:,1:r)\in\mathbb{R}^{3p^2\times r}$ is the external sub-dictionary and it includes the first $r$ most important eigenvectors of $\mathbf{U}_{k}$, and the internal sub-dictionary $\mathbf{D}_{k,\text{I}}$ is to be adaptively learned from the noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.\ The rationale to design $\mathbf{D}_{k}$ as a hybrid dictionary is as follows.\ The external sub-dictionary $\mathbf{D}_{k,\text{E}}$ is pre-trained from external clean data, and it represents the $k$-th latent subspace of natural images, which is helpful to reconstruct the common latent structures of images.
+We let the orthogonal dictionary $\mathbf{D}_{k}$ be $\mathbf{D}_{k}\triangleq[\mathbf{D}_{k,\text{E}}\ \mathbf{D}_{k,\text{I}}]\in \mathbb{R}^{3p^2\times 3p^2}$, where $\mathbf{D}_{k,\text{E}}=\mathbf{U}_{k}(:,1:r)\in\mathbb{R}^{3p^2\times r}$ is the external sub-dictionary and it includes the first $r$ most important eigenvectors of $\mathbf{U}_{k}$, and the internal sub-dictionary $\mathbf{D}_{k,\text{I}}\in\mathbb{R}^{3p^2\times (3p^2-r)}$ is to be adaptively learned from the noisy PGs $\{\mathbf{\overline{Y}}_{k_{n}}\}_{n=1}^{N_{k}}$.\ The rationale to design $\mathbf{D}_{k}$ as a hybrid dictionary is as follows.\ The external sub-dictionary $\mathbf{D}_{k,\text{E}}$ is pre-trained from external clean data, and it represents the $k$-th latent subspace of natural images, which is helpful to reconstruct the common latent structures of images.
 However, $\mathbf{D}_{k,\text{E}}$ is general to all images and it is not adaptive to the given noisy image.\ Some fine-scale details specific to the given image may not be well characterized by $\mathbf{D}_{k,\text{E}}$.

### 2016-11-15 1047_sp.tex
add

@@
 \begin{enumerate}
-\item The closed-form solution of the proposed weighted sparse coding model in the main paper.\vspace{-0.1in}
-\item Comparison of the \textsl{Patch Prior based Denoising} (PPD) method and the proposed \textsl{Patch Group Prior based Denoising} (PGPD) method.\vspace{-0.1in}
-\item More denoising results on the 20 widely used natural images. \vspace{-0.1in}
-\item The denoising results of the competing methods on the Berkeley Segmentation Data Set \cite{bsds}.
+\item The closed-form solution of the proposed weighted sparse coding model in the main paper.
+\vspace{-0.1in}
+\item More denoising results on the 20 real noisy images (with no ``ground truth") provided in the dataset \cite{ncwebsite}.
+\vspace{-0.1in}
+\item More denoising results on the 15 smaller real noisy images (with ``ground truth") used in the dataset \cite{crosschannel2016}.
+\vspace{-0.1in}
+\item More denoising results on the 60 real noisy images (with ``ground truth") cropped from \cite{crosschannel2016}.
 \end{enumerate}

### 2016-11-15 1047_sp.tex
ad

@@
 \vspace{-0.1in}
-\item More denoising results on the 20 real noisy images (with no ``ground truth") provided in the dataset \cite{ncwebsite}.
+\item More denoising results on the 20 real noisy imagessupp (with no ``ground truth") provided in the dataset \cite{ncwebsite}.
 \vspace{-0.1in}
-\item More denoising results on the 15 smaller real noisy images (with ``ground truth") used in the dataset \cite{crosschannel2016}.
+\item More denoising results on the 15 smaller real noisy imagessupp (with ``ground truth") used in the dataset \cite{crosschannel2016}.
 \vspace{-0.1in}
-\item More denoising results on the 60 real noisy images (with ``ground truth") cropped from \cite{crosschannel2016}.
+\item More denoising results on the 60 real noisy imagessupp (with ``ground truth") cropped from \cite{crosschannel2016}.
 \end{enumerate}
@@
 
-\begin{figure}\label{fig1}
+\begin{figure}
 \centering
 \subfigure{
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.33\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (a) Noisy Image \\ (33.30dB/0.8921) }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_noisy.png}}
+{\footnotesize (a) Noisy Image \cite{ncwebsite}  }
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.33\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (b) CBM3D \cite{cbm3d} \\ (33.33dB/0.8935)  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_cbm3d.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d} }
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.33\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (c) WNNM \cite{wnnm}\\ (33.30dB/0.8922)  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_wnnm.png}}
+{\footnotesize (c) WNNM \cite{wnnm}  }
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.33\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (d) MLP \cite{mlp}\\ (34.22dB/0.9603) }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_mlp.png}}
+{\footnotesize (d) MLP \cite{mlp} }
 \end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
+\begin{minipage}[t]{0.33\textwidth}
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (e) CSF \cite{csf}\\ (35.39dB/0.9677) }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_csf.png}}
+{\footnotesize (e) CSF \cite{csf} }
 \end{minipage}
+\begin{minipage}[t]{0.33\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_tnrd.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}  }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.33\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ni.png}}
+{\footnotesize (g) Neat Image \cite{neatimage}   }
+\end{minipage}
+\begin{minipage}[t]{0.33\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_nc.png}}
+{\footnotesize (h) Noise Clinic \cite{noiseclinic,ncwebsite} }
+\end{minipage}
+\begin{minipage}[t]{0.33\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ours.png}}
+{\footnotesize (i) Ours  }
+\end{minipage}
+}\vspace{-3mm}
+\caption{
+\vspace{-0.3mm}
+(a) A real noisy image captured by a digital camera \cite{ncwebsite}. (b)$\sim$(i) Denoised imagessupp by different methods.
+\vspace{-0.3mm}
+Among them, CBM3D \cite{bm3d,cbm3d} and WNNM \cite{wnnm} are prior model based methods; MLP \cite{mlp}, CSF \cite{csf} and TNRD 
+\vspace{-0.3mm}
+\cite{chen2015learning} are discriminative learning based methods; and Neat Image \cite{neatimage} and Noise Clinic \cite{noiseclinic,ncwebsite} are methods designed 
+\vspace{-0.3mm}
+for real noisy imagessupp. Clearly, our method produces a cleaner image.
 }
-\subfigure{
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (f) TRD \cite{chen2015learning} \\ (35.97dB/0.9705)   }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (g) Noise Clinic \cite{noiseclinic} \\ (35.33dB/0.9520)  }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (h) Neat Image \cite{neatimage}\\ (34.39dB/0.9314)  }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (i) Ours \\ (\textbf{37.28}dB/\textbf{0.9729})  }
-\end{minipage}
-\begin{minipage}[t]{0.195\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_66.png}}
-{\footnotesize (j) Mean Image }
-\end{minipage}
-}
-\caption{Denoised images of the real noisy image "$Nikon D800 ISO 3200 A3$" by different methods. The images are better to be zoomed in on screen.}
+\vspace{-8mm}
+\label{fig1}
 \end{figure}

### 2016-11-15 1047_sp.tex
ad

@@
 \vspace{-0.1in}
-\item More denoising results on the 20 real noisy imagessupp (with no ``ground truth") provided in the dataset \cite{ncwebsite}.
+\item More denoising results on the real noisy images (with no ``ground truth") provided in the dataset \cite{ncwebsite}.
 \vspace{-0.1in}
-\item More denoising results on the 15 smaller real noisy imagessupp (with ``ground truth") used in the dataset \cite{crosschannel2016}.
+\item More denoising results on the 15 smaller real noisy images (with ``ground truth") used in the dataset \cite{crosschannel2016}.
 \vspace{-0.1in}
-\item More denoising results on the 60 real noisy imagessupp (with ``ground truth") cropped from \cite{crosschannel2016}.
+\item More denoising results on the 60 real noisy images (with ``ground truth") cropped from \cite{crosschannel2016}.
 \end{enumerate}
@@
 
+\section{More Results on Dataset \cite{ncwebsite}}
+In this section, we give more visual comparisons of the competing methods on the real noisy images provided in \cite{ncwebsite}.
+As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method is much better than the state-of-the-art denoising methods.
+This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
+
 \begin{figure}
@@
 \end{minipage}
-}\vspace{-3mm}
+}\vspace{-2mm}
 \caption{
-\vspace{-0.3mm}
-(a) A real noisy image captured by a digital camera \cite{ncwebsite}. (b)$\sim$(i) Denoised imagessupp by different methods.
-\vspace{-0.3mm}
-Among them, CBM3D \cite{bm3d,cbm3d} and WNNM \cite{wnnm} are prior model based methods; MLP \cite{mlp}, CSF \cite{csf} and TNRD 
-\vspace{-0.3mm}
-\cite{chen2015learning} are discriminative learning based methods; and Neat Image \cite{neatimage} and Noise Clinic \cite{noiseclinic,ncwebsite} are methods designed 
-\vspace{-0.3mm}
-for real noisy imagessupp. Clearly, our method produces a cleaner image.
+Denoised images of the real noisy image ``Frog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.
 }
-\vspace{-8mm}
+\vspace{-3mm}
 \label{fig1}

### 2016-11-15 1047_sp.tex
addd

@@
 \subfigure{
-\begin{minipage}[t]{0.33\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_noisy.png}}
-{\footnotesize (a) Noisy Image \cite{ncwebsite}  }
+{\footnotesize (a) Noisy \cite{ncwebsite}   }
 \end{minipage}
-\begin{minipage}[t]{0.33\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
@@
 \end{minipage}
-\begin{minipage}[t]{0.33\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
@@
 \end{minipage}
-}\vspace{-3mm}
-\subfigure{
-\begin{minipage}[t]{0.33\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
@@
 \end{minipage}
-\begin{minipage}[t]{0.33\textwidth}
-\centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_csf.png}}
-{\footnotesize (e) CSF \cite{csf} }
-\end{minipage}
-\begin{minipage}[t]{0.33\textwidth}
+}\vspace{-2mm}
+\subfigure{
+\begin{minipage}[t]{0.244\textwidth}
 \centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_tnrd.png}}
-{\footnotesize (f) TNRD \cite{chen2015learning}  }
+{\footnotesize (e) TNRD \cite{chen2015learning}}
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ni.png}}
+{\footnotesize (f) NI \cite{neatimage}  }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_nc.png}}
+{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ours.png}}
+{\footnotesize (h) Ours  }
+\end{minipage}
+}
+\vspace{-2mm}
+\caption{Denoised images of the real noisy image ``Frog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
+\label{fig1}
+\end{figure}
+
+\begin{figure}\vspace{3mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_circuit.png}}
+{\footnotesize (a) Noisy \cite{ncwebsite}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_BM3D_circuit.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_circuit.png}}
+{\footnotesize (c) WNNM \cite{wnnm}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_circuit.png}}
+{\footnotesize (d) MLP \cite{mlp}  }
+\end{minipage}
+}\vspace{-2mm}
+\subfigure{
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_circuit.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}}
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_circuit.png}}
+{\footnotesize (f) NI \cite{neatimage}  }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_circuit.png}}
+{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_circuit.png}}
+{\footnotesize (h) Ours  }
+\end{minipage}
+}
+\vspace{-2mm}
+\caption{Denoised images of the real noisy image ``Circuit" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
+\label{fig2}
+\end{figure}
+
+\begin{figure}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_noisy.png}}
+{\footnotesize (a) Noisy \cite{ncwebsite}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_cbm3d.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_wnnm.png}}
+{\footnotesize (c) WNNM \cite{wnnm}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_mlp.png}}
+{\footnotesize (d) MLP \cite{mlp}  }
 \end{minipage}
@@
 \subfigure{
-\begin{minipage}[t]{0.33\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_tnrd.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}}
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ni.png}}
-{\footnotesize (g) Neat Image \cite{neatimage}   }
+{\footnotesize (f) NI \cite{neatimage}  }
 \end{minipage}
-\begin{minipage}[t]{0.33\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_nc.png}}
-{\footnotesize (h) Noise Clinic \cite{noiseclinic,ncwebsite} }
+{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}   }
 \end{minipage}
-\begin{minipage}[t]{0.33\textwidth}
+\begin{minipage}[t]{0.244\textwidth}
 \centering
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ours.png}}
-{\footnotesize (i) Ours  }
+{\footnotesize (h) Ours  }
 \end{minipage}
-}\vspace{-2mm}
-\caption{
-Denoised images of the real noisy image ``Frog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.
 }
 \vspace{-3mm}
-\label{fig1}
+\caption{Denoised images of the real noisy image ``Frog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
+%\vspace{-1mm}
+\label{fig2}
 \end{figure}

### 2016-11-15 1047_sp.tex
a

@@
 
-\begin{figure}
+\begin{figure}\vspace{3mm}
 \centering
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_noisy.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_woman.png}}
 {\footnotesize (a) Noisy \cite{ncwebsite}   }
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_cbm3d.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_BM3D_woman.png}}
 {\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_wnnm.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_woman.png}}
 {\footnotesize (c) WNNM \cite{wnnm}   }
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_mlp.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_woman.png}}
 {\footnotesize (d) MLP \cite{mlp}  }
 \end{minipage}
-}\vspace{-3mm}
+}\vspace{-2mm}
 \subfigure{
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_tnrd.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_woman.png}}
 {\footnotesize (e) TNRD \cite{chen2015learning}}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ni.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_woman.png}}
 {\footnotesize (f) NI \cite{neatimage}  }
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_nc.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_woman.png}}
 {\footnotesize (g) NC \cite{noiseclinic,ncwebsite}   }
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ours.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_woman.png}}
 {\footnotesize (h) Ours  }
@@
 }
-\vspace{-3mm}
-\caption{Denoised images of the real noisy image ``Frog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
-%\vspace{-1mm}
-\label{fig2}
+\vspace{-2mm}
+\caption{Denoised images of the real noisy image ``Woman" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
+\label{fig3}
 \end{figure}

### 2016-11-15 1047_sp.tex
a
add

@@
 \usepackage{color}
+\usepackage{float}
 
@@
 \vspace{-0.1in}
-\item More denoising results on the 15 smaller real noisy images (with ``ground truth") used in the dataset \cite{crosschannel2016}.
+\item More denoising results on the 15 cropped real noisy images (with ``ground truth") used in the dataset \cite{crosschannel2016}.
 \vspace{-0.1in}
-\item More denoising results on the 60 real noisy images (with ``ground truth") cropped from \cite{crosschannel2016}.
+\item More denoising results on the 60 cropped real noisy images (with ``ground truth") from \cite{crosschannel2016}.
 \end{enumerate}
-\section{Closed-Form Solution of the Weighted Sparse Coding Problem}
+\section{Closed-Form Solution of the Weighted Sparse Coding Problem (4)}
 The weighted sparse coding problem in the main paper is:
@@
 In this section, we give more visual comparisons of the competing methods on the real noisy images provided in \cite{ncwebsite}.
-As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method is much better than the state-of-the-art denoising methods.
+As can be seen from Fig.\ \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods.
 This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
 
-\begin{figure}
+\begin{figure}[H]
 \centering
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_nc.png}}
-{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}   }
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
 \end{minipage}
@@
 
-\begin{figure}\vspace{3mm}
+\begin{figure}[H]\vspace{3mm}
 \centering
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_circuit.png}}
-{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}   }
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
 \end{minipage}
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_woman.png}}
-{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}   }
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
 \end{minipage}
@@
 
+\begin{figure}[H]\vspace{3mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_vehicle.png}}
+{\footnotesize (a) Noisy \cite{ncwebsite}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_BM3D_vehicle.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_vehicle.png}}
+{\footnotesize (c) WNNM \cite{wnnm}   }
+\end{minipage} 
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_vehicle.png}}
+{\footnotesize (d) MLP \cite{mlp}  }
+\end{minipage}
+}\vspace{-2mm}
+\subfigure{
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_vehicle.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}}
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_vehicle.png}}
+{\footnotesize (f) NI \cite{neatimage}  }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_vehicle.png}}
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
+\end{minipage}
+\begin{minipage}[t]{0.244\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_vehicle.png}}
+{\footnotesize (h) Ours  }
+\end{minipage}
+}
+\vspace{-2mm}
+\caption{Denoised images of the real noisy image ``Vehicle" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
+\label{fig4}
+\end{figure}
+
 {\small

### 2016-11-15 1047_sp.tex
a

@@
 
+%------------------------------------------------------------------------------------
+%------------------------------------------------------------------------------------
+
 \section{More Results on Dataset \cite{ncwebsite}}
@@
 
-\begin{figure}[H]
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{3mm}
 \centering
@@
 
+%------------------------------------------------------------------------------------
 \begin{figure}[H]\vspace{3mm}
@@
 
+%------------------------------------------------------------------------------------
+%------------------------------------------------------------------------------------
+\clearpage
+\section{More Results on The 15 Cropped Images in \cite{crosschannel2016}}
+In this section, we give more visual comparisons of the competing methods on the real noisy images provided in \cite{ncwebsite}.
+As can be seen from Fig.\ \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods.
+This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Noisy_5dmark3_iso3200_1_real.png}}
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 37.00dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CBM3D_5dmark3_iso3200_1_real.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 37.02dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_WNNM_5dmark3_iso3200_1_real.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 37.01dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_MLP_5dmark3_iso3200_1_real.png}}
+{\footnotesize (d) MLP \cite{mlp}: 33.90dB }
+\end{minipage}
+\centering
+\begin{minipage}[t]{0.195\textwidth}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_TRD_5dmark3_iso3200_1_real.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}: 36.18dB  } 
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NI_5dmark3_iso3200_1_real.png}}
+{\footnotesize (f) NI \cite{neatimage}: 37.68dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_NC_5dmark3_iso3200_1_real.png}}
+{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}: 38.76dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_CCNoise_5dmark3_iso3200_1.png}}
+{\footnotesize (h) CC \cite{crosschannel2016}: 38.37dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Guided_5dmark3_iso3200_1_real.png}}
+{\footnotesize (i) Ours: \textbf{40.50}dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{images/resize_br_Mean_5dmark3_iso3200_1_real.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}\vspace{-1mm}
+\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\label{fig7}
+\vspace{1mm}
+\end{figure}
+
 {\small

### 2016-11-15 CVPR2017_Review_Unified.tex
add

@@
 \end{minipage}
-}\vspace{-1mm}
+}
 \caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods.\ The scene was shot 500 times with the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR index can be computed.
 The images are better viewed by zooming in on screen.}
-%\vspace{-1mm}
 \label{fig1}
@@
 
+\vspace{-1mm}
 \section{Related Work}
@@
 
-\section{External Prior Guided Internal Prior Learning and Image Denoising}
+\vspace{-2mm}
+\section{\parbox[t]{10cm}{External Prior Guided Internal Prior Learn-\\ing and Image Denoising}}
 
@@
 }
-\vspace{-2mm}
+\vspace{-2.5mm}
 \caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The 
-\vspace{-0.5mm}
+\vspace{-1mm}
 images are better to be zoomed in on screen.}
-\vspace{-2mm}
+
 \label{fig4}
@@
 }
+\vspace{-2.5mm}  
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The 
+\vspace{-1mm}
+images are better to be zoomed in on screen.}
 \vspace{-2mm}
-\caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The 
-\vspace{-0.5mm}
-images are better to be zoomed in on screen.}
-\vspace{-3mm}
 \label{fig5}
@@
 
-\subsection{Comparison among external, internal and guided internal priors}
+\subsection{\parbox[t]{8cm}{Comparison among external, internal and 
+\\guided internal priors}}
 
@@
 }
-\vspace{-3mm}
+\vspace{-2mm}
 \caption{Denoised images of the real noisy image ``Dog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
-%\vspace{-1mm}
 \label{fig6}
@@
 
-\subsection{Comparison with State-of-the-Art Denoising Methods}
+\subsection{\parbox[t]{10cm}{Comparison with State-of-the-Art Denoising 
+\\Methods}}
 
@@
 \label{tab1}
-%\begin{small}
 \vspace{-3mm}
@@
 \end{tabular}
-\end{center}\vspace{-2mm}
-%\end{small}
+\end{center}\vspace{-4mm}
 \end{table}
 
-\subsubsection{Results on Dataset \cite{ncwebsite}}
+\vspace{-3mm}
+\subsubsection{Results on Dataset \cite{ncwebsite}}\vspace{-1mm}
 
@@
 \caption{PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
+\vspace{0.5mm}
 \label{tab2}
@@
 
+\vspace{-2mm}
 \subsubsection{Results on Dataset \cite{crosschannel2016}}
@@
 Due to the space limitations, the visual comparisons are provided in the supplementary file.
-
-\begin{table}
-\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
-\vspace{-3mm}
-\label{tab3}
-\begin{center}
-\renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|}
-\hline
- Methods& \textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
-\\
-\hline
-PSNR &   34.58 & 34.52 & 36.19 & 37.40
-\\
-\hline
-Methods& \textbf{TNRD} & \textbf{NI} & \textbf{NC} &\textbf{Ours} 
-\\
-\hline
-PSNR & 37.75  & 36.53 & 37.57 & {\textbf{{ 38.75}}}
-\\
-\hline
-\end{tabular}
-\end{center}\vspace{-4mm}
-\end{table}
 
@@
 \end{minipage}
-}\vspace{-1mm}
+}\vspace{-0.5mm}
 \caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 1" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \label{fig7}
-\vspace{1mm}
+\vspace{0.5mm}
 \end{figure*}
+
+\begin{table}\vspace{1.5mm}
+\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
+\vspace{-3mm}
+\label{tab3}
+\begin{center}
+\renewcommand\arraystretch{1}
+\begin{tabular}{|c||c|c|c|c|}
+\hline
+ Methods& \textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
+\\
+\hline
+PSNR &   34.58 & 34.52 & 36.19 & 37.40
+\\
+\hline
+Methods& \textbf{TNRD} & \textbf{NI} & \textbf{NC} &\textbf{Ours} 
+\\
+\hline
+PSNR & 37.75  & 36.53 & 37.57 & {\textbf{{ 38.75}}}
+\\
+\hline
+\end{tabular}
+\end{center}\vspace{-2.5mm}
+\end{table}
 

### 2016-11-15 1047_sp.tex
add

@@
 
-\section{More Results on Dataset \cite{ncwebsite}}
+\section{More Results on Real Noisy Images in \cite{ncwebsite}}
 In this section, we give more visual comparisons of the competing methods on the real noisy images provided in \cite{ncwebsite}.
-As can be seen from Fig.\ \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods.
+The real noisy images in this dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.
+As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods.
 This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
@@
 %------------------------------------------------------------------------------------
-\begin{figure}[H]\vspace{3mm}
+\begin{figure}[H]\vspace{2mm}
 \centering
@@
 %------------------------------------------------------------------------------------
-\begin{figure}[H]\vspace{3mm}
+\begin{figure}[H]
 \centering
@@
 %------------------------------------------------------------------------------------
-\clearpage
-\section{More Results on The 15 Cropped Images in \cite{crosschannel2016}}
-In this section, we give more visual comparisons of the competing methods on the real noisy images provided in \cite{ncwebsite}.
-As can be seen from Fig.\ \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods.
+\section{More Results on the 15 Cropped Images in \cite{crosschannel2016}}
+In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.
+As can be seen from Fiures \ref{fig5}-\ref{fig8}, our proposed method achieves better performance than the the competing methods.
 This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

### 2016-11-15 1047_sp.tex
add

--- 2016-11-15 1047_sp.tex
@@
 
-\section{More Results on Dataset \cite{ncwebsite}}
+%------------------------------------------------------------------------------------
+%------------------------------------------------------------------------------------
+
+\section{More Results on Real Noisy Images in \cite{ncwebsite}}
 In this section, we give more visual comparisons of the competing methods on the real noisy images provided in \cite{ncwebsite}.
-As can be seen from Fig.\ \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods.
+The real noisy images in this dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.
+As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods.
 This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
 
-\begin{figure}[H]
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{2mm}
 \centering
@@
 }
-\vspace{-2mm}
 \caption{Denoised images of the real noisy image ``Frog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
@@
 
-\begin{figure}[H]\vspace{3mm}
+%------------------------------------------------------------------------------------
+\begin{figure}[H]
 \centering
@@
 }
-\vspace{-2mm}
 \caption{Denoised images of the real noisy image ``Circuit" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
@@
 }
-\vspace{-2mm}
 \caption{Denoised images of the real noisy image ``Woman" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
@@
 }
-\vspace{-2mm}
 \caption{Denoised images of the real noisy image ``Vehicle" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
 \label{fig4}
+\end{figure}
+
+%------------------------------------------------------------------------------------
+%------------------------------------------------------------------------------------
+\section{More Results on the 15 Cropped Images in \cite{crosschannel2016}}
+In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.
+As can be seen from Fiures \ref{fig5}-\ref{fig8}, our proposed method achieves better performance than the the competing methods.
+This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_5dmark3_iso3200_2_real.png}}
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 33.88dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_5dmark3_iso3200_2_real.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.91dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_5dmark3_iso3200_2_real.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 33.88dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_5dmark3_iso3200_2_real.png}}
+{\footnotesize (d) MLP \cite{mlp}: 33.23dB }
+\end{minipage}
+\centering
+\begin{minipage}[t]{0.195\textwidth}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_5dmark3_iso3200_2_real.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}: 34.33dB  } 
+\end{minipage}
+}\vspace{-2mm}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_5dmark3_iso3200_2_real.png}}
+{\footnotesize (f) NI \cite{neatimage}: 34.87dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_5dmark3_iso3200_2_real.png}}
+{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}: 35.69dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_5dmark3_iso3200_2.png}}
+{\footnotesize (h) CC \cite{crosschannel2016}: 35.37dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_5dmark3_iso3200_2_real.png}}
+{\footnotesize (i) Ours: \textbf{37.05}dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_5dmark3_iso3200_2_real.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}
+\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\label{fig5}
+\end{figure}
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_5dmark3_iso3200_2_real.png}}
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 33.88dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_5dmark3_iso3200_2_real.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.91dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_5dmark3_iso3200_2_real.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 33.88dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_5dmark3_iso3200_2_real.png}}
+{\footnotesize (d) MLP \cite{mlp}: 33.23dB }
+\end{minipage}
+\centering
+\begin{minipage}[t]{0.195\textwidth}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_5dmark3_iso3200_2_real.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}: 34.33dB  } 
+\end{minipage}
+}\vspace{-2mm}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_5dmark3_iso3200_2_real.png}}
+{\footnotesize (f) NI \cite{neatimage}: 34.87dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_5dmark3_iso3200_2_real.png}}
+{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}: 35.69dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_5dmark3_iso3200_2.png}}
+{\footnotesize (h) CC \cite{crosschannel2016}: 35.37dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_5dmark3_iso3200_2_real.png}}
+{\footnotesize (i) Ours: \textbf{37.05}dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_5dmark3_iso3200_2_real.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}
+\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\label{fig6}
 \end{figure}

### 2016-11-15 1047_sp.tex
a

@@
 %------------------------------------------------------------------------------------
+\clearpage
 \section{More Results on the 15 Cropped Images in \cite{crosschannel2016}}
 In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.
-As can be seen from Fiures \ref{fig5}-\ref{fig8}, our proposed method achieves better performance than the the competing methods.
+As can be seen from Fiures \ref{fig5}-\ref{fig8}, on most cases, our proposed method achieves better performance than the the competing methods.
 This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
@@
 %------------------------------------------------------------------------------------
-\begin{figure}[H]\vspace{1mm}
+\begin{figure}[H]\vspace{3mm}
 \centering
@@
 \raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_5dmark3_iso3200_2_real.png}}
-{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}: 35.69dB  }
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 35.69dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_5dmark3_iso3200_2_real.png}}
-{\footnotesize (a) Noisy  \cite{crosschannel2016}: 33.88dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_d600_iso3200_2_real.png}}
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 33.77dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_5dmark3_iso3200_2_real.png}}
-{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.91dB}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_d600_iso3200_2_real.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.80dB}
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_5dmark3_iso3200_2_real.png}}
-{\footnotesize (c) WNNM \cite{wnnm}: 33.88dB}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_d600_iso3200_2_real.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 33.77dB}
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_5dmark3_iso3200_2_real.png}}
-{\footnotesize (d) MLP \cite{mlp}: 33.23dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_d600_iso3200_2_real.png}}
+{\footnotesize (d) MLP \cite{mlp}: 34.13dB }
 \end{minipage}
@@
 \begin{minipage}[t]{0.195\textwidth}
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_5dmark3_iso3200_2_real.png}}
-{\footnotesize (e) TNRD \cite{chen2015learning}: 34.33dB  } 
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_d600_iso3200_2_real.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}: 35.32dB  } 
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_5dmark3_iso3200_2_real.png}}
-{\footnotesize (f) NI \cite{neatimage}: 34.87dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_d600_iso3200_2_real.png}}
+{\footnotesize (f) NI \cite{neatimage}: 35.36dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_5dmark3_iso3200_2_real.png}}
-{\footnotesize (g) NC \cite{noiseclinic,ncwebsite}: 35.69dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_d600_iso3200_2_real.png}}
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 36.70dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_5dmark3_iso3200_2.png}}
-{\footnotesize (h) CC \cite{crosschannel2016}: 35.37dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_d600_iso3200_2.png}}
+{\footnotesize (h) CC \cite{crosschannel2016}: 35.95dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_5dmark3_iso3200_2_real.png}}
-{\footnotesize (i) Ours: \textbf{37.05}dB}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_d600_iso3200_2_real.png}}
+{\footnotesize (i) Ours: \textbf{36.31}dB}
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_5dmark3_iso3200_2_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_d600_iso3200_2_real.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\label{fig6}
+\end{figure}
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_d600_iso3200_2_real.png}}
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 33.77dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_d600_iso3200_2_real.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.80dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_d600_iso3200_2_real.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 33.77dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_d600_iso3200_2_real.png}}
+{\footnotesize (d) MLP \cite{mlp}: 34.13dB }
+\end{minipage}
+\centering
+\begin{minipage}[t]{0.195\textwidth}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_d600_iso3200_2_real.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}: 35.32dB  } 
+\end{minipage}
+}\vspace{-2mm}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_d600_iso3200_2_real.png}}
+{\footnotesize (f) NI \cite{neatimage}: 35.36dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_d600_iso3200_2_real.png}}
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 36.70dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_d600_iso3200_2.png}}
+{\footnotesize (h) CC \cite{crosschannel2016}: 35.95dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_d600_iso3200_2_real.png}}
+{\footnotesize (i) Ours: \textbf{36.31}dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_d600_iso3200_2_real.png}}
 {\footnotesize (j) Mean Image \cite{crosschannel2016}}
@@
 \caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
-\label{fig6}
+\label{fig7}
 \end{figure}

### 2016-11-15 1047_sp.tex
ad

@@
 }
-\caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \label{fig6}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_d600_iso3200_2_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_d800_iso1600_2_real.png}}
 {\footnotesize (a) Noisy  \cite{crosschannel2016}: 33.77dB }
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_d600_iso3200_2_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_d800_iso1600_2_real.png}}
 {\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.80dB}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_d600_iso3200_2_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_d800_iso1600_2_real.png}}
 {\footnotesize (c) WNNM \cite{wnnm}: 33.77dB}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_d600_iso3200_2_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_d800_iso1600_2_real.png}}
 {\footnotesize (d) MLP \cite{mlp}: 34.13dB }
@@
 \begin{minipage}[t]{0.195\textwidth}
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_d600_iso3200_2_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_d800_iso1600_2_real.png}}
 {\footnotesize (e) TNRD \cite{chen2015learning}: 35.32dB  } 
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_d600_iso3200_2_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_d800_iso1600_2_real.png}}
 {\footnotesize (f) NI \cite{neatimage}: 35.36dB  }
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_d600_iso3200_2_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_d800_iso1600_2_real.png}}
 {\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 36.70dB  }
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_d600_iso3200_2.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_d800_iso1600_2.png}}
 {\footnotesize (h) CC \cite{crosschannel2016}: 35.95dB }
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_d600_iso3200_2_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_d800_iso1600_2_real.png}}
 {\footnotesize (i) Ours: \textbf{36.31}dB}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_d600_iso3200_2_real.png}}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_d800_iso1600_2_real.png}}
 {\footnotesize (j) Mean Image \cite{crosschannel2016}}
@@
 }
-\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 1600 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \label{fig7}
+\end{figure}
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_d800_iso1600_2_real.png}}
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 33.77dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_d800_iso1600_2_real.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.80dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_d800_iso1600_2_real.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 33.77dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_d800_iso1600_2_real.png}}
+{\footnotesize (d) MLP \cite{mlp}: 34.13dB }
+\end{minipage}
+\centering
+\begin{minipage}[t]{0.195\textwidth}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_d800_iso1600_2_real.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}: 35.32dB  } 
+\end{minipage}
+}\vspace{-2mm}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_d800_iso1600_2_real.png}}
+{\footnotesize (f) NI \cite{neatimage}: 35.36dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_d800_iso1600_2_real.png}}
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 36.70dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_d800_iso1600_2.png}}
+{\footnotesize (h) CC \cite{crosschannel2016}: 35.95dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_d800_iso1600_2_real.png}}
+{\footnotesize (i) Ours: \textbf{36.31}dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_d800_iso1600_2_real.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 1600 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\label{fig8}
 \end{figure}

### 2016-11-15 1047_sp.tex
a

--- 2016-11-15 1047_sp.tex
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_d600_iso3200_2_real.png}}
-{\footnotesize (a) Noisy  \cite{crosschannel2016}: 33.77dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_d800_iso1600_2_real.png}}
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 35.71dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_d600_iso3200_2_real.png}}
-{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.80dB}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_d800_iso1600_2_real.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.73dB}
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_d600_iso3200_2_real.png}}
-{\footnotesize (c) WNNM \cite{wnnm}: 33.77dB}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_d800_iso1600_2_real.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 35.71dB}
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_d600_iso3200_2_real.png}}
-{\footnotesize (d) MLP \cite{mlp}: 34.13dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_d800_iso1600_2_real.png}}
+{\footnotesize (d) MLP \cite{mlp}: 35.87dB }
 \end{minipage}
@@
 \begin{minipage}[t]{0.195\textwidth}
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_d600_iso3200_2_real.png}}
-{\footnotesize (e) TNRD \cite{chen2015learning}: 35.32dB  } 
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_d800_iso1600_2_real.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}: 38.61dB  } 
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_d600_iso3200_2_real.png}}
-{\footnotesize (f) NI \cite{neatimage}: 35.36dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_d800_iso1600_2_real.png}}
+{\footnotesize (f) NI \cite{neatimage}: 38.57dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_d600_iso3200_2_real.png}}
-{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 36.70dB  }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_d800_iso1600_2_real.png}}
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 39.05dB  }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_d600_iso3200_2.png}}
-{\footnotesize (h) CC \cite{crosschannel2016}: 35.95dB }
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_d800_iso1600_2.png}}
+{\footnotesize (h) CC \cite{crosschannel2016}: 40.36dB }
 \end{minipage}
@@
 \centering
-\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_d600_iso3200_2_real.png}}
-{\footnotesize (i) Ours: \textbf{36.31}dB}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_d800_iso1600_2_real.png}}
+{\footnotesize (i) Ours: \textbf{40.92}dB}
 \end{minipage}
@@
 }
-\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 1600 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \label{fig7}
+\end{figure}
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_d800_iso3200_2_real.png}}
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 32.89dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_d800_iso3200_2_real.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 32.91dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_d800_iso3200_2_real.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 32.94dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_d800_iso3200_2_real.png}}
+{\footnotesize (d) MLP \cite{mlp}: 34.87dB }
+\end{minipage}
+\centering
+\begin{minipage}[t]{0.195\textwidth}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_d800_iso3200_2_real.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}: 35.74dB  } 
+\end{minipage}
+}\vspace{-2mm}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_d800_iso3200_2_real.png}}
+{\footnotesize (f) NI \cite{neatimage}: 35.09dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_d800_iso3200_2_real.png}}
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 35.72dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_d800_iso3200_2.png}}
+{\footnotesize (h) CC \cite{crosschannel2016}: 36.75dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_d800_iso3200_2_real.png}}
+{\footnotesize (i) Ours: \textbf{37.07}dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_d800_iso3200_2_real.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 1600 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\label{fig8}
 \end{figure}

### 2016-11-15 1047_sp.tex
add

@@
 In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.
-As can be seen from Fiures \ref{fig5}-\ref{fig8}, on most cases, our proposed method achieves better performance than the the competing methods.
+As can be seen from Fiures \ref{fig5}-\ref{fig9}, on most cases, our proposed method achieves better performance than the the competing methods.
 This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
@@
 }
-\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 1600 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \label{fig8}
+\end{figure}
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_d800_iso6400_2_real.png}}
+{\footnotesize (a) Noisy  \cite{crosschannel2016}: 29.97dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_d800_iso6400_2_real.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 29.99dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_d800_iso6400_2_real.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 329.97dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_d800_iso6400_2_real.png}}
+{\footnotesize (d) MLP \cite{mlp}: 31.55dB }
+\end{minipage}
+\centering
+\begin{minipage}[t]{0.195\textwidth}
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_d800_iso6400_2_real.png}}
+{\footnotesize (e) TNRD \cite{chen2015learning}: 32.37dB  } 
+\end{minipage}
+}\vspace{-2mm}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_d800_iso6400_2_real.png}}
+{\footnotesize (f) NI \cite{neatimage}: 31.38dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_d800_iso6400_2_real.png}}
+{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 32.79dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CCNoise_d800_iso6400_2.png}}
+{\footnotesize (h) CC \cite{crosschannel2016}: 33.21dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_d800_iso6400_2_real.png}}
+{\footnotesize (i) Ours: \textbf{33.43}dB}
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_d800_iso6400_2_real.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016}}
+\end{minipage}
+}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 6400 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\label{fig9}
 \end{figure}

### 2016-11-15 1047_sp.tex
aad

@@
 %------------------------------------------------------------------------------------
-\clearpage
-\section{More Results on the 15 Cropped Images in \cite{crosschannel2016}}
+\section{More Results on the 15 Cropped Images Used in \cite{crosschannel2016}}
 In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.
@@
 
+\section{More Results on the 60 Cropped Images in \cite{crosschannel2016}}
+In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}.
+As can be seen from Fiures \ref{fig10}-\ref{fig15}, on most cases, our proposed method achieves better performance than the the competing methods.
+This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
+
 {\small

### 2016-11-15 1047_sp.tex
add

@@
 
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 36.15dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 36.20dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 36.15dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (d) MLP \cite{mlp}: 34.10dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (e) CSF \cite{csf}: 35.47dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 35.94dB   }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (g) NI \cite{neatimage}: 36.72dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 37.45dB   }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (i) Ours: \textbf{38.09}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C1" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig10}
+\end{figure}
+
 {\small

### 2016-11-15 1047_sp.tex
a

@@
 
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.97dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.99dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 36.00dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
+{\footnotesize (d) MLP \cite{mlp}: 36.84dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
+{\footnotesize (e) CSF \cite{csf}: 37.73dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 38.31dB   }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
+{\footnotesize (g) NI \cite{neatimage}: 37.45dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.01dB   }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
+{\footnotesize (i) Ours: \textbf{40.07}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C2" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig10}
+\end{figure}
+
 {\small

### 2016-11-15 1047_sp.tex
ad

@@
 
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.40dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.40dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 34.44dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
+{\footnotesize (d) MLP \cite{mlp}: 33.02dB }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
+{\footnotesize (e) CSF \cite{csf}: 33.71dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 34.03dB   }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
+{\footnotesize (g) NI \cite{neatimage}: 36.11dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 36.51dB   }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
+{\footnotesize (i) Ours: \textbf{38.32}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.195\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C3" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig10}
+\end{figure}
+
 {\small

### 2016-11-15 1047_sp.tex
ad

@@
 The images are better viewed by zooming in on screen.}
-\label{fig10}
+\label{fig11}
+\end{figure}
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.92dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 35.89dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (d) MLP \cite{mlp}: 34.82dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (e) CSF \cite{csf}: 36.85dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 37.35dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (g) NI \cite{neatimage}: 37.37dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.48dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (i) Ours: \textbf{39.66}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig12}
 \end{figure}

### 2016-11-15 1047_sp.tex
a

@@
 
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 36.39dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 36.41dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 36.39dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
+{\footnotesize (d) MLP \cite{mlp}: 35.62dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
+{\footnotesize (e) CSF \cite{csf}: 38.16dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 38.26dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
+{\footnotesize (g) NI \cite{neatimage}: 39.84dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 39.33dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
+{\footnotesize (i) Ours: \textbf{40.36}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C2" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig13}
+\end{figure}
+
 {\small

### 2016-11-15 1047_sp.tex
ad

@@
 
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.21dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.25dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 35.21dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
+{\footnotesize (d) MLP \cite{mlp}: 37.18dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
+{\footnotesize (e) CSF \cite{csf}: 38.10dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 38.62dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
+{\footnotesize (g) NI \cite{neatimage}: 37.41dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 39.53dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
+{\footnotesize (i) Ours: \textbf{39.87}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 1600 B2" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig14}
+\end{figure}
+
 {\small

### 2016-11-15 1047_sp.tex
a

@@
 The images are better viewed by zooming in on screen.}
-\label{fig10}
+\label{fig11}
 \end{figure}
@@
 The images are better viewed by zooming in on screen.}
-\label{fig11}
+\label{fig12}
 \end{figure}
@@
 The images are better viewed by zooming in on screen.}
-\label{fig12}
+\label{fig13}
 \end{figure}
@@
 The images are better viewed by zooming in on screen.}
-\label{fig13}
+\label{fig14}
 \end{figure}
@@
 The images are better viewed by zooming in on screen.}
-\label{fig14}
+\label{fig15}
+\end{figure}
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_1600_B3_3.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 38.50dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_1600_B3_3.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 38.52dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_1600_B3_3.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 38.50dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_1600_B3_3.png}}
+{\footnotesize (d) MLP \cite{mlp}: 40.54dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_1600_B3_3.png}}
+{\footnotesize (e) CSF \cite{csf}: 41.72dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_1600_B3_3.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 41.84dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D800_ISO_1600_B3_3.png}}
+{\footnotesize (g) NI \cite{neatimage}: 41.89dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D800_ISO_1600_B3_3.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 42.14dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_1600_B3_3.png}}
+{\footnotesize (i) Ours: \textbf{42.37}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_1600_B3_3.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 1600 B3" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig16}
 \end{figure}

### 2016-11-15 1047_sp.tex
a

--- 2016-11-15 1047_sp.tex
@@
 The images are better viewed by zooming in on screen.}
-\label{fig14}
+\label{fig15}
+\end{figure}
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.02dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.03dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 34.05dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (d) MLP \cite{mlp}: 32.24dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (e) CSF \cite{csf}: 32.94dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 33.48dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (g) NI \cite{neatimage}: 36.04dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 35.89dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (i) Ours: \textbf{37.50}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A1" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig16}
 \end{figure}

### 2016-11-15 1047_sp.tex
a

@@
 
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.90dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.92dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 34.99dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
+{\footnotesize (d) MLP \cite{mlp}: 37.01dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
+{\footnotesize (e) CSF \cite{csf}: 37.94dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 38.13dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
+{\footnotesize (g) NI \cite{neatimage}: 37.24dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.11dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
+{\footnotesize (i) Ours: \textbf{38.95}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A2" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig17}
+\end{figure}
+
 {\small

### 2016-11-15 1047_sp.tex
a

@@
 
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.60dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.63dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 33.60dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
+{\footnotesize (d) MLP \cite{mlp}: 34.35dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
+{\footnotesize (e) CSF \cite{csf}: 36.18dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 36.70dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
+{\footnotesize (g) NI \cite{neatimage}: 35.02dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 36.07dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
+{\footnotesize (i) Ours: \textbf{37.93}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig18}
+\end{figure}
+
 {\small

### 2016-11-15 1047_sp.tex
add

@@
 
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.51dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.54dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 33.51dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
+{\footnotesize (d) MLP \cite{mlp}: 37.17dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
+{\footnotesize (e) CSF \cite{csf}: 38.43dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 38.61dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
+{\footnotesize (g) NI \cite{neatimage}: 36.05dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 37.52dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
+{\footnotesize (i) Ours: \textbf{38.85}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A4" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig19}
+\end{figure}
+
 {\small

### 2016-11-15 1047_sp.tex
a

@@
 
+%------------------------------------------------------------------------------------
+\begin{figure}[H]\vspace{1mm}
+\centering
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
+{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.61dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
+{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.62dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
+{\footnotesize (c) WNNM \cite{wnnm}: 34.61dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
+{\footnotesize (d) MLP \cite{mlp}: 35.00dB }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
+{\footnotesize (e) CSF \cite{csf}: 36.03dB }
+\end{minipage}
+}\vspace{-3mm}
+\subfigure{
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
+{\footnotesize (f) TNRD \cite{chen2015learning}: 36.62dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
+{\footnotesize (g) NI \cite{neatimage}: 36.15dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
+{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 36.56dB   }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
+{\footnotesize (i) Ours: \textbf{37.79}dB  }
+\end{minipage}
+\begin{minipage}[t]{0.196\textwidth}
+\centering
+\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
+{\footnotesize (j) Mean Image \cite{crosschannel2016} }
+\end{minipage}
+}
+\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A5" \cite{crosschannel2016} by different methods.
+The images are better viewed by zooming in on screen.}
+\label{fig20}
+\end{figure}
+
 {\small

### 2016-11-15 1047_sp.tex
a
add

@@
 \usepackage{float}
-
+\usepackage{bm}
 % Include other packages here, before hyperref.
@@
 \begin{enumerate}
-\item The closed-form solution of the proposed weighted sparse coding model in the main paper.
+\item The closed-form solution of the sparse coding problem (6) in the main paper.
 \vspace{-0.1in}
@@
 \end{enumerate}
-\section{Closed-Form Solution of the Weighted Sparse Coding Problem (4)}
-The weighted sparse coding problem in the main paper is:
-\begin{equation}\label{equ1}
-\setlength{\abovedisplayskip}{1pt}
-\setlength{\belowdisplayskip}{1pt}
-\min_{\boldsymbol{\alpha}}\|\mathbf{y}-\mathbf{D}\boldsymbol{\alpha}\|_{2}^{2}+\|\mathbf{w}^{T}\boldsymbol{\alpha}\|_{1}.
+\section{Closed-Form Solution of the Weighted Sparse Coding Problem (6)}
+For notation simplicity, we ignore the index $n,m,t$ in the sparse coding problem (6) in the main paper. And it turns into the following weighted sparse coding problem:
+\vspace{-4mm}
+\begin{equation}\label{equ1}\vspace{-2mm}
+\min_{\bm{\alpha}}\|\mathbf{y}-\mathbf{D}\bm{\alpha}\|_{2}^{2}+\sum_{j=1}^{3p^2}\lambda_{j}|\bm{\alpha}_{j}|.
 \end{equation}
-Since $\mathbf{D}$ is an orthonormal matrix, problem (\ref{equ1}) is equivalent to 
-\begin{equation}\label{equ2}
-\setlength{\abovedisplayskip}{1pt}
-\setlength{\belowdisplayskip}{1pt}
-\min_{\boldsymbol{\alpha}}\|\mathbf{D}^{T}\mathbf{y}-\boldsymbol{\alpha}\|_{2}^{2}+\|\mathbf{w}^{T}\boldsymbol{\alpha}\|_{1}.
+Since $\mathbf{D}$ is an orthogonal matrix, problem (\ref{equ1}) is equivalent to 
+\vspace{-2mm}
+\begin{equation}\label{equ2}\vspace{-2mm}
+\min_{\bm{\alpha}}\|\mathbf{D}^{T}\mathbf{y}-\bm{\alpha}\|_{2}^{2}+\sum_{j=1}^{3p^2}\lambda_{j}|\bm{\alpha}_{j}|.
 \end{equation}
-For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$.
-Since $\mathbf{w}_{i}=c*2\sqrt{2}\sigma^{2}/(\mathbf{\Lambda}_{i}+\varepsilon)$ is positive (please refer to Eq.
-(18) in the main paper), problem (\ref{equ2}) can be written as
-\begin{equation}\label{equ3}
-\setlength{\abovedisplayskip}{0.01pt}
-\setlength{\belowdisplayskip}{0.01pt}
-\min_{\boldsymbol{\alpha}}\sum_{i=1}^{p^{2}}((\mathbf{z}_{i}-\boldsymbol{\alpha}_{i})^{2}+\mathbf{w}_{i}|\boldsymbol{\alpha}_{i}|).
+For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$. Here we have $\lambda_{j}\ge0$, $j=1,...,3p^2$, then problem (\ref{equ2}) can be written as
+\vspace{-2mm}
+\begin{equation}\label{equ3}\vspace{-2mm}
+\min_{\boldsymbol{\alpha}}\sum_{j=1}^{3p^2}((\mathbf{z}_{j}-\bm{\alpha}_{j})^{2}+\lambda_{j}|\bm{\alpha}_{i}|).
 \end{equation}
-The problem (\ref{equ3}) is separable w.r.t. $\boldsymbol{\alpha}_{i}$ and can be simplified to $p^{2}$ scalar minimization problems
-\begin{equation}\label{equ4}
-\setlength{\abovedisplayskip}{2pt}
-\setlength{\belowdisplayskip}{1pt}
-\min_{\boldsymbol{\alpha}_{i}}(\mathbf{z}_{i}-\boldsymbol{\alpha}_{i})^{2}+\mathbf{w}_{i}|\boldsymbol{\alpha}_{i}|,
+The problem (\ref{equ3}) is separable w.r.t. each $\bm{\alpha}_{j}$ and hence can be simplified to $3p^2$ independent  scalar minimization problems
+\vspace{-2mm}
+\begin{equation}\label{equ4}\vspace{-2mm}
+\min_{\bm{\alpha}_{j}}(\mathbf{z}_{j}-\bm{\alpha}_{j})^{2}+\lambda_{j}|\bm{\alpha}_{j}|,
 \end{equation}
-where $i=1,...,p^{2}$. Taking derivative of $\boldsymbol{\alpha}_{i}$ in problem (\ref{equ4}) and setting the derivative to be zero. There are two cases for the solution.
-
-(a) If $\boldsymbol{\alpha}_{i}\ge 0$, we have
-\begin{equation}\label{equ5}
-\setlength{\abovedisplayskip}{0.1pt}
-\setlength{\belowdisplayskip}{0.11pt}
-2(\boldsymbol{\alpha}_{i}-\mathbf{z}_{i})+\mathbf{w}_{i}=0.
+where $j=1,...,3p^2$. Taking derivative of $\boldsymbol{\alpha}_{j}$ in problem (\ref{equ4}) and setting the derivative to be zero. There are two cases for the solution.
+
+(a) If $\bm{\alpha}_{j}\ge 0$, we have
+\vspace{-1mm}
+\begin{equation}\label{equ5}\vspace{-1mm}
+2(\bm{\alpha}_{j}-\mathbf{z}_{j})+\lambda_{j}=0.
 \end{equation}
 \qquad\ \  The solution is
-\begin{equation}\label{equ6}
-\setlength{\abovedisplayskip}{0.1pt}
-\setlength{\belowdisplayskip}{0.1pt}
-\hat{\boldsymbol{\alpha}}_{i}=\mathbf{z}_{i}-\frac{\mathbf{w}_{i}}{2} \ge 0.
+\vspace{-1mm}
+\begin{equation}\label{equ6}\vspace{-1mm}
+\hat{\bm{\alpha}}_{j}=\mathbf{z}_{j}-\frac{\lambda_{j}}{2} \ge 0.
 \end{equation}
-\qquad\ \  So $\mathbf{z}_{i}\ge\frac{\mathbf{w}_{i}}{2}> 0$, and the solution $\hat{\boldsymbol{\alpha}}_{i}$ can be written as
-\begin{equation}\label{equ7}
-\setlength{\abovedisplayskip}{0.1pt}
-\setlength{\belowdisplayskip}{0.1pt}
-\hat{\boldsymbol{\alpha}}_{i}=\text{sgn}(\mathbf{z}_{i})*(|\mathbf{z}_{i}|-\frac{\mathbf{w}_{i}}{2}),
+\qquad\ \  So $\mathbf{z}_{j}\ge\frac{\lambda_{j}}{2}> 0$, and the solution $\hat{\bm{\alpha}}_{j}$ can be written as
+\vspace{-2mm}
+\begin{equation}\label{equ7}\vspace{-2mm}
+\hat{\bm{\alpha}}_{j}=\text{sgn}(\mathbf{z}_{j})*(|\mathbf{z}_{j}|-\frac{\lambda_{j}}{2}),
 \end{equation}
@@
 
-(b) If $\boldsymbol{\alpha}_{i}< 0$, we have
-\begin{equation}\label{equ8}
-\setlength{\abovedisplayskip}{0.1pt}
-\setlength{\belowdisplayskip}{0.1pt}
-2(\boldsymbol{\alpha}_{i}-\mathbf{z}_{i})-\mathbf{w}_{i}=0.
+(b) If $\bm{\alpha}_{i}< 0$, we have
+\vspace{-1mm}
+\begin{equation}\label{equ8}\vspace{-1mm}
+2(\bm{\alpha}_{j}-\mathbf{z}_{j})-\lambda_{j}=0.
 \end{equation}
 \qquad\ \  The solution is
-\begin{equation}\label{equ9}
-\setlength{\abovedisplayskip}{0.1pt}
-\setlength{\belowdisplayskip}{0.1pt}
-\hat{\boldsymbol{\alpha}}_{i}=\mathbf{z}_{i}+\frac{\mathbf{w}_{i}}{2} < 0.
+\vspace{-2mm}
+\begin{equation}\label{equ9}\vspace{-2mm}
+\hat{\bm{\alpha}}_{j}=\mathbf{z}_{j}+\frac{\lambda_{j}}{2} < 0.
 \end{equation}
-\qquad\ \  So $\mathbf{z}_{i}<-\frac{\mathbf{w}_{i}}{2}< 0$, and the solution $\hat{\boldsymbol{\alpha}}_{i}$ can be written as
-\begin{equation}\label{equ10}
-\setlength{\abovedisplayskip}{1pt}
-\setlength{\belowdisplayskip}{1pt}
-\hat{\boldsymbol{\alpha}}_{i}=\text{sgn}(\mathbf{z}_{i})*(-\mathbf{z}_{i}-\frac{\mathbf{w}_{i}}{2})=\text{sgn}(\mathbf{z}_{i})*(|\mathbf{z}_{i}|-\frac{\mathbf{w}_{i}}{2}).
+\qquad\ \  So $\mathbf{z}_{j}<-\frac{\lambda_{j}}{2}< 0$, and the solution $\hat{\bm{\alpha}}_{j}$ can be written as
+\vspace{-2mm}
+\begin{equation}\label{equ10}\vspace{-2mm}
+\hat{\bm{\alpha}}_{j}=\text{sgn}(\mathbf{z}_{j})*(-\mathbf{z}_{j}-\frac{\lambda_{j}}{2})=\text{sgn}(\mathbf{z}_{j})*(|\mathbf{z}_{j}|-\frac{\lambda_{j}}{2}).
 \end{equation}
@@
 In summary, we have the final solution of the weighted sparse coding problem (\ref{equ1}) as
-\begin{equation}\label{equ11}
-\setlength{\abovedisplayskip}{3pt}
-\setlength{\belowdisplayskip}{3pt}
-\hat{\boldsymbol{\alpha}}= \text{sgn}(\mathbf{D^{T}y})\odot \text{max}(|\mathbf{D^{T}y}|-\mathbf{w}/2,0),
+\vspace{-2mm}
+\begin{equation}\label{equ11}\vspace{-2mm}
+\hat{\bm{\alpha}}= \text{sgn}(\mathbf{D^{T}y})\odot \text{max}(|\mathbf{D^{T}y}|-\bm{\lambda}/2,0),
 \end{equation}
@@
 \end{minipage}
-}\vspace{-3mm}
+}\vspace{-2mm}
 \subfigure{
@@
 %------------------------------------------------------------------------------------
-\begin{figure}[H]\vspace{1mm}
+\begin{figure}\vspace{1mm}
 \centering
@@
 %------------------------------------------------------------------------------------
-\begin{figure}[H]\vspace{1mm}
+\begin{figure}\vspace{6mm}
 \centering

### 2016-11-15 CVPR2017_Review_Unified.tex
add

@@
 \end{equation}
-where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter, $\text{sgn}(\bullet)$ is the sign function and $\odot$ means element-wise multiplication.\ The detailed derivation of Eq.
+where $\bm{\lambda} = \frac{1}{2}[\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter, $\text{sgn}(\bullet)$ is the sign function and $\odot$ means element-wise multiplication.\ The detailed derivation of Eq.
 (\ref{equ7}) can be found in the supplementary file.

### 2016-11-15 1047_sp.tex
add

@@
 \section{Closed-Form Solution of the Weighted Sparse Coding Problem (6)}
-For notation simplicity, we ignore the index $n,m,t$ in the sparse coding problem (6) in the main paper. And it turns into the following weighted sparse coding problem:
+For notation simplicity, we ignore the indices $n,m,t$ in the problem (6) in the main paper. And it turns into the following weighted sparse coding problem:
 \vspace{-4mm}
@@
 \end{equation}
-For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$. Here we have $\lambda_{j}\ge0$, $j=1,...,3p^2$, then problem (\ref{equ2}) can be written as
+For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$. Here we have $\lambda_{j}>0$, $j=1,...,3p^2$, then problem (\ref{equ2}) can be written as
 \vspace{-2mm}
 \begin{equation}\label{equ3}\vspace{-2mm}
-\min_{\boldsymbol{\alpha}}\sum_{j=1}^{3p^2}((\mathbf{z}_{j}-\bm{\alpha}_{j})^{2}+\lambda_{j}|\bm{\alpha}_{i}|).
+\min_{\boldsymbol{\alpha}}\sum_{j=1}^{3p^2}((\mathbf{z}_{j}-\bm{\alpha}_{j})^{2}+\lambda_{j}|\bm{\alpha}_{j}|).
 \end{equation}
@@
 
-(b) If $\bm{\alpha}_{i}< 0$, we have
+(b) If $\bm{\alpha}_{j}< 0$, we have
 \vspace{-1mm}
@@
 \qquad\ \  So $\mathbf{z}_{j}<-\frac{\lambda_{j}}{2}< 0$, and the solution $\hat{\bm{\alpha}}_{j}$ can be written as
-\vspace{-2mm}
-\begin{equation}\label{equ10}\vspace{-2mm}
+\vspace{-1mm}
+\begin{equation}\label{equ10}\vspace{-1mm}
 \hat{\bm{\alpha}}_{j}=\text{sgn}(\mathbf{z}_{j})*(-\mathbf{z}_{j}-\frac{\lambda_{j}}{2})=\text{sgn}(\mathbf{z}_{j})*(|\mathbf{z}_{j}|-\frac{\lambda_{j}}{2}).
@@
 In summary, we have the final solution of the weighted sparse coding problem (\ref{equ1}) as
-\vspace{-2mm}
-\begin{equation}\label{equ11}\vspace{-2mm}
-\hat{\bm{\alpha}}= \text{sgn}(\mathbf{D^{T}y})\odot \text{max}(|\mathbf{D^{T}y}|-\bm{\lambda}/2,0),
+\vspace{-1mm}
+\begin{equation}\label{equ11}\vspace{-1mm}
+\hat{\bm{\alpha}}= \text{sgn}(\mathbf{D^{T}y})\odot \text{max}(|\mathbf{D^{T}y}|-\bm{\lambda},0),
 \end{equation}
-where $\odot$ means element-wise multiplication and $|\mathbf{D^{T}y}|$ is the absolute value of each entry of the vector $\mathbf{D^{T}y}$.
+where $\bm{\lambda} = \frac{1}{2}[\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\odot$ means element-wise multiplication.
 
@@
 \section{More Results on Real Noisy Images in \cite{ncwebsite}}
-In this section, we give more visual comparisons of the competing methods on the real noisy images provided in \cite{ncwebsite}.
-The real noisy images in this dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.
-As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method perfomrs better than the state-of-the-art denoising methods.
-This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
-
-%------------------------------------------------------------------------------------
-\begin{figure}[H]\vspace{2mm}
+In this section, we give more comparisons of the competing methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.
+One can seen from Figures \ref{fig1}-\ref{fig4} that, our proposed method perfomrs better than the state-of-the-art denoising methods.
+
+%------------------------------------------------------------------------------------
+\begin{figure}[H]
 \centering
@@
 \caption{Denoised images of the real noisy image ``Frog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
-\label{fig1}
+\label{fig1}\vspace{-2mm}
 \end{figure}
@@
 In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}.
-As can be seen from Fiures \ref{fig10}-\ref{fig15}, on most cases, our proposed method achieves better performance than the the competing methods.
+As can be seen from Fiures \ref{fig10}-\ref{fig20}, on most cases, our proposed method achieves better performance than the the competing methods.
 This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
@@
 %------------------------------------------------------------------------------------
-\begin{figure}\vspace{1mm}
+\begin{figure}[H]\vspace{1mm}
 \centering
@@
 %------------------------------------------------------------------------------------
-\begin{figure}\vspace{6mm}
+\begin{figure}[H]\vspace{6mm}
 \centering

### 2016-11-15 1047_supp.tex
add

\documentclass[10pt,onecolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfigure}
\usepackage{upgreek}
\usepackage{multirow}
\usepackage{color}
\usepackage{float}
\usepackage{bm}
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{1047} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi

\begin{document}

%%%%%%%%% TITLE
\title{Supplementary Material to ``External Prior Guided Internal Prior Learning for Real Noisy Image Denoising"}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle

%%%%%%%%% BODY TEXT
In this supplementary material, we provide:\vspace{-0.1in}
\begin{enumerate}
\item The closed-form solution of the sparse coding problem (6) in the main paper.
\vspace{-0.1in}
\item More denoising results on the real noisy images (with no ``ground truth") provided in the dataset \cite{ncwebsite}.
\vspace{-0.1in}
\item More denoising results on the 15 cropped real noisy images (with ``ground truth") used in the dataset \cite{crosschannel2016}.
\vspace{-0.1in}
\item More denoising results on the 60 cropped real noisy images (with ``ground truth") from \cite{crosschannel2016}.
\end{enumerate}
\section{Closed-Form Solution of the Weighted Sparse Coding Problem (6)}
For notation simplicity, we ignore the indices $n,m,t$ in the problem (6) in the main paper. And it turns into the following weighted sparse coding problem:
\vspace{-4mm}
\begin{equation}\label{equ1}\vspace{-2mm}
\min_{\bm{\alpha}}\|\mathbf{y}-\mathbf{D}\bm{\alpha}\|_{2}^{2}+\sum_{j=1}^{3p^2}\lambda_{j}|\bm{\alpha}_{j}|.
\end{equation}
Since $\mathbf{D}$ is an orthogonal matrix, problem (\ref{equ1}) is equivalent to 
\vspace{-2mm}
\begin{equation}\label{equ2}\vspace{-2mm}
\min_{\bm{\alpha}}\|\mathbf{D}^{T}\mathbf{y}-\bm{\alpha}\|_{2}^{2}+\sum_{j=1}^{3p^2}\lambda_{j}|\bm{\alpha}_{j}|.
\end{equation}
For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$. Here we have $\lambda_{j}>0$, $j=1,...,3p^2$, then problem (\ref{equ2}) can be written as
\vspace{-2mm}
\begin{equation}\label{equ3}\vspace{-2mm}
\min_{\boldsymbol{\alpha}}\sum_{j=1}^{3p^2}((\mathbf{z}_{j}-\bm{\alpha}_{j})^{2}+\lambda_{j}|\bm{\alpha}_{j}|).
\end{equation}
The problem (\ref{equ3}) is separable w.r.t. each $\bm{\alpha}_{j}$ and hence can be simplified to $3p^2$ independent  scalar minimization problems
\vspace{-2mm}
\begin{equation}\label{equ4}\vspace{-2mm}
\min_{\bm{\alpha}_{j}}(\mathbf{z}_{j}-\bm{\alpha}_{j})^{2}+\lambda_{j}|\bm{\alpha}_{j}|,
\end{equation}
where $j=1,...,3p^2$. Taking derivative of $\boldsymbol{\alpha}_{j}$ in problem (\ref{equ4}) and setting the derivative to be zero. There are two cases for the solution.

(a) If $\bm{\alpha}_{j}\ge 0$, we have
\vspace{-1mm}
\begin{equation}\label{equ5}\vspace{-1mm}
2(\bm{\alpha}_{j}-\mathbf{z}_{j})+\lambda_{j}=0.
\end{equation}
\qquad\ \  The solution is
\vspace{-1mm}
\begin{equation}\label{equ6}\vspace{-1mm}
\hat{\bm{\alpha}}_{j}=\mathbf{z}_{j}-\frac{\lambda_{j}}{2} \ge 0.
\end{equation}
\qquad\ \  So $\mathbf{z}_{j}\ge\frac{\lambda_{j}}{2}> 0$, and the solution $\hat{\bm{\alpha}}_{j}$ can be written as
\vspace{-2mm}
\begin{equation}\label{equ7}\vspace{-2mm}
\hat{\bm{\alpha}}_{j}=\text{sgn}(\mathbf{z}_{j})*(|\mathbf{z}_{j}|-\frac{\lambda_{j}}{2}),
\end{equation}
\qquad\ \  where $\text{sgn}(\bullet)$ is the sign function.

(b) If $\bm{\alpha}_{j}< 0$, we have
\vspace{-1mm}
\begin{equation}\label{equ8}\vspace{-1mm}
2(\bm{\alpha}_{j}-\mathbf{z}_{j})-\lambda_{j}=0.
\end{equation}
\qquad\ \  The solution is
\vspace{-2mm}
\begin{equation}\label{equ9}\vspace{-2mm}
\hat{\bm{\alpha}}_{j}=\mathbf{z}_{j}+\frac{\lambda_{j}}{2} < 0.
\end{equation}
\qquad\ \  So $\mathbf{z}_{j}<-\frac{\lambda_{j}}{2}< 0$, and the solution $\hat{\bm{\alpha}}_{j}$ can be written as
\vspace{-1mm}
\begin{equation}\label{equ10}\vspace{-1mm}
\hat{\bm{\alpha}}_{j}=\text{sgn}(\mathbf{z}_{j})*(-\mathbf{z}_{j}-\frac{\lambda_{j}}{2})=\text{sgn}(\mathbf{z}_{j})*(|\mathbf{z}_{j}|-\frac{\lambda_{j}}{2}).
\end{equation}

In summary, we have the final solution of the weighted sparse coding problem (\ref{equ1}) as
\vspace{-1mm}
\begin{equation}\label{equ11}\vspace{-1mm}
\hat{\bm{\alpha}}= \text{sgn}(\mathbf{D^{T}y})\odot \text{max}(|\mathbf{D^{T}y}|-\bm{\lambda},0),
\end{equation}
where $\bm{\lambda} = \frac{1}{2}[\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\odot$ means element-wise multiplication.

%------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------

\section{More Results on Real Noisy Images in \cite{ncwebsite}}
In this section, we give more comparisons of the competing methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods. One can seen from Figures \ref{fig1}-\ref{fig4} that, our proposed method perfomrs better than the state-of-the-art denoising methods.

%------------------------------------------------------------------------------------
\begin{figure}[H]
\centering
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_noisy.png}}
{\footnotesize (a) Noisy \cite{ncwebsite}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_cbm3d.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_wnnm.png}}
{\footnotesize (c) WNNM \cite{wnnm}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_mlp.png}}
{\footnotesize (d) MLP \cite{mlp}  }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_tnrd.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}}
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ni.png}}
{\footnotesize (f) NI \cite{neatimage}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_nc.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_frog_ours.png}}
{\footnotesize (h) Ours  }
\end{minipage}
}
\caption{Denoised images of the real noisy image ``Frog" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
\label{fig1}\vspace{-2mm}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]
\centering
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_circuit.png}}
{\footnotesize (a) Noisy \cite{ncwebsite}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_BM3D_circuit.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_circuit.png}}
{\footnotesize (c) WNNM \cite{wnnm}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_circuit.png}}
{\footnotesize (d) MLP \cite{mlp}  }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_circuit.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}}
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_circuit.png}}
{\footnotesize (f) NI \cite{neatimage}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_circuit.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_circuit.png}}
{\footnotesize (h) Ours  }
\end{minipage}
}
\caption{Denoised images of the real noisy image ``Circuit" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
\label{fig2}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{3mm}
\centering
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_woman.png}}
{\footnotesize (a) Noisy \cite{ncwebsite}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_BM3D_woman.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_woman.png}}
{\footnotesize (c) WNNM \cite{wnnm}   }
\end{minipage} 
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_woman.png}}
{\footnotesize (d) MLP \cite{mlp}  }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_woman.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}}
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_woman.png}}
{\footnotesize (f) NI \cite{neatimage}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_woman.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_woman.png}}
{\footnotesize (h) Ours  }
\end{minipage}
}
\caption{Denoised images of the real noisy image ``Woman" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
\label{fig3}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{3mm}
\centering
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Noisy_vehicle.png}}
{\footnotesize (a) Noisy \cite{ncwebsite}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_BM3D_vehicle.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_WNNM_vehicle.png}}
{\footnotesize (c) WNNM \cite{wnnm}   }
\end{minipage} 
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_MLP_vehicle.png}}
{\footnotesize (d) MLP \cite{mlp}  }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_TRD_vehicle.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}}
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NI_vehicle.png}}
{\footnotesize (f) NI \cite{neatimage}  }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_NC_vehicle.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}   }
\end{minipage}
\begin{minipage}[t]{0.244\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_br_Guided_vehicle.png}}
{\footnotesize (h) Ours  }
\end{minipage}
}
\caption{Denoised images of the real noisy image ``Vehicle" \cite{ncwebsite} by different methods. The images are better to be zoomed in on screen.}
\label{fig4}
\end{figure}

%------------------------------------------------------------------------------------
%------------------------------------------------------------------------------------
\section{More Results on the 15 Cropped Images Used in \cite{crosschannel2016}}
In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}. As can be seen from Fiures \ref{fig5}-\ref{fig9}, on most cases, our proposed method achieves better performance than the the competing methods. This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{3mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_5dmark3_iso3200_2_real.png}}
{\footnotesize (a) Noisy  \cite{crosschannel2016}: 33.88dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_5dmark3_iso3200_2_real.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.91dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_5dmark3_iso3200_2_real.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.88dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_5dmark3_iso3200_2_real.png}}
{\footnotesize (d) MLP \cite{mlp}: 33.23dB }
\end{minipage}
\centering
\begin{minipage}[t]{0.195\textwidth}
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_5dmark3_iso3200_2_real.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}: 34.33dB  } 
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_5dmark3_iso3200_2_real.png}}
{\footnotesize (f) NI \cite{neatimage}: 34.87dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_5dmark3_iso3200_2_real.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 35.69dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CCNoise_5dmark3_iso3200_2.png}}
{\footnotesize (h) CC \cite{crosschannel2016}: 35.37dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_5dmark3_iso3200_2_real.png}}
{\footnotesize (i) Ours: \textbf{37.05}dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_5dmark3_iso3200_2_real.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016}}
\end{minipage}
}
\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
\label{fig5}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_d600_iso3200_2_real.png}}
{\footnotesize (a) Noisy  \cite{crosschannel2016}: 33.77dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_d600_iso3200_2_real.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.80dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_d600_iso3200_2_real.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.77dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_d600_iso3200_2_real.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.13dB }
\end{minipage}
\centering
\begin{minipage}[t]{0.195\textwidth}
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_d600_iso3200_2_real.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}: 35.32dB  } 
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_d600_iso3200_2_real.png}}
{\footnotesize (f) NI \cite{neatimage}: 35.36dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_d600_iso3200_2_real.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 36.70dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CCNoise_d600_iso3200_2.png}}
{\footnotesize (h) CC \cite{crosschannel2016}: 35.95dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_d600_iso3200_2_real.png}}
{\footnotesize (i) Ours: \textbf{36.31}dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_d600_iso3200_2_real.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016}}
\end{minipage}
}
\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
\label{fig6}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_d800_iso1600_2_real.png}}
{\footnotesize (a) Noisy  \cite{crosschannel2016}: 35.71dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_d800_iso1600_2_real.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.73dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_d800_iso1600_2_real.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 35.71dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_d800_iso1600_2_real.png}}
{\footnotesize (d) MLP \cite{mlp}: 35.87dB }
\end{minipage}
\centering
\begin{minipage}[t]{0.195\textwidth}
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_d800_iso1600_2_real.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}: 38.61dB  } 
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_d800_iso1600_2_real.png}}
{\footnotesize (f) NI \cite{neatimage}: 38.57dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_d800_iso1600_2_real.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 39.05dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CCNoise_d800_iso1600_2.png}}
{\footnotesize (h) CC \cite{crosschannel2016}: 40.36dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_d800_iso1600_2_real.png}}
{\footnotesize (i) Ours: \textbf{40.92}dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_d800_iso1600_2_real.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016}}
\end{minipage}
}
\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 1600 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
\label{fig7}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_d800_iso3200_2_real.png}}
{\footnotesize (a) Noisy  \cite{crosschannel2016}: 32.89dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_d800_iso3200_2_real.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 32.91dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_d800_iso3200_2_real.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 32.94dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_d800_iso3200_2_real.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.87dB }
\end{minipage}
\centering
\begin{minipage}[t]{0.195\textwidth}
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_d800_iso3200_2_real.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}: 35.74dB  } 
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_d800_iso3200_2_real.png}}
{\footnotesize (f) NI \cite{neatimage}: 35.09dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_d800_iso3200_2_real.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 35.72dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CCNoise_d800_iso3200_2.png}}
{\footnotesize (h) CC \cite{crosschannel2016}: 36.75dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_d800_iso3200_2_real.png}}
{\footnotesize (i) Ours: \textbf{37.07}dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_d800_iso3200_2_real.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016}}
\end{minipage}
}
\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
\label{fig8}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_d800_iso6400_2_real.png}}
{\footnotesize (a) Noisy  \cite{crosschannel2016}: 29.97dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_d800_iso6400_2_real.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 29.99dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_d800_iso6400_2_real.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 329.97dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_d800_iso6400_2_real.png}}
{\footnotesize (d) MLP \cite{mlp}: 31.55dB }
\end{minipage}
\centering
\begin{minipage}[t]{0.195\textwidth}
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_d800_iso6400_2_real.png}}
{\footnotesize (e) TNRD \cite{chen2015learning}: 32.37dB  } 
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_d800_iso6400_2_real.png}}
{\footnotesize (f) NI \cite{neatimage}: 31.38dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_d800_iso6400_2_real.png}}
{\footnotesize (g) NC \cite{ncwebsite,noiseclinic}: 32.79dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CCNoise_d800_iso6400_2.png}}
{\footnotesize (h) CC \cite{crosschannel2016}: 33.21dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_d800_iso6400_2_real.png}}
{\footnotesize (i) Ours: \textbf{33.43}dB}
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_d800_iso6400_2_real.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016}}
\end{minipage}
}
\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 6400 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
\label{fig9}
\end{figure}

\section{More Results on the 60 Cropped Images in \cite{crosschannel2016}}
In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}. As can be seen from Fiures \ref{fig10}-\ref{fig20}, on most cases, our proposed method achieves better performance than the the competing methods. This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 36.15dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 36.20dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 36.15dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.10dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (e) CSF \cite{csf}: 35.47dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 35.94dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (g) NI \cite{neatimage}: 36.72dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 37.45dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (i) Ours: \textbf{38.09}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C1_47.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig10}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.97dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.99dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 36.00dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (d) MLP \cite{mlp}: 36.84dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (e) CSF \cite{csf}: 37.73dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 38.31dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.45dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.01dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (i) Ours: \textbf{40.07}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C2_44.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig11}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.40dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.40dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 34.44dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (d) MLP \cite{mlp}: 33.02dB }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (e) CSF \cite{csf}: 33.71dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 34.03dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (g) NI \cite{neatimage}: 36.11dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 36.51dB   }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (i) Ours: \textbf{38.32}dB  }
\end{minipage}
\begin{minipage}[t]{0.195\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Canon_EOS_5D_Mark3_ISO_3200_C3_26.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig12}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.89dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.92dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 35.89dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.82dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (e) CSF \cite{csf}: 36.85dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 37.35dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.37dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.48dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (i) Ours: \textbf{39.66}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C1_96.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig13}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 36.39dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 36.41dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 36.39dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
{\footnotesize (d) MLP \cite{mlp}: 35.62dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
{\footnotesize (e) CSF \cite{csf}: 38.16dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 38.26dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
{\footnotesize (g) NI \cite{neatimage}: 39.84dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 39.33dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
{\footnotesize (i) Ours: \textbf{40.36}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Nikon_D600_ISO_3200_C2_67.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig14}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 35.21dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 35.25dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 35.21dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (d) MLP \cite{mlp}: 37.18dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (e) CSF \cite{csf}: 38.10dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 38.62dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.41dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 39.53dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (i) Ours: \textbf{39.87}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Nikon_D800_ISO_1600_B2_109.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 1600 B2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig15}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.02dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.03dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 34.05dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (d) MLP \cite{mlp}: 32.24dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (e) CSF \cite{csf}: 32.94dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 33.48dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (g) NI \cite{neatimage}: 36.04dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 35.89dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (i) Ours: \textbf{37.50}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A1_111.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A1" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig16}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.90dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.92dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 34.99dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (d) MLP \cite{mlp}: 37.01dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (e) CSF \cite{csf}: 37.94dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 38.13dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (g) NI \cite{neatimage}: 37.24dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 38.11dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (i) Ours: \textbf{38.95}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A2_80.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig17}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{6mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.60dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.63dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.60dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
{\footnotesize (d) MLP \cite{mlp}: 34.35dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
{\footnotesize (e) CSF \cite{csf}: 36.18dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 36.70dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
{\footnotesize (g) NI \cite{neatimage}: 35.02dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 36.07dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
{\footnotesize (i) Ours: \textbf{37.93}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A3_96.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig18}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{1mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 33.51dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 33.54dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 33.51dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
{\footnotesize (d) MLP \cite{mlp}: 37.17dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
{\footnotesize (e) CSF \cite{csf}: 38.43dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 38.61dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
{\footnotesize (g) NI \cite{neatimage}: 36.05dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 37.52dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
{\footnotesize (i) Ours: \textbf{38.85}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A4_114.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A4" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig19}
\end{figure}

%------------------------------------------------------------------------------------
\begin{figure}[H]\vspace{6mm}
\centering
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Noisy_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
{\footnotesize (a) Noisy \cite{crosschannel2016}: 34.61dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CBM3D_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
{\footnotesize (b) CBM3D \cite{bm3d,cbm3d}: 34.62dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_WNNM_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
{\footnotesize (c) WNNM \cite{wnnm}: 34.61dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_MLP_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
{\footnotesize (d) MLP \cite{mlp}: 35.00dB }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_CSF_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
{\footnotesize (e) CSF \cite{csf}: 36.03dB }
\end{minipage}
}\vspace{-2mm}
\subfigure{
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_TRD_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
{\footnotesize (f) TNRD \cite{chen2015learning}: 36.62dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NI_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
{\footnotesize (g) NI \cite{neatimage}: 36.15dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_NC_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
{\footnotesize (h) NC \cite{ncwebsite,noiseclinic}: 36.56dB   }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Guided_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
{\footnotesize (i) Ours: \textbf{37.79}dB  }
\end{minipage}
\begin{minipage}[t]{0.196\textwidth}
\centering
\raisebox{-0.15cm}{\includegraphics[width=1\textwidth]{imagessupp/resize_resize_br_Mean_CC_Noisy_Nikon_D800_ISO_3200_A5_19.png}}
{\footnotesize (j) Mean Image \cite{crosschannel2016} }
\end{minipage}
}
\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A5" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
\label{fig20}
\end{figure}

{\small
\bibliographystyle{unsrt}
\bibliography{egbib}
}

\end{document}

### 2016-11-15 1047.tex
add

--- 2016-11-15 CVPR2017_Review_Unified.tex
@@
 \end{equation}
-where $\bm{\lambda} = [\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter, $\text{sgn}(\bullet)$ is the sign function and $\odot$ means element-wise multiplication.\ The detailed derivation of Eq.
+where $\bm{\lambda} = \frac{1}{2}[\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]^{\top}$ is the vector of regularization parameter, $\text{sgn}(\bullet)$ is the sign function and $\odot$ means element-wise multiplication.\ The detailed derivation of Eq.
 (\ref{equ7}) can be found in the supplementary file.

### 2016-11-16 1047_supp.tex
a

@@
 \end{equation}
-where $\bm{\lambda} = \frac{1}{2}[\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]$ is the vector of regularization parameter and $\odot$ means element-wise multiplication.
+where $\bm{\lambda} = \frac{1}{2}[\lambda_{1},\lambda_{2},...,\lambda_{3p^2}]^{\top}$ is the vector of regularization parameter and $\odot$ means element-wise multiplication.
 

### 2016-11-16 1047_supp.tex
a

@@
 \usepackage{bm}
+\usepackage[document]{ragged2e}
 % Include other packages here, before hyperref.
@@
 
-%%%%%%%%% BODY TEXT
+\vspace{-3mm}
 In this supplementary material, we provide:\vspace{-0.1in}
@@
 \item The closed-form solution of the sparse coding problem (6) in the main paper.
-\vspace{-0.1in}
-\item More denoising results on the real noisy images (with no ``ground truth") provided in the dataset \cite{ncwebsite}.
-\vspace{-0.1in}
-\item More denoising results on the 15 cropped real noisy images (with ``ground truth") used in the dataset \cite{crosschannel2016}.
-\vspace{-0.1in}
-\item More denoising results on the 60 cropped real noisy images (with ``ground truth") from \cite{crosschannel2016}.
+\vspace{-3mm}
+\item More denoising results on the real noisy images in dataset \cite{ncwebsite}.
+\vspace{-3mm}
+\item More denoising results on the 15 cropped real noisy images (with mean image of 500 shots as ``ground truth") in dataset \cite{crosschannel2016}.
+\vspace{-3mm}
+\item More denoising results on the 60 cropped real noisy images (with mean image of 500 shots as ``ground truth") from dataset \cite{crosschannel2016}.
 \end{enumerate}
+
 \section{Closed-Form Solution of the Weighted Sparse Coding Problem (6)}
-For notation simplicity, we ignore the indices $n,m,t$ in the problem (6) in the main paper. And it turns into the following weighted sparse coding problem:
+For notation simplicity, we ignore the indices $n,m,t$ in problem (6) of the main paper. And it turns into the following weighted sparse coding problem:
 \vspace{-4mm}

### 2016-11-16 1047_supp.tex
add
a

@@
 \section{Closed-Form Solution of the Weighted Sparse Coding Problem (6)}
-For notation simplicity, we ignore the indices $n,m,t$ in problem (6) of the main paper. And it turns into the following weighted sparse coding problem:
+For notation simplicity, we ignore the indices $n,m,t$ in problem (6) of the main paper. It turns into the following weighted sparse coding problem:
 \vspace{-4mm}
@@
 In this section, we give more comparisons of the competing methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.
-One can seen from Figures \ref{fig1}-\ref{fig4} that, our proposed method perfomrs better than the state-of-the-art denoising methods.
+As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method performs better than the state-of-the-art denoising methods.
 

### 2016-11-16 1047_supp.tex
a

@@
 \usepackage{bm}
-\usepackage[document]{ragged2e}
+
 % Include other packages here, before hyperref.
@@
 In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.
-As can be seen from Fiures \ref{fig5}-\ref{fig9}, on most cases, our proposed method achieves better performance than the the competing methods.
+In this dataset, each scene was shot 500 times under the same camera and camera setting.
+The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.
+As can be seen from Figures \ref{fig5}-\ref{fig9}, in most cases, our proposed method achieves better performance than the the competing methods.
 This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

### 2016-11-16 1047_supp.tex
a
ad

@@
 In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}.
-As can be seen from Fiures \ref{fig10}-\ref{fig20}, on most cases, our proposed method achieves better performance than the the competing methods.
+In this dataset, each scene was shot 500 times under the same camera and camera setting.
+The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.
+As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the the competing methods.
 This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C1" \cite{crosschannel2016} by different methods.
+\caption{Denoised images of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C1" \cite{crosschannel2016} by different methods.
 The images are better viewed by zooming in on screen.}
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C2" \cite{crosschannel2016} by different methods.
+\caption{Denoised images of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C2" \cite{crosschannel2016} by different methods.
 The images are better viewed by zooming in on screen.}
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C3" \cite{crosschannel2016} by different methods.
+\caption{Denoised images of a region cropped from the real noisy image ``Canon EOS 5D Mark3 ISO 3200 C3" \cite{crosschannel2016} by different methods.
 The images are better viewed by zooming in on screen.}
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods.
-The images are better viewed by zooming in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C1" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \label{fig13}
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C2" \cite{crosschannel2016} by different methods.
-The images are better viewed by zooming in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 C2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \label{fig14}
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 1600 B2" \cite{crosschannel2016} by different methods.
-The images are better viewed by zooming in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 1600 B2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \label{fig15}
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A1" \cite{crosschannel2016} by different methods.
-The images are better viewed by zooming in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A1" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \label{fig16}
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A2" \cite{crosschannel2016} by different methods.
-The images are better viewed by zooming in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A2" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \label{fig17}
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods.
-The images are better viewed by zooming in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A3" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \label{fig18}
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A4" \cite{crosschannel2016} by different methods.
-The images are better viewed by zooming in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A4" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \label{fig19}
@@
 }
-\caption{Denoised imagessupp of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A5" \cite{crosschannel2016} by different methods.
-The images are better viewed by zooming in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D800 ISO 3200 A5" \cite{crosschannel2016} by different methods. The images are better viewed by zooming in on screen.} 
 \label{fig20}

### 2016-11-16 1047_supp.tex
a

@@
 
-\vspace{-3mm}
+\vspace{-2mm}
 In this supplementary material, we provide:\vspace{-0.1in}
@@
 \item The closed-form solution of the sparse coding problem (6) in the main paper.
-\vspace{-3mm}
+\vspace{-2mm}
 \item More denoising results on the real noisy images in dataset \cite{ncwebsite}.
-\vspace{-3mm}
-\item More denoising results on the 15 cropped real noisy images (with mean image of 500 shots as ``ground truth") in dataset \cite{crosschannel2016}.
-\vspace{-3mm}
-\item More denoising results on the 60 cropped real noisy images (with mean image of 500 shots as ``ground truth") from dataset \cite{crosschannel2016}.
+\vspace{-2mm}
+\item More results on the 15 cropped real noisy images (with mean image of 500 shots as ``ground truth") in dataset \cite{crosschannel2016}.
+\vspace{-2mm}
+\item More results on the 60 cropped real noisy images (with mean image of 500 shots as ``ground truth") in dataset \cite{crosschannel2016}.
 \end{enumerate}

### 2016-11-16 1047_supp.tex
a
ad

@@
 \end{equation}
-For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$. Here we have $\lambda_{j}>0$, $j=1,...,3p^2$, then problem (\ref{equ2}) can be written as
+For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$. Here we have $\lambda_{j}>0$, $j=1,...,3p^2$, then problem (\ref{equ2}) can be written as:
 \vspace{-2mm}
@@
 
-\section{More Results on Real Noisy Images in \cite{ncwebsite}}
+\section{More Denoising Results on the Real Noisy Images in Dataset \cite{ncwebsite}}
 In this section, we give more comparisons of the competing methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.
@@
 %------------------------------------------------------------------------------------
-\section{More Results on the 15 Cropped Images Used in \cite{crosschannel2016}}
+\section{More Denoising Results on the 15 Cropped Images Used in \cite{crosschannel2016}}
 In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.
@@
 
-\section{More Results on the 60 Cropped Images in \cite{crosschannel2016}}
+\section{More Denoising Results on the 60 Cropped Real Noisy Images from \cite{crosschannel2016}}
 In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}.

### 2016-11-16 1047_supp.tex
a

@@
 }
-\caption{Denoised images of a region cropped from the real noisy image ``Canon 5D Mark 3 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
+\caption{Denoised images of a region cropped from the real noisy image ``Nikon D600 ISO 3200 2" \cite{crosschannel2016} by different methods. The images are better to be zoomed in on screen.}
 \label{fig6}
@@
 The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.
-As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the the competing methods.
+As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the competing methods.
 This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.

### 2016-11-16 1047_supp.tex
a

@@
 \section{Closed-Form Solution of the Weighted Sparse Coding Problem (6)}
-For notation simplicity, we ignore the indices $n,m,t$ in problem (6) of the main paper. It turns into the following weighted sparse coding problem:
+For notation simplicity, we ignore the indices $n,m,t$ in problem (6) of the main paper.\ It turns into the following weighted sparse coding problem:
 \vspace{-4mm}
@@
 \end{equation}
-Since $\mathbf{D}$ is an orthogonal matrix, problem (\ref{equ1}) is equivalent to 
+Since $\mathbf{D}$ is an orthogonal matrix, problem (\ref{equ1}) is equivalent to:
 \vspace{-2mm}
@@
 \end{equation}
-For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$. Here we have $\lambda_{j}>0$, $j=1,...,3p^2$, then problem (\ref{equ2}) can be written as:
+For simplicity, we denote $\mathbf{z} = \mathbf{D^{T}y}$.\ Here we have $\lambda_{j}>0$, $j=1,...,3p^2$, then problem (\ref{equ2}) can be written as:
 \vspace{-2mm}
@@
 \end{equation}
-The problem (\ref{equ3}) is separable w.r.t. each $\bm{\alpha}_{j}$ and hence can be simplified to $3p^2$ independent  scalar minimization problems
+The problem (\ref{equ3}) is separable w.r.t. each $\bm{\alpha}_{j}$ and hence can be simplified to $3p^2$ independent scalar minimization problems:
 \vspace{-2mm}
@@
 \end{equation}
-\qquad\ \  So $\mathbf{z}_{j}\ge\frac{\lambda_{j}}{2}> 0$, and the solution $\hat{\bm{\alpha}}_{j}$ can be written as
+\qquad\ \  So $\mathbf{z}_{j}\ge\frac{\lambda_{j}}{2}> 0$, and the solution $\hat{\bm{\alpha}}_{j}$ can be written as:
 \vspace{-2mm}
@@
 \end{equation}
-\qquad\ \  So $\mathbf{z}_{j}<-\frac{\lambda_{j}}{2}< 0$, and the solution $\hat{\bm{\alpha}}_{j}$ can be written as
+\qquad\ \  So $\mathbf{z}_{j}<-\frac{\lambda_{j}}{2}< 0$, and the solution $\hat{\bm{\alpha}}_{j}$ can be written as:
 \vspace{-1mm}
@@
 
-In summary, we have the final solution of the weighted sparse coding problem (\ref{equ1}) as
+In summary, we have the final solution of the weighted sparse coding problem (\ref{equ1}) as:
 \vspace{-1mm}
@@
 \section{More Denoising Results on the Real Noisy Images in Dataset \cite{ncwebsite}}
-In this section, we give more comparisons of the competing methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.
-As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method performs better than the state-of-the-art denoising methods.
+In this section, we give more comparisons of the competing methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.\ As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method performs better than the state-of-the-art denoising methods.
 
@@
 \section{More Denoising Results on the 15 Cropped Images Used in \cite{crosschannel2016}}
-In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.
-In this dataset, each scene was shot 500 times under the same camera and camera setting.
-The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.
-As can be seen from Figures \ref{fig5}-\ref{fig9}, in most cases, our proposed method achieves better performance than the the competing methods.
-This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
+In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig5}-\ref{fig9}, in most cases, our proposed method achieves better performance than the the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
 
@@
 \section{More Denoising Results on the 60 Cropped Real Noisy Images from \cite{crosschannel2016}}
-In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}.
-In this dataset, each scene was shot 500 times under the same camera and camera setting.
-The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.
-As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the competing methods.
-This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
+In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
 

### 2016-11-16 1047_supp.tex
s

@@
 \section{More Denoising Results on the 60 Cropped Real Noisy Images from \cite{crosschannel2016}}
-In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped fromfrom \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
+In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped from \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
 

### 2016-11-16 1047_supp.tex
add

@@
 \begin{enumerate}
-\item The closed-form solution of the sparse coding problem (6) in the main paper.
+\item The closed-form solution of the sparse coding problem (6) in the main paper;
 \vspace{-2mm}
-\item More denoising results on the real noisy images in dataset \cite{ncwebsite}.
+\item More denoising results on the real noisy images in dataset \cite{ncwebsite};
 \vspace{-2mm}
-\item More results on the 15 cropped real noisy images (with mean image of 500 shots as ``ground truth") in dataset \cite{crosschannel2016}.
+\item More results on the 15 cropped real noisy images (with mean image of 500 shots as ``ground truth") in dataset \cite{crosschannel2016};
 \vspace{-2mm}

### 2016-11-16 1047_supp.tex
a

@@
 \section{More Denoising Results on the Real Noisy Images in Dataset \cite{ncwebsite}}
-In this section, we give more comparisons of the competing methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.\ As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method performs better than the state-of-the-art denoising methods.
+In this section, we give more comparisons of the state-of-the-art denoising methods on the dataset \cite{ncwebsite}.\ The real noisy images in dataset \cite{ncwebsite} have no ``ground truth" images and hence we only compare the visual quality of the denoised images by different methods.\ As can be seen from Figures \ref{fig1}-\ref{fig4}, our proposed method performs better than the competing methods.
 
@@
 \section{More Denoising Results on the 15 Cropped Images Used in \cite{crosschannel2016}}
-In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig5}-\ref{fig9}, in most cases, our proposed method achieves better performance than the the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
+In this section, we provide more comparisons of the proposed method with the state-of-the-art denoising methods on the 15 cropped real noisy images used in \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig5}-\ref{fig9}, in most cases, our proposed method achieves better performance than the the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
 

### 2016-11-16 1047_supp.tex
ad

@@
 \section{More Denoising Results on the 60 Cropped Real Noisy Images from \cite{crosschannel2016}}
-In this section, we provide more visual comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped from \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
+In this section, we provide more comparisons of the proposed method with the state-of-the-art denoising methods on the 60 cropped real noisy images we cropped from \cite{crosschannel2016}.\ In this dataset, each scene was shot 500 times under the same camera and camera setting.\ The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed.\ As can be seen from Figures \ref{fig10}-\ref{fig20}, in most cases, our proposed method achieves better performance than the competing methods.\ This validates the effectiveness of our proposed external prior guided internal prior learning framework for real noisy image denoising.
 

### 2016-11-17 1047.tex
add
a

@@
 A PG is a group of similar patches to a local patch.\ In our method, each local patch is extracted from a RGB image with patch size $p\times p \times 3$.\ We search the $M$ most similar patches to this local patch (including the local patch itself) in a $W\times W$ local region around it.
-Each patch is stretched to a patch vector $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ to form the PG $\{\mathbf{x}_{m}\}_{m=1}^{M}$.
-The mean vector of this PG is $\bm{\mu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\bm{\mu}\}_{m=1}^{M}$.
+Each patch is stretched to a patch vector $\mathbf{x}_{m}\in \mathbb{R}^{3p^{2}\times1}$ to form the PG $\{\mathbf{x}_{m}\}_{m=1}^{M}$.\ The mean vector of this PG is $\bm{\mu}=\frac{1}{M}\sum_{m=1}^{M}\mathbf{x}_{m}$, and the group mean subtracted PG is defined as $\mathbf{\overline{X}}\triangleq \{\mathbf{\overline{x}}_{m}=\mathbf{x}_{m}-\bm{\mu}\}_{m=1}^{M}$.
 
@@
 \bm{\alpha}_{n,m}^{(t)}:=\argmin_{\bm{\alpha}_{n,m}}
-\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}^{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|
+\|\mathbf{\overline{y}}_{n,m}-\mathbf{D}^{(t)}\bm{\alpha}_{n,m}\|_{2}^{2}+\sum_{j=1}^{3p^{2}}\lambda_{j}|\bm{\alpha}_{n,m,j}|.
 \end{split}

### 2016-11-25 temp.tex
aa

--- 2016-11-17 1047.tex
@@
 \documentclass[10pt,twocolumn,letterpaper]{article}
-
-\usepackage{cvpr}
+\usepackage{iccv}
 \usepackage{times}
@@
 \usepackage{amssymb}
+% Include other packages here, before hyperref.
+\usepackage{url}
 \usepackage{subfigure}
+\usepackage{lineno}
+\usepackage{setspace}
 \usepackage{upgreek}
+\usepackage[numbers,sort]{natbib}
+\usepackage{color}
+\usepackage{authblk}
+\usepackage{xpatch}
+\usepackage{bm}
 \usepackage{multirow}
-\usepackage{color}
-\usepackage{bm}
 \DeclareMathOperator*{\argmin}{arg\,min}
 \usepackage{arydshln}
-\usepackage{cite}
 
-%\usepackage{sectsty}
-%\sectionfont{\fontsize{12}{11}\selectfont\leftskip=0pt\vspace{-2mm}}
-%\subsectionfont{\fontsize{11}{10}\selectfont\leftskip=0pt\vspace{-1mm}}
-%\subsubsectionfont{\fontsize{10}{10}\selectfont\leftskip=0pt\vspace{-1mm}}
+\setlength{\bibsep}{0.4ex}  % vertical spacing between references
+% If you comment hyperref and then uncomment it, you should delete
+% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
+% run, let it finish, and you should be clear).
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\renewcommand{\huge}{\fontsize{8.83pt}{\baselineskip}\selectfont}
 
@@
 % run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage[breaklinks=true,bookmarks=false]{hyperref}
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\iccvfinalcopy % *** Uncomment this line for the final submission
 
-\def\cvprPaperID{1047} % *** Enter the CVPR Paper ID here
+\def\iccvPaperID{****} % *** Enter the ICCV Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
-
+\ificcvfinal\pagestyle{empty}\fi
+\setcounter{page}{1}
 \begin{document}
@@
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
+\xpatchcmd{\author}{\relax#1\relax}{\relax\detokenize{#1}\relax}{}{}
+\author[\empty]{Jun Xu}
+\author[\empty]{Lei Zhang}
+\author[\empty]{David Zhang}
+\affil[\empty]{Department of Computing, The Hong Kong Polytechnic University, Hong Kong, China}
+%\renewcommand\Authands{ and }
 
 \maketitle
-
 %%%%%%%%% ABSTRACT
@@
 where $\mathbf{S}_{k}(j)$ is the $j$-th singular value of diagonal singular value matrix $\mathbf{S}_{k}$ (please refer to Eq.\ (\ref{equ2})) and $\varepsilon$ is a small positive number to avoid zero denominator.\ Note that $\mathbf{D}_{\text{E}}=\mathbf{U}_{k}$ if $r=3p^{2}$ and $\mathbf{D}_{\text{E}}=\emptyset$ if $r=0$.
-
-%The dictionary $\mathbf{D} = [\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}]$ is orthogonal by checking that:
-%\vspace{-2mm}
-%\begin{equation}\label{equ6}\vspace{-2mm}
-%\mathbf{D}^{\top}\mathbf{D} = 
-%\left[\begin{array}{c}
-%\mathbf{D}_{\text{E}}^{\top}
-%\\
-%\mathbf{D}_{\text{I}}^{\top}
-%\end{array}\right]
-%[\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}]
-%=
-%\left[\begin{array}{cc}
-%\mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{E}}^{\top}\mathbf{D}_{\text{I}}
-%\\
-%\mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{E}}\ \mathbf{D}_{\text{I}}^{\top}\mathbf{D}_{\text{I}}
-%\end{array}\right]
-%=
-%\mathbf{I}
-%\end{equation}
 
@@
 
+%-------------------------------------------------------------------------
+
 \section{Conclusion}
@@
 {
-\small
-\bibliographystyle{unsrt}
+\huge
+\bibliographystyle{unsrt}%{ieee}%{unsrt}
 \bibliography{egbib}

### 2016-11-25 1047 - 副本.tex
add

--- 2016-11-17 1047.tex
@@
 
-% \cvprfinalcopy % *** Uncomment this line for the final submission
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
+\author{Jun Xu \qquad Lei Zhang \qquad David Zhang\\
+Department of Computing, The Hong Kong Polytechnic University\\
+{\tt \small{\{csjunxu,cslzhang,csdzhang\}@comp.polyu.edu.hk}}
 % For a paper whose authors are all at the same institution,
@@
 % To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+%\and
+%Second Author\\
+%Institution2\\
+%First line of institution2 address\\
+%{\tt\small secondauthor@i2.org}
 }

### 2017-01-25 cvpr2017RebuttalKit/egrebuttal.tex
add

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Rebuttal for Paper ID 1047}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW

We appreciate all the reviewers for their constructive comments, especially R2 for your encouraging comments.
\\
\textbf{R1's Questions}
\\
\textbf{Q1}: Overstatement of claims
\\
The noise in real world images are very complex and cannot be modeled by Poisson or other more complex distribution. Since it is too hard to explicitly model the real noise, we gave up designing good models for real noise. Instead, we turn to model the signals by statistical models such as mixture of Gaussian (MoG). We believe that as long as we model the signals accurately enough, we do not need strong priors for the noise, and hence we employ the $\ell_{2}$ norm for the residual errors. We admit that if we describe the noise with a more suitable model, the performance of our algorithm will be better. But this is not the major point of this paper, as pointed out by the title of this paper.
\\
\textbf{Q2}: There is nothing new in terms of the prior model ...
\\
When taking the MoG model for learning priors from external data, we basically follow the framework of EPLL. However, this is not the exact work we have done in this paper. What we did is to employ the external priors learned from external data to guide the learning of internal priors which are more adaptive to the image being denoised. And we want to argue that this combination makes our model have stronger ability to characterize the signals in real noisy images. The results of two Poisson algorithm are listed in Table 1.
\\
\textbf{R2's Questions}
\\
\textbf{Q1}: The number and effect of parameters
\\
The key parameters of our model are the regularization parameter $\lambda$ and the number of atoms in external sub-dictionary,$r$. $r$ is very robust as long as it is in a reasonable range as demonstrated in experiments. $\lambda=0.001$ works well in the experiments. Other parameters are preset by hand and can work well as long as they are set in a reasonable range.
\\
\textbf{R3's Questions}
\\
\textbf{Q1}: hard to believe that it will work for all the cases
\\
We had tested our method on the two datasets which contains a lot of real noisy images for many cases, we will test our method and publish our code in the future for testing on more cases.
\\
\textbf{Q2}: not clear how to choose nonlocal similar patches
\\
Yes, we chose similar patches based on Euclidean distance and we added this detail to our revised paper. Thanks for pointing out.
\\
\textbf{Q3}: other noise types
\\
In this paper, we only deal with real noise in real noisy images.
\\
\textbf{Q4}: the likelihood term is Gaussian denoising
\\
Please kindly refer to the answers to \textbf{Q1} of \textbf{R1} and \textbf{Q3} above for this problem since the space is limited. 
\\
\textbf{Q5}: The competing algorithms would also work quite well
\\
We retained the TNRD, CSF or MLP model with the parameters set as the best performance cases as described in their corresponding paper, with Gaussian noise levels $\sigma = 5, 10, 15, 25, 35, 50, and 75$. We found that the best average PSNR results on the 15 and 60 images used in our paper happens with TNRD at $\sigma = 10$, which are 36.61dB and 38.32dB, respectively, 1.0dB and 0.57dB higher than the results with default parameter settings. But these results are still 0.55dB and 0.43dB, respectively, lower than the results of our method. The image qualities of TNRD at $\sigma = 10$ are still clearly inferior to those of our method. The whole retrained results are listed in Table 1.
\\
\textbf{Q6}: a single parameter setting for all the cases 
\\
The experiments demonstrate that a single parameter can deal with all the cases in the tested datasets. With more flexible parameters setting, the performance would be better and this is the line of our future work.
\\
\textbf{Q7}: why is the image resolution significantly smaller
\\
This is for smaller pdf size of the paper, and down scale the images would not affect much the image quality.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2017-01-25 cvpr2017RebuttalKit/egrebuttal.tex
add

@@
 The results of two Poisson algorithm are listed in Table 1.
+\begin{table}\vspace{1.5mm}
+\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
+\vspace{-3mm}
+\label{tab3}
+\begin{center}
+\renewcommand\arraystretch{1}
+\begin{tabular}{|c||c|c|c|c|}
+\hline
+ Methods& \textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
+\\
+\hline
+PSNR &   34.58 & 34.52 & 36.19 & 37.40
+\\
+\hline
+Methods& \textbf{TNRD} & \textbf{NI} & \textbf{NC} &\textbf{Ours} 
+\\
+\hline
+PSNR & 37.75  & 36.53 & 37.57 & {\textbf{{ 38.75}}}
+\\
+\hline
+\end{tabular}
+\end{center}\vspace{-2.5mm}
+\end{table}
 \\

### 2017-01-25 cvpr2017RebuttalKit/egrebuttal.tex
add

@@
 And we want to argue that this combination makes our model have stronger ability to characterize the signals in real noisy images.
-The results of two Poisson algorithm are listed in Table 1.
-\begin{table}\vspace{1.5mm}
-\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
-\vspace{-3mm}
-\label{tab3}
-\begin{center}
-\renewcommand\arraystretch{1}
-\begin{tabular}{|c||c|c|c|c|}
-\hline
- Methods& \textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}
+We evaluate two algorithms designed for Poisson noise reduction, NLSPCA \cite{nlpca} and \cite{makitalo2013optimal}.
+The results are listed in Table 1.
+Note that we had tune the parameters of these algorithms carefully to achieve their best performance.
 \\
-\hline
-PSNR &   34.58 & 34.52 & 36.19 & 37.40
-\\
-\hline
-Methods& \textbf{TNRD} & \textbf{NI} & \textbf{NC} &\textbf{Ours} 
-\\
-\hline
-PSNR & 37.75  & 36.53 & 37.57 & {\textbf{{ 38.75}}}
-\\
-\hline
-\end{tabular}
-\end{center}\vspace{-2.5mm}
-\end{table}
 \\
@@
 \\
+\\
 \textbf{R3's Questions}
@@
 \\
-Yes, we chose similar patches based on Euclidean distance and we added this detail to our revised paper. Thanks for pointing out.
+Yes, we chose similar patches based on Euclidean distance and we added this detail to our revised paper. Thanks for pointing it out.
 \\
@@
 \\
-In this paper, we only deal with real noise in real noisy images.
+In this paper, we only deal with real noise in real noisy images. Other noise types will be considered in future work.
 \\
@@
 \\
-We retained the TNRD, CSF or MLP model with the parameters set as the best performance cases as described in their corresponding paper, with Gaussian noise levels $\sigma = 5, 10, 15, 25, 35, 50, and 75$.
-We found that the best average PSNR results on the 15 and 60 images used in our paper happens with TNRD at $\sigma = 10$, which are 36.61dB and 38.32dB, respectively, 1.0dB and 0.57dB higher than the results with default parameter settings.
-But these results are still 0.55dB and 0.43dB, respectively, lower than the results of our method.
-The image qualities of TNRD at $\sigma = 10$ are still clearly inferior to those of our method.
-The whole retrained results are listed in Table 1.
+We retained the TNRD, CSF or MLP model with the carefully parameter tuning to achieve their corresponding best performance.
+For example, we retained these models with Gaussian noise levels in $\sigma = 5, 10, 15, 25, 35, 50$.
+We found that MLP achieves the best PSNR results on the 60 images used in our paper at $\sigma = 10$, which are 38.36dB.
+But this result is still 0.43dB lower than those of our method.
+The image qualities of MLP at $\sigma = 10$ are still clearly inferior to those of our method.
+The new results are listed in Table 1 in which we also evaluated the performance of two algorithms for Poisson noise removal, NLSPCA \cite{nlpca} and \cite{makitalo2013optimal}.
+\begin{table}\vspace{1.5mm}
+\caption{Average PSNR(dB) results of different methods on 60 real noisy images cropped from \cite{crosschannel2016}.}
+\vspace{-3mm}
+\label{tab3}
+\begin{center}
+\renewcommand\arraystretch{1}
+\begin{tabular}{|c||c|c|c|c|}
+\hline
+ Methods& \textbf{NLSPCA} & \cite{makitalo2013optimal} & \textbf{MLP}&\textbf{CSF}
+\\
+\hline
+PSNR & 24.39  &  25.67 &  38.36 & 38.21
+\\
+\hline
+Methods & \textbf{TNRD} & \textbf{NI} & \textbf{NC} &\textbf{Ours} 
+\\
+\hline
+PSNR & 38.32  & 36.53 & 37.57 & {\textbf{{ 38.75}}}
+\\
+\hline
+\end{tabular}
+\end{center}\vspace{-4mm}
+\end{table}
 \\

### 2017-01-25 cvpr2017RebuttalKit/egrebuttal.tex
add

@@
 \\
-The noise in real world images are very complex and cannot be modeled by Poisson or other more complex distribution.
+\textbf{A1}: The noise in real world images are very complex and cannot be modeled by Poisson or other more complex distribution.
 Since it is too hard to explicitly model the real noise, we gave up designing good models for real noise.
@@
 \\
-When taking the MoG model for learning priors from external data, we basically follow the framework of EPLL.
+\textbf{A2}: When taking the MoG model for learning priors from external data, we basically follow the framework of EPLL.
 However, this is not the exact work we have done in this paper.
@@
 \\
-The key parameters of our model are the regularization parameter $\lambda$ and the number of atoms in external sub-dictionary,$r$.
+\textbf{A1}: The key parameters of our model are the regularization parameter $\lambda$ and the number of atoms in external sub-dictionary,$r$.
 $r$ is very robust as long as it is in a reasonable range as demonstrated in experiments.
@@
 \\
-We had tested our method on the two datasets which contains a lot of real noisy images for many cases, we will test our method and publish our code in the future for testing on more cases.
+\textbf{A1}: We had tested our method on the two datasets which contains a lot of real noisy images for many cases, we will test our method and publish our code in the future for testing on more cases.
 \\
@@
 \\
-Yes, we chose similar patches based on Euclidean distance and we added this detail to our revised paper. Thanks for pointing it out.
+\textbf{A2}: Yes, we chose similar patches based on Euclidean distance and we added this detail to our revised paper. Thanks for pointing it out.
 \\
@@
 \\
-In this paper, we only deal with real noise in real noisy images. Other noise types will be considered in future work.
+\textbf{A3}: In this paper, we only deal with real noise in real noisy images. Other noise types will be considered in future work.
 \\
@@
 \\
-Please kindly refer to the answers to \textbf{Q1} of \textbf{R1} and \textbf{Q3} above for this problem since the space is limited. 
+\textbf{A4}: Please kindly refer to the answers \textbf{A1} to \textbf{Q1} of \textbf{R1} and \textbf{A3} to \textbf{Q3} above for this problem since the space is limited. 
 \\
@@
 \\
-We retained the TNRD, CSF or MLP model with the carefully parameter tuning to achieve their corresponding best performance.
+\textbf{A5}: We retained the TNRD, CSF or MLP model with the carefully parameter tuning to achieve their corresponding best performance.
 For example, we retained these models with Gaussian noise levels in $\sigma = 5, 10, 15, 25, 35, 50$.
@@
 \\
-The experiments demonstrate that a single parameter can deal with all the cases in the tested datasets.
+\textbf{A6}: The experiments demonstrate that a single parameter can deal with all the cases in the tested datasets.
 With more flexible parameters setting, the performance would be better and this is the line of our future work.
@@
 \\
-This is for smaller pdf size of the paper, and down scale the images would not affect much the image quality.
+\textbf{A7}: This is for smaller pdf size of the paper, and down scale the images would not affect much the image quality.
 

### 2017-02-07 egrebuttal.tex
add

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{1047} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Authors' Response to the Review of Paper 1047\\External Prior Guided Internal Prior Learning for Real Noisy Image Denoising}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
We appreciate all the reviewers for their constructive comments. We regret that R1 and R3 had obvious misunderstanding on our work. We sincerely ask them to read our paper again. What below are our responses to all the reviewers' comments.

\vspace{-1mm}
\section{Non-Gaussian noise (R1\&R3)}
In this work we presented an effective algorithm for real noisy image denoising, but we didn't claim that we developed a new model for non-Gaussian noise. The noise in real world images is too complex to be modeled by Poisson or other simple distributions. Therefore, we focused on the modeling of image priors, while using the simple $l_{2}$-norm to measure the residual. We agree that if a more complex noise model is used, the performance of our algorithm can be better. However, this is not the focus of this paper. Using the simple $l_{2}$-norm on residual, our method has already achieved very competitive results, which clearly demonstrated the effectiveness of our image prior model.

Both R1 and R3 asked us to compare with Poisson noise removal methods. In Table 1 we compared with 2 state-of-the-art Poisson noise reduction methods \cite{Makitalo2013Optimal} and \cite{Salmon}. Note that we have tuned their parameters carefully to achieve their best performance. Neither \cite{Makitalo2013Optimal} nor \cite{Salmon} works well. This is because real world noise is much more complex than Poisson.

\begin{table}[h!]
\begin{center}
\caption{Average PSNR (dB) results of different methods on 60 real noisy images from \cite{Nam2016A}}
\begin{tabular}{|l|c|c|c|c|}
  \hline
  \textbf{Methods}                             &\cite{Makitalo2013Optimal}          &\cite{Salmon}       &MLP &CSF        \\
  \hline
  PSNR                    &  24.39                     &   25.67 &38.36 &38.21                           \\
  \hline
  \textbf{Methods}                             &TNRD          &NI       &NC &Ours        \\
  \hline
  PSNR                    &  38.32                     &   36.53 &37.57 &\textbf{38.75}                           \\
  \hline
\end{tabular}
\end{center}
\label{tab:1}
\end{table}

\vspace{-9mm}
\section{Novelty of our prior model (R1\&R3)}
Most of the previous denoising methods either learn external priors or learn internal priors. Our method is among the first methods to learn hybrid prior models. We first learn external GMM priors from clean images (this part is basically the same as Zoran and Weiss' 2011 work and we have made this very clear in our paper), and then use the GMM prior to guide the learning of image internal priors (this part is totally new). We want to argue that this is a novel contribution and our method shows state-of-the-art performance on real noisy image denoising.

\section{The effect of parameters (R2)}
There are 6 model parameters in our method and all of them are fixed in our experiments (please refer to the section of implementation details). Based on our experience, our method will not be affected much when these parameters vary around our default setting. The most sensitive parameter is the regularization parameter $\lambda$ in Eq. (5), and we set $\lambda$=0.001 by experience.

\section{The setting of competing algorithms (R3)}
We re-trained carefully the TNRD, CSF and MLP models with Gaussian noise levels $\sigma$ = 5, 10, 15, 25, 35, 50, and re-run the experiments. The new results are listed in Table 1. One can see that our method is still the best one. The $2^{nd}$ best method is MLP with $\sigma$ =10, which is 0.39dB lower than our method.

\section{Single parameter setting for all cases (R3)}
Yes we do use a single parameter setting and it works well on the two very different datasets. Actually this is not a magic because the key parameter $\lambda_{j}$ (Eq. (5) in the main paper) in our algorithm is adaptively determined based on the statistics of the external and internal data. This is one advantage of our algorithm.

\section{Nonlocal similar patches (R3)}
Yes we chose similar patches based on the Euclidean distance. We will make this clear in the revised paper. A stronger patch matching algorithm can make our algorithm perform better but will increase the complexity.

\section{Image resolution (R3)}
The reason we down-sampled the images is to make the size of PDF file smaller. Actually, if we view the images with original size, the better visual quality of our method over other denoising methods will be more obvious.

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}
